### 2020-12-02 figures/ms.tex
Initial Overleaf Import

\documentclass{aastex63}

\newcommand{\be}{\begin{eqnarray}}
\newcommand{\ee}{\end{eqnarray}}
\def\la{\mathbin{\lower 3pt\hbox
      {$\rlap{\raise 5pt\hbox{$\char'074$}}\mathchar"7218$}}}
\def\ga{\mathbin{\lower 3pt\hbox
      {$\rlap{\raise 5pt\hbox{$\char'076$}}\mathchar"7218$}}} %> or of order
\renewcommand{\vec}[1]{\mathbf{#1}}
%\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}} %boldface vector style
\newcommand{\grad}{\mathbf{\nabla}}

\received{}
\revised{}
\accepted{\today}
\submitjournal{APJ}

\shorttitle{Lyman $\alpha$}
\shortauthors{Arras et al.}

\graphicspath{{./}{figures/}}

\begin{document}

\title{Resonant Scattering in a Uniform Sphere with Large Optical Depth}

\correspondingauthor{Phil Arras}
\email{arras@virginia.edu}

\author{student}
\author{Phil Arras}
\author{Shane Davis}
\affiliation{Department of Astronomy, University of Virginia, Charlottesville, VA 22904, USA}

\begin{abstract}

The solution of the radiative transfer equation for resonant scattering of Lyman $\alpha$ photons for a uniform sphere of constant gas density is found in the limit of large line center optical depth. A monochromatic source of photons is assumed at the center of the sphere, and the intensity within the sphere and at the surface is found with the Eddington approximation for the angular dependence. The solution can be represented a sum of three terms: a simple, analytic solution of the inhomogeneous equation which diverges at the center of the sphere and at the emission frequency; a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface; and finally, a solution of the homogeneous equation which enforces the correct, zero ingoing intensity boundary conditions at the surface. It is the compact, analytic form as well as the piece accounting for the correct, frequency dependent boundary condition that is novel in this study. The analytic solution is compared to numerical solutions with the Monte-Carlo method, which are valid at arbitrary optical depth, and the deviations from exact solution are investigated.

\end{abstract}

\keywords{}

\section{Introduction} \label{sec:intro}

Nice summary paragraph from recent Bourier  papers.

Hubble Space Telescope observations have found large Lyman $\alpha$ transit depths around the gas giants HD 209458b \citep{2003Natur.422..143V}, HD 189733b \citep{2012A&A...543L...4L} and 55 Cnc b \citep{2012A&A...547A..18E}, Neptune-size planets GJ 436 b 
\citep{2015Natur.522..459E}
%, 2017A&A...605L...7L,2019A&A...629A..47D}   
and GJ 3470 b \citep{2018A&A...620A.147B}, and possibly the super-Earth HD 219134b \citep{2019EPSC...13.1928L}.
Non-detections or marginal detections have been reported for the super-Earths 55 Cnc e \citep{2012A&A...547A..18E}, super-Earth HD 97658 b \citep{2017A&A...597A..26B} , super-Earth GJ 1132 b \citep{2019AJ....158...50W}, super-Earth $\pi$ Men c \citep{2020ApJ...888L..21G}, and marginal detections were  Earth-size TRAPPIST-1 \citep{2017A&A...599L...3B} and sub-Earth Kepler-444 \citep{2017A&A...602A.106B}.

\section{ previous analytic work }

\citet{1973MNRAS.162...43H, 1974MNRAS.166..373H} started work on analytic solutions as you get a Laplace equation. Doesn't get boundary condition right.
\citet{1990ApJ...350..216N} has analytic solutions following Harrington.
\citet{1990ApJ...350..216N} improved on Harrington. Does have divergent inhomogeneous solution in slab geometry! Also has discussion of absorption.
\citet{2006ApJ...649...14D} generalized Harrington to spherical geometry
\citet{1976ApJ...208..286W} tries to compute the radiation force
\citet{1994ApJ...427..603R} discuss an ansatz for the fokker-planck approximation where the full voigt profile is used.
\citet{2020arXiv200509692L} discusses solutions for the sphere. Follows \citet{2006ApJ...649...14D}. They cite \citet{2015MNRAS.449.4336S} on core skipping.
\citet{2002ApJ...567..922A,2015MNRAS.449.4336S} discusses acceleration.
\citet{2015MNRAS.449.4336S}: amounts to drawing the atom velocity from a truncated Gaussian distribution to force it back into the wing.  The logic seems to be that almost all of the core scattering results in zero spatial diffusion until you get far enough from the line wing.  It seems like this is just calibrated by modifying the truncation until the spectrum doesn’t seem to depend sensitively on the choice of truncation.

%\begin{figure}
%\plotone{KT_Eri.pdf}
%\caption{The Swift/XRT X-ray light curve for the first year after
%outburst of the suspected recurrent nova KT Eri. At a maximum count rate of 
%328 ct/s, KT Eri was the brightest nova in X-rays observed to date. All 
%the component figures (6) are available in the Figure Set. Note that
%these components that are {\bf not} shown in the compiled pdf. The figure
%set consists of the same figures as shown in Figure \ref{fig:pyramid}. 
%The example figure shown for figure sets can be one component or many. 
%\label{fig:fig4}}
%\end{figure}

\acknowledgments

\appendix

\section{ derivation of the transfer equation }

\citet{1973MNRAS.162...43H} first showed that the transfer equation for the mean  intensity $J$ will satisfy a Poisson equation involving second derivatives of space and frequency variables. In this section we will briefly review the derivation of this equation including photon destruction terms and an emission term.

The radiative intensity $I = dE/(dA dt d\Omega d\nu)$ is the energy per perpendicular area $dA$, per time $dt$, per solid angle $d\Omega$ and per frequency $d\nu$ \citep{1986rpa..book.....R}. Here the time-dependence of $I$ has been ignored, which assumes the fluid is changing on timescales long compared to a light-crossing time. The intensity $I=I(\vec{x},\vec{n}, \nu)$ will be considered a function of position $\vec{x}$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$. In the Eddington and two-stream approximations, $I(\vec{x},\nu) \simeq J(\vec{x},\nu) + 3 \vec{n} \cdot \vec{H}(\vec{x},\nu)$, where $J=(1/4\pi) \int d\Omega I$ is the mean intensity and $\vec{F} = 4\pi \vec{H}= \int d\Omega \vec{n} I$ is the flux.

Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered. The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light. The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$. For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$. 
The transfer equation is \citep{1986rpa..book.....R}
\be
\vec{n} \cdot \grad I & =& - \left( \alpha_{\rm sc} + \alpha_{\rm abs} \right) I + (1-p) j_{\rm sc} + j_{\rm em}.
\label{eq:rteqn}
\ee
The scattering coefficient, or inverse mean free path to scattering, is 
\be
\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{H(x,a)}{\sqrt{\pi} \Delta}
= k \phi   
\ee
where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ have their usual meaning, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$. The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section. Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons. ``Hummer Case II-b"  \citep{1962MNRAS.125...21H} will be used for the redistribution function, for which the incoming photon is absorbed by the atom according to the natural broadening in the rest frame, re-emitted with a dipole phase function $g(\vec{n},\vec{n}^\prime)=(3/16\pi)(1+[\vec{n}\cdot \vec{n}^\prime]^2)$, which is appropriate for a 1s-2p transition \citep{1982qe}, and the result is averaged over a Maxwell-Boltzmann distribution of speeds for the atom. The result can be written
\be
j_{\rm sc}(\vec{x},\vec{n},\nu) & = & k \int \frac{ d^3v}{ \pi^{3/2} v_{\rm th}^3} e^{-v^2/v_{\rm th}^2}\, 
\int d\Omega^\prime \int d\nu^\prime \,
g(\vec{n},\vec{n}^\prime) 
\nonumber \\ & \times & 
\delta \left( \nu - \nu^\prime - \nu_0 \vec{v} \cdot (\vec{n}-\vec{n}^\prime)/c \right)
\left( \frac{\Gamma/4\pi^2}{ \left(\nu^\prime - \nu_0 - \nu_0 \vec{v} \cdot \vec{n}^\prime/c \right)^2 + (\Gamma/4\pi)^2 } \right)  \,
I(\vec{x},\vec{n}^\prime,\nu^\prime)
\nonumber \\ & = & 4\pi k \int d\Omega^\prime \int d\nu^\prime R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) I(\vec{x},\vec{n}^\prime,\nu^\prime),
\ee
which defines the redistribution function
\be
R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) & = & \frac{ g(\vec{n},\vec{n}^\prime) }{ 4\pi }
\int \frac{ d^3v}{ \pi^{3/2} v_{\rm th}^3} e^{-v^2/v_{\rm th}^2}\,
\delta \left( \nu - \nu^\prime - \nu_0 \vec{v} \cdot (\vec{n}-\vec{n}^\prime)/c \right)
\left( \frac{\Gamma/4\pi^2}{ \left(\nu^\prime - \nu_0 - \nu_0 \vec{v} \cdot \vec{n}^\prime/c \right)^2 + (\Gamma/4\pi)^2 } \right).
\ee 
Our definition of $R$ differs from that of \citet{1962MNRAS.125...21H} by a factor of $4\pi$.

The integral of the redistribution function over outgoing and incoming frequency are
\be
\int d\nu\ R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) 
& = & \frac{1}{4\pi} g(\vec{n},\vec{n}^\prime) \phi(\nu^\prime)
\ee 
and
\be
\int d\nu^\prime \ R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) 
& = & \frac{1}{4\pi} g(\vec{n},\vec{n}^\prime) \phi(\nu)
\ee 
where the right hand side is the usual Voigt function, the thermal average of the Lorentzian. The former result implies that the integrated source and sink terms for scattering cancel for $p=1$. In addition, $d\nu d\Omega 4\pi R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime)/\phi(\nu^\prime) $ is the normalized distribution for the outgoing $\vec{n}$ and $\nu$ given the incoming $\vec{n}^\prime$ and $\nu^\prime$.

This probability distribution can be used to define the moments of the frequency shift
\be
\langle \Delta \nu^n \rangle & = & \frac{ \int d\nu^\prime R (\nu-\nu^\prime)^n}{\int d\nu^\prime R}
= \frac{1}{\phi(\nu)}
\int \frac{ d^3v}{ \pi^{3/2} v_{\rm th}^3} e^{-v^2/v_{\rm th}^2}\,
\left( \frac{\nu_0 \vec{v} \cdot (\vec{n}-\vec{n}^\prime) }{c} \right)^n
\left( \frac{\Gamma/4\pi^2}{ \left(\nu - \nu_0 - \nu_0 \vec{v} \cdot \vec{n}/c \right)^2 + (\Gamma/4\pi)^2 } \right),
\ee
which are functions of $\nu$, $\vec{n}$ and $\vec{n}^\prime$. These integrals can be evaluated in terms of the dimensionless moments of the parallel velocity distribution, defined as
\be
\langle u_\parallel^n \rangle(x) & = & \frac{a/\pi }{H(x,a)} \int 
\frac{du_\parallel u_\parallel^n e^{-u_\parallel^2}  }{(x-u_\parallel)^2 + a^2}.
\ee
The end results for the first and second moments are
\be
\langle \Delta \nu \rangle & = & \Delta \langle u_\parallel \rangle \left( 1 - \vec{n} \cdot \vec{n}^\prime \right)
\\
\langle \Delta \nu^2 \rangle & = & \Delta^2 
\left[ \langle u_\parallel^2 \rangle
\left( 1 - \vec{n} \cdot \vec{n}^\prime \right)^2
+ \frac{1}{2} \left( 1 - \vec{n} \cdot \vec{n}^\prime \right)^2 \right].
\ee

For small frequency shifts $\nu-\nu^\prime$, the incoming intensity may be expanded as 
\be
I(\vec{x},\vec{n}^\prime,\nu^\prime) & \simeq  &
I(\vec{x},\vec{n}^\prime,\nu) 
+ 
\frac{\partial I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu }(\nu^\prime-\nu)
+ \frac{1}{2} \frac{\partial^2 I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu^2} (\nu^\prime-\nu)^2 + ...
\ee 
and the Fokker-Planck expansion of $j_{\rm sc}$ is
\be
j_{\rm sc}(\vec{x},\vec{n},\nu) & \simeq  & 4\pi k \int d\Omega^\prime \int d\nu^\prime R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) 
\left[ 
I(\vec{x},\vec{n}^\prime,\nu) + \frac{\partial I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu }(\nu^\prime-\nu)
+ \frac{1}{2} \frac{\partial^2 I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu^2 }(\nu^\prime-\nu)^2
\right]
\nonumber \\ 
& =& 
k\phi(\nu) \int d\Omega^\prime g 
\left[ 
I(\vec{x},\vec{n}^\prime,\nu) 
- \frac{\partial I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu }
\langle \Delta \nu \rangle
+ \frac{1}{2} \frac{\partial^2 I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu^2 }
\langle \Delta \nu^2 \rangle
\right]
\ee 
To perform the integrals, the Eddington approximation for the angular dependence is inserted with the following result
\be
j_{\rm sc} & = & k\phi J - k\phi \Delta \langle u_\parallel \rangle \left( \frac{\partial J}{\partial \nu} - \frac{6}{5} \vec{n} \cdot \frac{\partial \vec{H}}{\partial \nu} \right)
+ \frac{1}{2} \Delta^2 k\phi \left[ 
\frac{\partial^2 J}{\partial \nu^2} \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10} \right)
- \frac{12}{5} \langle u_\parallel^2 \rangle 
\vec{n} \cdot \frac{\partial^2 \vec{H}}{\partial \nu^2} \right].
\label{eq:jsc}
\ee
The first term in Equation \ref{eq:jsc}, $k\phi J$, represents re-emission of the photon through de-excitation of the atom. It cancels the $-k\phi J$ term in Equation \ref{eq:rteqn} that corresponds to excitation of the atom. The third and fifth terms in Equation \ref{eq:jsc} involve frequency derivatives of $\vec{H}$. If carried through the calculation, they end up giving terms smaller than then largest terms by a factor of $1/x^2$, which is small on the line wing. These terms are ignored from here on.

This far the transfer equation is
\be
\vec{n} \cdot \grad \left( J + 3 \vec{n} \cdot \vec{H} \right)
& =& j_{\rm em}
- \left( k\phi + \alpha_{\rm abs} \right) \left( J + 3 \vec{n} \cdot \vec{H} \right)
\nonumber \\ & + & 
(1-p) \left[ k\phi J - k\phi \Delta \langle u_\parallel \rangle \frac{\partial J}{\partial \nu} 
+ \frac{1}{2} \Delta^2 k\phi 
\frac{\partial^2 J}{\partial \nu^2} \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10} \right)
\right].
\label{eq:rteqn2}
\ee
The moment equations are
\be
\grad \cdot \vec{H} & = & j_{\rm em} 
- \left( \alpha_{\rm abs} + pk\phi\right) J
- k\phi \Delta \langle u_\parallel \rangle \frac{\partial J}{\partial \nu} 
+ \frac{1}{2} \Delta^2 k\phi 
\frac{\partial^2 J}{\partial \nu^2} \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10} \right)
\ee
and
\be
\frac{1}{3} \grad J & =& - \left( k \phi + \alpha_{\rm abs} \right) \vec{H}.
\ee
Assuming the coefficients are constant in space, these two equations can be combined together to find
\be
- \frac{1}{3 (k\phi + \alpha_{\rm abs})} \nabla^2 J
& =& j_{\rm em} 
- \left( \alpha_{\rm abs} + pk\phi\right) J
- k\phi \Delta \langle u_\parallel \rangle \frac{\partial J}{\partial \nu} 
+ \frac{1}{2} \Delta^2 k\phi 
\frac{\partial^2 J}{\partial \nu^2} \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10} \right)
\ee

\bibliography{ref.bib}{}
\bibliographystyle{aasjournal}

\end{document}

### 2020-12-02 ms.tex
Initial Overleaf Import

\documentclass{aastex63}

\newcommand{\be}{\begin{eqnarray}}
\newcommand{\ee}{\end{eqnarray}}
\def\la{\mathbin{\lower 3pt\hbox
      {$\rlap{\raise 5pt\hbox{$\char'074$}}\mathchar"7218$}}}
\def\ga{\mathbin{\lower 3pt\hbox
      {$\rlap{\raise 5pt\hbox{$\char'076$}}\mathchar"7218$}}} %> or of order
\renewcommand{\vec}[1]{\mathbf{#1}}
%\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}} %boldface vector style
\newcommand{\grad}{\mathbf{\nabla}}

\received{}
\revised{}
\accepted{\today}
\submitjournal{APJ}

\shorttitle{Lyman $\alpha$}
\shortauthors{uva lyman alpha group}

\graphicspath{{./}{figures/}}

\begin{document}

\title{Resonant Scattering in a Uniform Sphere with Large Optical Depth}

\correspondingauthor{Phil Arras}
\email{arras@virginia.edu}

\author{uva lyman alpha group}
%\author{Phil Arras}
%\author{Shane Davis}
\affiliation{Department of Astronomy, University of Virginia, Charlottesville, VA 22904, USA}

\begin{abstract}

The solution of the radiative transfer equation for resonant scattering of Lyman $\alpha$ photons for a uniform sphere of constant gas density is found in the limit of large line center optical depth. A monochromatic source of photons is assumed at the center of the sphere, and the intensity within the sphere and at the surface is found with the Eddington approximation for the angular dependence. The solution can be represented a sum of three terms: a simple, analytic solution of the inhomogeneous equation which diverges at the center of the sphere and at the emission frequency; a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface; and finally, a solution of the homogeneous equation which enforces the correct, zero ingoing intensity boundary conditions at the surface. It is the compact, analytic form as well as the piece accounting for the correct, frequency dependent boundary condition that is novel in this study. The analytic solution is compared to numerical solutions with the Monte-Carlo method, which are valid at arbitrary optical depth, and the deviations from exact solution are investigated.

\end{abstract}

\keywords{}

ccc\section{Introduction} 
\label{sec:intro}

Nice summary paragraph from recent Bourier  papers.

Hubble Space Telescope observations have found large Lyman $\alpha$ transit depths around the gas giants HD 209458b \citep{2003Natur.422..143V}, HD 189733b \citep{2012A&A...543L...4L} and 55 Cnc b \citep{2012A&A...547A..18E}, Neptune-size planets GJ 436 b 
\citep{2015Natur.522..459E}
%, 2017A&A...605L...7L,2019A&A...629A..47D}   
and GJ 3470 b \citep{2018A&A...620A.147B}, and possibly the super-Earth HD 219134b \citep{2019EPSC...13.1928L}.
Non-detections or marginal detections have been reported for the super-Earths 55 Cnc e \citep{2012A&A...547A..18E}, super-Earth HD 97658 b \citep{2017A&A...597A..26B} , super-Earth GJ 1132 b \citep{2019AJ....158...50W}, super-Earth $\pi$ Men c \citep{2020ApJ...888L..21G}, and marginal detections were  Earth-size TRAPPIST-1 \citep{2017A&A...599L...3B} and sub-Earth Kepler-444 \citep{2017A&A...602A.106B}.

\section{ previous analytic work }

\citet{1973MNRAS.162...43H, 1974MNRAS.166..373H} started work on analytic solutions as you get a Laplace equation. Doesn't get boundary condition right.
\citet{1990ApJ...350..216N} has analytic solutions following Harrington.
\citet{1990ApJ...350..216N} improved on Harrington. Does have divergent inhomogeneous solution in slab geometry! Also has discussion of absorption.
\citet{2006ApJ...649...14D} generalized Harrington to spherical geometry
\citet{1976ApJ...208..286W} tries to compute the radiation force
\citet{1994ApJ...427..603R} discuss an ansatz for the fokker-planck approximation where the full voigt profile is used.
\citet{2020arXiv200509692L} discusses solutions for the sphere. Follows \citet{2006ApJ...649...14D}. They cite \citet{2015MNRAS.449.4336S} on core skipping.
\citet{2002ApJ...567..922A,2015MNRAS.449.4336S} discusses acceleration.
\citet{2015MNRAS.449.4336S}: amounts to drawing the atom velocity from a truncated Gaussian distribution to force it back into the wing.  The logic seems to be that almost all of the core scattering results in zero spatial diffusion until you get far enough from the line wing.  It seems like this is just calibrated by modifying the truncation until the spectrum doesn’t seem to depend sensitively on the choice of truncation.

\section{ no photon destruction }
\label{sec:no_destruction}

Three solutions will be considered for this problem. A ``divergent" solution due to the delta function source, a ``J=0" solution which includes the delta function solution at the source and satisfies $J=0$ at $r=R$, and the ``bc" solution that allows the boundary conditions to be satisfied. The divergent solution is discussed for qualitative understanding, and the full solution is the sum of the $J=0$ solution and the bc solution.

The problem is as follows. Consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$. The transfer Equation \ref{eq:finaleqn} with no photon destruction terms, $p=\alpha_{\rm abs}=0$, and with a  photon emission term given by Equation \ref{eq:jem}), which gives the transfer equation
\be
\nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} & = & 
- \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s})
\label{eq:rt_no_destr}
\ee
where the form of the source term is in Equation \ref{eq:jem_v2}. The boundary condition is no incoming flux at the surface, which can be written
\citep{1986rpa..book.....R}
\be
J & = & \sqrt{3} H
\label{eq:bc}
\ee
at $r=R$.

First consider the divergent solution. In terms of the dimensionless variables $x_1 = k(x-x_{\rm s})/\Delta$, $x_2=k(y-y_{\rm s})/\Delta$, $x_3=k(z-z_{\rm s})/\Delta$ and $x_4=\sigma - \sigma_{\rm s}$, this equation can be written as a Laplacian in the 4-dimensional space as
\be
\nabla_4^2 J & = & - \frac{\sqrt{6} k^2 L}{4\pi \Delta^3} \delta^4(x).
\ee
In terms of the 4-dimensional radius $r_4 = \sqrt{ (k/\Delta)^2\left[ (x-x_{\rm s})^2 + (y-y_{\rm s})^2 + (z-z_{\rm s})^2 \right] + (\sigma - \sigma_{\rm s})^2 }$, and assuming spherical symmetry about the source point, the equation becomes
\be
\frac{1}{r_4^3} \frac{\partial}{\partial r_4} \left( r_4^3 \frac{\partial J}{\partial r_4} \right) & = & - \frac{\sqrt{6} k^2 L}{4\pi \Delta^3} 
\frac{\delta(r_4)}{2\pi^2 r_4^3},
\ee
where the forms of the 4-dimensional Laplacian and delta function have been inserted. The ``divergent" solution due to the delta function is then
\be
J_{\rm d} & = & 
\frac{(\sqrt{6}k^2L)/(16\pi^3 \Delta^3)}{ (k/\Delta)^2\left[ (x-x_{\rm s})^2 + (y-y_{\rm s})^2 + (z-z_{\rm s})^2 \right] + (\sigma - \sigma_{\rm s})^2}.
\label{eq:Jd}
\ee
While this solution does not satisfy the surface boundary condition (Equation \ref{eq:bc}), it is accurate near the delta-function source.
This solution generalizes the particular solution for slab geometry found by \citet{1990ApJ...350..216N}. Henceforth we will focus on the source at the center of the sphere, although we will retain the emission frequency at $\sigma=\sigma_{\rm s}$. The radial flux corresponding to Equation \ref{eq:Jd} is
\be
H_{\rm d} & = & - \frac{1}{3k\phi} \frac{\partial J_d}{\partial r}
=  \left( \frac{1}{3k\phi} \right) 
\left( \frac{ \sqrt{6}k^3L }{ 8\pi^3 \Delta^4} \right)
\left( \frac{k r/\Delta}{ \left[ (kr/\Delta)^2 + (\sigma-\sigma_{\rm s})^2 \right]^2 } \right).
\label{eq:Hd}
\ee
It will be shown that Equation \ref{eq:Hd} is a good approximation at $r=R$ near line center. However Equation \ref{eq:Jd} is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$.

A better approximation to the true solution has been derived by \citet{2006ApJ...649...14D}, who generalized the closed-form solution in slab geometry found in \citet{1990ApJ...350..216N}. They found a closed-form solution which satisfies a $J=0$ boundary condition at $r=R$. We generalize their solution to allow emission at frequency $\nu_{\rm s}$ away from line center. The result is
\be
J_0 & = & \left( \frac{\sqrt{6}L}{32\pi^2 \Delta} \right)
\left( \frac{1}{Rr} \right)
\left( 
\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
\right)
\label{eq:J0}
\ee
and
\be
H_0 & = & \left( \frac{1}{3k\phi} \right)
\left( \frac{\sqrt{6}L}{32\pi^2 \Delta} \right)
\left( \frac{1}{Rr^2} \right)
\left( 
\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
\right. \nonumber \\ & & \left. - \left( \frac{\pi r}{R} \right)
\frac{ \cos(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
+ \left( \frac{\pi r}{R} \right)
\frac{ \sin^2(\pi r/R) }{ \left[ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R) \right]^2 }
\right).
\label{eq:H0}
\ee
Again $J_0 \gg H_0$, except very near the $r=R$, where it goes to zero. The flux at $r=R$ can be written
\be
H_0(R,\nu) & = & \left( \frac{1}{3k\phi} \right)
\left( \frac{\sqrt{6}L}{32\pi \Delta} \right)
\left( \frac{1}{R^3} \right)
\left( 
\frac{ 1 }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] +1 }
\right).
\label{eq:H0surf}
\ee
Equation \ref{eq:H0surf} will be shown to be a much better approximation to the solution, which is valid near the delta function at the center, and is a much better approximation at the surface. It will be shown that it is still only a good approximation near line center at the surface. It decreases exponentially rather than as a power-law in frequency, giving a much smaller flux on the line wings as compared to $H_{\rm d}$.

The question is how to satisfy the surface boundary condition in Equation \ref{eq:bc}. On this point, we note that the derivation in \citet{1973MNRAS.162...43H}, and numerous studies later studies, does not actually produce a valid solution of the transfer equation and boundary condition. The reason is as follows. In the notation of \citet{1973MNRAS.162...43H}, a separation of variables
$J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ is attempted (his Equations 16 and 23). The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$. In order to satisfy the boundary conditions, the separation constant must satisfy an eigenvalue equation of the form
\be
\lambda \tan(\lambda B) & = & \frac{3}{2} \phi,
\label{eq:evalue}
\ee
where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile ($\Delta \phi$ here). The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency. But then the separation constant is not constant, and it does not satisfy Equation \ref{eq:rt_no_destr} since the frequency derivatives will will act on the separation ``constant", giving extra terms. To our knowledge the errors introduced by this ansatz have never been quantified.

In the limit of large optical depth $B$, \citealt{1973MNRAS.162...43H} approximates the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$, which gives $J=0$ at the surface. This is essentially the result in Equation \ref{eq:J0} above. However, since this solution gives zero at the surface, his Equation 34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent. This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.

A different solution method is attempted here, namely a continuous Fourier expansion in the frequency variable $\sigma$. The full solution is written
\be
J(r,\nu) & = & J_0(r,\nu) + J_{\rm bc}(r,\nu)
\ee
and
\be
H(r,\nu) & = & H_0(r,\nu) + H_{\rm bc}(r,\nu).
\ee
Here $J_0$ and $H_0$ are the solutions of the inhomogeneous equation including the delta function source given in Equations \ref{eq:J0} and \ref{eq:H0}. The additional term $J_{\rm bc}$ must then be a solution of the homogeneous equation
\be
\frac{\partial^2J}{\partial r^2} + \frac{2}{r} \frac{\partial J}{\partial r}
+ \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} &= & 0
\ee
with no delta function source term, and it must allow the boundary conditions to be satisfied at the surface. Since $J_0(R,
\nu)=0$, the surface boundary condition becomes
\be
J_{\rm bc}(R,\nu) - \sqrt{3} H_{\rm bc}(R,\nu) & = & 
J_{\rm bc}(R,\nu) + \frac{1}{\sqrt{3}k\phi} \frac{\partial J_{\rm bc}(R,\nu)}{\partial r} = 
\sqrt{3} H_0(R,\nu).
\label{eq:bc2}
\ee
Plugging in a frequency dependence $J \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$. The solution can then be represented as
\be
J_{\rm bc}(r,\nu) & = & 
\int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s) 
\frac{i_0(krs/\Delta)}{i_0(kRs/\Delta)},
\label{eq:Jbc}
\ee
where $A(s)$ is the Fourier amplitude.

Plugging Equation \ref{eq:Jbc} into Equation \ref{eq:bc2} leads to the following equation for the Fourier amplitudes
\be
\int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s)
\left[ 1 + \left( \frac{s}{\sqrt{3} \Delta \phi} \right) \left( \frac{i_0^\prime(kRs/\Delta)}{i_0(kRs/\Delta)} \right) \right]
& = & \sqrt{3} H_0(R,\nu)
\label{eq:bc3}
\ee
where $H_0(R,\nu)$ is given by Equation \ref{eq:H0surf}. Discretization of Equation \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
leads to a set of coupled linear equations for the $A(s_j)$. We use equally space points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid. The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that  the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries. The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries. Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Equation \ref{eq:Jbc}, and the flux is given by
\be
H_{\rm bc}(r,\nu) & = & \left( \frac{-1}{3k\phi} \right)
\frac{\partial J_{\rm bc}(r,\nu)}{\partial r}
= \left( \frac{-1}{3k\phi} \right)
\int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s) 
\left( \frac{ks}{\Delta} \right) 
\left( \frac{i_0^\prime(krs/\Delta)}{i_0(kRs/\Delta)} \right).
\label{eq:Hbc}
\ee
The Bessel functions are finite at the center and rise steeply toward the surface when $kRs/\Delta \gg 1$.

\begin{figure}
    \centering
    \includegraphics{1m_x_pdf_residualv2_log.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at an optical depth of $1 \times 10^7$. It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings. The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, results in an overall smaller fractional deviation from the Monte Carlo and a much closer match to the Monte Carlo in the wing.}
    \label{fig:sol_mc_residual}
\end{figure}

% Discussion of various solutions compared with Monte Carlo
[Brief discussion of Monte Carlo runs to set up comparison]

In Fig. \ref{fig:sol_mc_residual}, the contribution of the flux from Eq. \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$. We find that $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ has considerably lower fractional error with the Monte Carlo in the line wing.

\section{ time-dependent diffusion }

In order to understand the wait time distribution, the time-dependent response to an impulse is found. For simplicity a $J=0$ boundary condition will be used. This is expected to be a good approximation for $\tau_0 \gg 1$.

The source is changed to the form
\be
j_{\rm em} & = & \frac{E}{4\pi} \delta^3(\vec{x} - \vec{x}_s) \delta(\nu-\nu_{\rm s})\delta (t) .
\label{eq:jem2}
\ee
where $E$ is the energy emitted in the impulse at time $t=0$. 
The resulting equation for $J(r,\sigma,t)$ is
\be
-3 \frac{k\phi}{c} \frac{\partial J}{\partial t} + \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2}
& = & - \frac{\sqrt{6} kE}{4\pi \Delta^2} \delta(\vec{x}) \delta (\sigma - \sigma_s ) \delta (t).
\label{eq:diffusion_eqn}
\ee
The coefficient of $\partial J/\partial t$ has explicit dependence on $\sigma$. Separation of variables may be achieved in Equation \ref{eq:diffusion_eqn} by assuming an expansion in terms of spherical Bessel functions in $r$ and a Fourier expansion in time to find the form
\be
J(r,\sigma,t) & = & \sum_{n=1}^\infty \int_{-\infty}^\infty \frac{d\omega}{2\pi} J(n,\sigma,\omega) j_0(\kappa_n r) e^{-i \omega t},
\ee
where $\kappa_n = n\pi/R$ enforces the $J(R,\sigma,t)=0$ boundary condition and the spherical Bessel function is $j_0(x)=\sin(x)/x$. For the solution to be real requires that $J(n,\sigma,-\omega) = J^*(n,\sigma,\omega)$. The equation for $J(n,\sigma,\omega)$ becomes
\be
\frac{\partial^2 J}{\partial \sigma^2} & = & \left( \frac{\Delta \kappa_n}{k} \right)^2 J
- 3i\omega \frac{\Delta^2 \phi}{ck} J
- \sqrt{ \frac{3}{32} } \frac{E}{kR^3} n^2 \delta(\sigma - \sigma_s).
\label{eq:response}
\ee
The $\delta(\sigma - \sigma_s)$ enforces a discontinuity
\be
\frac{\partial J(n,\sigma_s^{(+)},\omega)}{\partial \sigma} - \frac{\partial J(n,\sigma_s^{(-)},\omega)}{\partial \sigma} & = & 
- \sqrt{ \frac{3}{32} } \frac{E}{kR^3} n^2
\label{eq:discontinuity}
\ee
and the boundary conditions are $J(n,\pm \infty,\omega)=0$. Since $\phi \propto \sigma^{-2/3}$, the solution at large $\sigma$ is 
\be
J(n,\sigma,\omega) & \propto & e^{-\kappa_n \Delta |\sigma| /k}
= e^{-\sqrt{\pi} n |\sigma | / \tau_0}.
\label{eq:finite_bc}
\ee

To solve the second order Equation \ref{eq:response}, starting points at large $\pm |\sigma|$ are chosen, and the dependence in Equation \ref{eq:finite_bc} is used for the starting slope. The solution is then integrated toward the singularity at $\sigma_s$ from each side. The two starting values are varied until $J(n,\sigma,\omega)$ is continuous at $\sigma_s$ and satisfies the desired jump in slope in Equation \ref{eq:discontinuity}. Since the solution is linear in the starting conditions, only two integrations with different starting values are necessary.

For small $t$ the solution is nearly a delta function in radius

\end{frame}

%\begin{figure}
%\plotone{KT_Eri.pdf}
%\caption{The Swift/XRT X-ray light curve for the first year after 
%outburst of the suspected recurrent nova KT Eri. At a maximum count rate of 
%328 ct/s, KT Eri was the brightest nova in X-rays observed to date. All 
%the component figures (6) are available in the Figure Set. Note that
%these components that are {\bf not} shown in the compiled pdf. The figure
%set consists of the same figures as shown in Figure \ref{fig:pyramid}. 
%The example figure shown for figure sets can be one component or many. 
%\label{fig:fig4}}
%\end{figure}

\acknowledgments

\appendix

\section{ derivation of the transfer equation }

\citet{1973MNRAS.162...43H} first showed that the transfer equation for the mean  intensity $J$ will satisfy a Poisson equation involving second derivatives of space and frequency variables. In this section we will briefly review the derivation of this equation including photon destruction terms and an emission term.

The radiative intensity $I = dE/(dA dt d\Omega d\nu)$ is the energy per perpendicular area $dA$, per time $dt$, per solid angle $d\Omega$ and per frequency $d\nu$ \citep{1986rpa..book.....R}. Here the time-dependence of $I$ has been ignored, which assumes the fluid is changing on timescales long compared to a light-crossing time. The intensity $I=I(\vec{x},\vec{n}, \nu)$ will be considered a function of position $\vec{x}$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$. In the Eddington and two-stream approximations, $I(\vec{x},\nu) \simeq J(\vec{x},\nu) + 3 \vec{n} \cdot \vec{H}(\vec{x},\nu)$, where $J=(1/4\pi) \int d\Omega I$ is the mean intensity and $\vec{F} = 4\pi \vec{H}= \int d\Omega \vec{n} I$ is the flux.

Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered. The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light. The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$. For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$. 
The transfer equation is \citep{1986rpa..book.....R}
\be
\frac{1}{c} \frac{\partial I}{\partial t} + \vec{n} \cdot \grad I & =& - \left( \alpha_{\rm sc} + \alpha_{\rm abs} \right) I + (1-p) j_{\rm sc} + j_{\rm em}.
\label{eq:rteqn}
\ee
The scattering coefficient, or inverse mean free path to scattering, is 
\be
\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{H(x,a)}{\sqrt{\pi} \Delta}
= k \phi   
\ee
where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ have their usual meaning, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$. The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section. Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons. ``Hummer Case II-b"  \citep{1962MNRAS.125...21H} will be used for the redistribution function, for which the incoming photon is absorbed by the atom according to the natural broadening in the rest frame, re-emitted with a dipole phase function $g(\vec{n},\vec{n}^\prime)=(3/16\pi)(1+[\vec{n}\cdot \vec{n}^\prime]^2)$, which is appropriate for a 1s-2p transition \citep{1982qe}, and the result is averaged over a Maxwell-Boltzmann distribution of speeds for the atom. The result can be written
\be
j_{\rm sc}(\vec{x},\vec{n},\nu) & = & k \int \frac{ d^3v}{ \pi^{3/2} v_{\rm th}^3} e^{-v^2/v_{\rm th}^2}\, 
\int d\Omega^\prime \int d\nu^\prime \,
g(\vec{n},\vec{n}^\prime) 
\nonumber \\ & \times & 
\delta \left( \nu - \nu^\prime - \nu_0 \vec{v} \cdot (\vec{n}-\vec{n}^\prime)/c \right)
\left( \frac{\Gamma/4\pi^2}{ \left(\nu^\prime - \nu_0 - \nu_0 \vec{v} \cdot \vec{n}^\prime/c \right)^2 + (\Gamma/4\pi)^2 } \right)  \,
I(\vec{x},\vec{n}^\prime,\nu^\prime)
\nonumber \\ & = & 4\pi k \int d\Omega^\prime \int d\nu^\prime R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) I(\vec{x},\vec{n}^\prime,\nu^\prime),
\ee
which defines the Case II-b redistribution function
\be
R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) & = & \frac{ g(\vec{n},\vec{n}^\prime) }{ 4\pi }
\int \frac{ d^3v}{ \pi^{3/2} v_{\rm th}^3} e^{-v^2/v_{\rm th}^2}\,
\delta \left( \nu - \nu^\prime - \nu_0 \vec{v} \cdot (\vec{n}-\vec{n}^\prime)/c \right)
\left( \frac{\Gamma/4\pi^2}{ \left(\nu^\prime - \nu_0 - \nu_0 \vec{v} \cdot \vec{n}^\prime/c \right)^2 + (\Gamma/4\pi)^2 } \right)
\ee
found in \citet{1962MNRAS.125...21H}.

The integral of the redistribution function over outgoing and incoming frequency are
\be
\int d\nu\ R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) 
& = & \frac{1}{4\pi} g(\vec{n},\vec{n}^\prime) \phi(\nu^\prime)
\ee 
and
\be
\int d\nu^\prime \ R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) 
& = & \frac{1}{4\pi} g(\vec{n},\vec{n}^\prime) \phi(\nu)
\ee 
where the right hand side is the usual Voigt function, the thermal average of the Lorentzian. The former result implies that the integrated source and sink terms for scattering cancel for $p=1$. In addition, $d\nu d\Omega 4\pi R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime)/\phi(\nu^\prime) $ is the normalized distribution for the outgoing $\vec{n}$ and $\nu$ given the incoming $\vec{n}^\prime$ and $\nu^\prime$.

This probability distribution can be used to define the moments of the frequency shift
\be
\langle \Delta \nu^n \rangle & = & \frac{ \int d\nu^\prime R (\nu-\nu^\prime)^n}{\int d\nu^\prime R}
= \frac{1}{\phi(\nu)}
\int \frac{ d^3v}{ \pi^{3/2} v_{\rm th}^3} e^{-v^2/v_{\rm th}^2}\,
\left( \frac{\nu_0 \vec{v} \cdot (\vec{n}-\vec{n}^\prime) }{c} \right)^n
\left( \frac{\Gamma/4\pi^2}{ \left(\nu - \nu_0 - \nu_0 \vec{v} \cdot \vec{n}/c \right)^2 + (\Gamma/4\pi)^2 } \right),
\ee
which are functions of $\nu$, $\vec{n}$ and $\vec{n}^\prime$. These integrals can be evaluated in terms of the dimensionless moments of the parallel velocity distribution, defined as
\be
\langle u_\parallel^n \rangle(x,a) & = & \frac{a/\pi }{H(x,a)} \int 
\frac{du_\parallel u_\parallel^n e^{-u_\parallel^2}  }{(x-u_\parallel)^2 + a^2}.
\ee
The end results for the first and second moments are
\be
\langle \Delta \nu \rangle & = & \Delta \langle u_\parallel \rangle \left( 1 - \vec{n} \cdot \vec{n}^\prime \right)
\\
\langle \Delta \nu^2 \rangle & = & \Delta^2 
\left[ \langle u_\parallel^2 \rangle
\left( 1 - \vec{n} \cdot \vec{n}^\prime \right)^2
+ \frac{1}{2} \left( 1 - \left( \vec{n} \cdot \vec{n}^\prime\right)^2 \right) \right].
\ee

For small frequency shifts $\nu-\nu^\prime$, the incoming intensity may be expanded as 
\be
I(\vec{x},\vec{n}^\prime,\nu^\prime) & \simeq  &
I(\vec{x},\vec{n}^\prime,\nu) 
+ 
\frac{\partial I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu }(\nu^\prime-\nu)
+ \frac{1}{2} \frac{\partial^2 I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu^2} (\nu^\prime-\nu)^2 + ...
\ee 
and the Fokker-Planck expansion of $j_{\rm sc}$ is
\be
j_{\rm sc}(\vec{x},\vec{n},\nu) & \simeq  & 4\pi k \int d\Omega^\prime \int d\nu^\prime R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime) 
\left[ 
I(\vec{x},\vec{n}^\prime,\nu) + \frac{\partial I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu }(\nu^\prime-\nu)
+ \frac{1}{2} \frac{\partial^2 I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu^2 }(\nu^\prime-\nu)^2
\right]
\nonumber \\ 
& =& 
k\phi(\nu) \int d\Omega^\prime g 
\left[ 
I(\vec{x},\vec{n}^\prime,\nu) 
- \frac{\partial I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu }
\langle \Delta \nu \rangle
+ \frac{1}{2} \frac{\partial^2 I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu^2 }
\langle \Delta \nu^2 \rangle
\right]
\ee 
To perform the angular integrals, the Eddington approximation for the angular dependence is inserted with the following result
\be
j_{\rm sc} & = & k\phi J - k\phi \Delta \langle u_\parallel \rangle \left( \frac{\partial J}{\partial \nu} - \frac{6}{5} \vec{n} \cdot \frac{\partial \vec{H}}{\partial \nu} \right)
+ \frac{1}{2} \Delta^2 k\phi \left[ 
\frac{\partial^2 J}{\partial \nu^2} \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10} \right)
- \frac{12}{5} \langle u_\parallel^2 \rangle 
\vec{n} \cdot \frac{\partial^2 \vec{H}}{\partial \nu^2} \right]
\nonumber \\ & \simeq & 
k\phi J - k\phi \Delta \langle u_\parallel \rangle  \frac{\partial J}{\partial \nu} 
+ \frac{1}{2} \Delta^2 k\phi \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10} \right)
\frac{\partial^2 J}{\partial \nu^2} .
\label{eq:jsc}
\ee
The first term in Equation \ref{eq:jsc}, $k\phi J$, represents re-emission of the photon through de-excitation of the atom. It cancels the $-k\phi J$ term in Equation \ref{eq:rteqn} that corresponds to excitation of the atom. The terms involvingfrequency derivatives of $\vec{H}$, if carried through the calculation,end up giving terms smaller than then largest terms by a factor of $1/x^2$, which is small on the line wing. These terms are ignored from here on.

If only scattering is included, the transfer equation becomes
\be
\frac{1}{c} \frac{\partial }{\partial t} \left( J + 3\vec{n} \cdot \vec{H} \right)
+ \vec{n} \cdot \grad \left( J + 3\vec{n} \cdot \vec{H} \right)
& = & - k\phi \Delta \langle u_\parallel \rangle  \frac{\partial J}{\partial \nu} 
+ \frac{1}{2} \Delta^2 k\phi \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10} \right)
\frac{\partial^2 J}{\partial \nu^2}.
\ee
Integrating over angle and frequency then gives
\be
\frac{1}{c} \frac{\partial J(\vec{x}) }{\partial t} +  \grad \cdot \vec{H}(\vec{x}) & = & \int d\nu
\left( - k\phi \Delta \langle u_\parallel \rangle  \frac{\partial J}{\partial \nu} 
+ \frac{1}{2} \Delta^2 k\phi \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10} \right)
\frac{\partial^2 J}{\partial \nu^2}
\right) 
\nonumber \\ & =& 
k \int d\nu J \frac{\partial }{\partial \nu} 
\left( \phi \Delta \langle u_\parallel \rangle
+ \frac{\partial }{\partial \nu}\left[ \frac{1}{2} \phi \Delta^2 
\left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10}  \right) \right]
\right) = 0,
\ee
where $\vec{H}(\vec{x})$ is the frequency integrated flux, and $\grad \cdot \vec{H}(\vec{x})  = 0 $ if there are no sources or sinks of radiation. Integration by parts has been used to factor $J$ out, assuming each term goes to zero at infinity. The quantity inside brackets must be constant, and since each term should go to zero at infinity, that constant is zero. Hence the first and second moments of the frequency shift are related by
\be
\phi \Delta \langle u_\parallel \rangle
& = & -  \frac{\partial }{\partial \nu}\left[ \frac{1}{2} \phi \Delta^2 
\left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10}  \right) 
\right].
\ee
As an example, on the damping wing, $\phi \simeq a/(\pi x^2)$, $\langle u_\parallel \rangle \simeq 1/x$ and $\langle u_\parallel^2 \rangle \simeq 1/2$, and this identity is satisfied. The redistribution function can then be rewritten
\be
j_{\rm sc} & \simeq & k\phi J + \frac{1}{2} k \Delta^2 \frac{\partial }{\partial \nu} 
\left[ \phi  \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10}  \right)\frac{\partial J}{\partial \nu}  \right]
\simeq k\phi J + \frac{1}{2} k \Delta^2 \frac{\partial }{\partial \nu} 
\left( \phi \frac{\partial J}{\partial \nu}  \right)
\ee
where the last equality (see e.g. \citealt{1994ApJ...427..603R}) is valid on the damping wing where $\langle u_\parallel^2 \rangle \simeq 1/2$.
The following equations will use the approximations for the damping wing.

Thus far the transfer equation is
\be
\frac{1}{c} \frac{\partial }{\partial t} \left( J + 3\vec{n} \cdot \vec{H} \right) + \vec{n} \cdot \grad \left( J + 3 \vec{n} \cdot \vec{H} \right)
& =& j_{\rm em}
- \left( k\phi + \alpha_{\rm abs} \right) \left( J + 3 \vec{n} \cdot \vec{H} \right)
+
(1-p) \left[
k\phi J + \frac{1}{2} k \Delta^2 \frac{\partial }{\partial \nu} 
\left( \phi \frac{\partial J}{\partial \nu}  \right)
\right]
\nonumber \\ & \simeq & 
j_{\rm em} - 3k\phi \vec{n} \cdot \vec{H} - \left( p k\phi  + \alpha_{\rm abs} \right) J 
+ \frac{1}{2} k \Delta^2 \frac{\partial }{\partial \nu} 
\left( \phi \frac{\partial J}{\partial \nu}  \right),
\label{eq:rteqn2}
\ee
where leading order dissipative terms were kept in the second equality.
The moment equations are
\be
\frac{1}{c} \frac{\partial J}{\partial t} + \grad \cdot \vec{H} & = & j_{\rm em} 
- \left(p k\phi +  \alpha_{\rm abs} \right) J
+ \frac{1}{2} k \Delta^2 \frac{\partial }{\partial \nu} 
\left( \phi \frac{\partial J}{\partial \nu}  \right)
\ee
and
\be
\frac{1}{c} \frac{\partial \vec{H}}{\partial t} + \frac{1}{3} \grad J & =& - \left( k \phi + \alpha_{\rm abs} \right) \vec{H}.
\ee
The $\partial \vec{H}/\partial t$ term may be dropped for slowly changing sources.
Assuming the coefficients are constant in space, these two equations can be combined together to find
\be
\frac{1}{c} \frac{\partial J}{\partial t} - \frac{1}{3 (k\phi + \alpha_{\rm abs})} \nabla^2 J
& =& j_{\rm em} 
- \left( p k\phi +  \alpha_{\rm abs} \right) J
+ \frac{1}{2} k \Delta^2 \frac{\partial }{\partial \nu} 
\left( \phi \frac{\partial J}{\partial \nu}  \right).
\ee
Making the change of variables to $d\sigma = \sqrt{2/3}d\nu/(\Delta^2 \phi)$, the equation can be rewritten in the standard form \citep{1973MNRAS.162...43H}
\be
-3 \left( \frac{k\phi + \alpha_{\rm abs}}{c}\right) \frac{\partial J}{\partial t} + \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \left( 1 + \frac{\alpha_{\rm abs}}{k\phi} \right)\frac{\partial^2 J}{\partial \sigma^2} & = & 
-3 \left( k\phi + \alpha_{\rm abs}\right) j_{\rm em}
+ 3 \left( k\phi + \alpha_{\rm abs}\right) \left( pk\phi + \alpha_{\rm abs}\right) J.
\label{eq:finaleqn}
\ee

For emission with luminosity $L$, with a delta function in space $\delta^3(\vec{x} - \vec{x}_s)$ at source position $\vec{x}_s$, a delta function in frequency $\delta(\nu-\nu_{\rm s})$ at source frequency $\nu_{\rm s}$, and isotropic in angles, the emission coefficient is
\be
j_{\rm em} & = & \frac{L}{4\pi} \delta^3(\vec{x} - \vec{x}_s) \delta(\nu-\nu_{\rm s}).
\label{eq:jem}
\ee
Multiplying by a factor $-3k\phi$, as appears in Equation \ref{eq:finaleqn}, the delta function in $\nu$ becomes a delta function in $\sigma$ of the form
\be
-3k\phi j_{\rm em}  &= & - \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s}),
\label{eq:jem_v2}
\ee
where $\sigma_s = \sigma(\nu_s)$.

\bibliography{ref.bib}{}
\bibliographystyle{aasjournal}

\end{document}

### 2020-12-02 ms.tex
Adding in new figure and revising some wording in caption, MC results comparison

@@
     \centering
-    \includegraphics{1m_x_pdf_residualv2_log.pdf}
-    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at an optical depth of $1 \times 10^7$.
+    \includegraphics{pdf_xinit0.0.pdf}
+    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
 It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings.
@@
 \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$.
-We find that $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ has considerably lower fractional error with the Monte Carlo in the line wing.
+The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
 

### 2020-12-07 ms.tex
Adding x_init=6, 12 plots and filling out description paragraph of Monte Carlo and figures

@@
     \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
-It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings.
-The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, results in an overall smaller fractional deviation from the Monte Carlo and a much closer match to the Monte Carlo in the wing.}
-    \label{fig:sol_mc_residual}
+Photons are initialized with $\rm x = 0.0$.
+In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.}
+    \label{fig:sol_mc_residual_0}
 \end{figure}
 
-% Discussion of various solutions compared with Monte Carlo
-[Brief discussion of Monte Carlo runs to set up comparison]
+\begin{figure}
+    \centering
+    \includegraphics{pdf_xinit6.0.pdf}
+    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
+Photons are initialized with $\rm x = 6.0$.
+In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.}
+    \label{fig:sol_mc_residual_6}
+\end{figure}
 
+\begin{figure}
+    \centering
+    \includegraphics{pdf_xinit12.0.pdf}
+    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
+Photons are initialized with $\rm x = 12.0$.
+In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.}
+    \label{fig:sol_mc_residual_12}
+\end{figure}
+
+For each numerical solution, the monochromatic source of photons was initialized with a different starting frequency to evaluate the analytic solutions' accuracy with variation of the parameter $\rm \sigma_s$.
+This is related to $\rm x_{init}$ by
+
+\begin{equation} \label{sigma0_xinit}
+    \sigma_0 = \frac{\beta}{a} \rm x_{init}^3
+\end{equation}
+
+Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ...
+12.0)$ and optical depths $\tau_0 = (10^6, 10^7)$.
 In Fig.
-\ref{fig:sol_mc_residual}, the contribution of the flux from Eq.
+\ref{fig:sol_mc_residual_0}, \ref{fig:sol_mc_residual_6} and \ref{fig:sol_mc_residual_12}, these are compared with the analytic solutions at selected initial frequencies.
+In each of these figures, the contribution of the flux from Eq.
 \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$.
 The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
+It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings.
+The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, produces a successful analytical result that characterizes the probability distribution of frequencies for escaping photons, including situations in which the photons are given initial frequencies outside of the line core.
+
+This can best be seen by comparing the results shown in Fig.
+\ref{fig:sol_mc_residual_0} with those in Fig.
+\ref{fig:sol_mc_residual_12}.
+The $\rm H_{0+bc}$ analytic solution remains accurate in the line wing when photons are emitted away from line center, while the residuals of $\rm H_d$ and $\rm H_0$ become noticeably larger.
+It can be concluded that the $\rm H_{bc}$ correction term more accurately represents the additional flux from photons that escape without ever being scattered through the line core.
 

### 2020-12-10 ms.tex
adding two-stream approx comparison with Dijkstra et al 2006, still need to write out equations

@@
 Non-detections or marginal detections have been reported for the super-Earths 55 Cnc e \citep{2012A&A...547A..18E}, super-Earth HD 97658 b \citep{2017A&A...597A..26B} , super-Earth GJ 1132 b \citep{2019AJ....158...50W}, super-Earth $\pi$ Men c \citep{2020ApJ...888L..21G}, and marginal detections were  Earth-size TRAPPIST-1 \citep{2017A&A...599L...3B} and sub-Earth Kepler-444 \citep{2017A&A...602A.106B}.
+
+The main impediment to peforming magnetohydrodynamic simulations with fully a coupled radiative transfer solution via Monte Carlo methods is the prohibitive computational cost.
+A primary factor in the cost of Monte Carlo is that the number of scatterings a photon (packet/superphoton?) undergoes is proportional to the line center optical depth.
+Near the base of the atmosphere individual simulation cells can have optical depths of more than a million so most of the time is spent integrating photons in these cells.
+This means that any method that can treat these zone via an analytic solution has the potential to greatly accelerate the calculation.
+
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.
+The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.
+These methods focus Monte Carlo transfer on the wings of the line and avoid scatterings in the core.
+Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so tha opacity is lower and escape is more rapid.
+
+A second class of methods are hydbrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
+This involves designating sufficiently optically thick simulations cells for computation via a finite difference representaiton of radiation transfer equation.
+This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.
+For the resonant scattering problem, where the opacity is a strong function of frequnecy, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
+
+A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M,Robitaille2010}.
+In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
+An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation withing a uniform sphere.
 
@@
 
+% TODO: (Connor) Fill out the rest of this paragraph and include equations
+Rewriting Eq.
+C17 from \citet{2006ApJ...649...14D} in our notation, a comparison can be made with the surface flux derived from their closed-form solution, Eq.
+\ref{eq:H0surf}.
+Under the two-stream approximation, it is expected that the boundary condition in Eq.
+\ref{eq:bc} hold true if the solutions are consistent.
+
 In the limit of large optical depth $B$, \citealt{1973MNRAS.162...43H} approximates the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$, which gives $J=0$ at the surface.
@@
 This is related to $\rm x_{init}$ by
-
 \begin{equation} \label{sigma0_xinit}
@@
 
+where $\beta = \sqrt{2 \pi ^2 / 27}$.
 Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ...

### 2020-12-16 ms.tex
Revised section on Dijkstra derivation

@@
 
-% TODO: (Connor) Fill out the rest of this paragraph and include equations
-Rewriting Eq.
-C17 from \citet{2006ApJ...649...14D} in our notation, a comparison can be made with the surface flux derived from their closed-form solution, Eq.
-\ref{eq:H0surf}.
-Under the two-stream approximation, it is expected that the boundary condition in Eq.
-\ref{eq:bc} hold true if the solutions are consistent.
-
 In the limit of large optical depth $B$, \citealt{1973MNRAS.162...43H} approximates the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$, which gives $J=0$ at the surface.
@@
 This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
+
+% TODO: (Connor) Fill out the rest of this paragraph and include equations
+To characterize the internal consistency of the solution in \citet{2006ApJ...649...14D}, the approximation made in their Eq.
+C13 is checked to see if it yields a surface flux satisfying Eq.
+\ref{eq:bc}.
+Beginning with their Eq.
+C12, the surface flux is derived and compared with the total emerging flux density at the surface of the sphere (Eq.
+C17).
+Under the two-stream approximation, it is expected that the surface boundary condition $J=\sqrt{3}H$ hold true if the solutions are consistent.
+
+TODO: If the solutions end up being consistent, their prescription works better than one would expect, seeing as they started with a $J=0$ boundary condition and arrived at $J=\sqrt{3}H$ through their eigenvalue approximation.
+If the solutions are not consistent, then their emerging spectrum is inaccurate under their assumptions.
 

### 2021-02-26 ms.tex
Adding beginning of time-dependent spectrum comparison

--- 2020-12-10 ms.tex
@@
 This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
+Despite this treatment, a calculation of the surface flux from his Eq.
+13 compared with the total emerging flux density at the surface of the sphere (Eq.
+C17) yields a $J=2H$ surface boundary condition.
+Note that under the two-stream approximation, a surface boundary condition $J=\sqrt{3}H$ is necessary to properly normalize the radiation pressure.
 
-A different solution method is attempted here, namely a continuous Fourier expansion in the frequency variable $\sigma$. The full solution is written
+A different solution method is attempted here: namely, a continuous Fourier expansion in the frequency variable $\sigma$. The full solution is written
 \be
@@
 
-where $\beta = \sqrt{2 \pi ^2 / 27}$.
+where $\beta = \sqrt{2 \pi / 27}$.
 Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ...
@@
 
-For small $t$ the solution is nearly a delta function in radius
+For small $t$ the solution is nearly a delta function in radius TODO
+
+It is expected that the time-integrated spectrum of the response to an impulse will agree well with the time-independent spectrum.
+We first evaluate the time-dependent response using our eigenfrequency sweeping method.
+Once the probabilities $P_{nm}(\sigma)$ are calculated as above, the escape time distributions for all photon frequencies are calculated by summing over the frequency eigenfunctions $P_{nm} \exp(s_{nm}t)$.
+Integrating $P_{nm}$ with respect to $t$, we obtain
+
+\be
+\int 
+\ee
 

### 2021-04-07 ms.tex
Adding subsections

@@
 
+\subsection{Background}
+\label{subsec:no_destruction:background}
+
 Three solutions will be considered for this problem.
@@
 The divergent solution is discussed for qualitative understanding, and the full solution is the sum of the $J=0$ solution and the bc solution.
+
+\subsection{Equations}
+\label{subsec:no_destruction:equations}
 
@@
 
+\subsection{Numerical Methods}
+\label{subsec:no_destruction:methods}
+For each numerical solution, the monochromatic source of photons was initialized with a different starting frequency to evaluate the analytic solutions' accuracy with variation of the parameter $\rm \sigma_s$.
+This is related to $\rm x_{init}$ by
+\begin{equation} \label{sigma0_xinit}
+    \sigma_0 = \frac{\beta}{a} \rm x_{init}^3
+\end{equation}
+
+where $\beta = \sqrt{2 \pi / 27}$. Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ... 12.0)$ and optical depths $\tau_0 = (10^6, 10^7)$.
+
+\subsection{Results}
+\label{subsec:no_destruction:results}
 \begin{figure}
@@
 
-For each numerical solution, the monochromatic source of photons was initialized with a different starting frequency to evaluate the analytic solutions' accuracy with variation of the parameter $\rm \sigma_s$.
-This is related to $\rm x_{init}$ by
-\begin{equation} \label{sigma0_xinit}
-    \sigma_0 = \frac{\beta}{a} \rm x_{init}^3
-\end{equation}
-
-where $\beta = \sqrt{2 \pi / 27}$.
-Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ...
-12.0)$ and optical depths $\tau_0 = (10^6, 10^7)$.
  In Fig.
@@
 
-\section{ time-dependent diffusion }
+\section{Time-Dependent Diffusion}
+\label{sec:time_dependent}
+
+\subsection{Background}
+\label{subsec:time_dependent:background}
 
@@
 This is expected to be a good approximation for $\tau_0 \gg 1$.
+
+\subsection{Equations}
+\label{subsec:time_dependent:equations}
 
@@
 
+\subsection{Numerical Methods}
+\label{subsec:time_dependent:numerical_methods}
+
 To solve the second order Equation \ref{eq:response}, starting points at large $\pm |\sigma|$ are chosen, and the dependence in Equation \ref{eq:finite_bc} is used for the starting slope.
@@
 
-It is expected that the time-integrated spectrum of the response to an impulse will agree well with the time-independent spectrum.
+It is expected that the time-integrated spectrum of the response to an impulse will agree well with the solution for the steady-state spectrum (Eq.
+TODO: Steady state eqn).
 We first evaluate the time-dependent response using our eigenfrequency sweeping method.
@@
 
-\be
-\int 
-\ee
+\subsection{Results}
+\label{subsec:time_dependent:results}
 

### 2021-04-09 ms.tex
reorganizing, beginning to add Laplace solution for time dependent diffusion

@@
 The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
-But then the separation constant is not constant, and it does not satisfy Equation \ref{eq:rt_no_destr} since the frequency derivatives will will act on the separation ``constant", giving extra terms.
+But then the separation constant is not constant, and it does not satisfy Equation \ref{eq:rt_no_destr} since the frequency derivatives will act on the separation ``constant", giving extra terms.
 To our knowledge the errors introduced by this ansatz have never been quantified.
@@
 C17) yields a $J=2H$ surface boundary condition.
-Note that under the two-stream approximation, a surface boundary condition $J=\sqrt{3}H$ is necessary to properly normalize the radiation pressure.
+Under the two-stream approximation, a surface boundary condition $J=\sqrt{3}H$ is necessary to properly normalize the radiation pressure.
 
@@
 Plugging in a frequency dependence $J \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$.
+
+% Fourier analysis stuff which we can take out
+%\ifx
 The solution can then be represented as
@@
 leads to a set of coupled linear equations for the $A(s_j)$.
-We use equally space points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid.
+We use equally-spaced points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid.
 The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that  the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries.
@@
 The Bessel functions are finite at the center and rise steeply toward the surface when $kRs/\Delta \gg 1$. 
+%\fi
 
@@
 \ee
+
+We employ an expansion in terms of spherical Bessel functions in $r$ and a Laplace expansion with the imaginary frequency variable $s=-i\omega$.
+The eigenvalues $s$ are real and negative for damped solutions to the time-dependent equation.
+The expansion for $J(r, \sigma, t)$ is
+
+\be
+\label{eq:jrsigmat_expansion}
+J(r, \sigma, t) = \sum_{n=1}^{\infty} \int \frac{ds}{2\pi i} e^{st} j_0\left(\kappa_n r\right) J(n, \sigma, s).
+\ee
+
+The definition of the Laplace transform is
+
+\be
+J(n, \sigma, s) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{-st} J(r, \sigma, t).
+\ee
+
+Plugging this in to Eq. \ref{eq:diffusion_eqn} and evaluating the integral, we obtain
+
+%% FOURIER STUFF
+\ifx
 The coefficient of $\partial J/\partial t$ has explicit dependence on $\sigma$.
@@
 \ee
+\fi
 

### 2021-04-14 ms.tex
adding todo notes from group meeting
changing frequency variable to omega rather than s
adding matching conditions

@@
 
+TODO: Don't use s in these equations. Use damping rate omega here.
 We employ an expansion in terms of spherical Bessel functions in $r$ and a Laplace expansion with the imaginary frequency variable $s=-i\omega$.
@@
 \label{eq:jrsigmat_expansion}
-J(r, \sigma, t) = \sum_{n=1}^{\infty} \int \frac{ds}{2\pi i} e^{st} j_0\left(\kappa_n r\right) J(n, \sigma, s).
+J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega).
 \ee
 
-The definition of the Laplace transform is
+with
 
 \be
-J(n, \sigma, s) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{-st} J(r, \sigma, t).
+J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{i\omega t} J(r, \sigma, t).
 \ee
@@
 Plugging this in to Eq. \ref{eq:diffusion_eqn} and evaluating the integral, we obtain
+
+\be
+ \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{d^2J(n,\sigma,\omega)}{d\sigma^2} = \frac{2\kappa_n^2}{R} (-1) \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
+\ee
+
+Now at $\sigma=\sigma_s$ continuity must be enforced in $J$ and the discontinuity in $dJ/d\sigma$  must be equal to
+
+\be
+\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
+- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}.
+\ee
+
+Two numerical integrations are performed inward from large $\pm \sigma$ to the source $
+\sigma_s$.
+The starting values of J are set to be $J_1$ and $J_2$ for the rightward and leftward integrations, respectively.
+Choices of these starting values are adjusted to ensure that the matching conditions at the source are met.
+
+Separating the real and imaginary parts of the solution $J = J_r + i J_i$, we have
+
+\be
+ \frac{\partial^2 J_r}{\partial \sigma^2} &= & 
+  \frac{\Delta^2 \kappa_n^2}{k^2} J_r  
+ + 3 \omega \frac{\Delta^2 \phi}{kc}    J_i
+\ee
+and
+\be
+ \frac{\partial^2 J_i}{\partial \sigma^2} &= & 
+  \frac{\Delta^2 \kappa_n^2}{k^2} J_i   
+ - 3 \omega \frac{\Delta^2 \phi}{kc}    J_r.
+\ee
+
+The starting conditions are $J_{1,r}$, $J_{1,i}$, $J_{2,r}$, $J_{2,i}$.
+The rightgoing and leftgoing integrations then produce $J_{-,r}$, $J_{-,i}$, $J^\prime_{-,r}$, $J^\prime_{-,i}$,  $J_{+,r}$, $J_{+,i}$, $J^\prime_{+,r}$, $J^\prime_{+,i}$, where the prime means $\partial/\partial \sigma$.
+The matching conditions are then
+\be
+J_{-,r} & =& J_{+,r} \\
+J_{-,i} & =& J_{+,i} \\
+ J_{+,r}^\prime - J_{+,r}^\prime & = & 
+- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3} \\
+J_{+,i}^\prime - J_{+,i}^\prime & = & 0.
+\ee
 

### 2021-04-14 ms.tex
adding section about matrix matching conditions

@@
 
-TODO: Don't use s in these equations. Use damping rate omega here.
-We employ an expansion in terms of spherical Bessel functions in $r$ and a Laplace expansion with the imaginary frequency variable $s=-i\omega$.
-The eigenvalues $s$ are real and negative for damped solutions to the time-dependent equation.
+We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$.
+The eigenvalues $i\omega$ are real and positive for damped solutions to the time-dependent equation.
 The expansion for $J(r, \sigma, t)$ is
@@
 \be
- \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{d^2J(n,\sigma,\omega)}{d\sigma^2} = \frac{2\kappa_n^2}{R} (-1) \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
+ \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{d^2J(n,\sigma,\omega)}{d\sigma^2} = -\frac{2\kappa_n^2}{R} \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
 \ee
@@
 \frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
-- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}.
+- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}
 \ee
 
-Two numerical integrations are performed inward from large $\pm \sigma$ to the source $
-\sigma_s$.
+according to the differential equation.
+Two numerical integrations are performed inward from large $\pm \sigma$ to the source $\sigma_s$.
 The starting values of J are set to be $J_1$ and $J_2$ for the rightward and leftward integrations, respectively.
@@
 
-Separating the real and imaginary parts of the solution $J = J_r + i J_i$, we have
+Separating the real and imaginary parts of the solution $J = J_r + i J_i$, the differential equation becomes
 
@@
 
-The starting conditions are $J_{1,r}$, $J_{1,i}$, $J_{2,r}$, $J_{2,i}$.
-The rightgoing and leftgoing integrations then produce $J_{-,r}$, $J_{-,i}$, $J^\prime_{-,r}$, $J^\prime_{-,i}$,  $J_{+,r}$, $J_{+,i}$, $J^\prime_{+,r}$, $J^\prime_{+,i}$, where the prime means $\partial/\partial \sigma$.
-The matching conditions are then
+The starting conditions are then $J_1 = J_{1,r} + iJ_{1,i}$ and $J_2 = J_{2,r}+iJ_{2,i}$.
+The rightward and leftward integrations then produce $J_{-,r}$, $J_{-,i}$, $J^\prime_{-,r}$, $J^\prime_{-,i}$,  $J_{+,r}$, $J_{+,i}$, $J^\prime_{+,r}$, $J^\prime_{+,i}$, where a prime indicates a derivative $\partial/\partial \sigma$.
+The matching conditions at the source frequency $\sigma_s$ are then
 \be
@@
 \ee
+
+The solutions at $\sigma=\sigma_s$ are parametrized as a linear combination of the real and imaginary parts of the starting conditions and are solved as a $4\times4$ matrix equation.
 

### 2021-04-14 ms.tex
finishing matching conditions section

--- 2021-04-09 ms.tex
@@
 
-We employ an expansion in terms of spherical Bessel functions in $r$ and a Laplace expansion with the imaginary frequency variable $s=-i\omega$.
-The eigenvalues $s$ are real and negative for damped solutions to the time-dependent equation.
+We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$.
+The eigenvalues $i\omega$ are real and positive for damped solutions to the time-dependent equation.
 The expansion for $J(r, \sigma, t)$ is
@@
 Plugging this in to Eq. \ref{eq:diffusion_eqn} and evaluating the integral, we obtain
+
+\be \label{eq:diffusion_plugged_in}
+ \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2J(n,\sigma,\omega)}{\partial\sigma^2} = -\frac{2\kappa_n^2}{R} \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
+\ee
 
@@
 
-To solve the second order Equation \ref{eq:response}, starting points at large $\pm |\sigma|$ are chosen, and the dependence in Equation \ref{eq:finite_bc} is used for the starting slope.
-The solution is then integrated toward the singularity at $\sigma_s$ from each side.
-The two starting values are varied until $J(n,\sigma,\omega)$ is continuous at $\sigma_s$ and satisfies the desired jump in slope in Equation \ref{eq:discontinuity}.
+At $\sigma=\sigma_s$ continuity must be enforced in $J$
+
+\be \label{eq:matching_condition_1}
+J_+ = J_-
+\ee
+
+and the discontinuity in $dJ/d\sigma$  must be
+
+\be \label{matching_condition_2}
+\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
+- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}
+\ee
+
+according to the differential equation. At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes
+
+\be \label{eq:diffusion_at_large_sigma}
+\frac{\partial^2J(n, \sigma, \omega)}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J.
+\ee
+
+which has solutions
+
+\be
+J(n, \sigma, \omega)\ {\sim}\ e^{\pm \Delta \kappa_n \sigma / k}
+\ee
+
+and thus
+
+\be \label{eq:single_j_derivative}
+\frac{\partial J}{\partial \sigma} = \mp \frac{\Delta\kappa_n}{k} J
+\ee
+
+where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$.
+Two numerical integrations are performed inward from large $\pm \sigma$ to the source $\sigma_s$ to isolate the solution that increases exponentially toward the line center.
+Initial values for integration are obtained by setting $J=1$ in Eq.
+\ref{eq:single_j_derivative}.
+This yields values for $J_\pm$ and $J'_\pm$ on either side of the source, where a prime indicates the derivative $\partial/\partial \sigma$.
+By enforcing the matching conditions Eqs.
+\ref{eq:matching_condition_1} and \ref{matching_condition_2}, the solution for $J(n, \sigma, \omega)$ is obtained everywhere in the range of photon frequencies.
 Since the solution is linear in the starting conditions, only two integrations with different starting values are necessary.

### 2021-04-20 ms.tex
adding numerical fluence section for time dependent case

@@
 This is essentially the result in Equation \ref{eq:J0} above.
-However, since this solution gives zero at the surface, his Equation 34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
+However, since this solution gives zero at the surface, their Equation 34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
 This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
-Despite this treatment, a calculation of the surface flux from his Eq.
+Despite this treatment, a calculation of the surface flux from their Eq.
 13 compared with the total emerging flux density at the surface of the sphere (Eq.
@@
 \ref{eq:single_j_derivative}.
-This yields values for $J_\pm$ and $J'_\pm$ on either side of the source, where a prime indicates the derivative $\partial/\partial \sigma$.
+This gives $J_\pm$ and $J'_\pm$ on either side of the source, where a prime indicates the derivative $\partial/\partial \sigma$.
 By enforcing the matching conditions Eqs.
@@
 
-For small $t$ the solution is nearly a delta function in radius TODO
+There are certain values of $\omega$ for which a resonant response is produced. We will call these eigenfrequencies $\omega_{nm}$. Near these frequencies, the solution will have the form
+
+\be
+J(n,\sigma,s) & \simeq \frac{ J_{nm}(\sigma) }{s - s_{nm}} + {\rm terms\ which\ vary\ slowly\ in\ s}.
+\ee
+
+Obtaining the values of these eigenfrequencies and their corresponding eigenfunctions $J_{nm}(\sigma)$ allows us to obtain the contribution of this mode to the total solution via contour integration.
+
+\be
+J(r,\sigma,t) & = &  j_0(\kappa_n r)  \int \frac{d\omega}{2\pi} e^{-i\omega t}J(n,\sigma,\omega)
+\nonumber \\ & \simeq & j_0(\kappa_n r)  \int \frac{d\omega}{2\pi} e^{-i\omega t} \frac{ J_{nm}(\sigma) }{\omega - \omega_{nm}} 
+\nonumber \\ & \simeq & j_0(\kappa_n r)  J_{nm}(\sigma) e^{-i\omega_{nm}t}.
+\ee
+
+To find this result, we have closed the integral along the $i\omega$ axis by a semi-circle at infinity, and we then used the residue theorem to evaluate the answer.
+The contribution from the semi-circle at infinity is zero.
+Summing over all spatial n's and over all eigenmodes $m$ for a given $n$, we get the final form of the result
+\be
+J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_m J_{nm}(\sigma) e^{-i\omega_{nm}t}.
+\ee
+Using the derivative
+\be
+\frac{dj_0(\kappa_n r)}{dr} \rfloor_R & =& \frac{d}{dr}  \rfloor_R \left( \frac{\sin(\kappa_n r)}{\kappa_n r} \right)
+=  \left( \frac{\cos(\kappa_n R)}{R} - \frac{\sin(\kappa_n R)}{\kappa_n R^2} \right)\rfloor_R
+\nonumber \\ & = & \frac{(-1)^n}{R},
+\ee
+the flux at the surface is
+\be
+F(R,\sigma,t) & =& - \frac{4\pi}{3k\phi} \frac{dJ(R,\sigma,t)}{dr} 
+= - \frac{4\pi}{3k\phi R}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-i\omega_{nm}t}.
+\ee
+Multiplying by $4\pi R^2$ gives the energy per time per frequency
+\be
+\frac{dE}{dtd\nu} & = & - \frac{16\pi^2 R}{3k\phi}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-i\omega_{nm}t}.
+\label{eq:dEdtdnu}
+\ee
+If we integrate this expression over time, giving a factor $1/s_{nm}$, and over $d\nu = \sqrt{3/2} \Delta^2 \phi d\sigma$, a ``sum rule" results
+\be
+1 & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE} \sum_{nm} (-1)^n (-i\omega_{nm})^{-1} \int d\sigma J_{nm}(\sigma).
+\ee
+This non-trivial expression provides a check on the values of $s_{nm}$ and the functions $J_{nm}(\sigma)$. This expression can also be written as
+\be
+1 & =& \sum_{nm} P_{nm},
+\label{eq:sumrule}
+\ee
+where the contribution of each eigenfunction is
+\be
+P_{nm} & \equiv & -\sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE}  (-1)^n (i\omega_{nm})^{-1} \int d\sigma J_{nm}(\sigma).
+\ee
+These coefficients can have either sign depending on the value of $n$.
+
+Integrating $dE/dt d\nu$ over all times should give a distribution for the emitted frequencies, and this should agree with the steady state solution.
+Dividing by the energy $E$, we find the probability distribution
+\be \label{eq:spectrum}
+P(\nu) & = &  \frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^n s_{nm}^{-1} J_{nm}(\sigma).
+\ee
+Integrating over $\nu$ gives unity if the sum rule in Equation \ref{eq:sumrule} is true.
 
 It is expected that the time-integrated spectrum of the response to an impulse will agree well with the solution for the steady-state spectrum (Eq.
-TODO: Steady state eqn).
+\ref{eq:spectrum}).
 We first evaluate the time-dependent response using our eigenfrequency sweeping method.

### 2021-04-21 ms.tex
small changes

@@
 
-To find this result, we have closed the integral along the $i\omega$ axis by a semi-circle at infinity, and we then used the residue theorem to evaluate the answer.
+(TODO: Rewrite) To find this result, we have closed the integral along the $i\omega$ axis by a semi-circle at infinity, and we then used the residue theorem to evaluate the answer.
 The contribution from the semi-circle at infinity is zero.

### 2021-04-22 ms.tex
Adding time dependent derivation up to time-integrated spectra vs. steady state

--- 2021-04-20 ms.tex
@@
 
-There are certain values of $\omega$ for which a resonant response is produced. We will call these eigenfrequencies $\omega_{nm}$. Near these frequencies, the solution will have the form
+Let us define the damping time to be $\gamma \equiv i\omega$, which is real-valued and positive for damped solutions.
+There are certain values of $\gamma$ for which a resonant response is produced which we will call $\gamma_{nm}$.
+Here, $m$ is an index that represents individual temporal eigenmodes, as opposed to $n$ which represents the spatial mode number.
+Near these frequencies, the solution will have the form
 
 \be
-J(n,\sigma,s) & \simeq \frac{ J_{nm}(\sigma) }{s - s_{nm}} + {\rm terms\ which\ vary\ slowly\ in\ s}.
+J(n,\sigma,\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} + {\rm terms\ which\ vary\ slowly\ in\ \gamma}.
 \ee
@@
 \be
-J(r,\sigma,t) & = &  j_0(\kappa_n r)  \int \frac{d\omega}{2\pi} e^{-i\omega t}J(n,\sigma,\omega)
-\nonumber \\ & \simeq & j_0(\kappa_n r)  \int \frac{d\omega}{2\pi} e^{-i\omega t} \frac{ J_{nm}(\sigma) }{\omega - \omega_{nm}} 
-\nonumber \\ & \simeq & j_0(\kappa_n r)  J_{nm}(\sigma) e^{-i\omega_{nm}t}.
+J(r,\sigma,t) & = &  j_0(\kappa_n r)  \int \frac{d\omega}{2\pi} e^{-\gamma t}J(n,\sigma,\gamma)
+\nonumber \\ & \simeq & j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} 
+\nonumber \\ & \simeq & j_0(\kappa_n r)  J_{nm}(\sigma) e^{-\gamma_{nm}t}.
 \ee
 
-To find this result, we have closed the integral along the $i\omega$ axis by a semi-circle at infinity, and we then used the residue theorem to evaluate the answer.
+(TODO: Rewrite) Here we have closed the integral along the $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
 The contribution from the semi-circle at infinity is zero.
-Summing over all spatial n's and over all eigenmodes $m$ for a given $n$, we get the final form of the result
+Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result
 \be
-J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_m J_{nm}(\sigma) e^{-i\omega_{nm}t}.
+J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_m J_{nm}(\sigma) e^{-\gamma_{nm}t}.
 \ee
@@
 F(R,\sigma,t) & =& - \frac{4\pi}{3k\phi} \frac{dJ(R,\sigma,t)}{dr} 
-= - \frac{4\pi}{3k\phi R}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-i\omega_{nm}t}.
+= - \frac{4\pi}{3k\phi R}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-\gamma_{nm}t}.
 \ee
@@
 \be
-\frac{dE}{dtd\nu} & = & - \frac{16\pi^2 R}{3k\phi}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-i\omega_{nm}t}.
+\frac{dE}{dtd\nu} & = & - \frac{16\pi^2 R}{3k\phi}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-\gamma_{nm}t}.
 \label{eq:dEdtdnu}
 \ee
-If we integrate this expression over time, giving a factor $1/s_{nm}$, and over $d\nu = \sqrt{3/2} \Delta^2 \phi d\sigma$, a ``sum rule" results
+Integrating this over time yields a factor $-1/\gamma_{nm}$, and over $d\nu = \sqrt{3/2} \Delta^2 \phi d\sigma$, a ``sum rule" results
 \be
-1 & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE} \sum_{nm} (-1)^n (-i\omega_{nm})^{-1} \int d\sigma J_{nm}(\sigma).
+1 & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE} \sum_{nm} (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
 \ee
-This non-trivial expression provides a check on the values of $s_{nm}$ and the functions $J_{nm}(\sigma)$. This expression can also be written as
+This non-trivial expression provides a check on the values of $\gamma_{nm}$ and the functions $J_{nm}(\sigma)$. This expression can also be written as
 \be
@@
 \be
-P_{nm} & \equiv & -\sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE}  (-1)^n (i\omega_{nm})^{-1} \int d\sigma J_{nm}(\sigma).
+P_{nm} & \equiv & \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE}  (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
 \ee
@@
 
-Integrating $dE/dt d\nu$ over all times should give a distribution for the emitted frequencies, and this should agree with the steady state solution.
+Integrating $dE/dt d\nu$ over all times should give a distribution for the emitted frequencies.
+It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the steady-state spectrum (Eq.
+\ref{eq:spectrum}).
 Dividing by the energy $E$, we find the probability distribution
 \be \label{eq:spectrum}
-P(\nu) & = &  \frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^n s_{nm}^{-1} J_{nm}(\sigma).
+P(\nu) & = &  -\frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^n \gamma_{nm}^{-1} J_{nm}(\sigma).
 \ee
 Integrating over $\nu$ gives unity if the sum rule in Equation \ref{eq:sumrule} is true.
-
-It is expected that the time-integrated spectrum of the response to an impulse will agree well with the solution for the steady-state spectrum (Eq.
-\ref{eq:spectrum}).
-We first evaluate the time-dependent response using our eigenfrequency sweeping method.
-Once the probabilities $P_{nm}(\sigma)$ are calculated as above, the escape time distributions for all photon frequencies are calculated by summing over the frequency eigenfunctions $P_{nm} \exp(s_{nm}t)$.
-Integrating $P_{nm}$ with respect to $t$, we obtain
 

### 2021-04-22 ms.tex
Modifying no photon destruction section, removing previous (bad) explanation of monte carlo / solution fits

@@
 
-Three solutions will be considered for this problem.
-A ``divergent" solution due to the delta function source, a ``J=0" solution which includes the delta function solution at the source and satisfies $J=0$ at $r=R$, and the ``bc" solution that allows the boundary conditions to be satisfied.
+Three solutions will be considered for this problem: a ``divergent" solution due to the delta function source, a ``J=0" solution which includes the delta function solution at the source and satisfies $J=0$ at $r=R$, and the ``bc" solution that allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
 The divergent solution is discussed for qualitative understanding, and the full solution is the sum of the $J=0$ solution and the bc solution.
@@
 \ee
-where the form of the source term is in Equation \ref{eq:jem_v2}. The boundary condition is no incoming flux at the surface, which can be written
+where the form of the source term is in Equation \ref{eq:jem_v2}. The boundary condition is that there is no incoming flux at the surface, which can be written
 \citep{1986rpa..book.....R}
@@
 
+In Section \ref{subsec:no_destruction:results}, each of these solutions are compared with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$.
+
 \subsection{Numerical Methods}
 \label{subsec:no_destruction:methods}
-For each numerical solution, the monochromatic source of photons was initialized with a different starting frequency to evaluate the analytic solutions' accuracy with variation of the parameter $\rm \sigma_s$.
-This is related to $\rm x_{init}$ by
-\begin{equation} \label{sigma0_xinit}
-    \sigma_0 = \frac{\beta}{a} \rm x_{init}^3
-\end{equation}
 
-where $\beta = \sqrt{2 \pi / 27}$. Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ... 12.0)$ and optical depths $\tau_0 = (10^6, 10^7)$.
+TODO: Add Monte Carlo description
 
@@
 Photons are initialized with $\rm x = 0.0$.
-In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.}
+In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.
+Residuals of each solution to the Monte Carlo data points are shown in the third panel.}
     \label{fig:sol_mc_residual_0}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{pdf_xinit6.0.pdf}
-    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
-Photons are initialized with $\rm x = 6.0$.
-In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.}
-    \label{fig:sol_mc_residual_6}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics{pdf_xinit12.0.pdf}
-    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
-Photons are initialized with $\rm x = 12.0$.
-In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.}
-    \label{fig:sol_mc_residual_12}
-\end{figure}
-
  In Fig.
-\ref{fig:sol_mc_residual_0}, \ref{fig:sol_mc_residual_6} and \ref{fig:sol_mc_residual_12}, these are compared with the analytic solutions at selected initial frequencies.
-In each of these figures, the contribution of the flux from Eq.
+\ref{fig:sol_mc_residual_0}, the fluxes derived in Section \ref{subsec:no_destruction:equations} are compared with the Monte Carlo at selected initial frequencies.
+The contribution of the flux from Eq.
 \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$.
 The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
-It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings.
-The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, produces a successful analytical result that characterizes the probability distribution of frequencies for escaping photons, including situations in which the photons are given initial frequencies outside of the line core.
+It is evident that the ``divergent'' solution $H_{\rm d}$ fails by a large margin in the line wings.
+The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum as well as the slight deficit in the line wings, improving the agreement of the analytic solution with the numerical result.
 
-This can best be seen by comparing the results shown in Fig.
-\ref{fig:sol_mc_residual_0} with those in Fig.
-\ref{fig:sol_mc_residual_12}.
-The $\rm H_{0+bc}$ analytic solution remains accurate in the line wing when photons are emitted away from line center, while the residuals of $\rm H_d$ and $\rm H_0$ become noticeably larger.
-It can be concluded that the $\rm H_{bc}$ correction term more accurately represents the additional flux from photons that escape without ever being scattered through the line core.
+ TODO: Add optical depth comparison figure, $x_s$ comparison figure
 

### 2021-05-17 ms.tex
Adding three panel filler plot until replaced
Adding color coding for sections that are under construction

@@
 \newcommand{\grad}{\mathbf{\nabla}}
+
+%%% FOR DRAFTING: REMOVE AFTER PAPER IS COMPLETE!
+\usepackage{xcolor}
 
@@
 
-Nice summary paragraph from recent Bourier  papers.
+\textcolor{red}{Nice summary paragraph from recent Bourier  papers.}
 
@@
 
+\citet{1973MNRAS.162...43H, 1974MNRAS.166..373H} demonstrated that resonance-line radiation transfer in low-density, optically-thick media can be described by the Poisson equation.
+However, the accuracy of their solution is limited by the treatment of the boundary conditions.
+In their eigenfunction expansion, the spatial and frequency components of the differential equation are separated, yet the spatial eigenvalues are defined as being explicitly frequency-dependent.
+The resulting solution for large optical depths would suggest the mean intensity at the boundary of the slab is zero, which is unphysical.
+A more detailed discussion of the boundary condition is included in Section \ref{sec:no_destruction}.
+\citet{1990ApJ...350..216N} follows this approach in an attempt to extend the result to media of intermediate optical depth, including the effects of scattering in the Doppler core of the line, but again does not use the correct boundary condition.
+\citet{1990ApJ...350..216N} improved on this approach, producing a divergent, inhomogeneous solution to the problem in 1D slab geometry that includes the effect of photon absorption within the medium.
+\citet{2006ApJ...649...14D} generalize the problem to spherical geometry, which is the same physical set up used here.
+Following this, \citet{2020arXiv200509692L} discusses solutions for the sphere, utilizing the ``core skipping'' method discussed in \citet{2015MNRAS.449.4336S} to handle photon frequency redistribution within the Doppler core.
+
+%%%%%%%%% TEMPORARY %%%%%%%%%%%%%%%
+\textcolor{red}{
 \citet{1973MNRAS.162...43H, 1974MNRAS.166..373H} started work on analytic solutions as you get a Laplace equation. Doesn't get boundary condition right.
@@
 It seems like this is just calibrated by modifying the truncation until the spectrum doesn’t seem to depend sensitively on the choice of truncation.
-
+}
 \section{ no photon destruction }
@@
 
+\textcolor{red}{
 TODO: Add Monte Carlo description
-
+}
 \subsection{Results}
@@
 
+ \begin{figure}
+    \centering
+    \includegraphics{threepanel_test.png}
+    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
+Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency.
+TODO: Remove blue line.
+We really don't care about the divergent solution anymore.}
+    \label{fig:sol_mc_xinit}
+\end{figure}
+
+ \textcolor{red}{
  TODO: Add optical depth comparison figure, $x_s$ comparison figure
-
+}
 \section{Time-Dependent Diffusion}
@@
 
-\subsection{Numerical Methods}
-\label{subsec:time_dependent:numerical_methods}
+%%% TODO: NOTES
+% Can't solve this exactly, need a numerical scheme to solve.
+Now going to turn to solving this equation (without subsec).
+We start with a treatment of the boundary conditions.
+Continuity in J at the source, the discontinuity needs to be (Eq.
+24)
+
+% Solving the sigma dependence
+% Solving the time dependence
+% Solving the frequency dependence
+
+% Get different pieces of the solution and build it up.
+
+% Make sure that all variables that are introduced in the text are defined beforehand. Especially those that are defined only in the appendix.
 
@@
 
-(TODO: Rewrite) Here we have closed the integral along the $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
+\textcolor{red}{(TODO: Rewrite) Here we have closed the integral along the $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
 The contribution from the semi-circle at infinity is zero.
-Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result
+Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result}
 \be

### 2021-05-18 ms.tex
Adding proposed sections to the introduction --- more detailed explanation of previous work and brief introduction paragraph that's mostly fluff.

@@
 \newcommand{\grad}{\mathbf{\nabla}}
+\newcommand{\todo}[1]{\textcolor{red}{#1}}
+\newcommand{\proposed}[1]{\textcolor{blue}{#1}}
 
@@
 
-ccc\section{Introduction} 
+\section{Introduction} 
 \label{sec:intro}
 
-\textcolor{red}{Nice summary paragraph from recent Bourier  papers.}
+\proposed{
+The outer layers of planetary atmospheres are central to a planet's evolution, as they can shelter the lower atmosphere from high energy radiation and regulate the escape of gas into space.
+There exist several fundamental questions about the evolution and stability of irradiated exoplanet atmospheres; understanding which physical and chemical processes are important in these regions can assist in the creation of robust models which determine the rate of atmospheric mass loss.
+We seek to characterize one such mechanism: the transfer of resonance-line radiation in spherical symmetry at large optical depths.
+}
 
+\todo{
 Hubble Space Telescope observations have found large Lyman $\alpha$ transit depths around the gas giants HD 209458b \citep{2003Natur.422..143V}, HD 189733b \citep{2012A&A...543L...4L} and 55 Cnc b \citep{2012A&A...547A..18E}, Neptune-size planets GJ 436 b
@@
 Non-detections or marginal detections have been reported for the super-Earths 55 Cnc e \citep{2012A&A...547A..18E}, super-Earth HD 97658 b \citep{2017A&A...597A..26B} , super-Earth GJ 1132 b \citep{2019AJ....158...50W}, super-Earth $\pi$ Men c \citep{2020ApJ...888L..21G}, and marginal detections were  Earth-size TRAPPIST-1 \citep{2017A&A...599L...3B} and sub-Earth Kepler-444 \citep{2017A&A...602A.106B}.
+}
+
+\proposed{
+Hubble Space Telescope (HST) observations with STIS have found large Lyman $\alpha$ transit depths around the gas giants HD 209458b \citep{2003Natur.422..143V}, HD 189733b \citep{2012A&A...543L...4L} and 55 Cnc b \citep{2012A&A...547A..18E}, Neptune-size planets GJ 436 b
+\citep{2015Natur.522..459E}
+and GJ 3470 b \citep{2018A&A...620A.147B}, and possibly the super-Earth HD 219134b \citep{2019EPSC...13.1928L}.
+In the case of GJ 436 b, ultraviolet transit depths of 56\% are reported, claiming a total Ly-$\alpha$ eclipse would have been possible for a central transit.
+The most notable absorption is stated to occur in the blue wing of the Ly-$\alpha$ line.
+Non-detections or marginal detections have been reported for the super-Earths 55 Cnc e \citep{2012A&A...547A..18E}, super-Earth HD 97658 b \citep{2017A&A...597A..26B} , super-Earth GJ 1132 b \citep{2019AJ....158...50W}, super-Earth $\pi$ Men c \citep{2020ApJ...888L..21G}, and marginal detections were Earth-size TRAPPIST-1 \citep{2017A&A...599L...3B} and sub-Earth Kepler-444 \citep{2017A&A...602A.106B}.
+Observations of GJ 436b show blue-shifted absorption, possibly due to acceleration of the planet’s atmosphere by radiation pressure from the star.
+\cite{2021ApJ...907L..36M} reports a detection of CII ions in a single transit of the exoplanet $\pi$ Men c, with transit depths and Doppler velocities consistent with an escaping atmosphere.
+}
+
+\proposed{
+These observations of transiting planets have revealed a population of atoms extending out to distances of order the planetary radius for several planets around bright, nearby stars.
+In the case of HD 209458b, observations detected atomic hydrogen (H) absorption in the stellar Ly-$\alpha$ line during three transits.
+Observational data was taken from the Space Telescope Imaging Spectrograph (STIS) onboard the Hubble Space Telescope (HST) using the G140M grating to minimize contamination from Earth's Ly-$\alpha$ geocoronal emission.
+The planet's radius and mass suggest the absorption takes place beyond the Roche limit (i.e., the absorption is occurring in escaped H atoms).
+The magnitude of absorption (15\%) is larger than it should be for a planet that occults only 1.5\% of the star's visible surface.
+A maximally-filled Roche lobe would account for only 10\% absorption.
+The outlying 5\% suggests that hydrogen is escaping the planet's atmosphere.
+Models designed by \citet{2003Natur.422..143V} suggest that the escaping hydrogen atoms expand in an asymmetric comet-like tail and progressively disappear when moving away from the planet, which is consistent with their observations.
+The absorption is thought to last well after the end of the transit due to the large physical size of the evaporating tail.
+In this way, planetary mass and radius measurements allow detailed analysis of Ly-$\alpha$ spectral features, as it is possible to discern what fraction of the absorbing atoms are gravitationally bound to the planet.
+}
 
@@
 \citet{2006ApJ...649...14D} generalize the problem to spherical geometry, which is the same physical set up used here.
-Following this, \citet{2020arXiv200509692L} discusses solutions for the sphere, utilizing the ``core skipping'' method discussed in \citet{2015MNRAS.449.4336S} to handle photon frequency redistribution within the Doppler core.
+Following this, \citet{2020arXiv200509692L} presents closed-form solutions for the radiation field in spherical geometry, utilizing the ``core skipping'' method discussed in \citet{2015MNRAS.449.4336S} to handle photon frequency redistribution within the Doppler core.
+This technique involves drawing the atom's velocity from a truncated Gaussian distribution, forcing photons back into the wing when they scatter into the core.
+This is motivated by the assumption that all core scattering results in zero spatial diffusion until the photon is redistributed back out into the wing where the mean free path becomes much larger and it can diffuse in space again.
+\todo{However, it is not clear whether this prescription is fully independent of the choice of velocity distribution.}
+
+\todo{Elaborate on or reorganize these citations:}
+Radiation forces have been calculated in \citet{1976ApJ...208..286W}, and a discussion of Monte Carlo code acceleration for large optical depths in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
+\citet{1994ApJ...427..603R} introduce an ansatz for the Fokker-Planck approximation using the full Voigt function for the line profile.
 
 %%%%%%%%% TEMPORARY %%%%%%%%%%%%%%%
-\textcolor{red}{
+\ifx
+\todo{
 \citet{1973MNRAS.162...43H, 1974MNRAS.166..373H} started work on analytic solutions as you get a Laplace equation. Doesn't get boundary condition right.
@@
 }
+\fi
 \section{ no photon destruction }
@@
 
-\textcolor{red}{
+\todo{
 TODO: Add Monte Carlo description
@@
 
- \textcolor{red}{
+ \todo{
  TODO: Add optical depth comparison figure, $x_s$ comparison figure
@@
 
-\textcolor{red}{(TODO: Rewrite) Here we have closed the integral along the $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
+\todo{(TODO: Rewrite) Here we have closed the integral along the $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
 The contribution from the semi-circle at infinity is zero.

### 2021-05-20 ms.tex
Comments from Phil (hopefully not deleted!)

@@
 \shorttitle{Lyman $\alpha$}
-\shortauthors{uva lyman alpha group}
+\shortauthors{McClellan et al.}
 
@@
 
-\correspondingauthor{Phil Arras}
-\email{arras@virginia.edu}
+\correspondingauthor{Connor McClellan}
+\email{bcm2vn@virginia.edu}
 
-\author{uva lyman alpha group}
-%\author{Phil Arras}
-%\author{Shane Davis}
+\author{Connor McClellan}
+\author{Shane Davis}
+\author{Phil Arras}
 \affiliation{Department of Astronomy, University of Virginia, Charlottesville, VA 22904, USA}
@@
 \proposed{
-The outer layers of planetary atmospheres are central to a planet's evolution, as they can shelter the lower atmosphere from high energy radiation and regulate the escape of gas into space.
-There exist several fundamental questions about the evolution and stability of irradiated exoplanet atmospheres; understanding which physical and chemical processes are important in these regions can assist in the creation of robust models which determine the rate of atmospheric mass loss.
-We seek to characterize one such mechanism: the transfer of resonance-line radiation in spherical symmetry at large optical depths.
-}
+The outer layers of planetary atmospheres are central to a planet's evolution, as they can shelter the lower atmosphere from high energy radiation and regulate the escape of gas into space.} % Add something about lyman alpha here
+%There's a much thicker layer of atomic hydrogen
+%It's a very optically thick region
+% Care about lya going into the planet's atmosphere and dissociating molecules
+% Observational: observe the transits in lyman alpha
+%Chen liang's paper - focus on the section where he shows the results of the lya transfer - can cause heating deeper in the atmosphere, collisional de-excitation.
+Summarize some of the things that lya does to the atmosphere.
+Ionize low ionization-potential atoms (<10.2 eV)
+%Large Lya line intensity, lots of H atoms, then lya is constantly exciting and de-exciting.
+Then, n=2 is populated so Balmer lines can also be absorbed.
+This explains why strong balmer absorption is observed in transits to begin with.
+Otherwise, you would need very high temperatures to populate the n=2 state.
+% Focus on later sections, especially balmer absorption near the end of the paper.
+\todo{There exist several fundamental questions about the evolution and stability of exoplanet atmospheres that have become irradiated by their host stars; understanding which physical and chemical processes are important in these regions can assist in the creation of robust models to answer such questions.
+(TODO: This sentence reads mostly like fluff but I'm not sure how to outline the problem otherwise.)}
 
+\ifx
 \todo{
@@
 }
+\fi
+
+% Put emphasis on the fact that Lya is generated within the atmosphere --- ionization and rate equilibrium balanced by recombination.
+Recombination gives you lyman alpha again.
+Collisions decrease the density in the 2s states.
+The efficiency of producing lya is quite high, and that's immediately at high optical depth.
 
@@
 The most notable absorption is stated to occur in the blue wing of the Ly-$\alpha$ line.
+Follow-up observations of GJ 3470 b by \citet{2021arXiv210309864B} confirm the presence of an exospheric hydrogen cloud around the planet with a radius of 1.3 times its Roche lobe in the far-ultraviolet, implying that H atoms are escaping the atmosphere.
 Non-detections or marginal detections have been reported for the super-Earths 55 Cnc e \citep{2012A&A...547A..18E}, super-Earth HD 97658 b \citep{2017A&A...597A..26B} , super-Earth GJ 1132 b \citep{2019AJ....158...50W}, super-Earth $\pi$ Men c \citep{2020ApJ...888L..21G}, and marginal detections were Earth-size TRAPPIST-1 \citep{2017A&A...599L...3B} and sub-Earth Kepler-444 \citep{2017A&A...602A.106B}.
-Observations of GJ 436b show blue-shifted absorption, possibly due to acceleration of the planet’s atmosphere by radiation pressure from the star.
 \cite{2021ApJ...907L..36M} reports a detection of CII ions in a single transit of the exoplanet $\pi$ Men c, with transit depths and Doppler velocities consistent with an escaping atmosphere.
@@
 \proposed{
-These observations of transiting planets have revealed a population of atoms extending out to distances of order the planetary radius for several planets around bright, nearby stars.
+These observations have revealed a population of atoms extending out to distances of order the planetary radius for several planets around bright, nearby stars.
 In the case of HD 209458b, observations detected atomic hydrogen (H) absorption in the stellar Ly-$\alpha$ line during three transits.
@@
 The outlying 5\% suggests that hydrogen is escaping the planet's atmosphere.
-Models designed by \citet{2003Natur.422..143V} suggest that the escaping hydrogen atoms expand in an asymmetric comet-like tail and progressively disappear when moving away from the planet, which is consistent with their observations.
+Additionally, the transits show blue-shifted absorption, possibly due to acceleration of the planet’s atmosphere by radiation pressure from the star.
+Models designed by \citet{2003Natur.422..143V} suggest that the escaping hydrogen atoms expand in an asymmetric comet-like tail and progressively disappear when moving away from the planet, which is consistent with most observations mentioned here.
 The absorption is thought to last well after the end of the transit due to the large physical size of the evaporating tail.
@@
 }
+
+\todo{Transition to semi-analytic approach, justification for building models}
 

### 2021-05-26 ms.tex
Adding a few sentences about lyman alpha in the intro paragraph

@@
 \newcommand{\proposed}[1]{\textcolor{blue}{#1}}
+\newcommand\lya{Ly$\alpha$\ }
 
@@
 
-\correspondingauthor{Connor McClellan}
+\correspondingauthor{B. Connor McClellan}
 \email{bcm2vn@virginia.edu}
 
-\author{Connor McClellan}
+\author{B. Connor McClellan}
 \author{Shane Davis}
@@
 \proposed{
-The outer layers of planetary atmospheres are central to a planet's evolution, as they can shelter the lower atmosphere from high energy radiation and regulate the escape of gas into space.} % Add something about lyman alpha here
+The outer layers of planetary atmospheres are central to a planet's evolution, as they can shelter the lower atmosphere from high energy radiation and regulate the escape of gas into space.
+In atmospheres with thick layers of atomic hydrogen, stellar Lyman Alpha (\lya) radiation is especially important as the optical depth at line center is large.
+Recombination can generate \lya within the planet's atmosphere, dissociating molecules in lower layers and causing heating by collisional de-excitation.
+It can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy.
+} % Add something about lyman alpha here
 %There's a much thicker layer of atomic hydrogen
@@
 % Focus on later sections, especially balmer absorption near the end of the paper.
-\todo{There exist several fundamental questions about the evolution and stability of exoplanet atmospheres that have become irradiated by their host stars; understanding which physical and chemical processes are important in these regions can assist in the creation of robust models to answer such questions.
-(TODO: This sentence reads mostly like fluff but I'm not sure how to outline the problem otherwise.)}
 
@@
 
-\citet{1973MNRAS.162...43H, 1974MNRAS.166..373H} demonstrated that resonance-line radiation transfer in low-density, optically-thick media can be described by the Poisson equation.
+\proposed{\citet{1973MNRAS.162...43H, 1974MNRAS.166..373H} demonstrated that resonance-line radiation transfer in low-density, optically-thick media can be described by the Poisson equation.
 However, the accuracy of their solution is limited by the treatment of the boundary conditions.
@@
 This technique involves drawing the atom's velocity from a truncated Gaussian distribution, forcing photons back into the wing when they scatter into the core.
-This is motivated by the assumption that all core scattering results in zero spatial diffusion until the photon is redistributed back out into the wing where the mean free path becomes much larger and it can diffuse in space again.
-\todo{However, it is not clear whether this prescription is fully independent of the choice of velocity distribution.}
+This is motivated by the assumption that all core scattering results in zero spatial diffusion until the photon is redistributed back out into the wing where the mean free path becomes much larger and it can diffuse in space again.} \todo{However, it is not clear whether this prescription is fully independent of the choice of velocity distribution.}
 

### 2021-06-01 ms.tex
small changes
filling out transitions in introduction section

--- 2021-05-20 ms.tex
@@
 \newcommand{\grad}{\mathbf{\nabla}}
-\newcommand{\todo}[1]{\textcolor{red}{#1}}
-\newcommand{\proposed}[1]{\textcolor{blue}{#1}}
+\newcommand\lya{Ly$\alpha$\ }
 
@@
 \usepackage{xcolor}
+\newcommand{\todo}[1]{\textcolor{red}{#1}}
+\newcommand{\proposed}[1]{\textcolor{blue}{#1}}
 
@@
 
-\proposed{
-The outer layers of planetary atmospheres are central to a planet's evolution, as they can shelter the lower atmosphere from high energy radiation and regulate the escape of gas into space.} % Add something about lyman alpha here
+The outer layers of planetary atmospheres are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation and regulate the escape of gas into space.
+In atmospheres with thick layers of atomic hydrogen, stellar Lyman Alpha (Ly$\alpha$) radiation is especially important as the optical depth at line center is large.
+Ionization and subsequent recombination can generate \lya within the planet's atmosphere, dissociating molecules in lower layers and causing heating by collisional de-excitation.
+It can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy.
+
 %There's a much thicker layer of atomic hydrogen
@@
 
-% Put emphasis on the fact that Lya is generated within the atmosphere --- ionization and rate equilibrium balanced by recombination.
+% Put emphasis on the fact that Lya is generated within the atmosphere --- ionization balanced by recombination, rate equilibrium.
 Recombination gives you lyman alpha again.
@@
 
-\proposed{
 Hubble Space Telescope (HST) observations with STIS have found large Lyman $\alpha$ transit depths around the gas giants HD 209458b \citep{2003Natur.422..143V}, HD 189733b \citep{2012A&A...543L...4L} and 55 Cnc b \citep{2012A&A...547A..18E}, Neptune-size planets GJ 436 b
@@
 In the case of GJ 436 b, ultraviolet transit depths of 56\% are reported, claiming a total Ly-$\alpha$ eclipse would have been possible for a central transit.
-The most notable absorption is stated to occur in the blue wing of the Ly-$\alpha$ line.
 Follow-up observations of GJ 3470 b by \citet{2021arXiv210309864B} confirm the presence of an exospheric hydrogen cloud around the planet with a radius of 1.3 times its Roche lobe in the far-ultraviolet, implying that H atoms are escaping the atmosphere.
@@
 \cite{2021ApJ...907L..36M} reports a detection of CII ions in a single transit of the exoplanet $\pi$ Men c, with transit depths and Doppler velocities consistent with an escaping atmosphere.
-}
 
-\proposed{
 These observations have revealed a population of atoms extending out to distances of order the planetary radius for several planets around bright, nearby stars.
-In the case of HD 209458b, observations detected atomic hydrogen (H) absorption in the stellar Ly-$\alpha$ line during three transits.
-Observational data was taken from the Space Telescope Imaging Spectrograph (STIS) onboard the Hubble Space Telescope (HST) using the G140M grating to minimize contamination from Earth's Ly-$\alpha$ geocoronal emission.
-The planet's radius and mass suggest the absorption takes place beyond the Roche limit (i.e., the absorption is occurring in escaped H atoms).
-The magnitude of absorption (15\%) is larger than it should be for a planet that occults only 1.5\% of the star's visible surface.
-A maximally-filled Roche lobe would account for only 10\% absorption.
-The outlying 5\% suggests that hydrogen is escaping the planet's atmosphere.
-Additionally, the transits show blue-shifted absorption, possibly due to acceleration of the planet’s atmosphere by radiation pressure from the star.
-Models designed by \citet{2003Natur.422..143V} suggest that the escaping hydrogen atoms expand in an asymmetric comet-like tail and progressively disappear when moving away from the planet, which is consistent with most observations mentioned here.
-The absorption is thought to last well after the end of the transit due to the large physical size of the evaporating tail.
-In this way, planetary mass and radius measurements allow detailed analysis of Ly-$\alpha$ spectral features, as it is possible to discern what fraction of the absorbing atoms are gravitationally bound to the planet.
-}
-
-\todo{Transition to semi-analytic approach, justification for building models}
+The importance of the \lya line in the atmospheric dynamics of these systems necessitates a careful treatment of resonance-line radiation transfer in order to construct accurate models of atmospheric heating and escape.
+However, the extreme optical depths at \lya line center introduce a computational barrier to simulating radiative transfer via Monte Carlo methods.
 
@@
 \citet{1990ApJ...350..216N} follows this approach in an attempt to extend the result to media of intermediate optical depth, including the effects of scattering in the Doppler core of the line, but again does not use the correct boundary condition.
-\citet{1990ApJ...350..216N} improved on this approach, producing a divergent, inhomogeneous solution to the problem in 1D slab geometry that includes the effect of photon absorption within the medium.
+\citet{?} improved on this approach, producing a divergent, inhomogeneous solution to the problem in 1D slab geometry that includes the effect of photon absorption within the medium.
 \citet{2006ApJ...649...14D} generalize the problem to spherical geometry, which is the same physical set up used here.

### 2021-06-03 ms.tex
Nearing final draft of intro paragraph

@@
 The outer layers of planetary atmospheres are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation and regulate the escape of gas into space.
-In atmospheres with thick layers of atomic hydrogen, stellar Lyman Alpha (Ly$\alpha$) radiation is especially important as the optical depth at line center is large.
+In atmospheres with thick layers of atomic hydrogen, stellar Lyman Alpha (Ly$\alpha$) radiation is especially important in this process as the optical depth at line center is large.
 Ionization and subsequent recombination can generate \lya within the planet's atmosphere, dissociating molecules in lower layers and causing heating by collisional de-excitation.
@@
 
-\ifx
-\todo{
-Hubble Space Telescope observations have found large Lyman $\alpha$ transit depths around the gas giants HD 209458b \citep{2003Natur.422..143V}, HD 189733b \citep{2012A&A...543L...4L} and 55 Cnc b \citep{2012A&A...547A..18E}, Neptune-size planets GJ 436 b
-\citep{2015Natur.522..459E}
-%, 2017A&A...605L...7L,2019A&A...629A..47D}   
-and GJ 3470 b \citep{2018A&A...620A.147B}, and possibly the super-Earth HD 219134b \citep{2019EPSC...13.1928L}.
-Non-detections or marginal detections have been reported for the super-Earths 55 Cnc e \citep{2012A&A...547A..18E}, super-Earth HD 97658 b \citep{2017A&A...597A..26B} , super-Earth GJ 1132 b \citep{2019AJ....158...50W}, super-Earth $\pi$ Men c \citep{2020ApJ...888L..21G}, and marginal detections were  Earth-size TRAPPIST-1 \citep{2017A&A...599L...3B} and sub-Earth Kepler-444 \citep{2017A&A...602A.106B}.
-}
-\fi
-
 % Put emphasis on the fact that Lya is generated within the atmosphere --- ionization balanced by recombination, rate equilibrium.
@@
 
-Hubble Space Telescope (HST) observations with STIS have found large Lyman $\alpha$ transit depths around the gas giants HD 209458b \citep{2003Natur.422..143V}, HD 189733b \citep{2012A&A...543L...4L} and 55 Cnc b \citep{2012A&A...547A..18E}, Neptune-size planets GJ 436 b
-\citep{2015Natur.522..459E}
-and GJ 3470 b \citep{2018A&A...620A.147B}, and possibly the super-Earth HD 219134b \citep{2019EPSC...13.1928L}.
-In the case of GJ 436 b, ultraviolet transit depths of 56\% are reported, claiming a total Ly-$\alpha$ eclipse would have been possible for a central transit.
-Follow-up observations of GJ 3470 b by \citet{2021arXiv210309864B} confirm the presence of an exospheric hydrogen cloud around the planet with a radius of 1.3 times its Roche lobe in the far-ultraviolet, implying that H atoms are escaping the atmosphere.
-Non-detections or marginal detections have been reported for the super-Earths 55 Cnc e \citep{2012A&A...547A..18E}, super-Earth HD 97658 b \citep{2017A&A...597A..26B} , super-Earth GJ 1132 b \citep{2019AJ....158...50W}, super-Earth $\pi$ Men c \citep{2020ApJ...888L..21G}, and marginal detections were Earth-size TRAPPIST-1 \citep{2017A&A...599L...3B} and sub-Earth Kepler-444 \citep{2017A&A...602A.106B}.
-\cite{2021ApJ...907L..36M} reports a detection of CII ions in a single transit of the exoplanet $\pi$ Men c, with transit depths and Doppler velocities consistent with an escaping atmosphere.
-
-These observations have revealed a population of atoms extending out to distances of order the planetary radius for several planets around bright, nearby stars.
-The importance of the \lya line in the atmospheric dynamics of these systems necessitates a careful treatment of resonance-line radiation transfer in order to construct accurate models of atmospheric heating and escape.
+Hubble Space Telescope (HST) observations with STIS have found large Lyman $\alpha$ transit depths, indicating an extended distribution of hydrogen around a handful of exoplanets \todo{Organize these by date?} (\citealp{2003Natur.422..143V}; \citealp{2012A&A...543L...4L}; \citealp{2012A&A...547A..18E}; \citealp{2015Natur.522..459E}; \citealp{2018A&A...620A.147B}; \citealp{2019EPSC...13.1928L}; \citealp{2021arXiv210309864B}; \citealp{2012A&A...547A..18E}; \citealp{2017A&A...597A..26B}; \citealp{2019AJ....158...50W}; \citealp{2020ApJ...888L..21G}; \citealp{2017A&A...599L...3B}; \citealp{2017A&A...602A.106B}).
+These observations have revealed a population of atoms extending out to distances of order the planetary radius for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with H atoms surrounding a planet.
+The importance of the \lya line in the atmospheric dynamics of these systems necessitates a careful treatment of resonant scattering in order to construct accurate models of atmospheric heating and escape.
 However, the extreme optical depths at \lya line center introduce a computational barrier to simulating radiative transfer via Monte Carlo methods.
 
-The main impediment to peforming magnetohydrodynamic simulations with fully a coupled radiative transfer solution via Monte Carlo methods is the prohibitive computational cost.
-A primary factor in the cost of Monte Carlo is that the number of scatterings a photon (packet/superphoton?) undergoes is proportional to the line center optical depth.
-Near the base of the atmosphere individual simulation cells can have optical depths of more than a million so most of the time is spent integrating photons in these cells.
+The main impediment to performing magnetohydrodynamic simulations with fully a coupled radiative transfer solution via Monte Carlo methods is the prohibitive computational cost.
+A primary factor in the cost of Monte Carlo is that the number of scatterings a photon undergoes is proportional to the line center optical depth.
+Near the base of the atmosphere, individual simulation cells can have optical depths of more than a million, so most of the time is spent integrating photons in these cells.
 This means that any method that can treat these zone via an analytic solution has the potential to greatly accelerate the calculation.
@@
 The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.
-These methods focus Monte Carlo transfer on the wings of the line and avoid scatterings in the core.
-Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so tha opacity is lower and escape is more rapid.
+These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core.
+Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.
 
-A second class of methods are hydbrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
-This involves designating sufficiently optically thick simulations cells for computation via a finite difference representaiton of radiation transfer equation.
+A second class of methods are hybrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
+This involves designating sufficiently optically thick simulations cells for computation via a finite difference representation of the radiation transfer equation.
 This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.
-For the resonant scattering problem, where the opacity is a strong function of frequnecy, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
+For the resonant scattering problem, where the opacity is a strong function of frequency, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
 
@@
 An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation withing a uniform sphere.
+
+\todo{FOR REVIEW: a summative few sentences connecting the MC methods to what we're doing in this paper:}
+
+\proposed{In this work, we present an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry and a semi-analytic solution to time-dependent \lya diffusion through the same medium.
+These will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.}
 

### 2021-06-03 ms.tex
rephrasing summary paragraph at beginning of introduction

@@
 It can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy.
+\todo{Need citations for these statements?}
 
@@
 In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
-An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation withing a uniform sphere.
+An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation within a uniform sphere.
 
@@
 
-\proposed{In this work, we present an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry and a semi-analytic solution to time-dependent \lya diffusion through the same medium.
+\proposed{The need for accurate distributions from which to draw outgoing photon properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry and a semi-analytic solution to time-dependent \lya diffusion through the same medium.
 These will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.}

### 2021-06-04 ms.tex
Substantial changes to introduction, previous analytic methods, and steady state section

@@
 
-Hubble Space Telescope (HST) observations with STIS have found large Lyman $\alpha$ transit depths, indicating an extended distribution of hydrogen around a handful of exoplanets \todo{Organize these by date?} (\citealp{2003Natur.422..143V}; \citealp{2012A&A...543L...4L}; \citealp{2012A&A...547A..18E}; \citealp{2015Natur.522..459E}; \citealp{2018A&A...620A.147B}; \citealp{2019EPSC...13.1928L}; \citealp{2021arXiv210309864B}; \citealp{2012A&A...547A..18E}; \citealp{2017A&A...597A..26B}; \citealp{2019AJ....158...50W}; \citealp{2020ApJ...888L..21G}; \citealp{2017A&A...599L...3B}; \citealp{2017A&A...602A.106B}).
+Hubble Space Telescope (HST) observations with STIS have found large Lyman $\alpha$ transit depths, indicating an extended distribution of hydrogen around a handful of exoplanets: \citet{2003Natur.422..143V, 2012A&A...543L...4L, 2012A&A...547A..18E, 2015Natur.522..459E,  2017A&A...597A..26B, 2017A&A...599L...3B, 2017A&A...602A.106B, 2018A&A...620A.147B, 2019AJ....158...50W, 2019EPSC...13.1928L, 2020ApJ...888L..21G,2021arXiv210309864B}.
 These observations have revealed a population of atoms extending out to distances of order the planetary radius for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with H atoms surrounding a planet.
@@
 This is motivated by the assumption that all core scattering results in zero spatial diffusion until the photon is redistributed back out into the wing where the mean free path becomes much larger and it can diffuse in space again.
-\todo{However, it is not clear whether this prescription is fully independent of the choice of velocity distribution.}
+However, it is not clear whether this prescription is fully independent of the choice of velocity distribution.
 
-\todo{Elaborate on or reorganize these citations:}
-Radiation forces have been calculated in \citet{1976ApJ...208..286W}, and a discussion of Monte Carlo code acceleration for large optical depths in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
-\citet{1994ApJ...427..603R} introduce an ansatz for the Fokker-Planck approximation using the full Voigt function for the line profile.
+Radiation forces due to \lya transfer have been calculated in \citet{1976ApJ...208..286W} in plane-parallel geometry.
+However, these solutions are limited to optical depths below $2.5 \times 10^3$.
+In the grid cells of a radiation magnetohydrodynamic simulation that includes resonant scattering, for example, it would be necessary to calculate the radiation force on each cell face due to \lya at line center optical depths of up to 1 million.
+A discussion of Monte Carlo code acceleration for optical depths as large as these in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
+In terms of the time dependence, \citet{1994ApJ...427..603R} introduce an ansatz for the Fokker-Planck diffusion equation in order to quantify the relaxation timescale necessary to reach a quasi-static solution.
+Notably, the full Voigt function is used for the line profile rather than restricting scattering to the damping wing only.
 
-%%%%%%%%% TEMPORARY %%%%%%%%%%%%%%%
-\ifx
-\todo{
-\citet{1973MNRAS.162...43H, 1974MNRAS.166..373H} started work on analytic solutions as you get a Laplace equation. Doesn't get boundary condition right.
-\citet{1990ApJ...350..216N} has analytic solutions following Harrington.
-\citet{1990ApJ...350..216N} improved on Harrington. Does have divergent inhomogeneous solution in slab geometry! Also has discussion of absorption.
-\citet{2006ApJ...649...14D} generalized Harrington to spherical geometry
-\citet{1976ApJ...208..286W} tries to compute the radiation force
-\citet{1994ApJ...427..603R} discuss an ansatz for the fokker-planck approximation where the full voigt profile is used.
-\citet{2020arXiv200509692L} discusses solutions for the sphere. Follows \citet{2006ApJ...649...14D}. They cite \citet{2015MNRAS.449.4336S} on core skipping.
-\citet{2002ApJ...567..922A,2015MNRAS.449.4336S} discusses acceleration.
-\citet{2015MNRAS.449.4336S}: amounts to drawing the atom velocity from a truncated Gaussian distribution to force it back into the wing.
-The logic seems to be that almost all of the core scattering results in zero spatial diffusion until you get far enough from the line wing.
-It seems like this is just calibrated by modifying the truncation until the spectrum doesn’t seem to depend sensitively on the choice of truncation.
-}
-\fi
-\section{ no photon destruction }
-\label{sec:no_destruction}
+\section{STEADY-STATE SOLUTION}
+\label{sec:steadystate}
 
-\subsection{Background}
-\label{subsec:no_destruction:background}
+Three solutions will be considered for this problem.
 
-Three solutions will be considered for this problem: a ``divergent" solution due to the delta function source, a ``J=0" solution which includes the delta function solution at the source and satisfies $J=0$ at $r=R$, and the ``bc" solution that allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
-The divergent solution is discussed for qualitative understanding, and the full solution is the sum of the $J=0$ solution and the bc solution.
+\begin{enumerate}
+    \item a \textbf{divergent solution} ($\rm H_d$) due to the delta function source,
+    \item a \textbf{J=0 solution} ($\rm H_0$) which includes the delta function solution at the source and satisfies $J=0$ at $r=R$,
+    \item the \textbf{bc solution} ($\rm H_{bc}$) that allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
+\end{enumerate}
 
-\subsection{Equations}
-\label{subsec:no_destruction:equations}
+\noindent The divergent solution is discussed for qualitative understanding, and the full solution is the sum of the $J=0$ solution and the bc solution.
+The problem is as follows.
+The radiative intensity $I = dE/(dA dt d\Omega d\nu)$ is the energy per perpendicular area $dA$, per time $dt$, per solid angle $d\Omega$ and per frequency $d\nu$ \citep{1986rpa..book.....R}.
+Here the time-dependence of $I$ has been ignored, which assumes the fluid is changing on timescales long compared to a light-crossing time.
+The intensity $I=I(\vec{x},\vec{n}, \nu)$ will be considered a function of position $\vec{x}$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$.
+In the Eddington and two-stream approximations, $I(\vec{x},\nu) \simeq J(\vec{x},\nu) + 3 \vec{n} \cdot \vec{H}(\vec{x},\nu)$, where $J=(1/4\pi) \int d\Omega I$ is the mean intensity and $\vec{F} = 4\pi \vec{H}= \int d\Omega \vec{n} I$ is the flux.
 
-The problem is as follows.
-Consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
-The transfer Equation \ref{eq:finaleqn} with no photon destruction terms, $p=\alpha_{\rm abs}=0$, and with a  photon emission term given by Equation \ref{eq:jem}), which gives the transfer equation
+Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
+The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
+The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$.
+For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
+The transfer equation is \citep{1986rpa..book.....R}
+\be
+\frac{1}{c} \frac{\partial I}{\partial t} + \vec{n} \cdot \grad I & =& - \left( \alpha_{\rm sc} + \alpha_{\rm abs} \right) I + (1-p) j_{\rm sc} + j_{\rm em}.
+\label{eq:rteqn}
+\ee
+The scattering coefficient, or inverse mean free path to scattering, is 
+\be
+\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{H(x,a)}{\sqrt{\pi} \Delta}
+= k \phi   
+\ee
+where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section.
+Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons.
+
+Now, consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
+Here, the Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
+After changing the photon frequency variable in Eq.
+\ref{eq:rteqn} and performing all angular integrals, we obtain Eq.
+\ref{eq:finaleqn} (see Appendix \ref{app:rteqn_derivation}) and set $p=\alpha_{\rm abs}=0$ to eliminate photon destruction terms.
+With a photon emission term given by Eq.
+\ref{eq:jem}, this gives the transfer equation
 \be
@@
 \ee
-where the form of the source term is in Equation \ref{eq:jem_v2}. The boundary condition is that there is no incoming flux at the surface, which can be written
+where the form of the source term is in Eq. \ref{eq:jem_v2}. The boundary condition is that there is no incoming flux at the surface, which can be written
 \citep{1986rpa..book.....R}
@@
 \ee
-While this solution does not satisfy the surface boundary condition (Equation \ref{eq:bc}), it is accurate near the delta-function source.
+While this solution does not satisfy the surface boundary condition (Eq. \ref{eq:bc}), it is accurate near the delta-function source.
 This solution generalizes the particular solution for slab geometry found by \citet{1990ApJ...350..216N}.
 Henceforth we will focus on the source at the center of the sphere, although we will retain the emission frequency at $\sigma=\sigma_{\rm s}$.
-The radial flux corresponding to Equation \ref{eq:Jd} is
+The radial flux corresponding to Eq.
+\ref{eq:Jd} is
 \be
@@
 \ee
-It will be shown that Equation \ref{eq:Hd} is a good approximation at $r=R$ near line center.
-However Equation \ref{eq:Jd} is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$.
+It will be shown that Eq.
+\ref{eq:Hd} is a good approximation at $r=R$ near line center.
+However Eq.
+\ref{eq:Jd} is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$.
 
@@
 \ee
-Equation \ref{eq:H0surf} will be shown to be a much better approximation to the solution, which is valid near the delta function at the center, and is a much better approximation at the surface.
+Eq.
+\ref{eq:H0surf} will be shown to be a much better approximation to the solution, which is valid near the delta function at the center, and is a much better approximation at the surface.
 It will be shown that it is still only a good approximation near line center at the surface.
@@
 
-The question is how to satisfy the surface boundary condition in Equation \ref{eq:bc}.
+The question is how to satisfy the surface boundary condition in Eq.
+\ref{eq:bc}.
 On this point, we note that the derivation in \citet{1973MNRAS.162...43H}, and numerous studies later studies, does not actually produce a valid solution of the transfer equation and boundary condition.
@@
 The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
-But then the separation constant is not constant, and it does not satisfy Equation \ref{eq:rt_no_destr} since the frequency derivatives will act on the separation ``constant", giving extra terms.
+But then the separation constant is not constant, and it does not satisfy Eq.
+\ref{eq:rt_no_destr} since the frequency derivatives will act on the separation ``constant", giving extra terms.
 To our knowledge the errors introduced by this ansatz have never been quantified.
@@
 In the limit of large optical depth $B$, \citealt{1973MNRAS.162...43H} approximates the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$, which gives $J=0$ at the surface.
-This is essentially the result in Equation \ref{eq:J0} above.
-However, since this solution gives zero at the surface, their Equation 34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
+This is essentially the result in Eq.
+\ref{eq:J0} above.
+However, since this solution gives zero at the surface, their Eq.
+34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
 This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
@@
 
-Plugging Equation \ref{eq:Jbc} into Equation \ref{eq:bc2} leads to the following equation for the Fourier amplitudes
+Plugging Eq. \ref{eq:Jbc} into Eq. \ref{eq:bc2} leads to the following equation for the Fourier amplitudes
 \be
@@
 \ee
-where $H_0(R,\nu)$ is given by Equation \ref{eq:H0surf}. Discretization of Equation \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
+where $H_0(R,\nu)$ is given by Eq. \ref{eq:H0surf}. Discretization of Eq. \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
 leads to a set of coupled linear equations for the $A(s_j)$.
@@
 The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries.
-Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Equation \ref{eq:Jbc}, and the flux is given by
+Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq.
+\ref{eq:Jbc}, and the flux is given by
 \be
@@
 The Bessel functions are finite at the center and rise steeply toward the surface when $kRs/\Delta \gg 1$.
-%\fi
 
-In Section \ref{subsec:no_destruction:results}, each of these solutions are compared with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$.
+We now compare each of these solutions for surface flux with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$.
+In Fig.
+\ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ overplotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\sigma_s = \sigma_0$.
+The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
+It is evident that the divergent solution $H_{\rm d}$ fails in the line wings.
+The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum, which was also noted in \citet{2015MNRAS.449.4336S}.
+The boundary term also resolves the slight deficit of $H_{\rm0}$ in the line wings, improving agreement with the numerical result.
 
-\subsection{Numerical Methods}
-\label{subsec:no_destruction:methods}
-
-\todo{
-TODO: Add Monte Carlo description
-}
-\subsection{Results}
-\label{subsec:no_destruction:results}
 \begin{figure}
@@
 \end{figure}
-
- In Fig.
-\ref{fig:sol_mc_residual_0}, the fluxes derived in Section \ref{subsec:no_destruction:equations} are compared with the Monte Carlo at selected initial frequencies.
-The contribution of the flux from Eq.
-\ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$.
-The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
-It is evident that the ``divergent'' solution $H_{\rm d}$ fails by a large margin in the line wings.
-The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum as well as the slight deficit in the line wings, improving the agreement of the analytic solution with the numerical result.
 
@@
 }
+
 \section{Time-Dependent Diffusion}
@@
 The coefficient of $\partial J/\partial t$ has explicit dependence on $\sigma$.
-Separation of variables may be achieved in Equation \ref{eq:diffusion_eqn} by assuming an expansion in terms of spherical Bessel functions in $r$ and a Fourier expansion in time to find the form
+Separation of variables may be achieved in Eq.
+\ref{eq:diffusion_eqn} by assuming an expansion in terms of spherical Bessel functions in $r$ and a Fourier expansion in time to find the form
 \be
@@
 \ee
-Integrating over $\nu$ gives unity if the sum rule in Equation \ref{eq:sumrule} is true.
+Integrating over $\nu$ gives unity if the sum rule in Eq. \ref{eq:sumrule} is true.
 
@@
 
-\section{ derivation of the transfer equation }
+\section{ derivation of the transfer equation } \label{app:rteqn_derivation}
 
@@
 
-The radiative intensity $I = dE/(dA dt d\Omega d\nu)$ is the energy per perpendicular area $dA$, per time $dt$, per solid angle $d\Omega$ and per frequency $d\nu$ \citep{1986rpa..book.....R}.
-Here the time-dependence of $I$ has been ignored, which assumes the fluid is changing on timescales long compared to a light-crossing time.
-The intensity $I=I(\vec{x},\vec{n}, \nu)$ will be considered a function of position $\vec{x}$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$.
-In the Eddington and two-stream approximations, $I(\vec{x},\nu) \simeq J(\vec{x},\nu) + 3 \vec{n} \cdot \vec{H}(\vec{x},\nu)$, where $J=(1/4\pi) \int d\Omega I$ is the mean intensity and $\vec{F} = 4\pi \vec{H}= \int d\Omega \vec{n} I$ is the flux.
-
-Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
-The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
-The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$.
-For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
-The transfer equation is \citep{1986rpa..book.....R}
-\be
-\frac{1}{c} \frac{\partial I}{\partial t} + \vec{n} \cdot \grad I & =& - \left( \alpha_{\rm sc} + \alpha_{\rm abs} \right) I + (1-p) j_{\rm sc} + j_{\rm em}.
-\label{eq:rteqn}
-\ee
-The scattering coefficient, or inverse mean free path to scattering, is 
-\be
-\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{H(x,a)}{\sqrt{\pi} \Delta}
-= k \phi   
-\ee
-where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ have their usual meaning, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
-The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section.
-Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons.
  ``Hummer Case II-b"  \citep{1962MNRAS.125...21H} will be used for the redistribution function, for which the incoming photon is absorbed by the atom according to the natural broadening in the rest frame, re-emitted with a dipole phase function $g(\vec{n},\vec{n}^\prime)=(3/16\pi)(1+[\vec{n}\cdot \vec{n}^\prime]^2)$, which is appropriate for a 1s-2p transition \citep{1982qe}, and the result is averaged over a Maxwell-Boltzmann distribution of speeds for the atom.
@@
 \ee
-The first term in Equation \ref{eq:jsc}, $k\phi J$, represents re-emission of the photon through de-excitation of the atom.
-It cancels the $-k\phi J$ term in Equation \ref{eq:rteqn} that corresponds to excitation of the atom.
+The first term in Eq.
+\ref{eq:jsc}, $k\phi J$, represents re-emission of the photon through de-excitation of the atom.
+It cancels the $-k\phi J$ term in Eq.
+\ref{eq:rteqn} that corresponds to excitation of the atom.
 The terms involvingfrequency derivatives of $\vec{H}$, if carried through the calculation,end up giving terms smaller than then largest terms by a factor of $1/x^2$, which is small on the line wing.
@@
 \ee
-Multiplying by a factor $-3k\phi$, as appears in Equation \ref{eq:finaleqn}, the delta function in $\nu$ becomes a delta function in $\sigma$ of the form
+Multiplying by a factor $-3k\phi$, as appears in Eq. \ref{eq:finaleqn}, the delta function in $\nu$ becomes a delta function in $\sigma$ of the form
 \be

### 2021-06-04 ms.tex
adding citations to Neufeld, Smith regarding the excess in the spectrum at the peaks

@@
 
+\subsection{Derivation of the Steady-State Solution}
 Now, consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
@@
 
+\subsection{Comparison to Monte Carlo}
+
 We now compare each of these solutions for surface flux with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$.
@@
 It is evident that the divergent solution $H_{\rm d}$ fails in the line wings.
-The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum, which was also noted in \citet{2015MNRAS.449.4336S}.
-The boundary term also resolves the slight deficit of $H_{\rm0}$ in the line wings, improving agreement with the numerical result.
+The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum.
+This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S}.
+The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, improving agreement with the numerical result.
 

### 2021-06-04 ms.tex
adding TODO for beginning of Comparison to Monte Carlo subsection

@@
 
+\todo{Brief description of MC code, citing Chenliang's paper.
+Discuss how MC works briefly, reference some papers, talk about problem setup specific to this work.
+Basically want to show that the MC approach in this paper is not new and doesn't need to be justified extensively.}
+
 We now compare each of these solutions for surface flux with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$.
@@
 This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S}.
-The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, improving agreement with the numerical result.
+The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
 

### 2021-06-15 ms.tex
adding tau scaling plot to paper for steady state solution
changing colorscheme of tau and xinit three panel plots
Added definition of change of frequency variables in the derivation of the steady state solution

@@
 \ee
-where the form of the source term is in Eq. \ref{eq:jem_v2}. The boundary condition is that there is no incoming flux at the surface, which can be written
+where the form of the source term is in Eq.
+\ref{eq:jem_v2} and a change of variables in frequency has been performed using $d\sigma/dx = \sqrt{2/3}\ \phi(x)^{-1}$.
+The boundary condition is that there is no incoming flux at the surface, which can be written
 \citep{1986rpa..book.....R}
@@
     \centering
-    \includegraphics{threepanel_test.png}
+    \includegraphics{xinit_threepanel.pdf}
     \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
@@
 
- \todo{
- TODO: Add optical depth comparison figure, $x_s$ comparison figure
-}
+ \begin{figure}
+    \centering
+    \includegraphics{tau_threepanel_factorof2.pdf}
+    \caption{Increasing the line center optical depth.
+Shown here are $\tau_0 = 10^5, 10^6, 10^7$ with the $x$ and $y$ axes scaled by the characteristic frequency diffusion scale $(a\tau_0)^{1/3}$.
+Photons are initialized with $\rm x = 0.0$.}
+    \label{fig:sol_mc_tau}
+\end{figure}
 

### 2021-06-21 ms.tex
adding atau1/3 scaling beginnings
committing previous changes
changing some \nu to \sigma where appropriate
Adding in new taubc plot and short description / caption

@@
 \documentclass{aastex63}
-
+\usepackage{amsmath}
 \newcommand{\be}{\begin{eqnarray}}
@@
 An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation within a uniform sphere.
+A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution.
 
@@
 \be
-H_0(R,\nu) & = & \left( \frac{1}{3k\phi} \right)
+H_0(R, \sigma) & = & \left( \frac{1}{3k\phi} \right)
 \left( \frac{\sqrt{6}L}{32\pi \Delta} \right)
@@
 and
-\be
+\be \label{eq:totalflux}
 H(r,\nu) & = & H_0(r,\nu) + H_{\rm bc}(r,\nu).
@@
 J_{\rm bc}(R,\nu) - \sqrt{3} H_{\rm bc}(R,\nu) & = & 
-J_{\rm bc}(R,\nu) + \frac{1}{\sqrt{3}k\phi} \frac{\partial J_{\rm bc}(R,\nu)}{\partial r} = 
+J_{0}(R,\nu) + \frac{1}{\sqrt{3}k\phi} \frac{\partial J_{0}(R,\nu)}{\partial r} = 
 \sqrt{3} H_0(R,\nu).
@@
 The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that  the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries.
-The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries.
-Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq.
+\todo{The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries.
+(Is this still accurate?)} Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq.
 \ref{eq:Jbc}, and the flux is given by
@@
 The Bessel functions are finite at the center and rise steeply toward the surface when $kRs/\Delta \gg 1$.
+
+To examine the relative size of this corrective term as compared to $H_0$, we consider the case where the optical depth is large and thus the mean intensity will be considerably larger than the surface flux.
+Starting from Eq.
+\ref{eq:bc2}, we assume $H_{\rm bc} \ll J_{\rm bc}$ such that
+\be
+J_{\rm bc}(R,\sigma) & \approx & \sqrt{3} H_0(R,\sigma).
+\label{eq:bc4}
+\ee
+The Fourier transform for $J_{\rm bc}$ at the surface becomes
+\be
+J_{\rm bc}(R, \sigma) \equiv \int_{-\infty}^{\infty} \frac{ds}{2\pi} e^{is\sigma} A(s)
+\ee
+with Fourier amplitudes
+\be \label{eq:amps}
+A(s) = \sqrt{3} \int_{-\infty}^{\infty} d\sigma e^{-is\sigma} H_0(R, \sigma).
+\ee
+Plugging the expression for $H_0$ in Eq. \ref{eq:H0surf} into Eq. \ref{eq:amps} yields an expression for the Fourier amplitudes
+\be \label{eq:plugged_amps}
+A(s) = \sqrt{3}\frac{1}{3k}\frac{\sqrt{6}}{32\pi}\frac{L}{\Delta R^3} \int_{-\infty}^\infty d\sigma e^{-is\sigma}\frac{1}{\phi(\sigma)}\frac{1}{1+\cosh \left[\frac{\pi \Delta}{kR} |\sigma - \sigma_i|\right]}
+\ee
+with
+\be
+\phi(\sigma) = \left(\frac{2a}{27\pi}\right)^{1/3}\frac{1}{\Delta |\sigma|^{2/3}}.
+\ee
+With the line center optical depth defined as
+\be
+\tau_0 = \frac{kR}{\sqrt{\pi}\Delta}
+\ee
+we scale the variables $\sigma$ and $s$ by $\tau_0$, now using characteristic photon frequency $\bar \sigma = \sigma / \tau_0$ and characteristic wavenumber $\bar s = s \tau_0$.
+Eq.
+\ref{eq:plugged_amps} becomes
+\be
+A(\bar s) &=& \frac{\sqrt{2}}{32\pi}\frac{L}{kR^3}\int_{-\infty}^\infty d\bar\sigma \tau_0 e^{-i\bar s \bar\sigma} \left(\frac{27\pi}{2a}\right)^{1/3}\tau_0^{2/3}|\bar\sigma^{2/3}|\frac{1}{1+\cosh \left[\sqrt{\pi}|\bar\sigma - \bar\sigma_i|\right]}\\
+&=& \frac{\sqrt{2}}{32\pi}\left(\frac{27\pi}{2}\right)^{1/3}\frac{L}{kR^3}\frac{\tau_0^{5/3}}{a^{1/3}}\int_{-\infty}^\infty d\bar\sigma e^{-i\bar s \bar\sigma} |\bar\sigma^{2/3}|\frac{1}{1+\cosh \left[\sqrt{\pi}|\bar\sigma - \bar\sigma_i|\right]}
+\ee
+These coefficients are used to evaluate Eq. \ref{eq:Hbc} at the surface of the sphere. Dividing this flux $H_{\rm bc}$ by the $H_0$ (Eq. \ref{eq:H0surf}) yields an overall proportionality
+\be
+\frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto \frac{1}{(a\tau_0)^{1/3}}.
+\ee
+Thus, the fractional importance of the corrective frequency-dependent boundary condition term scales as the inverse cube root of the damping parameter $a$ times the line-center optical depth $\tau_0$.
+At very large optical depths, it is expected that the corrective term will be small, but will become increasingly important in less optically thick media.
+This is shown graphically in Fig.
+\ref{fig:taubc}, where the $H_{\rm bc}$ solution has been discretized in $s$ and $\sigma$ and solved via a matrix equation.
+
+\begin{figure}
+    \centering
+    \includegraphics{taubc.pdf}
+    \caption{Boundary condition term $H_{\rm bc}$ scaled by $(a\tau_0)^{1/3}$ shown for increasing line center optical depths.
+The $H_0$ solution minus the Monte Carlo data should be close to $H_{\rm bc}$ according to Eq.
+\ref{eq:totalflux}.
+As $\tau_0$ becomes larger, the agreement between these two improves, indicating that at large optical depths the relative size of the corrective boundary condition term scales as $(a\tau_0)^{-1/3}$}.
+    \label{fig:taubc}
+\end{figure}
 
@@
     \centering
-    \includegraphics{pdf_xinit0.0.pdf}
+    \includegraphics{final_residual.pdf}
     \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
@@
     \centering
-    \includegraphics{tau_threepanel_factorof2.pdf}
+    \includegraphics{tau_threepanel.pdf}
     \caption{Increasing the line center optical depth.

### 2021-06-22 ms.tex
Replacing \nu with \sigma in function declarations
Proof reading up to Monte Carlo section

@@
 A monochromatic source of photons is assumed at the center of the sphere, and the intensity within the sphere and at the surface is found with the Eddington approximation for the angular dependence.
-The solution can be represented a sum of three terms: a simple, analytic solution of the inhomogeneous equation which diverges at the center of the sphere and at the emission frequency; a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface; and finally, a solution of the homogeneous equation which enforces the correct, zero ingoing intensity boundary conditions at the surface.
+The solution can be represented a sum of three terms: a simple, analytic solution of the inhomogeneous equation which diverges at the center of the sphere and at the emission frequency; a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface; and finally, a solution of the homogeneous equation which enforces the correct, zero-ingoing intensity boundary conditions at the surface.
 It is the compact, analytic form as well as the piece accounting for the correct, frequency dependent boundary condition that is novel in this study.
@@
 Ionization and subsequent recombination can generate \lya within the planet's atmosphere, dissociating molecules in lower layers and causing heating by collisional de-excitation.
-It can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy.
-\todo{Need citations for these statements?}
+\lya can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy.
 
@@
 
-Hubble Space Telescope (HST) observations with STIS have found large Lyman $\alpha$ transit depths, indicating an extended distribution of hydrogen around a handful of exoplanets: \citet{2003Natur.422..143V, 2012A&A...543L...4L, 2012A&A...547A..18E, 2015Natur.522..459E,  2017A&A...597A..26B, 2017A&A...599L...3B, 2017A&A...602A.106B, 2018A&A...620A.147B, 2019AJ....158...50W, 2019EPSC...13.1928L, 2020ApJ...888L..21G,2021arXiv210309864B}.
+Hubble Space Telescope (HST) observations with STIS have found large \lya transit depths around a handful of exoplanets, indicating an extended distribution of hydrogen: \citet{2003Natur.422..143V, 2012A&A...543L...4L, 2012A&A...547A..18E, 2015Natur.522..459E,  2017A&A...597A..26B, 2017A&A...599L...3B, 2017A&A...602A.106B, 2018A&A...620A.147B, 2019AJ....158...50W, 2019EPSC...13.1928L, 2020ApJ...888L..21G,2021arXiv210309864B}.
 These observations have revealed a population of atoms extending out to distances of order the planetary radius for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with H atoms surrounding a planet.
@@
 
-A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M,Robitaille2010}.
+A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M, 2010A&A...520A..70R}.
 In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
@@
 
-\todo{FOR REVIEW: a summative few sentences connecting the MC methods to what we're doing in this paper:}
-
-\proposed{The need for accurate distributions from which to draw outgoing photon properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry and a semi-analytic solution to time-dependent \lya diffusion through the same medium.
-These will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.}
+The need for accurate distributions from which to draw outgoing photon properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
+In addition, a semi-analytic solution to time-dependent \lya diffusion through the same medium is explored to quantify how long the photons are expected to spend in the domain before escaping.
+These solutions will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.
 
@@
 The resulting solution for large optical depths would suggest the mean intensity at the boundary of the slab is zero, which is unphysical.
-A more detailed discussion of the boundary condition is included in Section \ref{sec:no_destruction}.
+A more detailed discussion of the boundary condition is included in Section \ref{sec:steadystate}.
 \citet{1990ApJ...350..216N} follows this approach in an attempt to extend the result to media of intermediate optical depth, including the effects of scattering in the Doppler core of the line, but again does not use the correct boundary condition.
@@
 Now, consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
-Here, the Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
-After changing the photon frequency variable in Eq.
+After changing variables from $\nu$ to $\sigma$ using $d\sigma = \sqrt{2/3}d\nu/(\Delta^2 \phi)$ in Eq.
 \ref{eq:rteqn} and performing all angular integrals, we obtain Eq.
@@
 \ee
-where the form of the source term is in Eq.
-\ref{eq:jem_v2} and a change of variables in frequency has been performed using $d\sigma/dx = \sqrt{2/3}\ \phi(x)^{-1}$.
-The boundary condition is that there is no incoming flux at the surface, which can be written
+where the form of the source term is in Eq. \ref{eq:jem_v2}. The boundary condition is that there is no incoming flux at the surface, which can be written
 \citep{1986rpa..book.....R}
@@
 at $r=R$.
-
 First consider the divergent solution.
@@
 C17) yields a $J=2H$ surface boundary condition.
-Under the two-stream approximation, a surface boundary condition $J=\sqrt{3}H$ is necessary to properly normalize the radiation pressure.
+However, under the two-stream approximation, a surface boundary condition $J=\sqrt{3}H$ is necessary to properly normalize the radiation pressure.
 
@@
 \be
-J(r,\nu) & = & J_0(r,\nu) + J_{\rm bc}(r,\nu)
+J(r,\sigma) & = & J_0(r,\sigma) + J_{\rm bc}(r,\sigma)
 \ee
@@
 \be \label{eq:totalflux}
-H(r,\nu) & = & H_0(r,\nu) + H_{\rm bc}(r,\nu).
+H(r,\sigma) & = & H_0(r,\sigma) + H_{\rm bc}(r,\sigma).
 \ee
@@
 \be
-J_{\rm bc}(R,\nu) - \sqrt{3} H_{\rm bc}(R,\nu) & = & 
-J_{0}(R,\nu) + \frac{1}{\sqrt{3}k\phi} \frac{\partial J_{0}(R,\nu)}{\partial r} = 
-\sqrt{3} H_0(R,\nu).
+J_{\rm bc}(R,\sigma) - \sqrt{3} H_{\rm bc}(R,\sigma) & = & 
+J_{0}(R,\sigma) + \frac{1}{\sqrt{3}k\phi} \frac{\partial J_{0}(R,\sigma)}{\partial r} = 
+\sqrt{3} H_0(R,\sigma).
 \label{eq:bc2}
@@
 \be
-J_{\rm bc}(r,\nu) & = & 
+J_{\rm bc}(r,\sigma) & = & 
 \int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s) 
@@
 \left[ 1 + \left( \frac{s}{\sqrt{3} \Delta \phi} \right) \left( \frac{i_0^\prime(kRs/\Delta)}{i_0(kRs/\Delta)} \right) \right]
-& = & \sqrt{3} H_0(R,\nu)
+& = & \sqrt{3} H_0(R,\sigma)
 \label{eq:bc3}
 \ee
-where $H_0(R,\nu)$ is given by Eq. \ref{eq:H0surf}. Discretization of Eq. \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
+where $H_0(R,\sigma)$ is given by Eq. \ref{eq:H0surf}. Discretization of Eq. \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
 leads to a set of coupled linear equations for the $A(s_j)$.
@@
 \be
-H_{\rm bc}(r,\nu) & = & \left( \frac{-1}{3k\phi} \right)
-\frac{\partial J_{\rm bc}(r,\nu)}{\partial r}
+H_{\rm bc}(r,\sigma) & = & \left( \frac{-1}{3k\phi} \right)
+\frac{\partial J_{\rm bc}(r,\sigma)}{\partial r}
 = \left( \frac{-1}{3k\phi} \right)
@@
     \caption{Boundary condition term $H_{\rm bc}$ scaled by $(a\tau_0)^{1/3}$ shown for increasing line center optical depths.
-The $H_0$ solution minus the Monte Carlo data should be close to $H_{\rm bc}$ according to Eq.
+The Monte Carlo data minus the $H_0$ solution should be close to $H_{\rm bc}$ according to Eq.
 \ref{eq:totalflux}.
@@
 
-\todo{Brief description of MC code, citing Chenliang's paper.
+%Brief description of MC code, citing Chenliang's paper.
 Discuss how MC works briefly, reference some papers, talk about problem setup specific to this work.
-Basically want to show that the MC approach in this paper is not new and doesn't need to be justified extensively.}
+Basically want to show that the MC approach in this paper is not new and doesn't need to be justified extensively.
 
-We now compare each of these solutions for surface flux with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$.
-In Fig.
-\ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ overplotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\sigma_s = \sigma_0$.
-The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
-It is evident that the divergent solution $H_{\rm d}$ fails in the line wings.
-The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum.
-This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S}.
-The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
+The Monte Carlo method is used to solve the transfer equation numerically as a point of reference for these analytic solutions.
+Photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and frequencies are logged.
+Frequency redistribution is calculated at each scattering, including the effects of recoil, to obtain the spectrum at the surface of the spherical simulation domain.
+Further details of the Monte Carlo simulation are discussed in \cite{2017ApJ...851..150H}.
 
@@
 \end{figure}
+
+We now compare each of the solutions for surface flux with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$.
+In Fig.
+\ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ overplotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\sigma_s = \sigma_0$.
+
+The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
+It is evident that the divergent solution $H_{\rm d}$ fails in the line wings.
+The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum.
+This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S}.
+The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
 

### 2021-06-23 ms.tex
Adding todo list, removing details about H_d, filling out description of tau0 scaling of Hbc

@@
 A monochromatic source of photons is assumed at the center of the sphere, and the intensity within the sphere and at the surface is found with the Eddington approximation for the angular dependence.
-The solution can be represented a sum of three terms: a simple, analytic solution of the inhomogeneous equation which diverges at the center of the sphere and at the emission frequency; a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface; and finally, a solution of the homogeneous equation which enforces the correct, zero-ingoing intensity boundary conditions at the surface.
+The solution can be represented a sum of two terms: a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface, and a solution of the homogeneous equation which enforces the correct, zero-ingoing intensity boundary conditions at the surface.
 It is the compact, analytic form as well as the piece accounting for the correct, frequency dependent boundary condition that is novel in this study.
@@
 \keywords{}
+
+\section{To Do List}
+$\square$ Change all plots to use just wing line profile, exclude Doppler core
+
+$\square$ Use larger n phot MC runs for tau=1e5
+
+$\blacksquare$ Remove details about $H_d$, change wording in abstract and derivations
+
+$\square$ Add eigenmodes plots
+
+$\square$ Add discussion of numerical solution of time-dependent equations
+
+$\square$ Add results, summary, conclusions, etc
 
@@
 
-Three solutions will be considered for this problem.
+Two solutions will be considered for this problem.
 
 \begin{enumerate}
-    \item a \textbf{divergent solution} ($\rm H_d$) due to the delta function source,
     \item a \textbf{J=0 solution} ($\rm H_0$) which includes the delta function solution at the source and satisfies $J=0$ at $r=R$,
@@
 
-\noindent The divergent solution is discussed for qualitative understanding, and the full solution is the sum of the $J=0$ solution and the bc solution.
+\noindent The full solution is the sum of the $J=0$ solution and the bc solution.
 The problem is as follows.
@@
 at $r=R$.
-First consider the divergent solution.
-In terms of the dimensionless variables $x_1 = k(x-x_{\rm s})/\Delta$, $x_2=k(y-y_{\rm s})/\Delta$, $x_3=k(z-z_{\rm s})/\Delta$ and $x_4=\sigma - \sigma_{\rm s}$, this equation can be written as a Laplacian in the 4-dimensional space as
-\be
-\nabla_4^2 J & = & - \frac{\sqrt{6} k^2 L}{4\pi \Delta^3} \delta^4(x).
-\ee
-In terms of the 4-dimensional radius $r_4 = \sqrt{ (k/\Delta)^2\left[ (x-x_{\rm s})^2 + (y-y_{\rm s})^2 + (z-z_{\rm s})^2 \right] + (\sigma - \sigma_{\rm s})^2 }$, and assuming spherical symmetry about the source point, the equation becomes
-\be
-\frac{1}{r_4^3} \frac{\partial}{\partial r_4} \left( r_4^3 \frac{\partial J}{\partial r_4} \right) & = & - \frac{\sqrt{6} k^2 L}{4\pi \Delta^3} 
-\frac{\delta(r_4)}{2\pi^2 r_4^3},
-\ee
-where the forms of the 4-dimensional Laplacian and delta function have been inserted. The ``divergent" solution due to the delta function is then
-\be
-J_{\rm d} & = & 
-\frac{(\sqrt{6}k^2L)/(16\pi^3 \Delta^3)}{ (k/\Delta)^2\left[ (x-x_{\rm s})^2 + (y-y_{\rm s})^2 + (z-z_{\rm s})^2 \right] + (\sigma - \sigma_{\rm s})^2}.
-\label{eq:Jd}
-\ee
-While this solution does not satisfy the surface boundary condition (Eq. \ref{eq:bc}), it is accurate near the delta-function source.
-This solution generalizes the particular solution for slab geometry found by \citet{1990ApJ...350..216N}.
-Henceforth we will focus on the source at the center of the sphere, although we will retain the emission frequency at $\sigma=\sigma_{\rm s}$.
-The radial flux corresponding to Eq.
-\ref{eq:Jd} is
-\be
-H_{\rm d} & = & - \frac{1}{3k\phi} \frac{\partial J_d}{\partial r}
-=  \left( \frac{1}{3k\phi} \right) 
-\left( \frac{ \sqrt{6}k^3L }{ 8\pi^3 \Delta^4} \right)
-\left( \frac{k r/\Delta}{ \left[ (kr/\Delta)^2 + (\sigma-\sigma_{\rm s})^2 \right]^2 } \right).
-\label{eq:Hd}
-\ee
-It will be shown that Eq.
-\ref{eq:Hd} is a good approximation at $r=R$ near line center.
-However Eq.
-\ref{eq:Jd} is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$.
+An analytic solution $J_d$ which is divergent at the center of the sphere and at the emission frequency may be found.
+However, it is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$.
+This solution is included in Fig.
+\ref{fig:sol_mc_residual_0} for qualitative understanding, but will not be discussed further.
 
@@
 \ref{eq:H0surf} will be shown to be a much better approximation to the solution, which is valid near the delta function at the center, and is a much better approximation at the surface.
-It will be shown that it is still only a good approximation near line center at the surface.
-It decreases exponentially rather than as a power-law in frequency, giving a much smaller flux on the line wings as compared to $H_{\rm d}$.
+It is still only a good approximation near line center at the surface.
+It decreases exponentially rather than as a power-law in frequency, giving a much smaller flux on the line wings as compared to the divergent solution.
 
@@
 In the notation of \citet{1973MNRAS.162...43H}, a separation of variables
-$J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ is attempted (his Equations 16 and 23).
+$J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ is attempted (their Equations 16 and 23).
 The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
@@
 \ee
-where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile ($\Delta \phi$ here).
+where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile ($\Delta \phi(\nu)$ here).
 The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
@@
 This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
-Despite this treatment, a calculation of the surface flux from their Eq.
+
+% Dijkstra
+%Despite this treatment, a calculation of the surface flux from their Eq.
 13 compared with the total emerging flux density at the surface of the sphere (Eq.
@@
 \ee
-Here $J_0$ and $H_0$ are the solutions of the inhomogeneous equation including the delta function source given in Equations \ref{eq:J0} and \ref{eq:H0}.
+Here, $J_0$ and $H_0$ are the solutions of the homogeneous equation, given in Equations \ref{eq:J0} and \ref{eq:H0}.
 The additional term $J_{\rm bc}$ must then be a solution of the homogeneous equation
@@
 Plugging in a frequency dependence $J \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$.
-
-% Fourier analysis stuff which we can take out
-%\ifx
 The solution can then be represented as
@@
 \ee
-where $A(s)$ is the Fourier amplitude.
-
-Plugging Eq. \ref{eq:Jbc} into Eq. \ref{eq:bc2} leads to the following equation for the Fourier amplitudes
+where $A(s)$ is the Fourier amplitude. Plugging Eq. \ref{eq:Jbc} into Eq. \ref{eq:bc2} leads to the following equation for the Fourier amplitudes,
 \be
@@
 leads to a set of coupled linear equations for the $A(s_j)$.
-We use equally-spaced points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid.
+We use equally-spaced points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid and solve the resulting matrix equation.
 The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that  the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries.
-\todo{The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries.
-(Is this still accurate?)} Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq.
+The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries.
+Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq.
 \ref{eq:Jbc}, and the flux is given by
@@
 These coefficients are used to evaluate Eq. \ref{eq:Hbc} at the surface of the sphere. Dividing this flux $H_{\rm bc}$ by the $H_0$ (Eq. \ref{eq:H0surf}) yields an overall proportionality
-\be
+\be \label{eq:hbc_scaling}
 \frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto \frac{1}{(a\tau_0)^{1/3}}.
@@
 At very large optical depths, it is expected that the corrective term will be small, but will become increasingly important in less optically thick media.
-This is shown graphically in Fig.
-\ref{fig:taubc}, where the $H_{\rm bc}$ solution has been discretized in $s$ and $\sigma$ and solved via a matrix equation.
-
-\begin{figure}
-    \centering
-    \includegraphics{taubc.pdf}
-    \caption{Boundary condition term $H_{\rm bc}$ scaled by $(a\tau_0)^{1/3}$ shown for increasing line center optical depths.
-The Monte Carlo data minus the $H_0$ solution should be close to $H_{\rm bc}$ according to Eq.
-\ref{eq:totalflux}.
-As $\tau_0$ becomes larger, the agreement between these two improves, indicating that at large optical depths the relative size of the corrective boundary condition term scales as $(a\tau_0)^{-1/3}$}.
-    \label{fig:taubc}
-\end{figure}
 
@@
     \centering
+    \includegraphics{taubc.pdf}
+    \caption{Boundary condition term $H_{\rm bc}$ scaled by $(a\tau_0)^{1/3}$ shown for increasing line center optical depths.
+The Monte Carlo data minus the $H_0$ solution should be close to $H_{\rm bc}$ according to Eq.
+\ref{eq:totalflux}.
+As $\tau_0$ becomes larger, the agreement between these two improves, indicating that at large optical depths the relative size of the corrective boundary condition term scales as $(a\tau_0)^{-1/3}$}.
+    \label{fig:taubc}
+\end{figure}
+
+The relative size of the boundary term $H_{\rm bc}$ with optical depth is shown graphically in Fig.
+\ref{fig:taubc}, where $H_{\rm bc}$ is shown for several optical depths along with Monte Carlo data.
+Since the Monte Carlo simulation represents the true solution, it can be compared directly against $H_{\rm bc}$ by subtracting off the homogeneous piece of the solution ($H_{\rm bc} = H - H_0$).
+From Eq.
+\ref{eq:hbc_scaling}, the size of the frequency-dependent boundary condition correction should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
+This factor has been scaled out of the figure such that solutions for different optical depths should show close agreement on the figure if the relation holds.
+Indeed, agreement between $H_{\rm bc}$ and the Monte Carl points improves as the optical depth becomes larger.
+At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely.
+The effects of core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift outward in frequency from the line core around $\tau_0 = 10^5$.
+Thus, the $(a\tau)^{1/3}$ scaling holds only for larger optical depths where scattering in the core can be ignored.
+
+\begin{figure}
+    \centering
     \includegraphics{final_residual.pdf}
@@
 \ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ overplotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\sigma_s = \sigma_0$.
-
 The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.

### 2021-06-24 ms.tex
changes from yesterday

@@
 
-\shorttitle{Lyman $\alpha$}
+\shorttitle{Resonant Scattering of \lya}
 \shortauthors{McClellan et al.}
@@
 \section{To Do List}
-$\square$ Change all plots to use just wing line profile, exclude Doppler core
+$\blacksquare$ Change all plots to use just wing line profile, exclude Doppler core
 
-$\square$ Use larger n phot MC runs for tau=1e5
+$\blacksquare$ Use larger n phot MC runs for tau=1e5
 

### 2021-06-24 ms.tex
Adding paragraph discussing x_s plot

@@
 The Monte Carlo method is used to solve the transfer equation numerically as a point of reference for these analytic solutions.
-Photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and frequencies are logged.
+For each simulation, a total of $2^20 \approx 10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and frequencies are logged.
+A constant temperature of $T=10000\ \rm K$ is set for the gas.
 Frequency redistribution is calculated at each scattering, including the effects of recoil, to obtain the spectrum at the surface of the spherical simulation domain.
@@
 \ref{eq:hbc_scaling}, the size of the frequency-dependent boundary condition correction should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-This factor has been scaled out of the figure such that solutions for different optical depths should show close agreement on the figure if the relation holds.
+This factor has been scaled out of the figure such that solutions for different optical depths should show close agreement if the relation holds.
 Indeed, agreement between $H_{\rm bc}$ and the Monte Carl points improves as the optical depth becomes larger.
@@
 
-We now compare each of the solutions for surface flux with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$.
+We now compare each of the solutions for surface flux with Monte Carlo simulations.
 In Fig.
-\ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ overplotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\sigma_s = \sigma_0$.
+\ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ over-plotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
 The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
@@
 The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
+Note that as in Fig.
+\ref{fig:taubc} the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term.
 
@@
 \end{figure}
+
+Since the solutions have been generalized to allow for a monochromatic source of photons at a frequency $\sigma_s$ away from line center, their agreement with Monte Carlo as a function of source frequency can also be characterized.
+Photons initialized closer to the line wing may travel larger mean free paths as the opacity is sensitively dependent on the line profile.
+The larger spatial diffusion contributes to greater escape probability, biasing the frequency distribution of escaping photons.
+In the limit that $|\rm x_s|$ becomes large, the distribution becomes a delta function in frequency as all photons escape the gas without scattering.
+Fig.
+\ref{fig:sol_mc_xinit} shows calculations performed for three initial photon frequencies $\rm x_s = 0.0, 6.0$, and $12.0$ for a line center optical depth of $\tau_0=10^7$.
+The bias in frequency distribution is slight for $\rm x_s = 6.0$ where the line profile is still relatively large, but the increase in spatial diffusion is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core.
+On this point, we note that the discrepancy between the Monte Carlo data and $H_0$ (effectively the scale of the corrective $H_{\rm bc}$ term) becomes larger as $\rm x_s$ increases.
+Thus, for sufficiently large optical depths and emission away from line center, the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows.
+%Note: should we characterize this scaling quantitatively?
 

### 2021-06-29 ms.tex
Adding tau scaling relations and location of peak derivation. Beginning to add doppler core extent derivation

@@
 The additional term $J_{\rm bc}$ must then be a solution of the homogeneous equation
-\be
+\be \label{eq:diffeq}
 \frac{\partial^2J}{\partial r^2} + \frac{2}{r} \frac{\partial J}{\partial r}
@@
 
-To examine the relative size of this corrective term as compared to $H_0$, we consider the case where the optical depth is large and thus the mean intensity will be considerably larger than the surface flux.
+\subsection{Scaling with Line Center Optical Depth}
+To examine the relative size of the corrective term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the optical depth is large and thus the mean intensity will be considerably larger than the surface flux.
 Starting from Eq.
@@
 With the line center optical depth defined as
-\be
+\be \label{eq:tau0}
 \tau_0 = \frac{kR}{\sqrt{\pi}\Delta}
@@
 \be
-A(\bar s) &=& \frac{\sqrt{2}}{32\pi}\frac{L}{kR^3}\int_{-\infty}^\infty d\bar\sigma \tau_0 e^{-i\bar s \bar\sigma} \left(\frac{27\pi}{2a}\right)^{1/3}\tau_0^{2/3}|\bar\sigma^{2/3}|\frac{1}{1+\cosh \left[\sqrt{\pi}|\bar\sigma - \bar\sigma_i|\right]}\\
-&=& \frac{\sqrt{2}}{32\pi}\left(\frac{27\pi}{2}\right)^{1/3}\frac{L}{kR^3}\frac{\tau_0^{5/3}}{a^{1/3}}\int_{-\infty}^\infty d\bar\sigma e^{-i\bar s \bar\sigma} |\bar\sigma^{2/3}|\frac{1}{1+\cosh \left[\sqrt{\pi}|\bar\sigma - \bar\sigma_i|\right]}
+A(\bar s) = \frac{\sqrt{2}}{32\pi}\left(\frac{27\pi}{2}\right)^{1/3}\frac{L}{kR^3}\frac{\tau_0^{5/3}}{a^{1/3}}\int_{-\infty}^\infty d\bar\sigma e^{-i\bar s \bar\sigma} |\bar\sigma^{2/3}|\frac{1}{1+\cosh \left[\sqrt{\pi}|\bar\sigma - \bar\sigma_i|\right]}.
 \ee
-These coefficients are used to evaluate Eq. \ref{eq:Hbc} at the surface of the sphere. Dividing this flux $H_{\rm bc}$ by the $H_0$ (Eq. \ref{eq:H0surf}) yields an overall proportionality
+These coefficients are used to evaluate Eq. \ref{eq:Hbc} at the surface of the sphere. Dividing $H_{\rm bc}$ by $H_0$ (Eq. \ref{eq:H0surf}) yields an overall proportionality
 \be \label{eq:hbc_scaling}
@@
 At very large optical depths, it is expected that the corrective term will be small, but will become increasingly important in less optically thick media.
+
+By replacing the differential operators in Eq.
+\ref{eq:rt_no_destr} with characteristic scales $R$ and $\sigma_0$ and equating the terms on the left-hand side of this equation, a dimensionless scaling relation between frequency and space emerges.
+\be
+\frac{J}{R^2} &=& \left(\frac{k}{\Delta}\right)^2 \frac{J}{\sigma_0^2}
+\ee
+Now, using Eq. \ref{eq:tau0} and the approximation $\sigma(x)=x^3\sqrt{2\pi/27}/a$ introduced in \cite{1973MNRAS.162...43H} for large $x$, we have
+\be
+\frac{\sqrt{2\pi/27}}{a}x_0^3 = \frac{kR}{\Delta} = \sqrt{\pi} \tau_0.
+\ee
+Simplifying, we obtain the proportionality
+\be
+x_0 &\propto& \left(a\tau_0\right)^{1/3}.
+\ee
+This predicts that the characteristic photon frequency in Doppler widths should scale as the cube root of the Voigt parameter $a$ multiplied by the line center optical depth $\tau_0$, indicating the location of the spectral peaks on either side of line center --- the locations where the photons most readily escape.
+Since our derivations were performed assuming a Lorentzian line profile (see Appendix \ref{app:rteqn_derivation}), our solutions are technically only valid far out into the line wing, where the Doppler component of the line profile is small.
+Since our choice of the damping parameter $a$ is constant, the solutions of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large optical depths.
+The boundary of the Doppler core is approximately where the Gaussian and Lorentzian pieces are equal:
+\be
+\frac{e^{-x^2}}{\sqrt{\pi}} = \frac{a}{\pi x^2}
+\ee
 
@@
 The Monte Carlo method is used to solve the transfer equation numerically as a point of reference for these analytic solutions.
-For each simulation, a total of $2^20 \approx 10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and frequencies are logged.
+For each simulation, a total of $2^{20} \approx 10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and frequencies are logged.
 A constant temperature of $T=10000\ \rm K$ is set for the gas.
@@
 This factor has been scaled out of the figure such that solutions for different optical depths should show close agreement if the relation holds.
-Indeed, agreement between $H_{\rm bc}$ and the Monte Carl points improves as the optical depth becomes larger.
+Indeed, agreement between $H_{\rm bc}$ and the Monte Carlo points improves as the optical depth becomes larger.
 At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely.
@@
 \end{figure}
+
+The line center optical depth dictates the position of the peak of
 
@@
 \label{subsec:time_dependent:results}
-
-\end{frame}
 

### 2021-06-29 ms.tex
Finishing Doppler core / line wing numerical estimation with location of peak of spectrum (a \tau_0)^{1/3}

@@
 Simplifying, we obtain the proportionality
-\be
+\be \label{eq:tau_peak_scaling}
 x_0 &\propto& \left(a\tau_0\right)^{1/3}.
@@
 \ee
-
+For \lya and a hydrogen gas of temperature $T=10^4$ K, the damping parameter $a = \Gamma / (4\pi\Delta)$ is equal to $4.72\times 10^{-4}$ in CGS units.
+The Doppler core is then significant over the range $-4.6 < x < 4.6$.
+Comparing with the locations of the spectral peaks at various optical depths using Eq.
+\ref{eq:tau_peak_scaling}, we find that $x_0=$3.6, 7.8, 16.8 for $\tau_0=10^5, 10^6,$ and $10^7$, respectively.
+Therefore, solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower line center optical depths where the peak of the spectrum lies near the core and improve for larger optical depths where the spectral peak is well outside of the line core.
 \subsection{Comparison to Monte Carlo}

### 2021-06-29 ms.tex
starting to work on time dependent stuff

@@
 Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons.
+Photon destruction will not be considered, so $p$ is set to 0.
 
@@
 A better approximation to the true solution has been derived by \citet{2006ApJ...649...14D}, who generalized the closed-form solution in slab geometry found in \citet{1990ApJ...350..216N}.
-They found a closed-form solution which satisfies a $J=0$ boundary condition at $r=R$.
+They found a solution which satisfies a $J=0$ boundary condition at $r=R$.
 We generalize their solution to allow emission at frequency $\nu_{\rm s}$ away from line center.
@@
 
+\ifx
 \begin{figure}
@@
 \end{figure}
-
-The relative size of the boundary term $H_{\rm bc}$ with optical depth is shown graphically in Fig.
-\ref{fig:taubc}, where $H_{\rm bc}$ is shown for several optical depths along with Monte Carlo data.
-Since the Monte Carlo simulation represents the true solution, it can be compared directly against $H_{\rm bc}$ by subtracting off the homogeneous piece of the solution ($H_{\rm bc} = H - H_0$).
-From Eq.
-\ref{eq:hbc_scaling}, the size of the frequency-dependent boundary condition correction should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-This factor has been scaled out of the figure such that solutions for different optical depths should show close agreement if the relation holds.
-Indeed, agreement between $H_{\rm bc}$ and the Monte Carlo points improves as the optical depth becomes larger.
-At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely.
-The effects of core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift outward in frequency from the line core around $\tau_0 = 10^5$.
-Thus, the $(a\tau)^{1/3}$ scaling holds only for larger optical depths where scattering in the core can be ignored.
+\fi
 
@@
 The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
-Note that as in Fig.
-\ref{fig:taubc} the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term.
+Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.
 
@@
     \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
-Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency.
-TODO: Remove blue line.
-We really don't care about the divergent solution anymore.}
+Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency.}
     \label{fig:sol_mc_xinit}
@@
 \ref{fig:sol_mc_xinit} shows calculations performed for three initial photon frequencies $\rm x_s = 0.0, 6.0$, and $12.0$ for a line center optical depth of $\tau_0=10^7$.
-The bias in frequency distribution is slight for $\rm x_s = 6.0$ where the line profile is still relatively large, but the increase in spatial diffusion is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core.
+The bias in frequency distribution is slight for $\rm x_s = 6.0$ where the line profile is still relatively large and emitted photons remain trapped in the core, but the increase in spatial diffusion is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core.
 On this point, we note that the discrepancy between the Monte Carlo data and $H_0$ (effectively the scale of the corrective $H_{\rm bc}$ term) becomes larger as $\rm x_s$ increases.
@@
 
-The line center optical depth dictates the position of the peak of
+Additionally, the size of the frequency-dependent boundary condition correction is dependent on the line center optical depth, which also dictates the x-position of the peak of spectrum according to Eq.
+\ref{eq:tau_peak_scaling}.
+One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis of Fig.
+\ref{fig:sol_mc_tau} such that the peaks of the distributions are vertically aligned.
+This scaling has also been applied to the y-axis to preserve normalization of the escape probability.
+From Eq.
+\ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
+Indeed, agreement between $H_{0 + \rm bc}$ and the Monte Carlo points in Fig.
+\ref{fig:sol_mc_tau} improves as the optical depth becomes larger.
+At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely.
+The effects of core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift substantially outward in frequency from the line core for $\tau_0 = 10^5$.
+
+\subsection{Summary}
+
+The solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere originally derived by \cite{2006ApJ...649...14D} has been generalized to allow a monochromatic source of photons with frequencies away from line center.
+However, this solution satisfies $J=0$ at the surface of the sphere, which is clearly unphysical as there could be no spectrum.
+A correction which allows the proper boundary condition $J=\sqrt{3}H$ to be satisfied comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$, which are solved using a continuous Fourier expansion in frequency.
+Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
+In practice, the continuous expansions are discretized and the Fourier coefficients solved for via a matrix equation.
+The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$ where $a$ is the damping parameter and $\tau_0$ is the line-center optical depth.
+Thus, for very large optical depths, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower optical depths.
+Additionally, since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
+Since the peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$, calculations performed at lower optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core.
+By comparison with Monte Carlo simulations, it is seen that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency is altered, provided a sufficiently large optical depth.
 
@@
 
-\subsection{Background}
+The diffusion equation for photons escaping a uniform sphere of gas is a function of time, which was ignored in the steady-state calculations in Section \ref{sec:steadystate}.
+To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a fluid that is dynamic on timescales shorter than the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to an impulse is found.
+For simplicity a $J=0$ boundary condition will be used, which is expected to be a decent approximation for $\tau_0 \gg 1$.
+
+\subsection{Derivation of the time-dependent solution}
 \label{subsec:time_dependent:background}
-
-In order to understand the wait time distribution, the time-dependent response to an impulse is found.
-For simplicity a $J=0$ boundary condition will be used.
-This is expected to be a good approximation for $\tau_0 \gg 1$.
-
-\subsection{Equations}
-\label{subsec:time_dependent:equations}
 
@@
 \ee
-
 We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$.
@@
 The expansion for $J(r, \sigma, t)$ is
-
 \be
@@
 \ee
-
 with
-
 \be
@@
 \ee
-
 Plugging this in to Eq. \ref{eq:diffusion_eqn} and evaluating the integral, we obtain
-
 \be \label{eq:diffusion_plugged_in}
@@
 \ee
-
-%% FOURIER STUFF
-\ifx
-The coefficient of $\partial J/\partial t$ has explicit dependence on $\sigma$.
-Separation of variables may be achieved in Eq.
-\ref{eq:diffusion_eqn} by assuming an expansion in terms of spherical Bessel functions in $r$ and a Fourier expansion in time to find the form
-\be
-J(r,\sigma,t) & = & \sum_{n=1}^\infty \int_{-\infty}^\infty \frac{d\omega}{2\pi} J(n,\sigma,\omega) j_0(\kappa_n r) e^{-i \omega t},
-\ee
-where $\kappa_n = n\pi/R$ enforces the $J(R,\sigma,t)=0$ boundary condition and the spherical Bessel function is $j_0(x)=\sin(x)/x$.
-For the solution to be real requires that $J(n,\sigma,-\omega) = J^*(n,\sigma,\omega)$.
-The equation for $J(n,\sigma,\omega)$ becomes
-\be
-\frac{\partial^2 J}{\partial \sigma^2} & = & \left( \frac{\Delta \kappa_n}{k} \right)^2 J
-- 3i\omega \frac{\Delta^2 \phi}{ck} J
-- \sqrt{ \frac{3}{32} } \frac{E}{kR^3} n^2 \delta(\sigma - \sigma_s).
-\label{eq:response}
-\ee
-The $\delta(\sigma - \sigma_s)$ enforces a discontinuity
-\be
-\frac{\partial J(n,\sigma_s^{(+)},\omega)}{\partial \sigma} - \frac{\partial J(n,\sigma_s^{(-)},\omega)}{\partial \sigma} & = & 
-- \sqrt{ \frac{3}{32} } \frac{E}{kR^3} n^2
-\label{eq:discontinuity}
-\ee
-and the boundary conditions are $J(n,\pm \infty,\omega)=0$. Since $\phi \propto \sigma^{-2/3}$, the solution at large $\sigma$ is 
-\be
-J(n,\sigma,\omega) & \propto & e^{-\kappa_n \Delta |\sigma| /k}
-= e^{-\sqrt{\pi} n |\sigma | / \tau_0}.
-\label{eq:finite_bc}
-\ee
-\fi
-
-%%% TODO: NOTES
-% Can't solve this exactly, need a numerical scheme to solve.
-Now going to turn to solving this equation (without subsec).
-We start with a treatment of the boundary conditions.
-Continuity in J at the source, the discontinuity needs to be (Eq.
-24)
-
-% Solving the sigma dependence
-% Solving the time dependence
-% Solving the frequency dependence
-
-% Get different pieces of the solution and build it up.
-
-% Make sure that all variables that are introduced in the text are defined beforehand. Especially those that are defined only in the appendix.
-
+This cannot be solved analytically, so we turn now to a semi-analytic scheme to solve this equation for $J$.
+We start with a treatment of the boundary conditions, after which we solve spatial dependence $n$, photon frequency dependence $\sigma$, and imaginary frequency dependence $\omega$ separately.
 At $\sigma=\sigma_s$ continuity must be enforced in $J$
-
 \be \label{eq:matching_condition_1}
@@
 \ee
-
 and the discontinuity in $dJ/d\sigma$  must be
-
 \be \label{matching_condition_2}
@@
 \ee
-
 according to the differential equation. At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes
-
 \be \label{eq:diffusion_at_large_sigma}
-\frac{\partial^2J(n, \sigma, \omega)}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J.
+\frac{\partial^2J}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J.
 \ee
-
 which has solutions 
-
 \be
@@
 \ee
-
 and thus
-
 \be \label{eq:single_j_derivative}
@@
 \ee
-
 where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$.
@@
 By enforcing the matching conditions Eqs.
-\ref{eq:matching_condition_1} and \ref{matching_condition_2}, the solution for $J(n, \sigma, \omega)$ is obtained everywhere in the range of photon frequencies.
+\ref{eq:matching_condition_1} and \ref{matching_condition_2}, the solution for $J(n, \sigma, \omega)$ is obtained for all photon frequencies $\sigma$.
 Since the solution is linear in the starting conditions, only two integrations with different starting values are necessary.
@@
 There are certain values of $\gamma$ for which a resonant response is produced which we will call $\gamma_{nm}$.
-Here, $m$ is an index that represents individual temporal eigenmodes, as opposed to $n$ which represents the spatial mode number.
+Here, $m$ is an index that represents individual frequency eigenmodes, as opposed to $n$ which represents the spatial mode number.
 Near these frequencies, the solution will have the form
-
 \be
@@
 \ee
-
 Obtaining the values of these eigenfrequencies and their corresponding eigenfunctions $J_{nm}(\sigma)$ allows us to obtain the contribution of this mode to the total solution via contour integration. 
-
 \be
@@
 \ee
-
-\todo{(TODO: Rewrite) Here we have closed the integral along the $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
+Here we have closed the integral along the $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
 The contribution from the semi-circle at infinity is zero.
-Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result}
+Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result
 \be
@@
 These coefficients can have either sign depending on the value of $n$.
-
 Integrating $dE/dt d\nu$ over all times should give a distribution for the emitted frequencies.
 It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the steady-state spectrum (Eq.
-\ref{eq:spectrum}).
+\ref{eq:H0surf}).
 Dividing by the energy $E$, we find the probability distribution
@@
 \ee
-Integrating over $\nu$ gives unity if the sum rule in Eq. \ref{eq:sumrule} is true.
+Integrating over $\nu$ gives unity if the sum rule in Eq.
+\ref{eq:sumrule} is true.
+The distribution of the times it takes each photon to escape the sphere (hereafter called the ``wait time distribution'') is calculated from Eq.
+\ref{eq:dEdtdnu} by integrating over all frequencies.
+We obtain
+\be
+P(t)  & = & - \sqrt{\frac{3}{2}} \frac{16\pi^2 R \Delta^2 }{3kE}     \sum_{nm} (-1)^n  e^{s_{nm}t} \int d\sigma J_{nm}(\sigma) 
+\nonumber \\ & = &  - \sum_{nm} P_{nm} s_{nm} e^{s_{nm}t},
+\label{eq:waittime}
+\ee
+which is also normalized to unity.
 
 \subsection{Results}
-\label{subsec:time_dependent:results}
 

### 2021-06-30 ms.tex
Adding numerical calculation subsection

@@
 This cannot be solved analytically, so we turn now to a semi-analytic scheme to solve this equation for $J$.
-We start with a treatment of the boundary conditions, after which we solve spatial dependence $n$, photon frequency dependence $\sigma$, and imaginary frequency dependence $\omega$ separately.
+We start with a treatment of the boundary conditions.
 At $\sigma=\sigma_s$ continuity must be enforced in $J$
@@
 Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result
-\be
+\be \label{eq:Jrsigmat}
 J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_m J_{nm}(\sigma) e^{-\gamma_{nm}t}.
 \ee
-Using the derivative
+Beginning with Eq. \ref{eq:Jrsigmat}, we use the derivative
 \be
@@
 \ee
-the flux at the surface is
+to obtain the flux at the surface, which is
 \be
@@
 These coefficients can have either sign depending on the value of $n$.
-Integrating $dE/dt d\nu$ over all times should give a distribution for the emitted frequencies.
+
+\subsection{Numerical calculation}
+
+We seek now to tabulate all eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\omega_{nm}$ for all spatial $n$ and for all eigenmodes $m$ at that given $n$.
+To do this, we generalize the equations for eigenfunctions $J(n,\sigma,\omega)$ to allow $\omega = \omega_r + i \omega_i$, where previously we were using the real frequency $\omega_r$ and now we use the imaginary part $\omega_i$ (hereafter referred to as simply $\chi$).
+A resonant response in $J(n,\sigma,\omega)$ is produced for $\omega_r=0$ and special values of $\chi<0$.
+
+To measure the size of the response to detect where resonances occur, we sum the absolute value of $J(n,\sigma,\omega)$ over $\sigma$ in array form.
+Call this response $f$, and use the index $j$ to represent the value of the response at discrete points over a range of $\chi$.
+In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bounded a resonance that occurs in the interval $(\chi_{j-1},\chi_{j+1})$.
+We then call the ``solve'' step to hone in on the eigenvalue before continuing the sweep in imaginary frequency $\omega_i$.
+
+In the solve step, we evaluate the eigenfunctions at the points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ to obtain the responses $f_{j-1}$, $f_j$, and $f_{j+1}$.
+A ``guess'' at the correct eigenvalue $\chi_{nm}$ can be calculated from
+\be
+\chi_{\rm guess} &=& \frac{a\chi_{j-1} - \chi_{j+1}}{a - 1}
+\ee
+where
+\be
+a &=& \left(\frac{f_{j} - f_{j-1}}{f_{j} - f_{j+1}}\right)\left(\frac{\chi_{j+1}-\chi_{j}}{\chi_{j-1}-\chi_{j}}\right).
+\ee
+This is repeated, replacing former points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ with closer estimates while the size of the response grows as we approach the resonance.
+Given a sufficiently accurate eigenvalue $\chi_{nm}$, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
+We can write down an approximate expression for the response near the resonances as
+\be
+J(n,\sigma,\chi) & \simeq & \frac{J_{nm}(\sigma)}{\chi-\chi_{nm}} + C(\sigma),
+\ee
+where $C(\sigma)$ is weakly dependent on $\chi$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance:
+\be
+J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2)& = &  \frac{J_{nm}(\sigma)}{\chi_1-\chi_{nm}} -  \frac{J_{nm}(\sigma)}{\chi_2-\chi_{nm}}
+\ee
+where $C(\sigma)$ has cancelled out in the difference. We can immediately solve as
+\be
+J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2) }{ 1/(\chi_1-\chi_{nm}) - 1/(\chi_2-\chi_{nm})}.
+\ee
+A set of eigenfunctions $J_{nm}(\sigma)$ are plotted in Fig.
+\ref{fig:jsoln} to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$.
+Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
+\begin{figure}
+    \centering
+    \includegraphics{Jsoln_n1_m100.pdf}
+    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and a range of frequency eigenmodes up to $m=100$.
+Their oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity.
+The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.}
+    \label{fig:jsoln}
+\end{figure}
+
+\subsection{Frequency dependence}
+
+Integrating $dE/dt d\nu$ from Eq.
+\ref{eq:dEdtdnu} over all times should give a distribution for the emitted frequencies.
 It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the steady-state spectrum (Eq.
@@
 \ee
-Integrating over $\nu$ gives unity if the sum rule in Eq.
-\ref{eq:sumrule} is true.
+Integrating over $\nu$ gives unity if the sum rule in Eq. \ref{eq:sumrule} is true.
+
+\subsection{Wait time distribution}
+
 The distribution of the times it takes each photon to escape the sphere (hereafter called the ``wait time distribution'') is calculated from Eq.

### 2021-06-30 ms.tex
proofread

@@
 
-$\square$ Add eigenmodes plots
+$\blacksquare$ Add eigenmodes plots
 
-$\square$ Add discussion of numerical solution of time-dependent equations
+$\blacksquare$ Add discussion of numerical solution of time-dependent equations
 
-$\square$ Add results, summary, conclusions, etc
+$\square$ Add discussion of frequency dependence in time dependent section (spectrum plots?)
+
+$\square$ Add discussion of wait times in time dependent section --- escape time plots, fitting function, etc
+
+$\square$ Add summary to time dependent section
+
+$\square$ Conclusions
 
@@
 \ee
-A set of eigenfunctions $J_{nm}(\sigma)$ are plotted in Fig.
-\ref{fig:jsoln} to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$.
-Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
 \begin{figure}
@@
 \end{figure}
+A set of eigenfunctions $J_{nm}(\sigma)$ are plotted in Fig.
+\ref{fig:jsoln} to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$.
+Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
 

### 2021-07-02 ms.tex
changing some omega to -i\gamma --- need to go through and make sure variables are consistent
Units for Eq. 30, discussion of oscillations in Jsoln plot, and derivation of sigma_tp

@@
 
-\subsection{Summary}
-
-The solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere originally derived by \cite{2006ApJ...649...14D} has been generalized to allow a monochromatic source of photons with frequencies away from line center.
-However, this solution satisfies $J=0$ at the surface of the sphere, which is clearly unphysical as there could be no spectrum.
-A correction which allows the proper boundary condition $J=\sqrt{3}H$ to be satisfied comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$, which are solved using a continuous Fourier expansion in frequency.
-Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
-In practice, the continuous expansions are discretized and the Fourier coefficients solved for via a matrix equation.
-The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$ where $a$ is the damping parameter and $\tau_0$ is the line-center optical depth.
-Thus, for very large optical depths, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower optical depths.
-Additionally, since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
-Since the peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$, calculations performed at lower optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core.
-By comparison with Monte Carlo simulations, it is seen that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency is altered, provided a sufficiently large optical depth.
-
 \section{Time-Dependent Diffusion}
@@
 To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a fluid that is dynamic on timescales shorter than the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to an impulse is found.
-For simplicity a $J=0$ boundary condition will be used, which is expected to be a decent approximation for $\tau_0 \gg 1$.
+This allows the distribution of photon escape times (the ``wait time distribution'') to be characterized and fit for efficient sampling.
+For simplicity a $J=0$ boundary condition will be used in the following derivations, which is expected to be a decent approximation for $\tau_0 \gg 1$.
 
@@
 \be
-j_{\rm em} & = & \frac{E}{4\pi} \delta^3(\vec{x} - \vec{x}_s) \delta(\nu-\nu_{\rm s})\delta (t) .
+j_{\rm em} & = & \frac{E}{4\pi} \delta^3(\vec{x} - \vec{x}_s) \delta(\nu-\nu_{\rm s})\delta (t) ,
 \label{eq:jem2}
 \ee
-where $E$ is the energy emitted in the impulse at time $t=0$. 
+which is a standard expression for emissivity in CGS units where $E$ is the energy emitted in the impulse at time $t=0$. 
 The resulting equation for $J(r,\sigma,t)$ is
@@
 -3 \frac{k\phi}{c} \frac{\partial J}{\partial t} + \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2}
-& = & - \frac{\sqrt{6} kE}{4\pi \Delta^2} \delta(\vec{x}) \delta (\sigma - \sigma_s ) \delta (t).
+& = & - \frac{\sqrt{6} kE}{4\pi \Delta^2} \delta^3(\vec{x}) \delta (\sigma - \sigma_s ) \delta (t).
 \label{eq:diffusion_eqn}
@@
 with
-\be
+\be \label{eq:jnsigmaomega}
 J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{i\omega t} J(r, \sigma, t).
 \ee
-Plugging this in to Eq. \ref{eq:diffusion_eqn} and evaluating the integral, we obtain
+Eq.
+\ref{eq:jrsigmat_expansion} is the standard specific mean intensity in units of energy per unit area per unit time per Hertz, expressed here in CGS units.
+Though the frequency variable used here is $\sigma$, the specific mean intensity is to be integrated with respect to $\nu$.
+Eq.
+\ref{eq:jnsigmaomega} is in the same units, but with an additional unit of time in the numerator as a result of the expansion.
+Plugging the expression for the eigenfunctions $J(n, \sigma, \omega)$ into the differential equation Eq.
+\ref{eq:diffusion_eqn} and evaluating the integrals, we obtain
 \be \label{eq:diffusion_plugged_in}
@@
 \be
-J(n,\sigma,\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} + {\rm terms\ which\ vary\ slowly\ in\ \gamma}.
+J(n,\sigma,-i\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma_{nm} - \gamma} + {\rm terms\ which\ vary\ slowly\ in\ \gamma}.
 \ee
@@
 \be
-J(r,\sigma,t) & = &  j_0(\kappa_n r)  \int \frac{d\omega}{2\pi} e^{-\gamma t}J(n,\sigma,\gamma)
-\nonumber \\ & \simeq & j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} 
+J(r,\sigma,t) & = &  -j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t}J(n,\sigma,-i\gamma)
+\nonumber \\ & \simeq & j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} 
 \nonumber \\ & \simeq & j_0(\kappa_n r)  J_{nm}(\sigma) e^{-\gamma_{nm}t}.
 \ee
-Here we have closed the integral along the $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
+Here we have closed the integral along the imaginary $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
 The contribution from the semi-circle at infinity is zero.
@@
 
-We seek now to tabulate all eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\omega_{nm}$ for all spatial $n$ and for all eigenmodes $m$ at that given $n$.
-To do this, we generalize the equations for eigenfunctions $J(n,\sigma,\omega)$ to allow $\omega = \omega_r + i \omega_i$, where previously we were using the real frequency $\omega_r$ and now we use the imaginary part $\omega_i$ (hereafter referred to as simply $\chi$).
-A resonant response in $J(n,\sigma,\omega)$ is produced for $\omega_r=0$ and special values of $\chi<0$.
-
-To measure the size of the response to detect where resonances occur, we sum the absolute value of $J(n,\sigma,\omega)$ over $\sigma$ in array form.
-Call this response $f$, and use the index $j$ to represent the value of the response at discrete points over a range of $\chi$.
-In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bounded a resonance that occurs in the interval $(\chi_{j-1},\chi_{j+1})$.
-We then call the ``solve'' step to hone in on the eigenvalue before continuing the sweep in imaginary frequency $\omega_i$.
-
-In the solve step, we evaluate the eigenfunctions at the points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ to obtain the responses $f_{j-1}$, $f_j$, and $f_{j+1}$.
-A ``guess'' at the correct eigenvalue $\chi_{nm}$ can be calculated from
+We seek now to tabulate all eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\gamma_{nm}$ for all spatial $n$ and for all eigenmodes $m$ at that given $n$.
+A resonant response in $J(n,\sigma,-i\gamma)$ is produced when the imaginary frequency is negative and has no real component.
+To measure the size of the response to detect where resonances occur, we sum the absolute value of $J(n,\sigma,-i\gamma)$ over $\sigma$ in array form.
+Call this response $f$, and use the index $j$ to represent the value of the response at discrete points over a range of $\gamma$.
+In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bounded a resonance that occurs in the interval $(\gamma_{j-1},\gamma_{j+1})$.
+We then call the ``solve'' step to hone in on the eigenvalue before continuing the sweep in $\gamma$.
+In the solve step, we evaluate the eigenfunctions at the points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ to obtain the responses $f_{j-1}$, $f_j$, and $f_{j+1}$.
+A ``guess'' at the correct eigenvalue $\gamma_{nm}$ can be calculated from
 \be
-\chi_{\rm guess} &=& \frac{a\chi_{j-1} - \chi_{j+1}}{a - 1}
+\gamma_{\rm guess} &=& \frac{a\gamma_{j-1} - \gamma_{j+1}}{a - 1}
 \ee
@@
 \be
-a &=& \left(\frac{f_{j} - f_{j-1}}{f_{j} - f_{j+1}}\right)\left(\frac{\chi_{j+1}-\chi_{j}}{\chi_{j-1}-\chi_{j}}\right).
+a &=& \left(\frac{f_{j} - f_{j-1}}{f_{j} - f_{j+1}}\right)\left(\frac{\gamma_{j+1}-\gamma_{j}}{\gamma_{j-1}-\gamma_{j}}\right).
 \ee
-This is repeated, replacing former points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ with closer estimates while the size of the response grows as we approach the resonance.
-Given a sufficiently accurate eigenvalue $\chi_{nm}$, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
+This is repeated by replacing former points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ with closer estimates while the size of the response grows as the resonance is approached.
+Given a sufficiently accurate eigenvalue $\gamma_{nm}$, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
 We can write down an approximate expression for the response near the resonances as
 \be
-J(n,\sigma,\chi) & \simeq & \frac{J_{nm}(\sigma)}{\chi-\chi_{nm}} + C(\sigma),
+J(n,\sigma,-i\gamma) & \simeq & \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma} + C(\sigma),
 \ee
-where $C(\sigma)$ is weakly dependent on $\chi$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance:
+where $C(\sigma)$ is weakly dependent on $\gamma$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance:
 \be
-J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2)& = &  \frac{J_{nm}(\sigma)}{\chi_1-\chi_{nm}} -  \frac{J_{nm}(\sigma)}{\chi_2-\chi_{nm}}
+J(n,\sigma,-i\gamma_1)  - J(n,\sigma,-i\gamma_2)& = &  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_1} -  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_2}
 \ee
@@
 \be
-J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2) }{ 1/(\chi_1-\chi_{nm}) - 1/(\chi_2-\chi_{nm})}.
+J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,\gamma_1)  - J(n,\sigma,\gamma_2) }{ 1/(\gamma_{nm}-\gamma_1) - 1/(\gamma_{nm}-\gamma_2)}.
 \ee
@@
 Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
+The oscillations of various modes must cancel perfectly to recreate the form of the solution in Eq.
+\ref{eq:Jrsigmat}, so many modes $m$ and $n$ are required for sufficient numerical precision in the final result.
+Too few (or imprecisely-calculated) modes creates ``ringing'' in the function that indicates the presence of imperfect cancellations in the positive and negative contributions of individual poles.
+
+A single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{tp}$, at which point the function becomes evanescent.
+The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Eq.
+\ref{eq:diffusion_plugged_in} and re-examining the resulting homogeneous differential equation.
+We obtain
+\be
+\frac{d^2J}{d\sigma^2} & = & \left[ \left( \frac{\kappa_n \Delta }{k} \right)^2 - \frac{3\phi \gamma\Delta^2}{ck}\right] J
+\ee
+where the line profile can be written approximately as $\phi = (2a/\pi)^{1/3}/(3 \Delta |\sigma|^{2/3})$.
+When the coefficient on the right hand side is positive, exponential growth or decay solutions are found (evanescence).
+This occurs on the line wings.
+When the coefficient on the right hand side is negative, oscillatory solutions are found (propagation), which occurs in the line core.
+The boundary between propagation and evanescence occurs at the turning point, given by
+\be
+\sigma_{tp} & = & \sqrt{\frac{2a}{\pi}}\left( \frac{k \gamma}{ \kappa_n^2 c \Delta} \right)^{3/2}
+\ee
+Thus, to ensure accuracy in the final sum of Eq.
+\ref{eq:Jrsigmat}, the bounds of $\sigma$ must be set sufficiently far outside of $\sigma_{tp}$ such that the function is small at the edges.
+The scale of an $e$-folding in $J_{nm}(\sigma)$ is $k/(\kappa_n \Delta) = \tau_0 / (\sqrt{\pi} n)$, so a grid of $\sigma$ is chosen that spans a large enough number of $e$-foldings that no oscillatory behavior is present at the boundaries of the calculation.
 
@@
 
-\subsection{Results}
+\section{Summary and Conclusions}
 
-%\begin{figure}
-%\plotone{KT_Eri.pdf}
-%\caption{The Swift/XRT X-ray light curve for the first year after 
-%outburst of the suspected recurrent nova KT Eri. At a maximum count rate of 
-%328 ct/s, KT Eri was the brightest nova in X-rays observed to date. All 
-%the component figures (6) are available in the Figure Set. Note that
-%these components that are {\bf not} shown in the compiled pdf. The figure
-%set consists of the same figures as shown in Figure \ref{fig:pyramid}. 
-%The example figure shown for figure sets can be one component or many. 
-%\label{fig:fig4}}
-%\end{figure}
+The solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere originally derived by \cite{2006ApJ...649...14D} has been generalized to allow a monochromatic source of photons with frequencies away from line center.
+However, this solution satisfies $J=0$ at the surface of the sphere, which is clearly unphysical as there could be no spectrum.
+A correction which allows the proper boundary condition $J=\sqrt{3}H$ to be satisfied comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$, which are solved using a continuous Fourier expansion in frequency.
+Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
+In practice, the continuous expansions are discretized and the Fourier coefficients solved for via a matrix equation.
+The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$ where $a$ is the damping parameter and $\tau_0$ is the line-center optical depth.
+Thus, for very large optical depths, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower optical depths.
+Additionally, since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
+Since the peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$, calculations performed at lower optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core.
+By comparison with Monte Carlo simulations, it is seen that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency is altered, provided a sufficiently large optical depth.
+
+The time-dependence of the problem can also be solved to
 

### 2021-07-02 ms.tex
Adding xinit plot for tau=1e6

@@
 
+ \begin{figure}
+    \centering
+    \includegraphics{xinit_threepanel_tau1e6.pdf}
+    \caption{Again shifting the initial photon frequency, but at a lower optical depth of $\tau_0 = 10^6$.
+The shift in $x$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the bias in the spectrum is much more drastic.
+}
+    \label{fig:sol_mc_xinit_lowtau}
+\end{figure}
+
 Since the solutions have been generalized to allow for a monochromatic source of photons at a frequency $\sigma_s$ away from line center, their agreement with Monte Carlo as a function of source frequency can also be characterized.
@@
 Thus, for sufficiently large optical depths and emission away from line center, the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows.
-%Note: should we characterize this scaling quantitatively?
+The bias in the escaping spectrum is much more noticeable at lower optical depths, shown in Fig.
+\ref{fig:sol_mc_xinit_lowtau}, where a $\Delta x_s$ of 6 is a significantly larger fraction of the spectral peak location $(a\tau_0)^{1/3}$.
+Here it is more clear that as the photon initialization frequency becomes further from the optically thick core, the spectrum approaches a delta function in frequency at $\sigma_s$.
 

### 2021-07-02 ms.tex
Adding new plots for escape time distribution and frequency dependence

@@
 The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum.
-This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S}.
+This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S} where the discrepancy is particularly noticeable for line center optical depths of $\tau_0=10^5$ and $10^6$.
 The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
@@
 Here it is more clear that as the photon initialization frequency becomes further from the optically thick core, the spectrum approaches a delta function in frequency at $\sigma_s$.
+
+\begin{figure}
+    \centering
+    \includegraphics{xinit.pdf}
+    \caption{$H_{\rm bc}$ solutions shown at three line center optical depths, $\tau_0=10^5, 10^7,$ and $10^9$, for $\sigma_s=0.0, \tau_0, 2\tau_0,$ etc.
+The axes are scaled to show that the size of the corrective factor agrees with the predicted $(a\tau_0)^{-1/3}$.
+scaling}
+    \label{fig:xinit}
+\end{figure}
+
+Fig.
+\ref{fig:xinit} shows how the boundary term scales with both optical depth and photon source frequency.
+The photon initialization frequency is shifted in integer multiples of $\tau_0$.
+For clarity, only the positive side of the spectrum is shown.
+From Eq.
+\ref{eq:hbc_scaling}, the size of the correction should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
+This factor has been scaled out of the figure such that solutions for different optical depths should show close agreement in scale on the figure if the relation holds, even while changing the source frequency of the photons.
+Indeed, the solutions converge as the optical depth becomes larger.
+The remaining discrepancy present is due to the width of the Doppler core with respect to the peak of the spectrum; at lower depths, this causes our assumptions about the functional form of the line profile to break down.
 
@@
 \ref{eq:dEdtdnu} over all times should give a distribution for the emitted frequencies.
-It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the steady-state spectrum (Eq.
+It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the $J=0$ steady-state spectrum (Eq.
 \ref{eq:H0surf}).
@@
 \ee
-Integrating over $\nu$ gives unity if the sum rule in Eq. \ref{eq:sumrule} is true.
+Integrating over $\nu$ gives unity if the sum rule in Eq. \ref{eq:sumrule} is true. In Fig. \ref{fig:steadystate}
+
+\begin{figure}
+    \centering
+    \includegraphics{steadystate.pdf}
+    \caption{Comparison of steady-state and time-integrated spectra for 20 spatial eigenmodes and 500 frequency eigenmodes.
+The accuracy of the red scatter points is limited by the number of frequency eigenmodes summed.
+The accuracy of the core behavior for the orange solid curve and red scatter points is limited by the number of spatial eigenmodes summed, which is why both solutions fail in the core.}
+    \label{fig:my_label}
+\end{figure}
 
@@
 
-The distribution of the times it takes each photon to escape the sphere (hereafter called the ``wait time distribution'') is calculated from Eq.
-\ref{eq:dEdtdnu} by integrating over all frequencies.
-We obtain
+The distribution of the times it takes each photon to escape the sphere is calculated from Eq. \ref{eq:dEdtdnu} by integrating over all frequencies. We obtain
 \be
@@
 which is also normalized to unity.
+
+The eigenfunction expansion method is an effective characterization of the time-to-escape, yet not a fast enough computational method to use as a distribution for sampling.
+However, the behavior of the solution is well-understood since the late-time distribution is simply an exponential falloff in photon escape probability.
+The $e$-folding of the function is the lowest-order damping rate, $\gamma_{00}$.
+This is shown in Fig.
+\ref{fig:escape_time}.
+The orange line, representing the exponential falloff piece, matches well with the late-time behavior past a point $ct/R = ct_{0}/R = (a\tau_0)^{1/3}$.
+The early-time behavior can be modeled well with a gamma distribution, provided an adequate fit.
+For sampling, however, these fitting coefficients would need to be derived as functions of the input parameters $\tau_0$, $a$, and $x_s$.
+
+\begin{figure}
+    \centering
+    \includegraphics{waittime.pdf}
+    \caption{A wait time distribution of escaping photons, which is fit using the lowest order eigenfrequency as a decay timescale for the exponential falloff.
+The solid blue curve is a full solution using a sum over $n$ and $m$ modes.
+A gamma function can also be found that characterizes the early time behavior well, but underestimates photons escaping at late times.}
+    \label{fig:escape_time}
+\end{figure}
 

### 2021-07-02 ms.tex
Removing to do list

@@
 \keywords{}
-
-\section{To Do List}
-$\blacksquare$ Change all plots to use just wing line profile, exclude Doppler core
-
-$\blacksquare$ Use larger n phot MC runs for tau=1e5
-
-$\blacksquare$ Remove details about $H_d$, change wording in abstract and derivations
-
-$\blacksquare$ Add eigenmodes plots
-
-$\blacksquare$ Add discussion of numerical solution of time-dependent equations
-
-$\square$ Add discussion of frequency dependence in time dependent section (spectrum plots?)
-
-$\square$ Add discussion of wait times in time dependent section --- escape time plots, fitting function, etc
-
-$\square$ Add summary to time dependent section
-
-$\square$ Conclusions
 

### 2021-07-03 ms.tex
Modifications to two figures for clarity: xinit and time-integrated spectrum plots

@@
     \includegraphics{xinit.pdf}
-    \caption{$H_{\rm bc}$ solutions shown at three line center optical depths, $\tau_0=10^5, 10^7,$ and $10^9$, for $\sigma_s=0.0, \tau_0, 2\tau_0,$ etc.
-The axes are scaled to show that the size of the corrective factor agrees with the predicted $(a\tau_0)^{-1/3}$.
-scaling}
+    \caption{$H_{\rm bc}$ solutions shown at three line center optical depths, $\tau_0=10^5, 10^7,$ and $10^9$, for photon source frequencies $\sigma_s=0.0, \tau_0, 2\tau_0,$ etc.
+Thicker lines indicate larger optical depth, and darker lines indicate a photon source frequency further from line center.
+The axes are scaled to show that the size of the corrective factor agrees with the predicted $(a\tau_0)^{-1/3}$ scaling.}
     \label{fig:xinit}
@@
 Their oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity.
-The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.}
+The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.
+\todo{Show dimensional factor out front of the eigenfunctions to explain why they are so small.
+Dimensional analysis of the mean intensity itself.
+Radius, energy (set to 1), delta, and dimensionless parameters a and tau0.}}
     \label{fig:jsoln}
@@
 The accuracy of the red scatter points is limited by the number of frequency eigenmodes summed.
-The accuracy of the core behavior for the orange solid curve and red scatter points is limited by the number of spatial eigenmodes summed, which is why both solutions fail in the core.}
+The accuracy of the core behavior for the orange solid curve and red scatter points is limited by the number of spatial eigenmodes summed, which is why both solutions fail in the core.
+\todo{Steady state, Steady state (partial sum), Fluence of time-dependent solution, start at 8 and go to 30.
+Make the red line thinner and plot it in the background.}}
     \label{fig:my_label}
@@
 The solid blue curve is a full solution using a sum over $n$ and $m$ modes.
-A gamma function can also be found that characterizes the early time behavior well, but underestimates photons escaping at late times.}
+A gamma function can also be found that characterizes the early time behavior well, but underestimates photons escaping at late times.
+\todo{Add optical depth and xinit info.
+Quantify what the error in the slope is as compared with the Monte Carlo.
+Redo the plot for the lower optical depths and do a comparison of the MC data for tau=$10^5$ and $10^6$ to see if the agreement is getting better.
+Could be that we're getting the wrong decay time because the photon is spending a long time in the doppler core and that's not represented in our solution.
+However, it could be a better and better approximation for larger tau.
+So if we see a worse disagreement for $10^5$ then we know it's actually converging.
+Could plot as a cumulative probability distribution --- the tail shouldn't be very important in the flux calculation.
+Do CDF for theory line as well --- integrate time dependence in exponent.}}
     \label{fig:escape_time}

### 2021-07-04 ms.tex
full readthrough up to monte carlo section

@@
 The solution can be represented a sum of two terms: a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface, and a solution of the homogeneous equation which enforces the correct, zero-ingoing intensity boundary conditions at the surface.
-It is the compact, analytic form as well as the piece accounting for the correct, frequency dependent boundary condition that is novel in this study.
-The analytic solution is compared to numerical solutions with the Monte-Carlo method, which are valid at arbitrary optical depth, and the deviations from exact solution are investigated.
+It is the compact analytic form as well as the piece accounting for the correct, frequency-dependent boundary condition that is novel in this study.
+The analytic solution is compared to numerical solutions with the Monte-Carlo method, which are valid at arbitrary optical depth.
+Discrepancies in the spectra of previous work are quantified, and it is shown that the surface boundary condition derived here corrects these discrepancies.
+Separately, the time-dependence of the homogeneous equation is calculated using an eigenfunction expansion and solved numerically to characterize the time-to-escape of photons initialized at the center of the sphere, including the effects of frequency redistribution.
+This distribution can be sampled to accelerate Monte Carlo radiation transfer calculations at very large optical depths, obtaining intensities and radiation forces on cell faces at a fraction of the computational cost.
 
@@
 
-The need for accurate distributions from which to draw outgoing photon properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
+The need for accurate distributions from which to draw outgoing photons' properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
 In addition, a semi-analytic solution to time-dependent \lya diffusion through the same medium is explored to quantify how long the photons are expected to spend in the domain before escaping.
@@
 In their eigenfunction expansion, the spatial and frequency components of the differential equation are separated, yet the spatial eigenvalues are defined as being explicitly frequency-dependent.
-The resulting solution for large optical depths would suggest the mean intensity at the boundary of the slab is zero, which is unphysical.
+The resulting solution is therefore invalid on the basis that the differential equation and boundary conditions cannot simultaneously be satisfied.
 A more detailed discussion of the boundary condition is included in Section \ref{sec:steadystate}.
@@
 However, these solutions are limited to optical depths below $2.5 \times 10^3$.
-In the grid cells of a radiation magnetohydrodynamic simulation that includes resonant scattering, for example, it would be necessary to calculate the radiation force on each cell face due to \lya at line center optical depths of up to 1 million.
+In the grid cells of a radiation hydrodynamic simulation, it would be necessary to calculate the radiation force on each cell face due to \lya at line center optical depths of up to 1 million or more.
 A discussion of Monte Carlo code acceleration for optical depths as large as these in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
@@
 Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons.
-Photon destruction will not be considered, so $p$ is set to 0.
+Photon destruction will not be considered, so $p$ is set to 0 in this work.
 
@@
 \ref{eq:rteqn} and performing all angular integrals, we obtain Eq.
-\ref{eq:finaleqn} (see Appendix \ref{app:rteqn_derivation}) and set $p=\alpha_{\rm abs}=0$ to eliminate photon destruction terms.
+\ref{app:rteqn_derivation}\ref{eq:finaleqn} (see Appendix \ref{app:rteqn_derivation}) and set $p=\alpha_{\rm abs}=0$ to eliminate photon destruction terms.
 With a photon emission term given by Eq.
-\ref{eq:jem}, this gives the transfer equation
+\ref{app:rteqn_derivation}\ref{eq:jem}, this gives the transfer equation
 \be
@@
 \ee
-where the form of the source term is in Eq. \ref{eq:jem_v2}. The boundary condition is that there is no incoming flux at the surface, which can be written
+where the form of the source term is in Eq. \ref{app:rteqn_derivation}\ref{eq:jem_v2}. The boundary condition is that there is no incoming flux at the surface, which can be written
 \citep{1986rpa..book.....R}
@@
 \ee
-where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile ($\Delta \phi(\nu)$ here).
+where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile ($\phi(\nu)\Delta$ here).
 The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
@@
 with no delta function source term, and it must allow the boundary conditions to be satisfied at the surface. Since $J_0(R,
-\nu)=0$, the surface boundary condition becomes
+\sigma)=0$, the surface boundary condition becomes
 \be
@@
 \be \label{eq:plugged_amps}
-A(s) = \sqrt{3}\frac{1}{3k}\frac{\sqrt{6}}{32\pi}\frac{L}{\Delta R^3} \int_{-\infty}^\infty d\sigma e^{-is\sigma}\frac{1}{\phi(\sigma)}\frac{1}{1+\cosh \left[\frac{\pi \Delta}{kR} |\sigma - \sigma_i|\right]}
+A(s) = \sqrt{3} \int_{-\infty}^\infty d\sigma e^{-is\sigma}\left(\frac{1}{3k\phi(\sigma)}\frac{\sqrt{6}}{32\pi}\frac{L}{\Delta R^3}\frac{1}{1+\cosh \left[\frac{\pi \Delta}{kR} |\sigma - \sigma_i|\right]}\right)
 \ee
@@
 \ee
-These coefficients are used to evaluate Eq. \ref{eq:Hbc} at the surface of the sphere. Dividing $H_{\rm bc}$ by $H_0$ (Eq. \ref{eq:H0surf}) yields an overall proportionality
+These coefficients are used to evaluate the boundary condition's contribution to the flux (Eq.
+\ref{eq:Hbc}) at the surface of the sphere.
+Dividing this additional flux $H_{\rm bc}$ by the contribution from the $J=0$ solution, $H_0$ (Eq.
+\ref{eq:H0surf}), yields an overall proportionality
 \be \label{eq:hbc_scaling}
@@
 \ee
-Now, using Eq. \ref{eq:tau0} and the approximation $\sigma(x)=x^3\sqrt{2\pi/27}/a$ introduced in \cite{1973MNRAS.162...43H} for large $x$, we have
+Now, using the line center optical depth (Eq. \ref{eq:tau0}) and the approximation $\sigma(x)=x^3\sqrt{2\pi/27}/a$ introduced in \cite{1973MNRAS.162...43H} for large $x$, we have
 \be
@@
 \ee
-This predicts that the characteristic photon frequency in Doppler widths should scale as the cube root of the Voigt parameter $a$ multiplied by the line center optical depth $\tau_0$, indicating the location of the spectral peaks on either side of line center --- the locations where the photons most readily escape.
-Since our derivations were performed assuming a Lorentzian line profile (see Appendix \ref{app:rteqn_derivation}), our solutions are technically only valid far out into the line wing, where the Doppler component of the line profile is small.
+This predicts that the characteristic photon frequency in Doppler widths should scale as the cube root of the parameter $a$ multiplied by the line center optical depth $\tau_0$, indicating the location of the spectral peaks on either side of line center --- the locations where the photons most readily escape.
+Since our derivations were performed assuming a Lorentzian line profile (see Appendix \ref{app:rteqn_derivation}), our solutions are technically only valid in the line wing, where the Doppler component of the line profile is small.
 Since our choice of the damping parameter $a$ is constant, the solutions of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large optical depths.
@@
 The Monte Carlo method is used to solve the transfer equation numerically as a point of reference for these analytic solutions.
-For each simulation, a total of $2^{20} \approx 10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and frequencies are logged.
+This method is valid at arbitrarily large optical depths, being restricted only by its computational demand which grows in proportion to the number of photons used.
+For each simulation, a total of $2^{20} \approx 10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and frequencies are stored.
 A constant temperature of $T=10000\ \rm K$ is set for the gas.
 Frequency redistribution is calculated at each scattering, including the effects of recoil, to obtain the spectrum at the surface of the spherical simulation domain.
+In the comparisons shown in this section, the raw photon data is binned in escape angle and frequency to obtain spectra.
+64 bins are used to ensure good statistics and minimal noise in each bin.
 Further details of the Monte Carlo simulation are discussed in \cite{2017ApJ...851..150H}.
@@
 \appendix
-
+\restartappendixnumbering
 \section{ derivation of the transfer equation } \label{app:rteqn_derivation}

### 2021-07-04 ms.tex
full readthrough up to discussion of xinit plots

@@
 
-We now compare each of the solutions for surface flux with Monte Carlo simulations.
+We now compare each of the previously-discussed solutions for surface flux with Monte Carlo simulations.
 In Fig.
@@
 Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.
+
+ \begin{figure}
+    \centering
+    \includegraphics{tau_threepanel.pdf}
+    \caption{Increasing the line center optical depth.
+Shown here are $\tau_0 = 10^5, 10^6, 10^7$ with the $x$ and $y$ axes scaled by the characteristic frequency diffusion scale $(a\tau_0)^{1/3}$.
+Photons are initialized with $\rm x = 0.0$ in each case.}
+    \label{fig:sol_mc_tau}
+\end{figure}
+
+The size of the frequency-dependent boundary condition correction is dependent on the line center optical depth, which also dictates the x-position of the peak of spectrum according to Eq.
+\ref{eq:tau_peak_scaling}.
+This term contributes a significant amount of flux correction even at line center optical depths of $10^7$ where the $J=0$ solution is expected to perform its best, i.e., the majority of photons are pushed further out into the wing and thus the simplifying assumptions made in the solution of the differential equation are better founded.
+One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis of Fig.
+\ref{fig:sol_mc_tau} such that the peaks of the distributions are vertically aligned.
+This scaling has also been applied to the y-axis to preserve normalization of the escape probability.
+From Eq.
+\ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
+Indeed, agreement between $H_{0 + \rm bc}$ and the Monte Carlo points in Fig.
+\ref{fig:sol_mc_tau} improves as the optical depth becomes larger.
+At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely.
+The effects of core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift substantially outward in frequency from the line core for $\tau_0 = 10^5$.
 
@@
 The remaining discrepancy present is due to the width of the Doppler core with respect to the peak of the spectrum; at lower depths, this causes our assumptions about the functional form of the line profile to break down.
-
- \begin{figure}
-    \centering
-    \includegraphics{tau_threepanel.pdf}
-    \caption{Increasing the line center optical depth.
-Shown here are $\tau_0 = 10^5, 10^6, 10^7$ with the $x$ and $y$ axes scaled by the characteristic frequency diffusion scale $(a\tau_0)^{1/3}$.
-Photons are initialized with $\rm x = 0.0$.}
-    \label{fig:sol_mc_tau}
-\end{figure}
-
-Additionally, the size of the frequency-dependent boundary condition correction is dependent on the line center optical depth, which also dictates the x-position of the peak of spectrum according to Eq.
-\ref{eq:tau_peak_scaling}.
-One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis of Fig.
-\ref{fig:sol_mc_tau} such that the peaks of the distributions are vertically aligned.
-This scaling has also been applied to the y-axis to preserve normalization of the escape probability.
-From Eq.
-\ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-Indeed, agreement between $H_{0 + \rm bc}$ and the Monte Carlo points in Fig.
-\ref{fig:sol_mc_tau} improves as the optical depth becomes larger.
-At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely.
-The effects of core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift substantially outward in frequency from the line core for $\tau_0 = 10^5$.
 

### 2021-07-07 ms.tex
previously uncommitted changes

@@
 Now, consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
-After changing variables from $\nu$ to $\sigma$ using $d\sigma = \sqrt{2/3}d\nu/(\Delta^2 \phi)$ in Eq.
+After changing variables from $\nu$ to $\sigma$ using $d\sigma = \sqrt{2/3}d\nu/(\phi \Delta^2)$ in Eq.
 \ref{eq:rteqn} and performing all angular integrals, we obtain Eq.
@@
 This method is valid at arbitrarily large optical depths, being restricted only by its computational demand which grows in proportion to the number of photons used.
-For each simulation, a total of $2^{20} \approx 10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and frequencies are stored.
+For each simulation, a total of $2^{20} \approx 10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and escape frequencies are stored.
 A constant temperature of $T=10000\ \rm K$ is set for the gas.
@@
 \ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-Indeed, agreement between $H_{0 + \rm bc}$ and the Monte Carlo points in Fig.
-\ref{fig:sol_mc_tau} improves as the optical depth becomes larger.
+Indeed, agreement between both analytic flux calculations and the Monte Carlo points in Fig.
+\ref{fig:sol_mc_tau} improves with $H_{\rm bc}$ providing a fractionally smaller correction to $H_0$ as the optical depth becomes larger.
 At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely.
@@
 The bias in frequency distribution is slight for $\rm x_s = 6.0$ where the line profile is still relatively large and emitted photons remain trapped in the core, but the increase in spatial diffusion is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core.
-On this point, we note that the discrepancy between the Monte Carlo data and $H_0$ (effectively the scale of the corrective $H_{\rm bc}$ term) becomes larger as $\rm x_s$ increases.
+It is seen here that the discrepancy between the Monte Carlo data and $H_0$ (effectively the scale of the corrective $H_{\rm bc}$ term) becomes larger as $\rm x_s$ increases.
 Thus, for sufficiently large optical depths and emission away from line center, the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows.
@@
     \includegraphics{xinit.pdf}
-    \caption{$H_{\rm bc}$ solutions shown at three line center optical depths, $\tau_0=10^5, 10^7,$ and $10^9$, for photon source frequencies $\sigma_s=0.0, \tau_0, 2\tau_0,$ etc.
+    \caption{$H_{\rm bc}$ solutions shown at three line center optical depths, $\tau_0=10^5, 10^7,$ and $10^9$, for photon source frequencies $\sigma_s=0.0, \tau_0, 2\tau_0$.
 Thicker lines indicate larger optical depth, and darker lines indicate a photon source frequency further from line center.
@@
 \ref{fig:xinit} shows how the boundary term scales with both optical depth and photon source frequency.
-The photon initialization frequency is shifted in integer multiples of $\tau_0$.
+The photon initialization frequency (in units of $\sigma$, as in the differential equation) is shifted in integer multiples of $\tau_0$.
 For clarity, only the positive side of the spectrum is shown.
@@
 \ref{eq:hbc_scaling}, the size of the correction should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-This factor has been scaled out of the figure such that solutions for different optical depths should show close agreement in scale on the figure if the relation holds, even while changing the source frequency of the photons.
-Indeed, the solutions converge as the optical depth becomes larger.
-The remaining discrepancy present is due to the width of the Doppler core with respect to the peak of the spectrum; at lower depths, this causes our assumptions about the functional form of the line profile to break down.
+This factor has been scaled out of the figure such that solutions for different optical depths and the same source frequency $\sigma_s$ should show close agreement in scale on the figure if the relation holds.
+Indeed, the scaled solutions converge as the optical depth becomes larger, indicating general agreement with the $(a\tau_0)^{1/3}$ scaling.
+The remaining discrepancy present is due to the width of the Doppler core with respect to the peak of the spectrum; at lower depths, this causes the assumptions about the functional form of the line profile to break down.
+From this, we conclude that the errors introduced by the incorrect separation of variables in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others are proportional to $(a\tau_0)^{1/3}$, where $a$ is the ratio of natural to Doppler broadening and $\tau_0$ is the optical depth at line center.
+An additional amount of error of order $(a\tau_0)^{1/3}$ is introduced as the photon frequency $\sigma_s$ from line center is increased by a factor of $\tau_0$.
 
@@
 \be
-\gamma_{\rm guess} &=& \frac{a\gamma_{j-1} - \gamma_{j+1}}{a - 1}
+\gamma_{\rm guess} &=& \frac{b\gamma_{j-1} - \gamma_{j+1}}{b - 1}
 \ee
@@
 \be
-a &=& \left(\frac{f_{j} - f_{j-1}}{f_{j} - f_{j+1}}\right)\left(\frac{\gamma_{j+1}-\gamma_{j}}{\gamma_{j-1}-\gamma_{j}}\right).
+b &=& \left(\frac{f_{j} - f_{j-1}}{f_{j} - f_{j+1}}\right)\left(\frac{\gamma_{j+1}-\gamma_{j}}{\gamma_{j-1}-\gamma_{j}}\right).
 \ee
@@
 Their oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity.
-The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.
-\todo{Show dimensional factor out front of the eigenfunctions to explain why they are so small.
-Dimensional analysis of the mean intensity itself.
-Radius, energy (set to 1), delta, and dimensionless parameters a and tau0.}}
+The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.}
     \label{fig:jsoln}
@@
 \ref{fig:jsoln} to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$.
+The overall scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$ with $E$ arbitrarily set to 1, $k = \tau_0 \sqrt{\pi} \Delta / R$, and $R = 10^{11}$ cm.
+With this normalization, an eigenfunction has typical size ${\sim} E a / \left(R^2 \Delta \right) = 10^{-37}$.
 Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
@@
 \ee
-Integrating over $\nu$ gives unity if the sum rule in Eq. \ref{eq:sumrule} is true. In Fig. \ref{fig:steadystate}
+Integrating over $\nu$ gives unity if the sum rule in Eq.
+\ref{eq:sumrule} is true.
+In Fig.
+\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the expected result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum'').
+This graphic illustrates the physics modeled by each variable in the expansion.
+For example, the spatial modes contribute to the solutions' accuracy in the core of the line.
+If more spatial modes were calculated, the agreement between the lines extends further into the core.
+If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over the imaginary frequency variable $\gamma$ which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
+Modeling the physics deep into the line core could have an impact on the accuracy of the escape time distribution, but this would only affect late times since core photons are trapped for a longer duration before escaping.
 
@@
     \caption{Comparison of steady-state and time-integrated spectra for 20 spatial eigenmodes and 500 frequency eigenmodes.
-The accuracy of the red scatter points is limited by the number of frequency eigenmodes summed.
-The accuracy of the core behavior for the orange solid curve and red scatter points is limited by the number of spatial eigenmodes summed, which is why both solutions fail in the core.
-\todo{Steady state, Steady state (partial sum), Fluence of time-dependent solution, start at 8 and go to 30.
-Make the red line thinner and plot it in the background.}}
-    \label{fig:my_label}
+The accuracy of the time-integrated solution is limited by the number of frequency eigenmodes summed.
+The accuracy of the core behavior for both the partial sum and the time-integrated solution is limited by the number of spatial eigenmodes summed, which is why both solutions fail in the core.}
+    \label{fig:steadystate}
 \end{figure}
@@
 \be
-P(t)  & = & - \sqrt{\frac{3}{2}} \frac{16\pi^2 R \Delta^2 }{3kE}     \sum_{nm} (-1)^n  e^{s_{nm}t} \int d\sigma J_{nm}(\sigma) 
-\nonumber \\ & = &  - \sum_{nm} P_{nm} s_{nm} e^{s_{nm}t},
+P(t)  & = & \sqrt{\frac{3}{2}} \frac{16\pi^2 R \Delta^2 }{3kE}     \sum_{nm} (-1)^n  e^{-\gamma_{nm}t} \int d\sigma J_{nm}(\sigma) 
+\nonumber \\ & = &  \sum_{nm} P_{nm} \gamma_{nm} e^{-\gamma_{nm}t},
 \label{eq:waittime}

### 2021-07-07 ms.tex
Fixing sign on eq 54
adding discussion of the scaling of Pnm with m

@@
 These coefficients can have either sign depending on the value of $n$.
+The size of each contribution scales roughly as $0.5/(m+1/8)^{2/3}$, with a very weak dependence on $n$.
+This indicates the need for a large number of $n$ and $m$ to converge, i.e., it takes roughly ten times as many $m$ modes to reduce the size of $P_{nm}$ by a factor of ${\sim}$5.
+Numerical convergence would be obtained only when the size of additional $P_{nm}$ are negligible in the sum.
 
@@
 \be \label{eq:spectrum}
-P(\nu) & = &  -\frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^n \gamma_{nm}^{-1} J_{nm}(\sigma).
+P(\nu) & = &  \frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^n \gamma_{nm}^{-1} J_{nm}(\sigma).
 \ee
@@
 Modeling the physics deep into the line core could have an impact on the accuracy of the escape time distribution, but this would only affect late times since core photons are trapped for a longer duration before escaping.
+This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated.
 

### 2021-07-08 ms.tex
adding optical depth at source for xinit plots

@@
     \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
-Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency.}
+Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency.
+The optical depth at each of these source frequencies is $\tau_s = 10^7, 77.2,$ and $18.6$, respectively.}
     \label{fig:sol_mc_xinit}
@@
 The shift in $x$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the bias in the spectrum is much more drastic.
+The optical depth at the source frequency is $\tau_s = 10^6$, $7.7$, and $1.9$ for $x_s=0.0, 6.0,$ and $12.0$, respectively.
 }

### 2021-07-13 ms.tex
Removing undefined reference, rewording Neufeld solution description
Finished first draft?

@@
 \citet{1990ApJ...350..216N} follows this approach in an attempt to extend the result to media of intermediate optical depth, including the effects of scattering in the Doppler core of the line, but again does not use the correct boundary condition.
-\citet{?} improved on this approach, producing a divergent, inhomogeneous solution to the problem in 1D slab geometry that includes the effect of photon absorption within the medium.
+This produces a divergent, inhomogeneous solution to the problem in 1D slab geometry.
 \citet{2006ApJ...649...14D} generalize the problem to spherical geometry, which is the same physical set up used here.
@@
 
-The diffusion equation for photons escaping a uniform sphere of gas is a function of time, which was ignored in the steady-state calculations in Section \ref{sec:steadystate}.
-To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a fluid that is dynamic on timescales shorter than the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to an impulse is found.
+In order to understand how long it takes for the photons to escape the uniform sphere of gas we must reintroduce the time dependence of the diffusion equation, which was ignored in the steady-state calculations in Section \ref{sec:steadystate}.
+To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a fluid that is dynamic on timescales shorter than the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to an impulse is found, i.e., a delta function in time.
 This allows the distribution of photon escape times (the ``wait time distribution'') to be characterized and fit for efficient sampling.
@@
 
-Let us define the damping time to be $\gamma \equiv i\omega$, which is real-valued and positive for damped solutions.
+Let us define the damping frequency to be $\gamma \equiv i\omega$, which is real-valued and positive for damped solutions.
 There are certain values of $\gamma$ for which a resonant response is produced which we will call $\gamma_{nm}$.
@@
 where the contribution of each eigenfunction is
-\be
+\be \label{eq:pnmsoln}
 P_{nm} & \equiv & \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE}  (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
@@
 
-We seek now to tabulate all eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\gamma_{nm}$ for all spatial $n$ and for all eigenmodes $m$ at that given $n$.
-A resonant response in $J(n,\sigma,-i\gamma)$ is produced when the imaginary frequency is negative and has no real component.
+We seek now to calculate all eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\gamma_{nm}$ for all spatial $n$ and for all eigenmodes $m$ at that given $n$.
+A resonant response in $J(n,\sigma,-i\gamma)$ is produced for special values of $\gamma \equiv \gamma_{nm}$.
 To measure the size of the response to detect where resonances occur, we sum the absolute value of $J(n,\sigma,-i\gamma)$ over $\sigma$ in array form.
@@
 
-\subsection{Frequency dependence}
+\subsection{Comparison with Steady State and Monte Carlo}
 
@@
 \ee
-Integrating over $\nu$ gives unity if the sum rule in Eq.
-\ref{eq:sumrule} is true.
+Integrating over $\nu$ gives unity according to the sum rule in Eq.
+\ref{eq:sumrule}.
 In Fig.
-\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the expected result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum'').
+\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum'').
 This graphic illustrates the physics modeled by each variable in the expansion.
@@
 If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over the imaginary frequency variable $\gamma$ which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
-Modeling the physics deep into the line core could have an impact on the accuracy of the escape time distribution, but this would only affect late times since core photons are trapped for a longer duration before escaping.
+Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would only affect the distribution at late times since core photons are trapped for a longer duration before escaping.
 This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated.
+As a result of this choice, we expect that our semianalytic approach will underestimate the number of escaping photon at late times as compared with the Monte Carlo.
 
@@
 
-\subsection{Wait time distribution}
-
 The distribution of the times it takes each photon to escape the sphere is calculated from Eq. \ref{eq:dEdtdnu} by integrating over all frequencies. We obtain
@@
 which is also normalized to unity.
+For a sufficient number of spatial modes $n$ and frequency modes $m$, this sum approaches the ``true'' distribution of photon escape times as modeled by Monte Carlo simulations.
 
@@
 However, the behavior of the solution is well-understood since the late-time distribution is simply an exponential falloff in photon escape probability.
-The $e$-folding of the function is the lowest-order damping rate, $\gamma_{00}$.
+The rate constant of the function is the lowest-order eigenfrequency, $\gamma_{00}$, and its scale is determined by the coefficient $P_{00}$ as in Eq.
+\ref{eq:pnmsoln}.
+Thus, an approximate ``fitting function'' that captures both the peak of the escape time distribution and the exponential falloff is
+\be \label{eq:fitting_function}
+P(t) = \exp{\left[-\left(\frac{t_{\rm diff}}{t}\right)^2\right]} \times \gamma_{00} P_{00} e^{-\gamma_{00}t}.
+\ee
+The first term represents the early-time distribution, which then transitions to an exponential falloff past a point $ct/R = ct_{\rm diff}/R = (a\tau_0)^{1/3}$, where $t_{\rm diff}$ is a characteristic diffusion timescale.
 This is shown in Fig.
-\ref{fig:escape_time}.
-The orange line, representing the exponential falloff piece, matches well with the late-time behavior past a point $ct/R = ct_{0}/R = (a\tau_0)^{1/3}$.
-The early-time behavior can be modeled well with a gamma distribution, provided an adequate fit.
-For sampling, however, these fitting coefficients would need to be derived as functions of the input parameters $\tau_0$, $a$, and $x_s$.
+\ref{fig:escape_time} for two different line center optical depths.
+It is seen that the fitting function matches well with the late-time behavior of the eigenfunction solution, indicating that the tail of the escape time distribution can be modeled effectively by simple exponential decay.
+The only remaining discrepancy between the tail of the distribution and the Monte Carlo data is due to core scattering, which is not accurately modeled by the eigenfunction solution as previously discussed.
+A cumulative distribution function can be created from Eq.
+\ref{eq:fitting_function} using a simple rejection method, which allows the function to be sampled rapidly.
 
@@
     \centering
-    \includegraphics{waittime.pdf}
-    \caption{A wait time distribution of escaping photons, which is fit using the lowest order eigenfrequency as a decay timescale for the exponential falloff.
-The solid blue curve is a full solution using a sum over $n$ and $m$ modes.
-A gamma function can also be found that characterizes the early time behavior well, but underestimates photons escaping at late times.
-\todo{Add optical depth and xinit info.
-Quantify what the error in the slope is as compared with the Monte Carlo.
-Redo the plot for the lower optical depths and do a comparison of the MC data for tau=$10^5$ and $10^6$ to see if the agreement is getting better.
-Could be that we're getting the wrong decay time because the photon is spending a long time in the doppler core and that's not represented in our solution.
-However, it could be a better and better approximation for larger tau.
-So if we see a worse disagreement for $10^5$ then we know it's actually converging.
-Could plot as a cumulative probability distribution --- the tail shouldn't be very important in the flux calculation.
-Do CDF for theory line as well --- integrate time dependence in exponent.}}
+    \includegraphics{fitting_formula.pdf}
+    \caption{A wait time distribution of escaping photons for two different line center optical depths $\tau_0$, which is fit using Eq.
+\ref{eq:fitting_function}.
+A sum over 20 spatial eigenmodes and 500 frequency eigenmodes is labeled ``Eigenfunctions''.
+All calculations were performed with a monochromatic source of photons at line center ($x_s = 0.0$).}
     \label{fig:escape_time}
@@
 
+The effect of many scatterings in the Doppler core affects the tail of the escape-time distribution, since photons that become trapped here will take much longer to escape on average.
+This explains the deficit of photons in the semi-analytic escape time distributions at late times, i.e., the rate constant for the exponential falloff is overestimated slightly as compared with the Monte Carlo.
+The error in this rate constant is a function of line center optical depth, since the effect from the Doppler core is greatest when it extends into the area of the spectrum where photons most readily escape.
+In Fig.
+\ref{fig:tau_scaling}, it is shown that the rate constant of exponential decay converges with the lowest-order eigenfrequency $\gamma_{00}$ at sufficiently high optical depths, following a $t\propto(a\tau_0)^{1/3}$ scaling.
+At lower optical depths $\tau_0$, the effects of core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
+Here, the Monte Carlo accurately characterizes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile and does not use enough spatial modes to accurately model the frequency regime near line center.
+However, as the optical depth grows, the effect of core scattering becomes smaller and the approximations hold much better, agreeing well with the expected analytic scaling for the rate constant.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.75\textwidth]{tau_scaling.pdf}
+    \caption{Characteristic timescales as a function of optical depth.
+The reciprocal of the lowest-order eigenfrequency, $\gamma_{00}$, and a fit of the exponential falloff for the Monte Carlo data are shown to converge to a $t \propto (a\tau_0)^{1/3}$ scaling at large optical depths.
+The Monte Carlo points on this figure are obtained by fitting only the exponential piece of the escape time distribution to obtain the rate constant.}
+    \label{fig:tau_scaling}
+\end{figure}
+
 \section{Summary and Conclusions}
@@
 The solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere originally derived by \cite{2006ApJ...649...14D} has been generalized to allow a monochromatic source of photons with frequencies away from line center.
-However, this solution satisfies $J=0$ at the surface of the sphere, which is clearly unphysical as there could be no spectrum.
-A correction which allows the proper boundary condition $J=\sqrt{3}H$ to be satisfied comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$, which are solved using a continuous Fourier expansion in frequency.
+A correction to the $J=0$ surface boundary condition which allows the proper condition $J=\sqrt{3}H$ to be satisfied comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$, which are solved using a continuous Fourier expansion in frequency.
 Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
@@
 
-The time-dependence of the problem can also be solved to
+The time-dependence of the problem is solved under a $J=0$ boundary condition to characterize the distribution of photon escape times.
+The differential equation cannot be solved except with a semi-analytic approach, utilizing an expansion in both space and photon frequency.
+By matching boundary conditions on either side of the photon source frequency, the flux at the surface of the sphere is found as a function of time and photon frequency, expressed as a sum over many eigenmodes $n$ and $m$---spatial and frequency modes, respectively.
+Calculating additional spatial eigenmodes provide a more accurate model of the physics nearer to line center, but convergence is slow due to each eigenmode's weak dependence on $n$.
+Additional frequency eigenmodes introduce fast-oscillating terms that improve the accuracy of the sum, as their contributions cancel with components of lower-order terms to better represent the true solution.
+Integrating the solution over time produces a spectrum that is shown to agree well with the steady-state calculations in Section \ref{sec:steadystate}, provided a sufficient number of terms in the sum.
+Integrating the solution over frequency leads to a distribution of photon escape times, which can be compared directly with Monte Carlo simulations.
+The sum over eigenmodes produces an escape-time distribution that broadly captures the behavior shown by Monte Carlo data---a rise at early times, transitioning to exponential decay in the tail of the distribution.
+It is expected that the accuracy of the rate constant for the tail of the distribution is limited by the number of spatial terms included in the sum over eigenmodes, as the Doppler core can trap photons at low mean free paths until they diffuse outward in frequency, biasing the distribution toward later times.
+This physics is not modeled by our solution for two reasons: 1) our calculations ignored the Gaussian component of the Voigt line profile, leaving the Lorentzian piece which is accurate only in the line wing, and 2) knowing the core is not modeled accurately, we do not include a large enough number of spatial eigenmodes in the sum to resolve it.
+However, a fitting function dependent on parameters $a$ and $\tau_0$ is found that adequately represents the escape time distribution within these constraints.
+When calculated as a cumulative distribution function using a rejection method, the fit can be used to sample photon escape times directly rather than computing their travel times by the Monte Carlo method.
+As will be shown in future work, these calculations can be implemented as an acceleration scheme for Monte Carlo resonance-line radiation transfer at optical depths that would nominally be prohibitive in computational cost.
 

### 2021-07-16 ms.tex
Adding gamma_nm plot and beginnings of explanation

@@
 The analytic solution is compared to numerical solutions with the Monte-Carlo method, which are valid at arbitrary optical depth.
-Discrepancies in the spectra of previous work are quantified, and it is shown that the surface boundary condition derived here corrects these discrepancies.
-Separately, the time-dependence of the homogeneous equation is calculated using an eigenfunction expansion and solved numerically to characterize the time-to-escape of photons initialized at the center of the sphere, including the effects of frequency redistribution.
-This distribution can be sampled to accelerate Monte Carlo radiation transfer calculations at very large optical depths, obtaining intensities and radiation forces on cell faces at a fraction of the computational cost.
+It is shown that the scale of corrective term depends on the line center optical depth, accounting for discrepancies in the spectra of previous studies that used a $J=0$ boundary condition.
+Separately, the time-dependence of the diffusion equation is expressed using an eigenfunction expansion and solved numerically to characterize the time-to-escape of photons initialized at the center of the sphere.
+It is shown that the semi-analytic calculation agrees well with the Monte Carlo escape time distribution, converging for large line center optical depths around $\tau_0=10^7$.
+A fitting function for this distribution is found which can be sampled to accelerate Monte Carlo radiation transfer calculations at very large optical depths.
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{gamma_nm.pdf}
+    \caption{The scaling of numerically-obtained resonant frequencies as compared with the analytic expression in Eq. \ref{eq:gamma_nm}.}
+    \label{fig:gamma_nm}
+\end{figure}
+
+TODO: The values of the $\gamma_{nm}$ resonant frequencies are calculable analytically. Their scale depends on $m$, $n$, and the factor $(a\tau_0)^{1/3}$ according to 
+\be \label{eq:gamma_nm}
+2**(-1/3) * np.pi**(13/6)*n**(4/3)*(m-7/8)**(2/3)*fc.clight/p.radius/(p.a * p.tau0)**(1/3.) 
+\ee
+The size of additional eigenfrequencies scales as a powerlaw in $m$, yet as is seen in Fig.
+\ref{fig:gamma_nm} the scaling is weak, requiring up to 500 $m$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
+
 A single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{tp}$, at which point the function becomes evanescent.
@@
 It is seen that the fitting function matches well with the late-time behavior of the eigenfunction solution, indicating that the tail of the escape time distribution can be modeled effectively by simple exponential decay.
-The only remaining discrepancy between the tail of the distribution and the Monte Carlo data is due to core scattering, which is not accurately modeled by the eigenfunction solution as previously discussed.
+The remaining discrepancy between the tail of the distribution and the Monte Carlo data is due to core scattering, which is not accurately modeled by the eigenfunction solution.
 A cumulative distribution function can be created from Eq.
@@
 By matching boundary conditions on either side of the photon source frequency, the flux at the surface of the sphere is found as a function of time and photon frequency, expressed as a sum over many eigenmodes $n$ and $m$---spatial and frequency modes, respectively.
-Calculating additional spatial eigenmodes provide a more accurate model of the physics nearer to line center, but convergence is slow due to each eigenmode's weak dependence on $n$.
+Calculating additional spatial eigenmodes provides a more accurate model of the physics nearer to line center, but convergence is slow due to each eigenmode's weak dependence on $n$.
 Additional frequency eigenmodes introduce fast-oscillating terms that improve the accuracy of the sum, as their contributions cancel with components of lower-order terms to better represent the true solution.
@@
 The sum over eigenmodes produces an escape-time distribution that broadly captures the behavior shown by Monte Carlo data---a rise at early times, transitioning to exponential decay in the tail of the distribution.
-It is expected that the accuracy of the rate constant for the tail of the distribution is limited by the number of spatial terms included in the sum over eigenmodes, as the Doppler core can trap photons at low mean free paths until they diffuse outward in frequency, biasing the distribution toward later times.
+It is expected that the accuracy of the rate constant for the tail of the distribution is limited by the number of spatial terms included in the sum over eigenmodes, as the Doppler core can trap photons at high optical depths until they diffuse outward in frequency, biasing the distribution toward later times.
 This physics is not modeled by our solution for two reasons: 1) our calculations ignored the Gaussian component of the Voigt line profile, leaving the Lorentzian piece which is accurate only in the line wing, and 2) knowing the core is not modeled accurately, we do not include a large enough number of spatial eigenmodes in the sum to resolve it.
@@
 When calculated as a cumulative distribution function using a rejection method, the fit can be used to sample photon escape times directly rather than computing their travel times by the Monte Carlo method.
-As will be shown in future work, these calculations can be implemented as an acceleration scheme for Monte Carlo resonance-line radiation transfer at optical depths that would nominally be prohibitive in computational cost.
+As will be shown in future work, these calculations can be implemented as an acceleration scheme for Monte Carlo resonance-line radiation transfer at optical depths that would nominally be computationally prohibitive.
 

### 2021-07-18 ms.tex
Filling out gamma nm description

@@
 Too few (or imprecisely-calculated) modes creates ``ringing'' in the function that indicates the presence of imperfect cancellations in the positive and negative contributions of individual poles.
-
 \begin{figure}
@@
 \end{figure}
-
-TODO: The values of the $\gamma_{nm}$ resonant frequencies are calculable analytically. Their scale depends on $m$, $n$, and the factor $(a\tau_0)^{1/3}$ according to 
+The values of the $\gamma_{nm}$ resonant frequencies are calculable analytically. Their scale depends on $m$, $n$, and the factor $(a\tau_0)^{1/3}$ according to 
 \be \label{eq:gamma_nm}
-2**(-1/3) * np.pi**(13/6)*n**(4/3)*(m-7/8)**(2/3)*fc.clight/p.radius/(p.a * p.tau0)**(1/3.) 
+\gamma_{nm} = 2^{-1/3} \pi^{13/6} n^{4/3}\left(m-\frac{7}{8}\right)^{2/3}\frac{c}{R}(a\tau_0)^{-1/3} 
 \ee
@@
 \ref{fig:gamma_nm} the scaling is weak, requiring up to 500 $m$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
-
-A single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{tp}$, at which point the function becomes evanescent.
+When sweeping through the imaginary frequency domain to find resonances, this expression is used to set the scale of the sweep points to ensure no $\gamma_{nm}$ are missed.
+The continuity and close agreement with the analytic expression shown in Fig.
+\ref{fig:gamma_nm} indicate that the sweep routine accurately brackets and refines the locations of resonances.
+
+The form of a single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{tp}$, at which point the function becomes evanescent.
 The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Eq.

### 2021-07-26 ms_reorg.tex
adding optical depth information to steady state spec plot

--- 2021-07-18 ms.tex
@@
 This means that any method that can treat these zone via an analytic solution has the potential to greatly accelerate the calculation.
-
-There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.
-The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.
-These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core.
-Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.
-
-A second class of methods are hybrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
-This involves designating sufficiently optically thick simulations cells for computation via a finite difference representation of the radiation transfer equation.
-This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.
-For the resonant scattering problem, where the opacity is a strong function of frequency, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
-
-A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M, 2010A&A...520A..70R}.
-In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
-An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation within a uniform sphere.
-A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution.
-
-The need for accurate distributions from which to draw outgoing photons' properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
-In addition, a semi-analytic solution to time-dependent \lya diffusion through the same medium is explored to quantify how long the photons are expected to spend in the domain before escaping.
-These solutions will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.
-
-\section{ previous analytic work }
+A complete, general analytic solution for the resonance scattering has never been derived but approximate solutions exist in certain limits.
+
+{\color{red} Moved text on Harrington into the introduction since it is a primary driver of the calculation.}
 
@@
 
-Radiation forces due to \lya transfer have been calculated in \citet{1976ApJ...208..286W} in plane-parallel geometry.
-However, these solutions are limited to optical depths below $2.5 \times 10^3$.
-In the grid cells of a radiation hydrodynamic simulation, it would be necessary to calculate the radiation force on each cell face due to \lya at line center optical depths of up to 1 million or more.
-A discussion of Monte Carlo code acceleration for optical depths as large as these in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
-In terms of the time dependence, \citet{1994ApJ...427..603R} introduce an ansatz for the Fokker-Planck diffusion equation in order to quantify the relaxation timescale necessary to reach a quasi-static solution.
-Notably, the full Voigt function is used for the line profile rather than restricting scattering to the damping wing only.
+The question is how to satisfy the surface boundary condition in Eq.
+\ref{eq:bc}.
+On this point, we note that the derivation in \citet{1973MNRAS.162...43H}, and numerous studies later studies, does not actually produce a valid solution of the transfer equation and boundary condition.
+The reason is as follows.
+In the notation of \citet{1973MNRAS.162...43H}, a separation of variables
+$J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ is attempted (their Equations 16 and 23).
+The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
+In order to satisfy the boundary conditions, the separation constant must satisfy an eigenvalue equation of the form
+\be
+\lambda \tan(\lambda B) & = & \frac{3}{2} \phi,
+\label{eq:evalue}
+\ee
+where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile ($\phi(\nu)\Delta$ here).
+The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
+But then the separation constant is not constant, and it does not satisfy Eq.
+\ref{eq:rt_no_destr} since the frequency derivatives will act on the separation ``constant", giving extra terms.
+To our knowledge the errors introduced by this ansatz have never been quantified.
+
+In the limit of large optical depth $B$, \citealt{1973MNRAS.162...43H} approximates the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$, which gives $J=0$ at the surface.
+This is essentially the result in Eq.
+\ref{eq:J0} above.
+However, since this solution gives zero at the surface, their Eq.
+34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
+This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
 
@@
 
-\noindent The full solution is the sum of the $J=0$ solution and the bc solution.
-The problem is as follows.
-The radiative intensity $I = dE/(dA dt d\Omega d\nu)$ is the energy per perpendicular area $dA$, per time $dt$, per solid angle $d\Omega$ and per frequency $d\nu$ \citep{1986rpa..book.....R}.
-Here the time-dependence of $I$ has been ignored, which assumes the fluid is changing on timescales long compared to a light-crossing time.
-The intensity $I=I(\vec{x},\vec{n}, \nu)$ will be considered a function of position $\vec{x}$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$.
-In the Eddington and two-stream approximations, $I(\vec{x},\nu) \simeq J(\vec{x},\nu) + 3 \vec{n} \cdot \vec{H}(\vec{x},\nu)$, where $J=(1/4\pi) \int d\Omega I$ is the mean intensity and $\vec{F} = 4\pi \vec{H}= \int d\Omega \vec{n} I$ is the flux.
-
-Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
-The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
-The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$.
-For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
-The transfer equation is \citep{1986rpa..book.....R}
-\be
-\frac{1}{c} \frac{\partial I}{\partial t} + \vec{n} \cdot \grad I & =& - \left( \alpha_{\rm sc} + \alpha_{\rm abs} \right) I + (1-p) j_{\rm sc} + j_{\rm em}.
-\label{eq:rteqn}
-\ee
-The scattering coefficient, or inverse mean free path to scattering, is 
-\be
-\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{H(x,a)}{\sqrt{\pi} \Delta}
-= k \phi   
-\ee
-where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
-The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section.
-Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons.
-Photon destruction will not be considered, so $p$ is set to 0 in this work.
-
 \subsection{Derivation of the Steady-State Solution}
+
+{\color{red} Moved the time dependent part back to the appendix.
+It is probably sufficient to just state eq.
+\ref{eq:finaleqn} as the starting point, referring to the reader to the appendix.
+We may want a short paragraph defining some of the key notation, though, so the reader is not forced to extensively reference the appendix.}
+
 Now, consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
@@
 \ref{fig:sol_mc_residual_0} for qualitative understanding, but will not be discussed further.
+
+{\color{red} We do not need an extensive discussion fo the divergent solution, but we should probably right it down here for compelteness, since we include it in the figure.}
 
@@
 
-The question is how to satisfy the surface boundary condition in Eq.
-\ref{eq:bc}.
-On this point, we note that the derivation in \citet{1973MNRAS.162...43H}, and numerous studies later studies, does not actually produce a valid solution of the transfer equation and boundary condition.
-The reason is as follows.
-In the notation of \citet{1973MNRAS.162...43H}, a separation of variables
-$J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ is attempted (their Equations 16 and 23).
-The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
-In order to satisfy the boundary conditions, the separation constant must satisfy an eigenvalue equation of the form
-\be
-\lambda \tan(\lambda B) & = & \frac{3}{2} \phi,
-\label{eq:evalue}
-\ee
-where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile ($\phi(\nu)\Delta$ here).
-The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
-But then the separation constant is not constant, and it does not satisfy Eq.
-\ref{eq:rt_no_destr} since the frequency derivatives will act on the separation ``constant", giving extra terms.
-To our knowledge the errors introduced by this ansatz have never been quantified.
-
-In the limit of large optical depth $B$, \citealt{1973MNRAS.162...43H} approximates the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$, which gives $J=0$ at the surface.
-This is essentially the result in Eq.
-\ref{eq:J0} above.
-However, since this solution gives zero at the surface, their Eq.
-34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
-This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
-
 % Dijkstra
@@
 \subsection{Scaling with Line Center Optical Depth}
+
+{\color{red} This section can probably be shortened to a couple of paragraphs with most of the equations removed and the results just stated.}
+
 To examine the relative size of the corrective term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the optical depth is large and thus the mean intensity will be considerably larger than the surface flux.
@@
     \includegraphics[width=\textwidth]{gamma_nm.pdf}
-    \caption{The scaling of numerically-obtained resonant frequencies as compared with the analytic expression in Eq. \ref{eq:gamma_nm}.}
+    \caption{The scaling of numerically-obtained resonant frequencies as compared with the analytic expression in Eq. \ref{eq:gamma_nm}. The data shown is for $\tau_0=10^7$ and $x_s=0.0$.}
     \label{fig:gamma_nm}
 \end{figure}
-The values of the $\gamma_{nm}$ resonant frequencies are calculable analytically. Their scale depends on $m$, $n$, and the factor $(a\tau_0)^{1/3}$ according to 
+The values of the $\gamma_{nm}$ resonant frequencies can be described approximately with Eq. \ref{eq:gamma_nm}. Their scale depends on $m$, $n$, and the factor $(a\tau_0)^{1/3}$ according to 
 \be \label{eq:gamma_nm}
@@
     \centering
-    \includegraphics{fitting_formula.pdf}
+    \includegraphics{waittime.pdf}
     \caption{A wait time distribution of escaping photons for two different line center optical depths $\tau_0$, which is fit using Eq.
@@
 \end{figure}
+
+\section{ Discussion }
+
+{\color{red} Moved the acceleration content to discussion}
+
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.
+The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.
+These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core.
+Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.
+
+A second class of methods are hybrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
+This involves designating sufficiently optically thick simulations cells for computation via a finite difference representation of the radiation transfer equation.
+This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.
+For the resonant scattering problem, where the opacity is a strong function of frequency, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
+
+A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M, 2010A&A...520A..70R}.
+In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
+An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation within a uniform sphere.
+A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution.
+
+The need for accurate distributions from which to draw outgoing photons' properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
+In addition, a semi-analytic solution to time-dependent \lya diffusion through the same medium is explored to quantify how long the photons are expected to spend in the domain before escaping.
+These solutions will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.
+
+Radiation forces due to \lya transfer have been calculated in \citet{1976ApJ...208..286W} in plane-parallel geometry.
+However, these solutions are limited to optical depths below $2.5 \times 10^3$.
+In the grid cells of a radiation hydrodynamic simulation, it would be necessary to calculate the radiation force on each cell face due to \lya at line center optical depths of up to 1 million or more.
+A discussion of Monte Carlo code acceleration for optical depths as large as these in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
+In terms of the time dependence, \citet{1994ApJ...427..603R} introduce an ansatz for the Fokker-Planck diffusion equation in order to quantify the relaxation timescale necessary to reach a quasi-static solution.
+Notably, the full Voigt function is used for the line profile rather than restricting scattering to the damping wing only.
 
@@
 \section{ derivation of the transfer equation } \label{app:rteqn_derivation}
+
+\noindent The full solution is the sum of the $J=0$ solution and the bc solution.
+The problem is as follows.
+The radiative intensity $I = dE/(dA dt d\Omega d\nu)$ is the energy per perpendicular area $dA$, per time $dt$, per solid angle $d\Omega$ and per frequency $d\nu$ \citep{1986rpa..book.....R}.
+Here the time-dependence of $I$ has been ignored, which assumes the fluid is changing on timescales long compared to a light-crossing time.
+The intensity $I=I(\vec{x},\vec{n}, \nu)$ will be considered a function of position $\vec{x}$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$.
+In the Eddington and two-stream approximations, $I(\vec{x},\nu) \simeq J(\vec{x},\nu) + 3 \vec{n} \cdot \vec{H}(\vec{x},\nu)$, where $J=(1/4\pi) \int d\Omega I$ is the mean intensity and $\vec{F} = 4\pi \vec{H}= \int d\Omega \vec{n} I$ is the flux.
+
+Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
+The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
+The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$.
+For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
+The transfer equation is \citep{1986rpa..book.....R}
+\be
+\frac{1}{c} \frac{\partial I}{\partial t} + \vec{n} \cdot \grad I & =& - \left( \alpha_{\rm sc} + \alpha_{\rm abs} \right) I + (1-p) j_{\rm sc} + j_{\rm em}.
+\label{eq:rteqn}
+\ee
+The scattering coefficient, or inverse mean free path to scattering, is 
+\be
+\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{H(x,a)}{\sqrt{\pi} \Delta}
+= k \phi   
+\ee
+where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section.
+Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons.
+Photon destruction will not be considered, so $p$ is set to 0 in this work.
 

### 2021-07-30 ms.tex
Recalculating location of doppler wing

@@
 For \lya and a hydrogen gas of temperature $T=10^4$ K, the damping parameter $a = \Gamma / (4\pi\Delta)$ is equal to $4.72\times 10^{-4}$ in CGS units.
-The Doppler core is then significant over the range $-4.6 < x < 4.6$.
+The Doppler core is then significant over the range $-3.3 < x < 3.3$.
 Comparing with the locations of the spectral peaks at various optical depths using Eq.
@@
     \includegraphics{steadystate.pdf}
-    \caption{Comparison of steady-state and time-integrated spectra for 20 spatial eigenmodes and 500 frequency eigenmodes.
+    \caption{Comparison of steady-state and time-integrated spectra for 20 spatial eigenmodes and 500 frequency eigenmodes at a line center optical depth of $\tau_0=10^7$.
 The accuracy of the time-integrated solution is limited by the number of frequency eigenmodes summed.

### 2021-07-30 ms.tex
Changing "Scaling with Line Center Optical Depth" section to be much shorter --- removing derivations and adding in critical tau explanation

@@
 To examine the relative size of the corrective term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the optical depth is large and thus the mean intensity will be considerably larger than the surface flux.
-Starting from Eq.
-\ref{eq:bc2}, we assume $H_{\rm bc} \ll J_{\rm bc}$ such that
+We obtain the proportionality
+
+%%%% DERIVATION EDITED OUT
+\ifx
+Starting from Eq. \ref{eq:bc2}, we assume $H_{\rm bc} \ll J_{\rm bc}$ such that
 \be
@@
 \ref{eq:H0surf}), yields an overall proportionality
+\fi
+
 \be \label{eq:hbc_scaling}
@@
 
+\ifx
 By replacing the differential operators in Eq.
@@
 \ee
-Simplifying, we obtain the proportionality
+\fi
+
+The location of the spectral peak of the distribution is
 \be \label{eq:tau_peak_scaling}
@@
 Since our choice of the damping parameter $a$ is constant, the solutions of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large optical depths.
-The boundary of the Doppler core is approximately where the Gaussian and Lorentzian pieces are equal:
-\be
-\frac{e^{-x^2}}{\sqrt{\pi}} = \frac{a}{\pi x^2}
-\ee
 For \lya and a hydrogen gas of temperature $T=10^4$ K, the damping parameter $a = \Gamma / (4\pi\Delta)$ is equal to $4.72\times 10^{-4}$ in CGS units.
-The Doppler core is then significant over the range $-3.3 < x < 3.3$.
-Comparing with the locations of the spectral peaks at various optical depths using Eq.
-\ref{eq:tau_peak_scaling}, we find that $x_0=$3.6, 7.8, 16.8 for $\tau_0=10^5, 10^6,$ and $10^7$, respectively.
-Therefore, solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower line center optical depths where the peak of the spectrum lies near the core and improve for larger optical depths where the spectral peak is well outside of the line core.
+Thus, the value of $\tau_0$ at which the Doppler and Lorentzian components of the line wing are equal is $\tau_0=7.3\times10^5$.
+Solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower line center optical depths where the peak of the spectrum lies near the core and improve for larger optical depths where the spectral peak is well outside of the line core.
 \subsection{Comparison to Monte Carlo}

### 2021-08-16 ms.tex
Beginning to incorporate edits from reorganized version

@@
 A monochromatic source of photons is assumed at the center of the sphere, and the intensity within the sphere and at the surface is found with the Eddington approximation for the angular dependence.
-The solution can be represented a sum of two terms: a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface, and a solution of the homogeneous equation which enforces the correct, zero-ingoing intensity boundary conditions at the surface.
+The solution can be represented as a sum of two terms: a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface, and a solution of the homogeneous equation which enforces the correct, zero-ingoing intensity boundary conditions at the surface.
 It is the compact analytic form as well as the piece accounting for the correct, frequency-dependent boundary condition that is novel in this study.
@@
 
-%There's a much thicker layer of atomic hydrogen
-%It's a very optically thick region
-% Care about lya going into the planet's atmosphere and dissociating molecules
-% Observational: observe the transits in lyman alpha
-%Chen liang's paper - focus on the section where he shows the results of the lya transfer - can cause heating deeper in the atmosphere, collisional de-excitation.
-Summarize some of the things that lya does to the atmosphere.
-Ionize low ionization-potential atoms (<10.2 eV)
-%Large Lya line intensity, lots of H atoms, then lya is constantly exciting and de-exciting.
-Then, n=2 is populated so Balmer lines can also be absorbed.
-This explains why strong balmer absorption is observed in transits to begin with.
-Otherwise, you would need very high temperatures to populate the n=2 state.
-% Focus on later sections, especially balmer absorption near the end of the paper.
-
-% Put emphasis on the fact that Lya is generated within the atmosphere --- ionization balanced by recombination, rate equilibrium.
-Recombination gives you lyman alpha again.
-Collisions decrease the density in the 2s states.
-The efficiency of producing lya is quite high, and that's immediately at high optical depth.
-
 Hubble Space Telescope (HST) observations with STIS have found large \lya transit depths around a handful of exoplanets, indicating an extended distribution of hydrogen: \citet{2003Natur.422..143V, 2012A&A...543L...4L, 2012A&A...547A..18E, 2015Natur.522..459E,  2017A&A...597A..26B, 2017A&A...599L...3B, 2017A&A...602A.106B, 2018A&A...620A.147B, 2019AJ....158...50W, 2019EPSC...13.1928L, 2020ApJ...888L..21G,2021arXiv210309864B}.
@@
 This means that any method that can treat these zone via an analytic solution has the potential to greatly accelerate the calculation.
-
-There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.
-The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.
-These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core.
-Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.
-
-A second class of methods are hybrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
-This involves designating sufficiently optically thick simulations cells for computation via a finite difference representation of the radiation transfer equation.
-This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.
-For the resonant scattering problem, where the opacity is a strong function of frequency, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
-
-A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M, 2010A&A...520A..70R}.
-In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
-An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation within a uniform sphere.
-A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution.
-
-The need for accurate distributions from which to draw outgoing photons' properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
-In addition, a semi-analytic solution to time-dependent \lya diffusion through the same medium is explored to quantify how long the photons are expected to spend in the domain before escaping.
-These solutions will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.
-
-\section{ previous analytic work }
+A complete, general analytic solution for the resonance scattering has never been derived but approximate solutions exist in certain limits.
 
@@
 \begin{enumerate}
-    \item a \textbf{J=0 solution} ($\rm H_0$) which includes the delta function solution at the source and satisfies $J=0$ at $r=R$,
-    \item the \textbf{bc solution} ($\rm H_{bc}$) that allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
+    \item a \textbf{J=0 solution} ($\rm H_0$) which includes the delta function source and satisfies $J=0$ at $r=R$,
+    \item the \textbf{bc solution} ($\rm H_{bc}$) that allows the boundary condition $J=\sqrt{3}H$ to be satisfied. %TODO: Shane wants def here? Where?
 \end{enumerate}
-
-\noindent The full solution is the sum of the $J=0$ solution and the bc solution.
-The problem is as follows.
-The radiative intensity $I = dE/(dA dt d\Omega d\nu)$ is the energy per perpendicular area $dA$, per time $dt$, per solid angle $d\Omega$ and per frequency $d\nu$ \citep{1986rpa..book.....R}.
-Here the time-dependence of $I$ has been ignored, which assumes the fluid is changing on timescales long compared to a light-crossing time.
-The intensity $I=I(\vec{x},\vec{n}, \nu)$ will be considered a function of position $\vec{x}$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$.
-In the Eddington and two-stream approximations, $I(\vec{x},\nu) \simeq J(\vec{x},\nu) + 3 \vec{n} \cdot \vec{H}(\vec{x},\nu)$, where $J=(1/4\pi) \int d\Omega I$ is the mean intensity and $\vec{F} = 4\pi \vec{H}= \int d\Omega \vec{n} I$ is the flux.
 
@@
 For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
-The transfer equation is \citep{1986rpa..book.....R}
-\be
-\frac{1}{c} \frac{\partial I}{\partial t} + \vec{n} \cdot \grad I & =& - \left( \alpha_{\rm sc} + \alpha_{\rm abs} \right) I + (1-p) j_{\rm sc} + j_{\rm em}.
-\label{eq:rteqn}
-\ee
-The scattering coefficient, or inverse mean free path to scattering, is 
-\be
-\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{H(x,a)}{\sqrt{\pi} \Delta}
-= k \phi   
-\ee
-where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
-The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section.
-Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons.
-Photon destruction will not be considered, so $p$ is set to 0 in this work.
-
-\subsection{Derivation of the Steady-State Solution}
+$n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+
 Now, consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
-After changing variables from $\nu$ to $\sigma$ using $d\sigma = \sqrt{2/3}d\nu/(\phi \Delta^2)$ in Eq.
-\ref{eq:rteqn} and performing all angular integrals, we obtain Eq.
-\ref{app:rteqn_derivation}\ref{eq:finaleqn} (see Appendix \ref{app:rteqn_derivation}) and set $p=\alpha_{\rm abs}=0$ to eliminate photon destruction terms.
-With a photon emission term given by Eq.
-\ref{app:rteqn_derivation}\ref{eq:jem}, this gives the transfer equation
+Starting with the full transfer equation, Eq.
+\ref{app:rteqn_derivation}\ref{eq:finaleqn}, with no photon destruction and a photon emission term given by Eq.
+\ref{app:rteqn_derivation}\ref{eq:jem}, the steady-state transfer equation is
 \be
 \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} & = & 
-- \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s})
+- \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s}).
 \label{eq:rt_no_destr}
 \ee
-where the form of the source term is in Eq. \ref{app:rteqn_derivation}\ref{eq:jem_v2}. The boundary condition is that there is no incoming flux at the surface, which can be written
+The boundary condition is that there is no incoming intensity at the surface, which can be written
 \citep{1986rpa..book.....R}
@@
 This solution is included in Fig.
-\ref{fig:sol_mc_residual_0} for qualitative understanding, but will not be discussed further.
+\ref{fig:sol_mc_residual_0} for illustration, but will not be discussed further.
+
+\be
+J_{\rm d} & = & 
+\frac{(\sqrt{6}k^2L)/(16\pi^3 \Delta^3)}{ (k/\Delta)^2\left[ (x-x_{\rm s})^2 + (y-y_{\rm s})^2 + (z-z_{\rm s})^2 \right] + (\sigma - \sigma_{\rm s})^2}.
+\label{eq:Jd}
+\ee
+
+\be
+H_{\rm d} & = & - \frac{1}{3k\phi} \frac{\partial J_d}{\partial r}
+=  \left( \frac{1}{3k\phi} \right) 
+\left( \frac{ \sqrt{6}k^3L }{ 8\pi^3 \Delta^4} \right)
+\left( \frac{k r/\Delta}{ \left[ (kr/\Delta)^2 + (\sigma-\sigma_{\rm s})^2 \right]^2 } \right).
+\label{eq:Hd}
+\ee
 
@@
 
-The question is how to satisfy the surface boundary condition in Eq.
-\ref{eq:bc}.
-On this point, we note that the derivation in \citet{1973MNRAS.162...43H}, and numerous studies later studies, does not actually produce a valid solution of the transfer equation and boundary condition.
-The reason is as follows.
-In the notation of \citet{1973MNRAS.162...43H}, a separation of variables
-$J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ is attempted (their Equations 16 and 23).
-The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
-In order to satisfy the boundary conditions, the separation constant must satisfy an eigenvalue equation of the form
-\be
-\lambda \tan(\lambda B) & = & \frac{3}{2} \phi,
-\label{eq:evalue}
-\ee
-where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile ($\phi(\nu)\Delta$ here).
-The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
-But then the separation constant is not constant, and it does not satisfy Eq.
-\ref{eq:rt_no_destr} since the frequency derivatives will act on the separation ``constant", giving extra terms.
-To our knowledge the errors introduced by this ansatz have never been quantified.
-
-In the limit of large optical depth $B$, \citealt{1973MNRAS.162...43H} approximates the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$, which gives $J=0$ at the surface.
-This is essentially the result in Eq.
-\ref{eq:J0} above.
-However, since this solution gives zero at the surface, their Eq.
-34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
-This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
-
-% Dijkstra
-%Despite this treatment, a calculation of the surface flux from their Eq.
-13 compared with the total emerging flux density at the surface of the sphere (Eq.
-C17) yields a $J=2H$ surface boundary condition.
-However, under the two-stream approximation, a surface boundary condition $J=\sqrt{3}H$ is necessary to properly normalize the radiation pressure.
-
 A different solution method is attempted here: namely, a continuous Fourier expansion in the frequency variable $\sigma$. The full solution is written
@@
 For \lya and a hydrogen gas of temperature $T=10^4$ K, the damping parameter $a = \Gamma / (4\pi\Delta)$ is equal to $4.72\times 10^{-4}$ in CGS units.
-Thus, the value of $\tau_0$ at which the Doppler and Lorentzian components of the line wing are equal is $\tau_0=7.3\times10^5$.
+Thus, the value of $\tau$ at which the Doppler and Lorentzian components of the line wing are equal is $\tau_{\rm cw}=7.3\times10^4$.
 Solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower line center optical depths where the peak of the spectrum lies near the core and improve for larger optical depths where the spectral peak is well outside of the line core.
@@
 
+The problem is as follows.
+The radiative intensity $I = dE/(dA dt d\Omega d\nu)$ is the energy per perpendicular area $dA$, per time $dt$, per solid angle $d\Omega$ and per frequency $d\nu$ \citep{1986rpa..book.....R}.
+Here the time-dependence of $I$ has been ignored, which assumes the fluid is changing on timescales long compared to a light-crossing time.
+The intensity $I=I(\vec{x},\vec{n}, \nu)$ will be considered a function of position $\vec{x}$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$.
+In the Eddington and two-stream approximations, $I(\vec{x},\nu) \simeq J(\vec{x},\nu) + 3 \vec{n} \cdot \vec{H}(\vec{x},\nu)$, where $J=(1/4\pi) \int d\Omega I$ is the mean intensity and $\vec{F} = 4\pi \vec{H}= \int d\Omega \vec{n} I$ is the flux.
+
+Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
+The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
+The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$.
+For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
+The transfer equation is \citep{1986rpa..book.....R}
+\be
+\frac{1}{c} \frac{\partial I}{\partial t} + \vec{n} \cdot \grad I & =& - \left( \alpha_{\rm sc} + \alpha_{\rm abs} \right) I + (1-p) j_{\rm sc} + j_{\rm em}.
+\label{eq:rteqn}
+\ee
+The scattering coefficient, or inverse mean free path to scattering, is 
+\be
+\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{H(x,a)}{\sqrt{\pi} \Delta}
+= k \phi   
+\ee
+where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section.
+Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons.
+Photon destruction will not be considered, so $p$ is set to 0 in this work.
+
 \citet{1973MNRAS.162...43H} first showed that the transfer equation for the mean  intensity $J$ will satisfy a Poisson equation involving second derivatives of space and frequency variables.
@@
 \ee
-As an example, on the damping wing, $\phi \simeq a/(\pi x^2)$, $\langle u_\parallel \rangle \simeq 1/x$ and $\langle u_\parallel^2 \rangle \simeq 1/2$, and this identity is satisfied.
-The redistribution function can then be rewritten
+As an example, on the damping wing, the line profile can be approximated as 
+\be \label{eq:line_profile_wing}
+\phi \simeq \frac{a}{\pi x^2}
+\ee
+with $\langle u_\parallel \rangle \simeq 1/x$ and $\langle u_\parallel^2 \rangle \simeq 1/2$, and so this identity is satisfied. The redistribution function can then be rewritten
 \be
@@
 \ee
-Making the change of variables to $d\sigma = \sqrt{2/3}d\nu/(\Delta^2 \phi)$, the equation can be rewritten in the standard form \citep{1973MNRAS.162...43H}
+Making the change of variables to $d\sigma$ using
+\be \label{eq:change_of_variables}
+d\sigma = \sqrt{\frac{2}{3}}\frac{d\nu}{\phi \Delta^2},
+\ee
+the equation can be rewritten in the standard form \citep{1973MNRAS.162...43H}
 \be

### 2021-08-20 ms.tex
Edits for steady state section from Shane's copy and some of Phil's comments

@@
 \ee
-and
+
 \be
@@
 
-The Monte Carlo method is used to solve the transfer equation numerically as a point of reference for these analytic solutions.
+The Monte Carlo method is used to solve the transfer equation numerically.
 This method is valid at arbitrarily large optical depths, being restricted only by its computational demand which grows in proportion to the number of photons used.
@@
 Frequency redistribution is calculated at each scattering, including the effects of recoil, to obtain the spectrum at the surface of the spherical simulation domain.
-In the comparisons shown in this section, the raw photon data is binned in escape angle and frequency to obtain spectra.
+In the comparisons shown in this section, the raw photon data is binned in frequency to obtain spectra.
 64 bins are used to ensure good statistics and minimal noise in each bin.
-Further details of the Monte Carlo simulation are discussed in \cite{2017ApJ...851..150H}.
+Further details of the Monte Carlo implementation are discussed in \cite{2017ApJ...851..150H}.
 
@@
 Here it is more clear that as the photon initialization frequency becomes further from the optically thick core, the spectrum approaches a delta function in frequency at $\sigma_s$.
+Additionally, since the material is optically thin here, we expect there to be a stronger disagreement between the Monte Carlo and the analytic solution as derivations assumed large optical depths.
 

### 2021-08-20 ms.tex
removing excess line profile definition, changing mentions of "photon source frequency" to just x_s

@@
     \includegraphics{xinit_threepanel_tau1e6.pdf}
-    \caption{Again shifting the initial photon frequency, but at a lower optical depth of $\tau_0 = 10^6$.
+    \caption{Again changing $x_s$, but at a lower optical depth of $\tau_0 = 10^6$.
 The shift in $x$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the bias in the spectrum is much more drastic.
@@
 \ref{fig:sol_mc_xinit_lowtau}, where a $\Delta x_s$ of 6 is a significantly larger fraction of the spectral peak location $(a\tau_0)^{1/3}$.
-Here it is more clear that as the photon initialization frequency becomes further from the optically thick core, the spectrum approaches a delta function in frequency at $\sigma_s$.
+Here it is more clear that as $x_s$ becomes further from the optically thick core, the spectrum approaches a delta function in frequency at $\sigma_s$.
 Additionally, since the material is optically thin here, we expect there to be a stronger disagreement between the Monte Carlo and the analytic solution as derivations assumed large optical depths.
@@
     \caption{$H_{\rm bc}$ solutions shown at three line center optical depths, $\tau_0=10^5, 10^7,$ and $10^9$, for photon source frequencies $\sigma_s=0.0, \tau_0, 2\tau_0$.
-Thicker lines indicate larger optical depth, and darker lines indicate a photon source frequency further from line center.
+Thicker lines indicate larger optical depth, and darker lines indicate $\sigma_s$ further from line center.
 The axes are scaled to show that the size of the corrective factor agrees with the predicted $(a\tau_0)^{-1/3}$ scaling.}
@@
 Fig.
-\ref{fig:xinit} shows how the boundary term scales with both optical depth and photon source frequency.
+\ref{fig:xinit} shows how the boundary term scales with both $\tau_0$ and $\sigma_s$.
 The photon initialization frequency (in units of $\sigma$, as in the differential equation) is shifted in integer multiples of $\tau_0$.
@@
 \ee
-where the line profile can be written approximately as $\phi = (2a/\pi)^{1/3}/(3 \Delta |\sigma|^{2/3})$.
+where the line profile is approximated as in Eq.
+\ref{app:rteqn_derivation}\ref{eq:line_profile_wing}.
 When the coefficient on the right hand side is positive, exponential growth or decay solutions are found (evanescence).
@@
 Since the peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$, calculations performed at lower optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core.
-By comparison with Monte Carlo simulations, it is seen that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency is altered, provided a sufficiently large optical depth.
+By comparison with Monte Carlo simulations, it is seen that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency $x_s$ is altered, provided a sufficiently large optical depth $\tau_0$.
 
@@
 The differential equation cannot be solved except with a semi-analytic approach, utilizing an expansion in both space and photon frequency.
-By matching boundary conditions on either side of the photon source frequency, the flux at the surface of the sphere is found as a function of time and photon frequency, expressed as a sum over many eigenmodes $n$ and $m$---spatial and frequency modes, respectively.
+By matching boundary conditions on either side of the photon source frequency $x_s$, the flux at the surface of the sphere is found as a function of $t$ and $\nu$, expressed as a sum over many eigenmodes $n$ and $m$---spatial and frequency modes, respectively.
 Calculating additional spatial eigenmodes provides a more accurate model of the physics nearer to line center, but convergence is slow due to each eigenmode's weak dependence on $n$.

### 2021-08-20 ms.tex
Writing J0 as a sum over spatial modes
fixing Jd

@@
 J_{\rm d} & = & 
-\frac{(\sqrt{6}k^2L)/(16\pi^3 \Delta^3)}{ (k/\Delta)^2\left[ (x-x_{\rm s})^2 + (y-y_{\rm s})^2 + (z-z_{\rm s})^2 \right] + (\sigma - \sigma_{\rm s})^2}.
+\frac{(\sqrt{6}k^2L)/(16\pi^3 \Delta^3)}{ (kr/\Delta)^2 + (\sigma - \sigma_{\rm s})^2}.
 \label{eq:Jd}
@@
 We generalize their solution to allow emission at frequency $\nu_{\rm s}$ away from line center.
-The result is
+The result can be written as a sum over spatial modes,
+\be
+J_0 = \frac{\sqrt{6}}{16\pi} \frac{L}{R^2}\sum_{n=1}^{\infty}n\frac{\sin{\kappa_n r}}{\kappa_n r}\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
+\ee
+which evaluates to
 \be
@@
 In Fig.
-\ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ over-plotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
+\ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown with that of the solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
+The escape probability $P(x)$ is defined as the total luminosity at the surface divided by the source luminosity, or
+\be
+P(x) = \frac{16\pi^2R^2H(x)}{L}
+\ee
 The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.

### 2021-08-20 ms.tex
Adding todo's and comments from Friday meeting

@@
 
-Two solutions will be considered for this problem.
-
-\begin{enumerate}
-    \item a \textbf{J=0 solution} ($\rm H_0$) which includes the delta function source and satisfies $J=0$ at $r=R$,
-    \item the \textbf{bc solution} ($\rm H_{bc}$) that allows the boundary condition $J=\sqrt{3}H$ to be satisfied. %TODO: Shane wants def here? Where?
-\end{enumerate}
-
+Two ~solutions~ will be considered for this problem. % Add the fact that J=J0 + Jbc. Don't refer to them as two different solutions --- they're two parts / pieces of the true solution.
+
+a \textbf{J=0 solution} ($\rm H_0$) which includes the delta function source and satisfies $J=0$ at $r=R$,
+
+the \textbf{bc solution} ($\rm H_{bc}$) that allows the boundary condition $J=\sqrt{3}H$ to be satisfied. 
+% Incorporate into paragraph instead
+
+%TODO: Change the voigt H to be a script H
 Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
@@
 The escape probability $P(x)$ is defined as the total luminosity at the surface divided by the source luminosity, or
-\be
-P(x) = \frac{16\pi^2R^2H(x)}{L}
-\ee
+%When you integrate over d\nu
+\be
+P(x) = \frac{16\pi^2R^2H(R, x)\Delta}{L}
+\ee
+% We have defined this such that Integral of P(x)dx = 1
+% Mention that H is written per dnu (see appendix for exact details)
 The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
@@
 
+% Go through and tell them why you're shifting by integer multiples of tau0. Little abrupt here
+% Motivate why we're doing the plot the way we are in the first few lines. Build it up for a first time reader. Add more motivation!
+% Introduce this by saying the previous figures show that as we go to larger optical depth, the solution appears to get more and more accurate. To more quantitatively explore this, fig 5 shows...
+% Write a thesis statement at the start of your paragraph and tell the reader what this is all about. It's good if the first line describes what the paragraph is about.
 Fig.

### 2021-08-23 ms.tex
Making all edits suggested in reorg.tex

@@
 
-Two ~solutions~ will be considered for this problem. % Add the fact that J=J0 + Jbc. Don't refer to them as two different solutions --- they're two parts / pieces of the true solution.
-
-a \textbf{J=0 solution} ($\rm H_0$) which includes the delta function source and satisfies $J=0$ at $r=R$,
-
-the \textbf{bc solution} ($\rm H_{bc}$) that allows the boundary condition $J=\sqrt{3}H$ to be satisfied. 
-% Incorporate into paragraph instead
-
-%TODO: Change the voigt H to be a script H
+The solution of this problem is split into two pieces: $\rm J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
+The total solution is $J = J_0 + J_{\rm bc}$.
+
 Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
@@
 For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
-$n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+$n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
 
@@
 We obtain the proportionality
-
-%%%% DERIVATION EDITED OUT
-\ifx
-Starting from Eq. \ref{eq:bc2}, we assume $H_{\rm bc} \ll J_{\rm bc}$ such that
-\be
-J_{\rm bc}(R,\sigma) & \approx & \sqrt{3} H_0(R,\sigma).
-\label{eq:bc4}
-\ee
-The Fourier transform for $J_{\rm bc}$ at the surface becomes
-\be
-J_{\rm bc}(R, \sigma) \equiv \int_{-\infty}^{\infty} \frac{ds}{2\pi} e^{is\sigma} A(s)
-\ee
-with Fourier amplitudes
-\be \label{eq:amps}
-A(s) = \sqrt{3} \int_{-\infty}^{\infty} d\sigma e^{-is\sigma} H_0(R, \sigma).
-\ee
-Plugging the expression for $H_0$ in Eq. \ref{eq:H0surf} into Eq. \ref{eq:amps} yields an expression for the Fourier amplitudes
-\be \label{eq:plugged_amps}
-A(s) = \sqrt{3} \int_{-\infty}^\infty d\sigma e^{-is\sigma}\left(\frac{1}{3k\phi(\sigma)}\frac{\sqrt{6}}{32\pi}\frac{L}{\Delta R^3}\frac{1}{1+\cosh \left[\frac{\pi \Delta}{kR} |\sigma - \sigma_i|\right]}\right)
-\ee
-with
-\be
-\phi(\sigma) = \left(\frac{2a}{27\pi}\right)^{1/3}\frac{1}{\Delta |\sigma|^{2/3}}.
-\ee
-With the line center optical depth defined as
-\be \label{eq:tau0}
-\tau_0 = \frac{kR}{\sqrt{\pi}\Delta}
-\ee
-we scale the variables $\sigma$ and $s$ by $\tau_0$, now using characteristic photon frequency $\bar \sigma = \sigma / \tau_0$ and characteristic wavenumber $\bar s = s \tau_0$.
-Eq.
-\ref{eq:plugged_amps} becomes
-\be
-A(\bar s) = \frac{\sqrt{2}}{32\pi}\left(\frac{27\pi}{2}\right)^{1/3}\frac{L}{kR^3}\frac{\tau_0^{5/3}}{a^{1/3}}\int_{-\infty}^\infty d\bar\sigma e^{-i\bar s \bar\sigma} |\bar\sigma^{2/3}|\frac{1}{1+\cosh \left[\sqrt{\pi}|\bar\sigma - \bar\sigma_i|\right]}.
-\ee
-These coefficients are used to evaluate the boundary condition's contribution to the flux (Eq.
-\ref{eq:Hbc}) at the surface of the sphere.
-Dividing this additional flux $H_{\rm bc}$ by the contribution from the $J=0$ solution, $H_0$ (Eq.
-\ref{eq:H0surf}), yields an overall proportionality
-\fi
-
 \be \label{eq:hbc_scaling}
@@
 At very large optical depths, it is expected that the corrective term will be small, but will become increasingly important in less optically thick media.
-
-\ifx
-By replacing the differential operators in Eq.
-\ref{eq:rt_no_destr} with characteristic scales $R$ and $\sigma_0$ and equating the terms on the left-hand side of this equation, a dimensionless scaling relation between frequency and space emerges.
-\be
-\frac{J}{R^2} &=& \left(\frac{k}{\Delta}\right)^2 \frac{J}{\sigma_0^2}
-\ee
-Now, using the line center optical depth (Eq. \ref{eq:tau0}) and the approximation $\sigma(x)=x^3\sqrt{2\pi/27}/a$ introduced in \cite{1973MNRAS.162...43H} for large $x$, we have
-\be
-\frac{\sqrt{2\pi/27}}{a}x_0^3 = \frac{kR}{\Delta} = \sqrt{\pi} \tau_0.
-\ee
-\fi
 
@@
 Solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower line center optical depths where the peak of the spectrum lies near the core and improve for larger optical depths where the spectral peak is well outside of the line core.
+
 \subsection{Comparison to Monte Carlo}
-
-%Brief description of MC code, citing Chenliang's paper.
-Discuss how MC works briefly, reference some papers, talk about problem setup specific to this work.
-Basically want to show that the MC approach in this paper is not new and doesn't need to be justified extensively.
-
 The Monte Carlo method is used to solve the transfer equation numerically.
@@
 We now compare each of the previously-discussed solutions for surface flux with Monte Carlo simulations.
+The escape probability $P(x)$ is defined as the total luminosity at the surface divided by the source luminosity, or
+\be
+P(x) = \frac{16\pi^2R^2H(R, x)\Delta}{L}
+\ee
+This is defined such that $\int P(x)dx = 1$.
+Since $H(r, \nu)$ is implicitly written per $d\nu$, a factor of $\Delta$ gives the expression the correct units.
 In Fig.
 \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown with that of the solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
-The escape probability $P(x)$ is defined as the total luminosity at the surface divided by the source luminosity, or
-%When you integrate over d\nu
-\be
-P(x) = \frac{16\pi^2R^2H(R, x)\Delta}{L}
-\ee
-% We have defined this such that Integral of P(x)dx = 1
-% Mention that H is written per dnu (see appendix for exact details)
 The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
@@
 
-% Go through and tell them why you're shifting by integer multiples of tau0. Little abrupt here
+% TODO: Go through and tell them why you're shifting by integer multiples of tau0. Little abrupt here
 % Motivate why we're doing the plot the way we are in the first few lines. Build it up for a first time reader. Add more motivation!
@@
 
+\subsection{Dependence on Source Frequency}
+
+\section{Acceleration Schemes}
+
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.
+The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.
+These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core.
+Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.
+
+A second class of methods are hybrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
+This involves designating sufficiently optically thick simulations cells for computation via a finite difference representation of the radiation transfer equation.
+This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.
+For the resonant scattering problem, where the opacity is a strong function of frequency, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
+
+A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M, 2010A&A...520A..70R}.
+In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
+An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation within a uniform sphere.
+A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution.
+
+%The need for accurate distributions from which to draw outgoing photons' properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
+In addition, a semi-analytic solution to time-dependent \lya diffusion through the same medium is explored to quantify how long the photons are expected to spend in the domain before escaping.
+These solutions will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.
+
+Radiation forces due to \lya transfer have been calculated in \citet{1976ApJ...208..286W} in plane-parallel geometry.
+However, these solutions are limited to optical depths below $2.5 \times 10^3$.
+In the grid cells of a radiation hydrodynamic simulation, it would be necessary to calculate the radiation force on each cell face due to \lya at line center optical depths of up to 1 million or more.
+A discussion of Monte Carlo code acceleration for optical depths as large as these in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
+In terms of the time dependence, \citet{1994ApJ...427..603R} introduce an ansatz for the Fokker-Planck diffusion equation in order to quantify the relaxation timescale necessary to reach a quasi-static solution.
+Notably, the full Voigt function is used for the line profile rather than restricting scattering to the damping wing only.
+
 \section{Summary and Conclusions}
@@
 \be
-\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{H(x,a)}{\sqrt{\pi} \Delta}
+\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{\mathcal{H}(x,a)}{\sqrt{\pi} \Delta}
 = k \phi   
 \ee
-where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $H(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = H(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
 The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section.
@@
 \be
-\langle u_\parallel^n \rangle(x,a) & = & \frac{a/\pi }{H(x,a)} \int 
+\langle u_\parallel^n \rangle(x,a) & = & \frac{a/\pi }{\mathcal{H}(x,a)} \int 
 \frac{du_\parallel u_\parallel^n e^{-u_\parallel^2}  }{(x-u_\parallel)^2 + a^2}.
@@
 \ref{eq:rteqn} that corresponds to excitation of the atom.
-The terms involvingfrequency derivatives of $\vec{H}$, if carried through the calculation,end up giving terms smaller than then largest terms by a factor of $1/x^2$, which is small on the line wing.
+The terms involving frequency derivatives of $\vec{H}$, if carried through the calculation,end up giving terms smaller than then largest terms by a factor of $1/x^2$, which is small on the line wing.
 These terms are ignored from here on.

### 2021-08-30 ms.tex
Notes on discussion and summary section added
Changing \rfloor to \rvert in equation 33

@@
 J_{\rm d} & = & 
-\frac{(\sqrt{6}k^2L)/(16\pi^3 \Delta^3)}{ (kr/\Delta)^2 + (\sigma - \sigma_{\rm s})^2}.
+\left(\frac{\sqrt{6}k^2L}{16\pi^3 \Delta^3}\right)\left(\frac{1}{(kr/\Delta)^2 + (\sigma - \sigma_{\rm s})^2}\right).
 \label{eq:Jd}
@@
 The result can be written as a sum over spatial modes,
-\be
+\be \label{eq:J0_sum}
 J_0 = \frac{\sqrt{6}}{16\pi} \frac{L}{R^2}\sum_{n=1}^{\infty}n\frac{\sin{\kappa_n r}}{\kappa_n r}\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
@@
 \ref{fig:xinit} shows how the boundary term scales with both $\tau_0$ and $\sigma_s$.
-The photon initialization frequency (in units of $\sigma$, as in the differential equation) is shifted in integer multiples of $\tau_0$.
-For clarity, only the positive side of the spectrum is shown.
+The photon initialization frequency $\sigma_s$ is shifted in integer multiples of $\tau_0$.
+For clarity, only the $\sigma > 0$ side of the spectrum is shown.
 From Eq.
@@
 \be
-J(r,\sigma,t) & = &  -j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t}J(n,\sigma,-i\gamma)
-\nonumber \\ & \simeq & j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} 
-\nonumber \\ & \simeq & j_0(\kappa_n r)  J_{nm}(\sigma) e^{-\gamma_{nm}t}.
+J(r,\sigma,t) & = &  -\sum_{n=1}^{\infty}j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t}J(n,\sigma,-i\gamma)
+\nonumber \\ & \simeq & \sum_{n=1}^{\infty}j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} 
+\nonumber \\ & \simeq & \sum_{n=1}^{\infty}j_0(\kappa_n r)  J_{nm}(\sigma) e^{-\gamma_{nm}t}.
 \ee
@@
 \be
-\frac{dj_0(\kappa_n r)}{dr} \rfloor_R & =& \frac{d}{dr}  \rfloor_R \left( \frac{\sin(\kappa_n r)}{\kappa_n r} \right)
-=  \left( \frac{\cos(\kappa_n R)}{R} - \frac{\sin(\kappa_n R)}{\kappa_n R^2} \right)\rfloor_R
+\frac{dj_0(\kappa_n r)}{dr} \bigg\rvert_R & =& \frac{d}{dr} \left( \frac{\sin(\kappa_n r)}{\kappa_n r} \right)\bigg\rvert_R
+=  \left( \frac{\cos(\kappa_n R)}{R} - \frac{\sin(\kappa_n R)}{\kappa_n R^2} \right)
 \nonumber \\ & = & \frac{(-1)^n}{R},
@@
 In Fig.
-\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum'').
+\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq.
+\ref{eq:J0_sum}.
 This graphic illustrates the physics modeled by each variable in the expansion.
@@
 
-\subsection{Dependence on Source Frequency}
-
-\section{Acceleration Schemes}
-
+\subsection{Emission Away From Line Center}
+
+\section{Discussion}
+% How can you apply the solution?
+Talk about it as an application of the problem that justifies going through the effort of implementing it.
+It reads like an introduction right now, but we can modify it to include less detail.
+% Don't explain exactly what hybrid diffusion models are.
+Remove that paragraph.
+Put a ref in for Smith and Densmore - lot of applications to speed up lya, including core skipping & hybrid diffusion methods.
+Another method that's been widely applied is modified random walk methods, but htose require a solution of transfer in a sphere.
+So, the primary application of this calcuation is to develop that random walk model that will be used in future applicaitons.
+Keep reference to Ahn et al, since they did basically this but not in spherical symmetry.
+% Discussion section: tlak about the differences between what we find and the other results from other papers. Add this as well. 
+% First part of discussion - compare to previous work and summarize differences. Move some of the comparison with Dijkstra to the discussion.
+% Second part - application of solution
+% Move summary to discussion - currently written more like a discussion. 
+% Write summary like it's a complement to the abstract. Cliffnotes version for people who don't want to read it.
+% We re-examined previous solutions, noting that they use this incorrect boundary conditoin.
+We re-examined the problem with an appropriate bc, examine spectral and time dpeendence, key results are these, plan to use in a MC acceleration scheme in the future.
+Comment on comparison with MC.
+One, maybe two paragraphs.
 There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.

### 2021-08-30 ms.tex
Adding the rest of the time dependent section edits from Shane

@@
 \ee
-These coefficients can have either sign depending on the value of $n$.
+These coefficients are negative for odd values of $n$ and positive for even $n$.
 The size of each contribution scales roughly as $0.5/(m+1/8)^{2/3}$, with a very weak dependence on $n$.
-This indicates the need for a large number of $n$ and $m$ to converge, i.e., it takes roughly ten times as many $m$ modes to reduce the size of $P_{nm}$ by a factor of ${\sim}$5.
-Numerical convergence would be obtained only when the size of additional $P_{nm}$ are negligible in the sum.
+This indicates the need for a large number of $n$ and $m$ to converge, i.e., it takes roughly ten times as many $m$ modes to reduce the size of $P_{nm}$ by a factor of ${\sim}$5, so convergence is slow.
 
@@
 \be
-J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,\gamma_1)  - J(n,\sigma,\gamma_2) }{ 1/(\gamma_{nm}-\gamma_1) - 1/(\gamma_{nm}-\gamma_2)}.
+J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,-i\gamma_1)  - J(n,\sigma,-i\gamma_2) }{ 1/(\gamma_{nm}-\gamma_1) - 1/(\gamma_{nm}-\gamma_2)}.
 \ee
@@
 The oscillations of various modes must cancel perfectly to recreate the form of the solution in Eq.
-\ref{eq:Jrsigmat}, so many modes $m$ and $n$ are required for sufficient numerical precision in the final result.
+\ref{eq:Jrsigmat}, so many modes $m$ and $n$ are required for convergence to the correct solution.
 Too few (or imprecisely-calculated) modes creates ``ringing'' in the function that indicates the presence of imperfect cancellations in the positive and negative contributions of individual poles.
@@
 This occurs on the line wings.
-When the coefficient on the right hand side is negative, oscillatory solutions are found (propagation), which occurs in the line core.
+When the coefficient on the right hand side is negative, oscillatory solutions are found (propagation), which occurs near the line core.
 The boundary between propagation and evanescence occurs at the turning point, given by
@@
 \ref{eq:dEdtdnu} over all times should give a distribution for the emitted frequencies.
-It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the $J=0$ steady-state spectrum (Eq.
+It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the $H_0$ steady-state spectrum (Eq.
 \ref{eq:H0surf}).
@@
 In Fig.
-\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq.
+\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as TODO: in Eq.
 \ref{eq:J0_sum}.

### 2021-08-30 ms.tex
Cleaning up equations in Hd and H0 derivation, adding sum representations of each solution
Changing reference to H0surf_sum

@@
 \be \label{eq:J0_sum}
-J_0 = \frac{\sqrt{6}}{16\pi} \frac{L}{R^2}\sum_{n=1}^{\infty}n\frac{\sin{\kappa_n r}}{\kappa_n r}\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
-\ee
-which evaluates to
-\be
-J_0 & = & \left( \frac{\sqrt{6}L}{32\pi^2 \Delta} \right)
-\left( \frac{1}{Rr} \right)
+J_0 = \frac{\sqrt{6}L}{16\pi \Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\frac{\sin{\kappa_n r}}{\kappa_n r}\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
+\ee
+\be \label{eq:H0_sum}
+H_0 = - \frac{1}{3k\phi} \frac{\partial J_0}{\partial r} = -\frac{1}{3k\phi}\frac{\sqrt{6}L}{16\pi\Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\left(\frac{\cos{\kappa_n r}}{r} - \frac{\sin{\kappa_n r}}{\kappa_n r^2}\right)\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
+\ee
+which evaluate to
+\be
+J_0 & = & \frac{\sqrt{6}L}{32\pi^2 \Delta}
+\frac{1}{Rr}
 \left( 
@@
 \be
-H_0 & = & \left( \frac{1}{3k\phi} \right)
-\left( \frac{\sqrt{6}L}{32\pi^2 \Delta} \right)
-\left( \frac{1}{Rr^2} \right)
+H_0 & = &\frac{1}{3k\phi}
+\frac{\sqrt{6}L}{32\pi^2 \Delta}
+\frac{1}{Rr^2}
 \left( 
@@
 \be
-H_0(R, \sigma) & = & \left( \frac{1}{3k\phi} \right)
-\left( \frac{\sqrt{6}L}{32\pi \Delta} \right)
-\left( \frac{1}{R^3} \right)
+H_0(R, \sigma) & = & - \frac{1}{3k\phi}
+\frac{\sqrt{6}L}{16\pi \Delta}
+\frac{1}{R^3}
+\sum_{n=1}^{\infty} 
+n (-1)^n \exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)}
+,
+\label{eq:H0surf_sum}
+\ee
+or
+\be
+H_0(R, \sigma) & = &  \frac{1}{3k\phi}
+\frac{\sqrt{6}L}{32\pi \Delta}
+\frac{1}{R^3}
 \left( 
@@
 In Fig.
-\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as TODO: in Eq.
-\ref{eq:J0_sum}.
+\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq.
+\ref{eq:H0surf_sum}.
 This graphic illustrates the physics modeled by each variable in the expansion.

### 2021-08-30 ms.tex
Adding more motivation to fig 5 paragraph

@@
 \ref{fig:sol_mc_xinit} shows calculations performed for three initial photon frequencies $\rm x_s = 0.0, 6.0$, and $12.0$ for a line center optical depth of $\tau_0=10^7$.
-The bias in frequency distribution is slight for $\rm x_s = 6.0$ where the line profile is still relatively large and emitted photons remain trapped in the core, but the increase in spatial diffusion is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core.
+The bias in frequency distribution is slight for $\rm x_s = 6.0$ where the line profile is still relatively large and emitted photons remain trapped in the core, but the increase in mean free path is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core.
 It is seen here that the discrepancy between the Monte Carlo data and $H_0$ (effectively the scale of the corrective $H_{\rm bc}$ term) becomes larger as $\rm x_s$ increases.
-Thus, for sufficiently large optical depths and emission away from line center, the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows.
-The bias in the escaping spectrum is much more noticeable at lower optical depths, shown in Fig.
-\ref{fig:sol_mc_xinit_lowtau}, where a $\Delta x_s$ of 6 is a significantly larger fraction of the spectral peak location $(a\tau_0)^{1/3}$.
-Here it is more clear that as $x_s$ becomes further from the optically thick core, the spectrum approaches a delta function in frequency at $\sigma_s$.
+Thus, for sufficiently large $\tau_0$ and emission away from line center $x_s \neq 0$, the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows.
+The bias in the escaping spectrum is substantial at lower optical depths, shown in Fig.
+\ref{fig:sol_mc_xinit_lowtau}, where a $\Delta x_s$ of 6 is a larger fraction of the spectral peak location $(a\tau_0)^{1/3}$.
+It is clear from the figure that as $x_s$ becomes further from the optically thick core, the spectrum approaches a delta function in frequency at $\sigma_s$.
 Additionally, since the material is optically thin here, we expect there to be a stronger disagreement between the Monte Carlo and the analytic solution as derivations assumed large optical depths.
@@
 
-% TODO: Go through and tell them why you're shifting by integer multiples of tau0. Little abrupt here
-% Motivate why we're doing the plot the way we are in the first few lines. Build it up for a first time reader. Add more motivation!
-% Introduce this by saying the previous figures show that as we go to larger optical depth, the solution appears to get more and more accurate. To more quantitatively explore this, fig 5 shows...
-% Write a thesis statement at the start of your paragraph and tell the reader what this is all about. It's good if the first line describes what the paragraph is about.
-Fig.
-\ref{fig:xinit} shows how the boundary term scales with both $\tau_0$ and $\sigma_s$.
-The photon initialization frequency $\sigma_s$ is shifted in integer multiples of $\tau_0$.
+The previous figures show that as $\tau_0$ increases, $H_0$ appears to become more accurate.
+There is agreement between the Monte Carlo and $H_0$ when $H_{\rm bc}$ is small which motivates a quantitative examination of how the boundary term $H_{\rm bc}$ scales with both $\tau_0$ and $\sigma_s$, shown in Fig.
+\ref{fig:xinit}.
+In this graphic, the photon initialization frequency $\sigma_s$ is shifted in integer multiples of $\tau_0$ such that each curve at a fixed $\sigma_s$ will overlap.
 For clarity, only the $\sigma > 0$ side of the spectrum is shown.
 From Eq.
-\ref{eq:hbc_scaling}, the size of the correction should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-This factor has been scaled out of the figure such that solutions for different optical depths and the same source frequency $\sigma_s$ should show close agreement in scale on the figure if the relation holds.
+\ref{eq:hbc_scaling}, it is expected that the size of the correction $H_{\rm bc}$ should become smaller with larger optical depths following a $(a\tau_0)^{-1/3}$ scaling.
+This factor has been scaled out of the figure such that solutions for different optical depths and the same source frequency $\sigma_s$ should show close agreement in scale on the figure's vertical axis if the relation holds.
 Indeed, the scaled solutions converge as the optical depth becomes larger, indicating general agreement with the $(a\tau_0)^{1/3}$ scaling.
-The remaining discrepancy present is due to the width of the Doppler core with respect to the peak of the spectrum; at lower depths, this causes the assumptions about the functional form of the line profile to break down.
+The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ is due to the width of the Doppler core with respect to the peak of the spectrum; at lower depths, this causes the assumptions about the functional form of the line profile to break down.
 From this, we conclude that the errors introduced by the incorrect separation of variables in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others are proportional to $(a\tau_0)^{1/3}$, where $a$ is the ratio of natural to Doppler broadening and $\tau_0$ is the optical depth at line center.
-An additional amount of error of order $(a\tau_0)^{1/3}$ is introduced as the photon frequency $\sigma_s$ from line center is increased by a factor of $\tau_0$.
+Furthermore, an additional amount of error of order $(a\tau_0)^{1/3}$ is introduced as the photon frequency $\sigma_s$ from line center is increased by a factor of $\tau_0$.
 

### 2021-08-31 ms.tex
Updates to figures

@@
 Photons are initialized with $\rm x = 0.0$.
-In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.
+In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$ to examine the contributions of both positive and negative pieces.
 Residuals of each solution to the Monte Carlo data points are shown in the third panel.}
@@
 It is evident that the divergent solution $H_{\rm d}$ fails in the line wings.
-The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum.
+The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, it adequately corrects for the apparent excess of flux in the peaks of the spectrum.
 This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S} where the discrepancy is particularly noticeable for line center optical depths of $\tau_0=10^5$ and $10^6$.
@@
     \includegraphics{tau_threepanel.pdf}
-    \caption{Increasing the line center optical depth.
-Shown here are $\tau_0 = 10^5, 10^6, 10^7$ with the $x$ and $y$ axes scaled by the characteristic frequency diffusion scale $(a\tau_0)^{1/3}$.
+    \caption{The same spectrum as in Fig.
+\ref{fig:sol_mc_residual_0}, but for three different line center optical depths $\tau_0 = 10^5, 10^6, 10^7$ with the $x$ and $y$ axes scaled by the characteristic frequency diffusion scale $(a\tau_0)^{1/3}$.
 Photons are initialized with $\rm x = 0.0$ in each case.}
@@
 Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency.
-The optical depth at each of these source frequencies is $\tau_s = 10^7, 77.2,$ and $18.6$, respectively.}
+The optical depth at each of these source frequencies is $\tau_s = 10^7, 77,$ and $19$, respectively.}
     \label{fig:sol_mc_xinit}
@@
     \centering
-    \includegraphics{xinit.pdf}
+    \includegraphics[width=\textwidth]{xinit.pdf}
     \caption{$H_{\rm bc}$ solutions shown at three line center optical depths, $\tau_0=10^5, 10^7,$ and $10^9$, for photon source frequencies $\sigma_s=0.0, \tau_0, 2\tau_0$.
@@
 \ref{fig:xinit}.
-In this graphic, the photon initialization frequency $\sigma_s$ is shifted in integer multiples of $\tau_0$ such that each curve at a fixed $\sigma_s$ will overlap.
+In this graphic, the photon initialization frequency $\sigma_s$ is shifted in integer multiples of $\tau_0$ such that $\sigma_s$ falls near the peak of the spectrum for each $\tau_0$.
 For clarity, only the $\sigma > 0$ side of the spectrum is shown.

### 2021-09-01 ms.tex
Starting to rework discussion section

@@
 % Second part - application of solution
+
+The solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere originally derived by \cite{2006ApJ...649...14D} (called $H_0$ here) has been generalized to allow a monochromatic source of photons with frequencies away from line center, and a correction to the incorrect $J=0$ surface boundary condition is made.
+This correction allows the proper condition $J=\sqrt{3}H$ to be satisfied, and comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$ which are solved using a continuous Fourier expansion in frequency.
+Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
+In practice, the continuous expansions are discretized and the Fourier coefficients solved for via a matrix equation.
+The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$ where $a$ is the damping parameter and $\tau_0$ is the line-center optical depth.
+Thus, for very large optical depths, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower optical depths.
+Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
+The peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$; as such, calculations performed at low optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core of the line profile.
+By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions %and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency $x_s$ is altered,
+provided a sufficiently large optical depth $\tau_0$.
+Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition, such as \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others.
+The surface boundary condition correction $H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which suggests the previously cited solutions are too large at the spectral peaks and too small further out in the wing.
+This appears to be the consequence of not enforcing the correct frequency-dependent boundary conditions at the surface of the medium.
+
+The primary application of this solution for resonance-line radiation transfer at large optical depths is to develop a computationally efficient random walk model in spherical geometry.
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.
+The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.
+These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core, but
+
+Previous work by \citet{2002ApJ...567..922A,2015MNRAS.449.4336S} discussed Monte Carlo code acceleration for optical depths as large as these in a uniform plane-parallel medium with no absorption, but these calculations would need to be generalized to spherical symmetry in order to construct a model of resonant scattering in exoplanet atmospheres as discussed in Section \ref{sec:intro}.
+
+   Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.
+
+A second class of methods are hybrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
+This involves designating sufficiently optically thick simulations cells for computation via a finite difference representation of the radiation transfer equation.
+This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.
+For the resonant scattering problem, where the opacity is a strong function of frequency, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
+
+A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M, 2010A&A...520A..70R}.
+In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
+An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation within a uniform sphere.
+A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution.
+
+%The need for accurate distributions from which to draw outgoing photons' properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
+In addition, a semi-analytic solution to time-dependent \lya diffusion through the same medium is explored to quantify how long the photons are expected to spend in the domain before escaping.
+These solutions will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.
+
+Radiation forces due to \lya transfer have been calculated in \citet{1976ApJ...208..286W} in plane-parallel geometry.
+However, these solutions are limited to optical depths below $2.5 \times 10^3$.
+In the grid cells of a radiation hydrodynamic simulation, it would be necessary to calculate the radiation force on each cell face due to \lya at line center optical depths of up to 1 million or more.
+A discussion of Monte Carlo code acceleration for optical depths as large as these in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
+In terms of the time dependence, \citet{1994ApJ...427..603R} introduce an ansatz for the Fokker-Planck diffusion equation in order to quantify the relaxation timescale necessary to reach a quasi-static solution.
+Notably, the full Voigt function is used for the line profile rather than restricting scattering to the damping wing only.
+
+\section{Summary and Conclusions}
+
 % Move summary to discussion - currently written more like a discussion. 
@@
 One, maybe two paragraphs.
-There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.
-The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.
-These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core.
-Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.
-
-A second class of methods are hybrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
-This involves designating sufficiently optically thick simulations cells for computation via a finite difference representation of the radiation transfer equation.
-This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.
-For the resonant scattering problem, where the opacity is a strong function of frequency, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
-
-A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M, 2010A&A...520A..70R}.
-In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
-An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation within a uniform sphere.
-A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution.
-
-%The need for accurate distributions from which to draw outgoing photons' properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
-In addition, a semi-analytic solution to time-dependent \lya diffusion through the same medium is explored to quantify how long the photons are expected to spend in the domain before escaping.
-These solutions will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.
-
-Radiation forces due to \lya transfer have been calculated in \citet{1976ApJ...208..286W} in plane-parallel geometry.
-However, these solutions are limited to optical depths below $2.5 \times 10^3$.
-In the grid cells of a radiation hydrodynamic simulation, it would be necessary to calculate the radiation force on each cell face due to \lya at line center optical depths of up to 1 million or more.
-A discussion of Monte Carlo code acceleration for optical depths as large as these in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
-In terms of the time dependence, \citet{1994ApJ...427..603R} introduce an ansatz for the Fokker-Planck diffusion equation in order to quantify the relaxation timescale necessary to reach a quasi-static solution.
-Notably, the full Voigt function is used for the line profile rather than restricting scattering to the damping wing only.
-
-\section{Summary and Conclusions}
-
-The solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere originally derived by \cite{2006ApJ...649...14D} has been generalized to allow a monochromatic source of photons with frequencies away from line center.
-A correction to the $J=0$ surface boundary condition which allows the proper condition $J=\sqrt{3}H$ to be satisfied comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$, which are solved using a continuous Fourier expansion in frequency.
-Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
-In practice, the continuous expansions are discretized and the Fourier coefficients solved for via a matrix equation.
-The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$ where $a$ is the damping parameter and $\tau_0$ is the line-center optical depth.
-Thus, for very large optical depths, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower optical depths.
-Additionally, since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
-Since the peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$, calculations performed at lower optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core.
-By comparison with Monte Carlo simulations, it is seen that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency $x_s$ is altered, provided a sufficiently large optical depth $\tau_0$.
 

### 2021-09-01 ms.tex
finishing edits to discussion and summary

@@
 
-The solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere originally derived by \cite{2006ApJ...649...14D} (called $H_0$ here) has been generalized to allow a monochromatic source of photons with frequencies away from line center, and a correction to the incorrect $J=0$ surface boundary condition is made.
+Models of heating and escape of hydrogen gas in exoplanet atmospheres can be constructed with an accurate treatment of resonant scattering of \lya in spherical geometry.
+The Monte Carlo method can be used for this problem, but requires a solution of radiative transfer in a sphere and is limited by its high computational demand for large optical depths where there are many photon scatterings before escape.
+The primary goal of this work is to present a solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere.
+We have generalized a solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center, and we have made a correction to the incorrect $J=0$ surface boundary condition.
 This correction allows the proper condition $J=\sqrt{3}H$ to be satisfied, and comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$ which are solved using a continuous Fourier expansion in frequency.
@@
 Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition, such as \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others.
-The surface boundary condition correction $H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which suggests the previously cited solutions are too large at the spectral peaks and too small further out in the wing.
+The surface boundary condition correction $H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which suggests the previously cited solutions are too large at the spectral peaks and too small further out in the wing, where the error scales approximately as $(a\tau_0)^{-1/3}$.
 This appears to be the consequence of not enforcing the correct frequency-dependent boundary conditions at the surface of the medium.
 
-The primary application of this solution for resonance-line radiation transfer at large optical depths is to develop a computationally efficient random walk model in spherical geometry.
-There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.
-The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.
-These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core, but
-
-Previous work by \citet{2002ApJ...567..922A,2015MNRAS.449.4336S} discussed Monte Carlo code acceleration for optical depths as large as these in a uniform plane-parallel medium with no absorption, but these calculations would need to be generalized to spherical symmetry in order to construct a model of resonant scattering in exoplanet atmospheres as discussed in Section \ref{sec:intro}.
-
-   Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.
-
-A second class of methods are hybrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}.
-This involves designating sufficiently optically thick simulations cells for computation via a finite difference representation of the radiation transfer equation.
-This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.
-For the resonant scattering problem, where the opacity is a strong function of frequency, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.
-
-A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M, 2010A&A...520A..70R}.
-In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.
-An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation within a uniform sphere.
-A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution.
-
-%The need for accurate distributions from which to draw outgoing photons' properties motivates this work; namely, an analytic solution to the steady-state problem of \lya resonant scattering in spherical geometry.
-In addition, a semi-analytic solution to time-dependent \lya diffusion through the same medium is explored to quantify how long the photons are expected to spend in the domain before escaping.
-These solutions will be shown to accurately represent the photon distributions in frequency and time-to-escape at the surface of a spherical volume of gas, highlighting their potential for use as a Monte Carlo accelerant in magnetohydrodynamic calculations of phenomena involving \lya resonance-line radiation.
-
-Radiation forces due to \lya transfer have been calculated in \citet{1976ApJ...208..286W} in plane-parallel geometry.
-However, these solutions are limited to optical depths below $2.5 \times 10^3$.
-In the grid cells of a radiation hydrodynamic simulation, it would be necessary to calculate the radiation force on each cell face due to \lya at line center optical depths of up to 1 million or more.
-A discussion of Monte Carlo code acceleration for optical depths as large as these in a uniform, plane-parallel medium with no absorption is presented in  \citet{2002ApJ...567..922A,2015MNRAS.449.4336S}.
-In terms of the time dependence, \citet{1994ApJ...427..603R} introduce an ansatz for the Fokker-Planck diffusion equation in order to quantify the relaxation timescale necessary to reach a quasi-static solution.
-Notably, the full Voigt function is used for the line profile rather than restricting scattering to the damping wing only.
-
-\section{Summary and Conclusions}
-
-% Move summary to discussion - currently written more like a discussion. 
-% Write summary like it's a complement to the abstract. Cliffnotes version for people who don't want to read it.
-% We re-examined previous solutions, noting that they use this incorrect boundary conditoin.
-We re-examined the problem with an appropriate bc, examine spectral and time dpeendence, key results are these, plan to use in a MC acceleration scheme in the future.
-Comment on comparison with MC.
-One, maybe two paragraphs.
-
-The time-dependence of the problem is solved under a $J=0$ boundary condition to characterize the distribution of photon escape times.
+Additionally, the time-dependence of the problem is solved under a $J=0$ boundary condition to characterize the distribution of photon escape times.
 The differential equation cannot be solved except with a semi-analytic approach, utilizing an expansion in both space and photon frequency.
@@
 However, a fitting function dependent on parameters $a$ and $\tau_0$ is found that adequately represents the escape time distribution within these constraints.
-When calculated as a cumulative distribution function using a rejection method, the fit can be used to sample photon escape times directly rather than computing their travel times by the Monte Carlo method.
-As will be shown in future work, these calculations can be implemented as an acceleration scheme for Monte Carlo resonance-line radiation transfer at optical depths that would nominally be computationally prohibitive.
+The cumulative distribution function could be calculated using a rejection method, which would then be used to sample photon escape times directly rather than computing their travel times by the Monte Carlo method.
+
+This leads in to the primary application of this work: to develop a computationally efficient random walk model in spherical geometry.
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}.
+Another approach with wide application is modified random walk methods, such as those discussed in \citet{2002ApJ...567..922A,2015MNRAS.449.4336S} in which Monte Carlo code acceleration is performed for large optical depths in a uniform plane-parallel medium with no absorption.
+These calculations would need to be generalized to spherical symmetry in order to construct a models of resonant scattering in exoplanet atmospheres as discussed in Section \ref{sec:intro}.
+The underlying principle is the same, however: an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation.
+A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution, but this solution of course does not use the correct frequency-dependent boundary condition at the surface of the sphere.
+Furthermore, to perform a full radiation hydrodynamic simulation with Monte Carlo acceleration, it will be necessary to calculate radiation forces due to \lya transfer on the faces of each grid cell in the simulation.
+Similar calculations have been done in \citet{1976ApJ...208..286W} in plane-parallel geometry.
+However, these solutions are limited to optical depths below $2.5 \times 10^3$.
+For this work, it would be necessary to model line center optical depths of up to 1 million or more.
+Such considerations will be taken in future work while developing this solution into a 1D hydrodynamic simulation using radiation forces from accelerated Monte Carlo \lya transfer.
+
+\section{Summary}
+
+We have examined previous solutions to \lya transfer in the limit of large optical depth, noting that the separation of variables and treatment of the boundary condition in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others does not produce a valid solution to the transfer equation.
+Here, we have derived the solution in spherical geometry with an appropriate treatment of the surface boundary condition as a frequency-dependent quantity, examining the spectral and time dependence of the resulting equations.
+The key result is that the errors in the previously-cited works have been quantified via a corrective boundary term, $H_{\rm bc}$, which resolves an excess in flux at the spectral peak and a deficit in the line wing of the calculated spectrum of \lya radiation as compared with Monte Carlo.
+The size of $H_{\rm bc}$ diminishes at larger optical depths, following a predictable $(a\tau_0)^{-1/3}$ scaling.
+Introducing time-dependence back into the transfer equation leads to another solution which is obtained with a discretized eigenfunction expansion and solved numerically.
+We demonstrate that it agrees with the steady-state result when integrated over time, though its rate of numerical convergence is quite slow and requires a sum over many modes to become accurate.
+The time-dependent solution is utilized to create wait-time distributions for photons escaping the sphere of optically-thick hydrogen gas, which can be sampled in lieu of direct Monte Carlo simulations that would ordinarily be computationally demanding.
+We compare the calculations from the time-dependent solution with Monte Carlo for a sample of line-center optical depths, noting general agreement in the resulting escape time distributions.
+In future work, these distributions will be fitted and used to accelerate Monte Carlo \lya transfer at large optical depths with potential applications in radiation hydrodynamic simulations of the atmospheres of exoplanets.
 

### 2021-09-10 ms.tex
Fixing Eq. 15, removing unclear middle step
Implementing phil's edits to the abstract

@@
 
-The solution of the radiative transfer equation for resonant scattering of Lyman $\alpha$ photons for a uniform sphere of constant gas density is found in the limit of large line center optical depth.
-A monochromatic source of photons is assumed at the center of the sphere, and the intensity within the sphere and at the surface is found with the Eddington approximation for the angular dependence.
-The solution can be represented as a sum of two terms: a semi-analytic solution of the homogeneous equation which is required for the mean intensity $J=0$ at the surface, and a solution of the homogeneous equation which enforces the correct, zero-ingoing intensity boundary conditions at the surface.
-It is the compact analytic form as well as the piece accounting for the correct, frequency-dependent boundary condition that is novel in this study.
-The analytic solution is compared to numerical solutions with the Monte-Carlo method, which are valid at arbitrary optical depth.
-It is shown that the scale of corrective term depends on the line center optical depth, accounting for discrepancies in the spectra of previous studies that used a $J=0$ boundary condition.
-Separately, the time-dependence of the diffusion equation is expressed using an eigenfunction expansion and solved numerically to characterize the time-to-escape of photons initialized at the center of the sphere.
-It is shown that the semi-analytic calculation agrees well with the Monte Carlo escape time distribution, converging for large line center optical depths around $\tau_0=10^7$.
-A fitting function for this distribution is found which can be sampled to accelerate Monte Carlo radiation transfer calculations at very large optical depths.
+The solution of the radiative transfer equation for resonant scattering of Lyman $\alpha$ photons is explored in spherical geometry.
+A monochromatic source of photons is assumed at the center of a uniform sphere of constant gas density.
+The intensity within the sphere and at its surface is found in the limit of large line-center optical depth using the Eddington approximation for the angular dependence.
+Two specific problems are studied: a steady source and an impulsive source.
+For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the homogeneous equation with the mean intensity $J=0$ at the surface, and a novel, semi-analytic solution of the homogeneous equation which enforces the correct, zero-ingoing intensity boundary conditions at the surface.
+This solution is compared to that of the Monte-Carlo method, which is valid at arbitrary optical depth.
+It is shown that the size of corrective term depends on the line center optical depth, and may explain discrepancies in previous studies that used a $J=0$ boundary condition.
+For the impulsive problem, the time dependence, spatial dependence, and photon frequency dependence of the diffusion equation is expressed using an eigenfunction expansion and solved numerically to characterize the escape time distribution and spectra of photons initialized at the center of the sphere.
+It is shown that the lowest-order eigenfrequency of the semi-analytic calculation agrees well with the decay constant of the Monte Carlo escape time distribution at line-center optical depths above ${\sim} 10^7$.
+A fitting function for the distribution is found which can be sampled to accelerate Monte Carlo radiation transfer calculations at very large optical depths.
 
@@
 \be
-J_{\rm bc}(R,\sigma) - \sqrt{3} H_{\rm bc}(R,\sigma) & = & 
-J_{0}(R,\sigma) + \frac{1}{\sqrt{3}k\phi} \frac{\partial J_{0}(R,\sigma)}{\partial r} = 
+J_{\rm bc}(R,\sigma) - \sqrt{3} H_{\rm bc}(R,\sigma) & = 
 \sqrt{3} H_0(R,\sigma).

### 2021-09-10 ms.tex
Page 1 edits finished

@@
 
-%%% FOR DRAFTING: REMOVE AFTER PAPER IS COMPLETE!
-\usepackage{xcolor}
-\newcommand{\todo}[1]{\textcolor{red}{#1}}
-\newcommand{\proposed}[1]{\textcolor{blue}{#1}}
-
 \received{}
@@
 
-The outer layers of planetary atmospheres are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation and regulate the escape of gas into space.
-In atmospheres with thick layers of atomic hydrogen, stellar Lyman Alpha (Ly$\alpha$) radiation is especially important in this process as the optical depth at line center is large.
-Ionization and subsequent recombination can generate \lya within the planet's atmosphere, dissociating molecules in lower layers and causing heating by collisional de-excitation.
-\lya can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy.
-
-Hubble Space Telescope (HST) observations with STIS have found large \lya transit depths around a handful of exoplanets, indicating an extended distribution of hydrogen: \citet{2003Natur.422..143V, 2012A&A...543L...4L, 2012A&A...547A..18E, 2015Natur.522..459E,  2017A&A...597A..26B, 2017A&A...599L...3B, 2017A&A...602A.106B, 2018A&A...620A.147B, 2019AJ....158...50W, 2019EPSC...13.1928L, 2020ApJ...888L..21G,2021arXiv210309864B}.
-These observations have revealed a population of atoms extending out to distances of order the planetary radius for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with H atoms surrounding a planet.
-The importance of the \lya line in the atmospheric dynamics of these systems necessitates a careful treatment of resonant scattering in order to construct accurate models of atmospheric heating and escape.
+The outer layers of planetary atmospheres are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
+Ionization and subsequent recombination can generate \lya within the planet's atmosphere, dissociating molecules in lower layers and creating pressure forces that drive an outflow of escaping H atoms.
+\lya can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy \citep{2017ApJ...851..150H}.
+
+Hubble Space Telescope (HST) observations with STIS have found large \lya transit depths around a handful of exoplanets \citep{2003Natur.422..143V, 2012A&A...543L...4L, 2012A&A...547A..18E, 2015Natur.522..459E,  2017A&A...597A..26B, 2017A&A...599L...3B, 2017A&A...602A.106B, 2018A&A...620A.147B, 2019AJ....158...50W, 2019EPSC...13.1928L, 2020ApJ...888L..21G,2021arXiv210309864B}.
+These observations have revealed a population of atoms extending out to distances of order a few planetary radii for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with the H atom population.
+In atmospheres with thick layers of atomic hydrogen, stellar Lyman Alpha (Ly$\alpha$) radiation is especially important in the atmospheric dynamics of these systems as the optical depth at line center is large.
+The importance of the \lya line in this process necessitates a careful treatment of resonant scattering in order to construct accurate models of H atom excitation, heating, and radiative forces.
 However, the extreme optical depths at \lya line center introduce a computational barrier to simulating radiative transfer via Monte Carlo methods.

### 2021-09-13 ms.tex
Note for elaboration between computational methods and observational background
Introducing numerical simulations paragraph better, edits through that paragraph of the intro

@@
 
-Hubble Space Telescope (HST) observations with STIS have found large \lya transit depths around a handful of exoplanets \citep{2003Natur.422..143V, 2012A&A...543L...4L, 2012A&A...547A..18E, 2015Natur.522..459E,  2017A&A...597A..26B, 2017A&A...599L...3B, 2017A&A...602A.106B, 2018A&A...620A.147B, 2019AJ....158...50W, 2019EPSC...13.1928L, 2020ApJ...888L..21G,2021arXiv210309864B}.
+Hubble Space Telescope (HST) observations with the STIS have found large \lya transit depths around a handful of exoplanets \citep{2003Natur.422..143V, 2012A&A...543L...4L, 2012A&A...547A..18E, 2015Natur.522..459E,  2017A&A...597A..26B, 2017A&A...599L...3B, 2017A&A...602A.106B, 2018A&A...620A.147B, 2019AJ....158...50W, 2019EPSC...13.1928L, 2020ApJ...888L..21G,2021arXiv210309864B}.
 These observations have revealed a population of atoms extending out to distances of order a few planetary radii for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with the H atom population.
@@
 The importance of the \lya line in this process necessitates a careful treatment of resonant scattering in order to construct accurate models of H atom excitation, heating, and radiative forces.
+
+Numerical simulations can be used to understand the complex layers of these irradiated exoplanet atmospheres.
 However, the extreme optical depths at \lya line center introduce a computational barrier to simulating radiative transfer via Monte Carlo methods.
-
 The main impediment to performing magnetohydrodynamic simulations with fully a coupled radiative transfer solution via Monte Carlo methods is the prohibitive computational cost.
-A primary factor in the cost of Monte Carlo is that the number of scatterings a photon undergoes is proportional to the line center optical depth.
-Near the base of the atmosphere, individual simulation cells can have optical depths of more than a million, so most of the time is spent integrating photons in these cells.
-This means that any method that can treat these zone via an analytic solution has the potential to greatly accelerate the calculation.
+The number of scatterings a photon undergoes is proportional to the line center optical depth.
+Near the base of the atmosphere, the line center optical depth is ${\sim}10^9$, so most of the time is spent integrating photons in these cells.
+A method that can treat these zones via a simple solution has the potential to greatly accelerate the calculation.
 A complete, general analytic solution for the resonance scattering has never been derived but approximate solutions exist in certain limits.

### 2021-09-14 ms.tex
Fixing section in introduction describing Harrington. Removed duplicated info, made description of errors more direct

@@
 The number of scatterings a photon undergoes is proportional to the line center optical depth.
-Near the base of the atmosphere, the line center optical depth is ${\sim}10^9$, so most of the time is spent integrating photons in these cells.
-A method that can treat these zones via a simple solution has the potential to greatly accelerate the calculation.
+Near the base of the atmosphere, the line center optical depth is ${\sim}10^9$, so most of the time is spent following photons in these cells.
+A method that can treat these zones via a simple solution rather than Monte Carlo has the potential to greatly accelerate the calculation.
 A complete, general analytic solution for the resonance scattering has never been derived but approximate solutions exist in certain limits.
 
-\citet{1973MNRAS.162...43H, 1974MNRAS.166..373H} demonstrated that resonance-line radiation transfer in low-density, optically-thick media can be described by the Poisson equation.
-However, the accuracy of their solution is limited by the treatment of the boundary conditions.
-In their eigenfunction expansion, the spatial and frequency components of the differential equation are separated, yet the spatial eigenvalues are defined as being explicitly frequency-dependent.
-The resulting solution is therefore invalid on the basis that the differential equation and boundary conditions cannot simultaneously be satisfied.
-A more detailed discussion of the boundary condition is included in Section \ref{sec:steadystate}.
+\citet{1973MNRAS.162...43H} demonstrated in slab geometry that resonance-line radiation transfer in optically-thick media can be described by the Poisson equation.
+However, their solution contains an incorrect treatment of the boundary condition.
+To our knowledge, the errors introduced by this treatment have never been quantified.
+They attempt a separation of variables $J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ (their Equations 16 and 23).
+The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
+In order to satisfy the boundary conditions, the separation constant must satisfy an eigenvalue equation of the form
+\be
+\lambda \tan(\lambda B) & = & \frac{3}{2} \phi \Delta,
+\label{eq:evalue}
+\ee
+where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile.
+The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
+Thus, the separation constant is not constant, and it does not satisfy the Poisson equation since the frequency derivatives will act on the separation ``constant", giving extra terms.
+In the limit of large optical depth $B$, they approximate the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$.
+However, this solution gives zero mean intensity at the surface.
+Their Eq.
+34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
+This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
+Our treatment, using the correct boundary condition, quantifies the errors in their ansatz.
+
 \citet{1990ApJ...350..216N} follows this approach in an attempt to extend the result to media of intermediate optical depth, including the effects of scattering in the Doppler core of the line, but again does not use the correct boundary condition.
@@
 However, it is not clear whether this prescription is fully independent of the choice of velocity distribution.
-
-The question is how to satisfy the surface boundary condition in Eq.
-\ref{eq:bc}.
-On this point, we note that the derivation in \citet{1973MNRAS.162...43H}, and numerous studies later studies, does not actually produce a valid solution of the transfer equation and boundary condition.
-The reason is as follows.
-In the notation of \citet{1973MNRAS.162...43H}, a separation of variables
-$J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ is attempted (their Equations 16 and 23).
-The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
-In order to satisfy the boundary conditions, the separation constant must satisfy an eigenvalue equation of the form
-\be
-\lambda \tan(\lambda B) & = & \frac{3}{2} \phi,
-\label{eq:evalue}
-\ee
-where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile ($\phi(\nu)\Delta$ here).
-The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
-But then the separation constant is not constant, and it does not satisfy Eq.
-\ref{eq:rt_no_destr} since the frequency derivatives will act on the separation ``constant", giving extra terms.
-To our knowledge the errors introduced by this ansatz have never been quantified.
-
-In the limit of large optical depth $B$, \citealt{1973MNRAS.162...43H} approximates the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$, which gives $J=0$ at the surface.
-This is essentially the result in Eq.
-\ref{eq:J0} above.
-However, since this solution gives zero at the surface, their Eq.
-34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
-This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
 

### 2021-09-14 ms.tex
Reworking first two paragraphs of the steady state solution, adding better description of divergent solution.

@@
 
-\citet{1990ApJ...350..216N} follows this approach in an attempt to extend the result to media of intermediate optical depth, including the effects of scattering in the Doppler core of the line, but again does not use the correct boundary condition.
-This produces a divergent, inhomogeneous solution to the problem in 1D slab geometry.
-\citet{2006ApJ...649...14D} generalize the problem to spherical geometry, which is the same physical set up used here.
-Following this, \citet{2020arXiv200509692L} presents closed-form solutions for the radiation field in spherical geometry, utilizing the ``core skipping'' method discussed in \citet{2015MNRAS.449.4336S} to handle photon frequency redistribution within the Doppler core.
+Several other works have followed \citet{1973MNRAS.162...43H}, building upon their result without addressing the incorrect boundary condition.
+\citet{1990ApJ...350..216N} attempts to extend the solution to media of intermediate optical depth, including the effects of scattering in the Doppler core of the line, but again does not use the correct boundary condition.
+\citet{2006ApJ...649...14D} generalize the same problem to spherical geometry, as is used here.
+Following this, \citet{2015MNRAS.449.4336S} employ a ``core skipping'' method to handle photon frequency redistribution within the Doppler core.
 This technique involves drawing the atom's velocity from a truncated Gaussian distribution, forcing photons back into the wing when they scatter into the core.
-This is motivated by the assumption that all core scattering results in zero spatial diffusion until the photon is redistributed back out into the wing where the mean free path becomes much larger and it can diffuse in space again.
+% This is motivated by the assumption that all core scattering results in zero spatial diffusion until the photon is redistributed back out into the wing where the mean free path becomes much larger and it can diffuse in space again.
 However, it is not clear whether this prescription is fully independent of the choice of velocity distribution.
@@
 
-The solution of this problem is split into two pieces: $\rm J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
-The total solution is $J = J_0 + J_{\rm bc}$.
-
+Consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0$.
+We aim to find the intensity within the sphere as a function of radius and photon frequency.
 Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
@@
 $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
-
-Now, consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
+The line center optical depth is then $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
+
 Starting with the full transfer equation, Eq.
@@
 \ee
+where $\sigma$ comes from a change of variables in photon frequency (Eq.
+\ref{app:rteqn_derivation}\ref{eq:change_of_variables}) and $\sigma_s$ is the photon frequency of the source.
 The boundary condition is that there is no incoming intensity at the surface, which can be written
@@
 at $r=R$.
-An analytic solution $J_d$ which is divergent at the center of the sphere and at the emission frequency may be found.
-However, it is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$.
-This solution is included in Fig.
-\ref{fig:sol_mc_residual_0} for illustration, but will not be discussed further.
-
+
+A solution for the mean intensity $J_d$ which is divergent at the center of the coordinate system and at the emission frequency is presented in \citet{1990ApJ...350..216N}.
+Here it is extended to spherical geometry and generalized to allow emission frequencies away from line center:
 \be
 J_{\rm d} & = & 
-\left(\frac{\sqrt{6}k^2L}{16\pi^3 \Delta^3}\right)\left(\frac{1}{(kr/\Delta)^2 + (\sigma - \sigma_{\rm s})^2}\right).
+\left(\frac{\sqrt{6}k^2L}{16\pi^3 \Delta^3}\right)\left(\frac{1}{(kr/\Delta)^2 + (\sigma - \sigma_{\rm s})^2}\right)
 \label{eq:Jd}
@@
 \ee
+This solution is useful as a very simple analytic formula.
+However, it is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$.
+This solution is included in Fig.
+\ref{fig:sol_mc_residual_0} for illustration, but will not be discussed further.
 
@@
 It decreases exponentially rather than as a power-law in frequency, giving a much smaller flux on the line wings as compared to the divergent solution.
+
+The solution of this problem is split into two pieces: $\rm J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
+The total solution is $J = J_0 + J_{\rm bc}$.
+%TODO
 

### 2021-09-14 ms.tex
Changes up to pg 4

@@
 This solution is useful as a very simple analytic formula.
-However, it is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$.
+However, it is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$ and does not adhere to the correct boundary condition.
 This solution is included in Fig.
@@
 They found a solution which satisfies a $J=0$ boundary condition at $r=R$.
-We generalize their solution to allow emission at frequency $\nu_{\rm s}$ away from line center.
+Again, we generalize their solution to allow emission at frequency $\sigma_{\rm s}$ away from line center.
 The result can be written as a sum over spatial modes,
@@
 \ee
+and
 \be \label{eq:H0_sum}
@@
 \ee
-which evaluate to
+which can be summed to give the closed form expressions
 \be
@@
 \ee
-
+and
 \be
@@
 \be
+\nonumber
 H_0(R, \sigma) & = & - \frac{1}{3k\phi}
@@
 \sum_{n=1}^{\infty} 
-n (-1)^n \exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)}
-,
-\label{eq:H0surf_sum}
-\ee
-or
-\be
-H_0(R, \sigma) & = &  \frac{1}{3k\phi}
+n (-1)^n \exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)}\\
+& = &  \frac{1}{3k\phi}
 \frac{\sqrt{6}L}{32\pi \Delta}
@@
 Eq.
-\ref{eq:H0surf} will be shown to be a much better approximation to the solution, which is valid near the delta function at the center, and is a much better approximation at the surface.
-It is still only a good approximation near line center at the surface.
-It decreases exponentially rather than as a power-law in frequency, giving a much smaller flux on the line wings as compared to the divergent solution.
-
-The solution of this problem is split into two pieces: $\rm J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
-The total solution is $J = J_0 + J_{\rm bc}$.
+\ref{eq:H0surf} will be shown to be a much better approximation to the solution than Eq.
+\ref{eq:Hd}.
+It is still valid near the delta function at $r=0$, but is also a much better approximation at $r=R$.
+$J_0$ decreases exponentially rather than as a power-law in frequency as for $J_d$, giving a much smaller flux on the line wings as compared to the divergent solution.
+
  %TODO
 
-A different solution method is attempted here: namely, a continuous Fourier expansion in the frequency variable $\sigma$. The full solution is written
+A different solution method is attempted here, namely, a continuous Fourier expansion in the frequency variable $\sigma$.
+The solution of this problem is split into two pieces: $J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
+The total solution is
 \be
@@
 \be \label{eq:diffeq}
-\frac{\partial^2J}{\partial r^2} + \frac{2}{r} \frac{\partial J}{\partial r}
-+ \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} &= & 0
+\frac{\partial^2J_{\rm bc}}{\partial r^2} + \frac{2}{r} \frac{\partial J_{\rm bc}}{\partial r}
++ \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J_{\rm bc}}{\partial \sigma^2} &= & 0
 \ee
@@
 \ee
-Plugging in a frequency dependence $J \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$.
+Plugging in a frequency dependence $J_{\rm bc} \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$.
 The solution can then be represented as
@@
 leads to a set of coupled linear equations for the $A(s_j)$.
-We use equally-spaced points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid and solve the resulting matrix equation.
+We use equally-spaced points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid.
+The result is a linear system to solve for the $A(s)$.
 The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that  the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries.
-The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries.
+The number of points was increased until the solution was well-resolved near line center, and only became inaccurate very near the boundaries.
 Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq.
@@
 \subsection{Scaling with Line Center Optical Depth}
-To examine the relative size of the corrective term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the optical depth is large and thus the mean intensity will be considerably larger than the surface flux.
+To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the $\tau_0$ is large and thus $J_{\rm bc}$ will be considerably larger than $H_{\rm bc}$.
 We obtain the proportionality

### 2021-09-14 ms.tex
Finished edits up to Monte Carlo section - rewriting x_peak, doppler core boundary section

@@
 \subsection{Scaling with Line Center Optical Depth}
-To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the $\tau_0$ is large and thus $J_{\rm bc}$ will be considerably larger than $H_{\rm bc}$.
+To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$.
 We obtain the proportionality
@@
 \ee
-Thus, the fractional importance of the corrective frequency-dependent boundary condition term scales as the inverse cube root of the damping parameter $a$ times the line-center optical depth $\tau_0$.
-At very large optical depths, it is expected that the corrective term will be small, but will become increasingly important in less optically thick media.
+Thus, the fractional importance of the correct frequency-dependent boundary condition term $H_{\rm bc}$ scales as $(a\tau_0)^{-1/3}$.
+At very large $\tau_0$, it is expected that the correction term will be small, but will become increasingly important as $\tau_0$ decreases.
 
@@
 \be \label{eq:tau_peak_scaling}
-x_0 &\propto& \left(a\tau_0\right)^{1/3}.
-\ee
-This predicts that the characteristic photon frequency in Doppler widths should scale as the cube root of the parameter $a$ multiplied by the line center optical depth $\tau_0$, indicating the location of the spectral peaks on either side of line center --- the locations where the photons most readily escape.
-Since our derivations were performed assuming a Lorentzian line profile (see Appendix \ref{app:rteqn_derivation}), our solutions are technically only valid in the line wing, where the Doppler component of the line profile is small.
-Since our choice of the damping parameter $a$ is constant, the solutions of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large optical depths.
-For \lya and a hydrogen gas of temperature $T=10^4$ K, the damping parameter $a = \Gamma / (4\pi\Delta)$ is equal to $4.72\times 10^{-4}$ in CGS units.
-Thus, the value of $\tau$ at which the Doppler and Lorentzian components of the line wing are equal is $\tau_{\rm cw}=7.3\times10^4$.
+x_{\rm peak} {\sim} \left(a\tau_0\right)^{1/3}.
+\ee
+The solutions of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
+For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$.
+Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$.
+Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value of the line-center optical depth at which the core of the line moves into the peak of the spectrum, which is $\tau_{\rm cp}=7.3\times10^4$.
 Solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower line center optical depths where the peak of the spectrum lies near the core and improve for larger optical depths where the spectral peak is well outside of the line core.

### 2021-09-21 ms.tex
Incorporating Phil's edits up to the time-dependent diffusion section

@@
 The Monte Carlo method is used to solve the transfer equation numerically.
-This method is valid at arbitrarily large optical depths, being restricted only by its computational demand which grows in proportion to the number of photons used.
-For each simulation, a total of $2^{20} \approx 10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the medium until escaping, at which point their positions, outgoing angles, and escape frequencies are stored.
-A constant temperature of $T=10000\ \rm K$ is set for the gas.
+This method is valid at arbitrarily large optical depths, being restricted only by its computational demand which grows proportionally to the number of photons used and $\tau_0$.
+For each simulation, a total of ${\sim}10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the sphere until escaping, at which point their positions, outgoing angles, and escape frequencies are stored.
+A constant temperature of $T=10,000\ \rm K$ is set for the gas.
 Frequency redistribution is calculated at each scattering, including the effects of recoil, to obtain the spectrum at the surface of the spherical simulation domain.
@@
 We now compare each of the previously-discussed solutions for surface flux with Monte Carlo simulations.
-The escape probability $P(x)$ is defined as the total luminosity at the surface divided by the source luminosity, or
-\be
-P(x) = \frac{16\pi^2R^2H(R, x)\Delta}{L}
-\ee
-This is defined such that $\int P(x)dx = 1$.
-Since $H(r, \nu)$ is implicitly written per $d\nu$, a factor of $\Delta$ gives the expression the correct units.
-In Fig.
-\ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown with that of the solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
+We return to the Doppler units $x$ for the photon frequency rather than the $\sigma$ units used in the solutions of the transfer equation.
+The spectrum $P(x)$ is defined as the specific luminosity at the surface divided by the source luminosity, or
+\be
+P(x) = \frac{16\pi^2R^2H(R, x)\Delta}{L}.
+\ee
+This is normalized such that $\int P(x)dx = 1$. Since $H(r, x)$ is per $d\nu$, a factor of $\Delta$ gives the expression the correct units.
+
+% TODO: Edits unclear. Organization of sentences OK? "Describe what's in the figure and then discuss" - Mention of Hd moved to end of paragraph, details of the Hbc term moved higher up.
+In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown with that of the solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
+The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, it adequately corrects for the apparent excess of flux in the peaks of the spectrum.
+This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S} where the discrepancy is particularly noticeable for line center optical depths of $\tau_0=10^5$ and $10^6$ in the top panel of their Figure 5.
 The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
+The boundary term corrects the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
+Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.
 It is evident that the divergent solution $H_{\rm d}$ fails in the line wings.
-The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, it adequately corrects for the apparent excess of flux in the peaks of the spectrum.
-This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S} where the discrepancy is particularly noticeable for line center optical depths of $\tau_0=10^5$ and $10^6$.
-The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
-Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.
 
@@
     \includegraphics{tau_threepanel.pdf}
-    \caption{The same spectrum as in Fig.
-\ref{fig:sol_mc_residual_0}, but for three different line center optical depths $\tau_0 = 10^5, 10^6, 10^7$ with the $x$ and $y$ axes scaled by the characteristic frequency diffusion scale $(a\tau_0)^{1/3}$.
-Photons are initialized with $\rm x = 0.0$ in each case.}
+    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\tau_0 = 10^5, 10^6, 10^7$.
+The $x$ and $y$ axes are scaled by $(a\tau_0)^{1/3}$.
+Photons are initialized with $\rm x_s = 0.0$ in each case.}
     \label{fig:sol_mc_tau}
@@
 
-The size of the frequency-dependent boundary condition correction is dependent on the line center optical depth, which also dictates the x-position of the peak of spectrum according to Eq.
+The size of $H_{\rm bc}$ is dependent on $\tau_0$, which also dictates the x-position of the peak of spectrum according to Eq.
 \ref{eq:tau_peak_scaling}.
-This term contributes a significant amount of flux correction even at line center optical depths of $10^7$ where the $J=0$ solution is expected to perform its best, i.e., the majority of photons are pushed further out into the wing and thus the simplifying assumptions made in the solution of the differential equation are better founded.
-One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis of Fig.
-\ref{fig:sol_mc_tau} such that the peaks of the distributions are vertically aligned.
-This scaling has also been applied to the y-axis to preserve normalization of the escape probability.
+This term is significant even at $\tau_0 {\sim} 10^7$ where $H_0$ solution is expected to perform its best, i.e., photons are pushed further out into the wing and thus the simplifying assumptions made in the solution of the differential equation are a better approximation.
+
+In Figure \ref{fig:sol_mc_tau} we show the solutions alongside Monte Carlo for $\tau_0=10^5, 10^6$, and $10^7$.
 From Eq.
 \ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-Indeed, agreement between both analytic flux calculations and the Monte Carlo points in Fig.
-\ref{fig:sol_mc_tau} improves with $H_{\rm bc}$ providing a fractionally smaller correction to $H_0$ as the optical depth becomes larger.
-At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely.
-The effects of core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift substantially outward in frequency from the line core for $\tau_0 = 10^5$.
+Indeed, agreement between Eq.
+\ref{eq:H0surf} and the Monte Carlo points in Fig.
+\ref{fig:sol_mc_tau} improves as $\tau_0$ increases, with $H_{\rm bc}$ providing a fractionally smaller correction to $H_0$.
+One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis such that the peaks of the distributions are vertically aligned.
+This scaling has also been applied to the y-axis to preserve normalization of the escape probability.
+At lower $\tau_0$, the scattering of photons within the Doppler core of the line becomes important, yet our solution does not include this effect.
+The effects of line core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift substantially outward in frequency from the line core for $\tau_0 = 10^5$.
 
@@
 
-Since the solutions have been generalized to allow for a monochromatic source of photons at a frequency $\sigma_s$ away from line center, their agreement with Monte Carlo as a function of source frequency can also be characterized.
-Photons initialized closer to the line wing may travel larger mean free paths as the opacity is sensitively dependent on the line profile.
-The larger spatial diffusion contributes to greater escape probability, biasing the frequency distribution of escaping photons.
+Since the solutions have been generalized to allow for a monochromatic source of photons at a frequency $x_s \neq 0$, their agreement with Monte Carlo as a function of source frequency can also be characterized.
+Photons initialized further out in the line wing have larger mean free paths.
+The larger spatial diffusion contributes to greater escape probability for these photons.
 In the limit that $|\rm x_s|$ becomes large, the distribution becomes a delta function in frequency as all photons escape the gas without scattering.
-Fig.
-\ref{fig:sol_mc_xinit} shows calculations performed for three initial photon frequencies $\rm x_s = 0.0, 6.0$, and $12.0$ for a line center optical depth of $\tau_0=10^7$.
-The bias in frequency distribution is slight for $\rm x_s = 6.0$ where the line profile is still relatively large and emitted photons remain trapped in the core, but the increase in mean free path is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core.
-It is seen here that the discrepancy between the Monte Carlo data and $H_0$ (effectively the scale of the corrective $H_{\rm bc}$ term) becomes larger as $\rm x_s$ increases.
-Thus, for sufficiently large $\tau_0$ and emission away from line center $x_s \neq 0$, the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows.
-The bias in the escaping spectrum is substantial at lower optical depths, shown in Fig.
-\ref{fig:sol_mc_xinit_lowtau}, where a $\Delta x_s$ of 6 is a larger fraction of the spectral peak location $(a\tau_0)^{1/3}$.
-It is clear from the figure that as $x_s$ becomes further from the optically thick core, the spectrum approaches a delta function in frequency at $\sigma_s$.
+
+Figure \ref{fig:sol_mc_xinit} shows calculations performed for three initial photon frequencies $\rm x_s = 0.0, 6.0$, and $12.0$ for a line center optical depth of $\tau_0=10^7$.
+The asymmetry of the spectrum is slight for $\rm x_s = 6.0$ where the cross section is still relatively large, but the increase in mean free path is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core.
+It is seen here that the difference between the Monte Carlo data and $H_0$ becomes larger as $\rm x_s$ increases.
+Thus, for sufficiently large $\tau_0$ and emission away from line center ($x_s \neq 0$), the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows.
+
+Figure \ref{fig:sol_mc_xinit_lowtau} shows emission away from line center at the same values of $x_s$ as in Figure \ref{fig:sol_mc_xinit}, but for $\tau_0=10^6$ rather than $10^7$.
+The difference between the left and right side of the escaping spectrum is substantial at lower optical depths, since a change in $x_s$ of 6 is a larger fraction of the spectral peak location $(a\tau_0)^{1/3}$ for lower $\tau_0$.
+It is clear from the figure that as $x_s$ becomes further from the line core, the spectrum approaches a delta function in frequency.
 Additionally, since the material is optically thin here, we expect there to be a stronger disagreement between the Monte Carlo and the analytic solution as derivations assumed large optical depths.
@@
 
-The previous figures show that as $\tau_0$ increases, $H_0$ appears to become more accurate.
-There is agreement between the Monte Carlo and $H_0$ when $H_{\rm bc}$ is small which motivates a quantitative examination of how the boundary term $H_{\rm bc}$ scales with both $\tau_0$ and $\sigma_s$, shown in Fig.
-\ref{fig:xinit}.
-In this graphic, the photon initialization frequency $\sigma_s$ is shifted in integer multiples of $\tau_0$ such that $\sigma_s$ falls near the peak of the spectrum for each $\tau_0$.
-For clarity, only the $\sigma > 0$ side of the spectrum is shown.
+Figure \ref{fig:xinit} shows quantitative examination of how the boundary term $H_{\rm bc}$ scales with both $\tau_0$ and $x_s$, motivated by the previous figures' demonstration that $H_0$ appears to become more accurate as $\tau_0$ increases.
+In this figure, the photon initialization frequency $x_s$ is shifted by integer multiples of $\tau_0$ in $\sigma$ frequency units (Eq.
+\ref{app:rteqn_derivation}\ref{eq:change_of_variables}) such that the source, now written $\sigma_s$, falls near the peak of the spectrum for each $\tau_0$.
+For clarity, only the $x > 0$ side of the spectrum is shown.
 From Eq.
-\ref{eq:hbc_scaling}, it is expected that the size of the correction $H_{\rm bc}$ should become smaller with larger optical depths following a $(a\tau_0)^{-1/3}$ scaling.
+\ref{eq:hbc_scaling}, it is expected that the size of $H_{\rm bc}$ should become smaller with larger optical depths following a $(a\tau_0)^{-1/3}$ scaling as compared to $H_0$.
 This factor has been scaled out of the figure such that solutions for different optical depths and the same source frequency $\sigma_s$ should show close agreement in scale on the figure's vertical axis if the relation holds.
-Indeed, the scaled solutions converge as the optical depth becomes larger, indicating general agreement with the $(a\tau_0)^{1/3}$ scaling.
-The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ is due to the width of the Doppler core with respect to the peak of the spectrum; at lower depths, this causes the assumptions about the functional form of the line profile to break down.
-From this, we conclude that the errors introduced by the incorrect separation of variables in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others are proportional to $(a\tau_0)^{1/3}$, where $a$ is the ratio of natural to Doppler broadening and $\tau_0$ is the optical depth at line center.
-Furthermore, an additional amount of error of order $(a\tau_0)^{1/3}$ is introduced as the photon frequency $\sigma_s$ from line center is increased by a factor of $\tau_0$.
+Indeed, the scaled solutions converge as the optical depth becomes larger, indicating general agreement with the $(a\tau_0)^{-1/3}$ scaling.
+The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ is due to the width of the Doppler core with respect to the peak of the spectrum; at lower $\tau_0$, this causes the line profile approximation in the wing (Eq.
+\ref{app:rteqn_derivation}\ref{eq:line_profile_wing}) to break down.
+From this, we conclude that the errors introduced by the incorrect separation of variables in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others are proportional to $(a\tau_0)^{-1/3}$.
 

### 2021-09-22 ms.tex
BEGINNING TIME DEPENDENT EDITS

@@
 This allows the distribution of photon escape times (the ``wait time distribution'') to be characterized and fit for efficient sampling.
-For simplicity a $J=0$ boundary condition will be used in the following derivations, which is expected to be a decent approximation for $\tau_0 \gg 1$.
+For simplicity a $J=0$ boundary condition will be used in the following derivations, which is a decent approximation for $\tau_0 \gg 1$.
 
@@
 \label{eq:jrsigmat_expansion}
-J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega).
+J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega),
 \ee
@@
 \ee
+Eq. \ref{eq:jrsigmat_expansion} is the standard specific mean intensity $dE/dA dt d\nu$ in CGS units. %energy per unit area per unit time per Hertz, expressed here in CGS units.
+Though $J(r, \sigma, t)$ is written as a function of the photon frequency variable $\sigma$, it should be integrated over $d\nu$ to preserve its normalization.
 Eq.
-\ref{eq:jrsigmat_expansion} is the standard specific mean intensity in units of energy per unit area per unit time per Hertz, expressed here in CGS units.
-Though the frequency variable used here is $\sigma$, the specific mean intensity is to be integrated with respect to $\nu$.
-Eq.
-\ref{eq:jnsigmaomega} is in the same units, but with an additional unit of time in the numerator as a result of the expansion.
-Plugging the expression for the eigenfunctions $J(n, \sigma, \omega)$ into the differential equation Eq.
+\ref{eq:jnsigmaomega} is in the same units, but with an additional unit of $t$ in the numerator as a result of the expansion.
+Plugging in Eq.
+\ref{eq:jnsigmaomega} for the eigenfunctions in Eq.
 \ref{eq:diffusion_eqn} and evaluating the integrals, we obtain
@@
 We start with a treatment of the boundary conditions.
-At $\sigma=\sigma_s$ continuity must be enforced in $J$
+At $\sigma=\sigma_s$ continuity must be enforced,
 \be \label{eq:matching_condition_1}
-J_+ = J_-
+J_+ = J_-,
 \ee
@@
 \frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
-- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}
-\ee
-according to the differential equation. At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes
+- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}.
+\ee
+At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes
 \be \label{eq:diffusion_at_large_sigma}

### 2021-09-22 ms.tex
Starting to rework residue theorem section, changing equations and phrasing up to that point

@@
 \be \label{eq:diffusion_at_large_sigma}
-\frac{\partial^2J}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J.
+\frac{\partial^2J}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J,
 \ee
@@
 \be
-J(n, \sigma, \omega)\ {\sim}\ e^{\pm \Delta \kappa_n \sigma / k}
-\ee
-and thus
+J(n, \sigma, \omega)\ {\sim}\ e^{\pm \Delta \kappa_n \sigma / k}.
+\ee
+We then have
 \be \label{eq:single_j_derivative}
-\frac{\partial J}{\partial \sigma} = \mp \frac{\Delta\kappa_n}{k} J
+\frac{\partial J}{\partial \sigma} = \mp \frac{\Delta\kappa_n}{k} J,
 \ee
 where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$.
-Two numerical integrations are performed inward from large $\pm \sigma$ to the source $\sigma_s$ to isolate the solution that increases exponentially toward the line center.
+Two numerical integrations are performed inward from large $\pm \sigma$ to $\sigma_s$, isolating the solution that increases exponentially toward the line center.
 Initial values for integration are obtained by setting $J=1$ in Eq.
 \ref{eq:single_j_derivative}.
-This gives $J_\pm$ and $J'_\pm$ on either side of the source, where a prime indicates the derivative $\partial/\partial \sigma$.
-By enforcing the matching conditions Eqs.
+This gives $J$ and $J'$ on either side of $\sigma_s$, where a prime indicates the derivative $\partial/\partial \sigma$.
+By enforcing the matching conditions, Eqs.
 \ref{eq:matching_condition_1} and \ref{matching_condition_2}, the solution for $J(n, \sigma, \omega)$ is obtained for all photon frequencies $\sigma$.
@@
 There are certain values of $\gamma$ for which a resonant response is produced which we will call $\gamma_{nm}$.
-Here, $m$ is an index that represents individual frequency eigenmodes, as opposed to $n$ which represents the spatial mode number.
-Near these frequencies, the solution will have the form
+Here, $n$ and $m$ are indices that represent individual spatial and frequency modes, respectively.
+Near these $\gamma_{nm}$, the solution will have the form
 \be
@@
 \ee
-Obtaining the values of these eigenfrequencies and their corresponding eigenfunctions $J_{nm}(\sigma)$ allows us to obtain the contribution of this mode to the total solution via contour integration. 
+The contribution of the $J_{nm}(\sigma)$ eigenmode to the total solution is obtained by the residue theorem:
 \be
@@
 \nonumber \\ & \simeq & \sum_{n=1}^{\infty}j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} 
-\nonumber \\ & \simeq & \sum_{n=1}^{\infty}j_0(\kappa_n r)  J_{nm}(\sigma) e^{-\gamma_{nm}t}.
-\ee
-Here we have closed the integral along the imaginary $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer.
-The contribution from the semi-circle at infinity is zero.
+\nonumber \\ & \simeq & \sum_{n=1}^{\infty}j_0(\kappa_n r)  \sum_{m=1}^{\infty}J_{nm}(\sigma) e^{-\gamma_{nm}t}.
+\ee
+Here we have closed the integral along the imaginary $\gamma$-axis  with a semi-circle at infinity.
+The contribution from the semi-circle at infinity is zero, so we then obtain the residue of the $(n, m)$ pole.
 Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result

### 2021-09-22 ms.tex
Residue theorem section made more clear / explicit

@@
 \ee
-We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$.
-The eigenvalues $i\omega$ are real and positive for damped solutions to the time-dependent equation.
-The expansion for $J(r, \sigma, t)$ is
+We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$. The expansion for $J(r, \sigma, t)$ is
 \be
@@
 By enforcing the matching conditions, Eqs.
-\ref{eq:matching_condition_1} and \ref{matching_condition_2}, the solution for $J(n, \sigma, \omega)$ is obtained for all photon frequencies $\sigma$.
-Since the solution is linear in the starting conditions, only two integrations with different starting values are necessary.
-
-Let us define the damping frequency to be $\gamma \equiv i\omega$, which is real-valued and positive for damped solutions.
+\ref{eq:matching_condition_1} and \ref{matching_condition_2}, the eigenfunctions $J(n, \sigma, \omega)$ are obtained for all photon frequencies $\sigma$.
+Since the eigenfunctions are linear in the starting conditions, only two integrations with different starting values are necessary.
+
+Let us define the damping frequency to be $\gamma \equiv i\omega$, which is real-valued and positive for damped solutions to the time-dependent equation.
 There are certain values of $\gamma$ for which a resonant response is produced which we will call $\gamma_{nm}$.
-Here, $n$ and $m$ are indices that represent individual spatial and frequency modes, respectively.
-Near these $\gamma_{nm}$, the solution will have the form
-\be
+Near these $\gamma_{nm}$ poles, the eigenfunctions will have the form
+\be \label{eq:jnsigmaomega_approx}
 J(n,\sigma,-i\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma_{nm} - \gamma} + {\rm terms\ which\ vary\ slowly\ in\ \gamma}.
 \ee
-The contribution of the $J_{nm}(\sigma)$ eigenmode to the total solution is obtained by the residue theorem:
-\be
-J(r,\sigma,t) & = &  -\sum_{n=1}^{\infty}j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t}J(n,\sigma,-i\gamma)
-\nonumber \\ & \simeq & \sum_{n=1}^{\infty}j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} 
-\nonumber \\ & \simeq & \sum_{n=1}^{\infty}j_0(\kappa_n r)  \sum_{m=1}^{\infty}J_{nm}(\sigma) e^{-\gamma_{nm}t}.
-\ee
-Here we have closed the integral along the imaginary $\gamma$-axis  with a semi-circle at infinity.
-The contribution from the semi-circle at infinity is zero, so we then obtain the residue of the $(n, m)$ pole.
-Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result
+From Eq. \ref{eq:jrsigmat_expansion}, the contribution of a single pole to the total solution is
+\be
+J_{nm}(r,\sigma,t) & = &  -j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t}J(n,\sigma,-i\gamma)
+\\ & \simeq & j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}}.
+\ee
+We close the integral along the imaginary $\gamma$-axis  with a semi-circle at infinity and apply the residue theorem. The contribution from the semi-circle is zero, so we obtain
+\be
+J_{nm}(r,\sigma,t) & \simeq & j_0(\kappa_n r) J_{nm}(\sigma) e^{-\gamma_{nm}t}.
+\ee
+Summing over all spatial modes $n$ and over all eigenmodes $m$ for a given $n$, we get the final form of the result:
 \be \label{eq:Jrsigmat}
-J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_m J_{nm}(\sigma) e^{-\gamma_{nm}t}.
+J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_m^{\infty} J_{nm}(\sigma) e^{-\gamma_{nm}t}.
 \ee

### 2021-09-23 ms.tex
editing phrasing of paragraph discussing Fig. 8

@@
 \ee
-Integrating over $\nu$ gives unity according to the sum rule in Eq.
-\ref{eq:sumrule}.
+Integrating over $\nu$ gives unity according to the sum rule in Eq. \ref{eq:sumrule}.
+
 In Fig.
-\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq.
+\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq.
 \ref{eq:H0surf_sum}.
-This graphic illustrates the physics modeled by each variable in the expansion.
-For example, the spatial modes contribute to the solutions' accuracy in the core of the line.
-If more spatial modes were calculated, the agreement between the lines extends further into the core.
-If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over the imaginary frequency variable $\gamma$ which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
-Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would only affect the distribution at late times since core photons are trapped for a longer duration before escaping.
+Additional spatial modes contribute to the solutions' accuracy in the core of the line.
+If more spatial modes are calculated, the agreement with the steady state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x_s$.
+If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over $\gamma$ which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
+Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would only affect the distribution at late times since photons are trapped for a longer duration before escaping.
 This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated.
+%TODO: Include?
 As a result of this choice, we expect that our semianalytic approach will underestimate the number of escaping photon at late times as compared with the Monte Carlo.

### 2021-09-24 ms.tex
Reorganizing figures in monte carlo comparison section of time dependent diffusion

@@
 \ee
-Eq. \ref{eq:jrsigmat_expansion} is the standard specific mean intensity $dE/dA dt d\nu$ in CGS units. %energy per unit area per unit time per Hertz, expressed here in CGS units.
+Eq.
+\ref{eq:jrsigmat_expansion} is the standard specific mean intensity $dE/dA dt d\nu$.
 Though $J(r, \sigma, t)$ is written as a function of the photon frequency variable $\sigma$, it should be integrated over $d\nu$ to preserve its normalization.
@@
 \ee
-Summing over all spatial modes $n$ and over all eigenmodes $m$ for a given $n$, we get the final form of the result:
+Summing over all spatial modes $n$ and over all eigenmodes $m$ for a given $n$, we obtain
 \be \label{eq:Jrsigmat}
-J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_m^{\infty} J_{nm}(\sigma) e^{-\gamma_{nm}t}.
-\ee
-Beginning with Eq. \ref{eq:Jrsigmat}, we use the derivative
+J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_{m=1}^{\infty} J_{nm}(\sigma) e^{-\gamma_{nm}t}.
+\ee
+
+% State that this works for some of the poles, but others are missing. Can't capture asymmetry in spectrum. There is some other term that's missing from this analysis.
+
+%The divergent pieces don't contain the piece that can be asymmetric --- the poles we're finding don't allow asymmetry in the specturm.
+
+% Missing something in our contour? Residue theorem doesn't apply in this case? Missing a pole or poles that are not present?
+
+% We're losing some poles due to the boundary but we think that the sum of the decaying solutions is converging fast enough to cut it off somewhere.
+
+% We try this ansatz for the symmetric case and it basically seems to work.
+We show this by numerical calculation.
+We have to point out that we've shown it doesn't work for an off-center source.
+But then what do we say?
+We don't really have an explanation for how it doens't work.
+WKB gives info about it, but we don't discuss thta in the paper either.
+
+% Put a little wkb in the appendix?
+We could show the dispersion relation, for instnace.
+d^2Jdsigma^2, equation for discontinuity...
+here is the solution far from LC, here is the solution near LC, by requiring these two solutions to match in the raea where they're both valid, here are the matching conditions.
+4-5 lines.
+Here's the presence of simple poles, gives us dispersion relation, but also here's the piece that is not divergent and containts the discontinuity.
+This term is not included in the sum over simple poles.
+Don't go through the derivation in a lot of detail.
+
+% After we do the symmetric case, note that due to what we found in the WKB, this does not capture the asymmetry in the source function.
+Leave it there and just.
+Don't say it's left for future work.
+Just leave it.
+Note that there's an issue and say "this suggests that our ansatz is incomplete in the asymmetric case."
+
+% WKB Approximation - could cite (Bender & Norzog)? Arfken might have it too?
+
+% Change ordering of figures. Have current fig 8 and 9 be the last thing since they contain a sum over modes. Put solid results first.
+
+% Go through derivation of dispersion relation, then say "the denominator being zero leads to the dispersion relation (cite eq 47 in time dependent section)".
+
+Taking a derivative with respect to $r$ and evaluating at the surface $r=R$, we use
 \be
@@
 =  \left( \frac{\cos(\kappa_n R)}{R} - \frac{\sin(\kappa_n R)}{\kappa_n R^2} \right)
-\nonumber \\ & = & \frac{(-1)^n}{R},
-\ee
-to obtain the flux at the surface, which is
+\nonumber \\ & = & \frac{(-1)^n}{R}
+\ee
+to obtain the flux, which is
 \be
@@
 \ee
-Integrating this over time yields a factor $-1/\gamma_{nm}$, and over $d\nu = \sqrt{3/2} \Delta^2 \phi d\sigma$, a ``sum rule" results
-\be
+Integrating over time yields a factor $-1/\gamma_{nm}$, and by integrating over $d\nu$ we find
+\be \label{eq:sum_rule}
 1 & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE} \sum_{nm} (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
 \ee
-This non-trivial expression provides a check on the values of $\gamma_{nm}$ and the functions $J_{nm}(\sigma)$. This expression can also be written as
+This non-trivial ``sum rule'' provides a check on the values of $\gamma_{nm}$ and $J_{nm}(\sigma)$. This expression can also be written as
 \be
@@
 \ee
-where the contribution of each eigenfunction is
+where the contribution of each mode is
 \be \label{eq:pnmsoln}
@@
 These coefficients are negative for odd values of $n$ and positive for even $n$.
-The size of each contribution scales roughly as $0.5/(m+1/8)^{2/3}$, with a very weak dependence on $n$.
-This indicates the need for a large number of $n$ and $m$ to converge, i.e., it takes roughly ten times as many $m$ modes to reduce the size of $P_{nm}$ by a factor of ${\sim}$5, so convergence is slow.
+The size of each contribution scales roughly as $0.5/(m-7/8)^{2/3}$, with a very weak dependence on $n$.
+This indicates the need for a large number of $n$ and $m$ to converge, in that it takes roughly ten times as many $m$ modes to reduce the size of $P_{nm}$ by a factor of ${\sim}$5.
 
@@
 We seek now to calculate all eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\gamma_{nm}$ for all spatial $n$ and for all eigenmodes $m$ at that given $n$.
-A resonant response in $J(n,\sigma,-i\gamma)$ is produced for special values of $\gamma \equiv \gamma_{nm}$.
 To measure the size of the response to detect where resonances occur, we sum the absolute value of $J(n,\sigma,-i\gamma)$ over $\sigma$ in array form.
-Call this response $f$, and use the index $j$ to represent the value of the response at discrete points over a range of $\gamma$.
+We call this response $f$, and use the index $j$ to represent the value of the response at discrete points over a range of $\gamma$.
 In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bounded a resonance that occurs in the interval $(\gamma_{j-1},\gamma_{j+1})$.
@@
 \be
-\gamma_{\rm guess} &=& \frac{b\gamma_{j-1} - \gamma_{j+1}}{b - 1}
+\gamma_{\rm guess} &=& \frac{b\gamma_{j-1} - \gamma_{j+1}}{b - 1},
 \ee
@@
 \ee
-This is repeated by replacing former points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ with closer estimates while the size of the response grows as the resonance is approached.
-Given a sufficiently accurate eigenvalue $\gamma_{nm}$, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
+This is repeated by replacing initial points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ with closer estimates while the size of the response grows as the resonance is approached.
+After iterating until an eigenvalue $\gamma_{nm}$ is accurately determined, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
 We can write down an approximate expression for the response near the resonances as
@@
 \ee
-where $C(\sigma)$ is weakly dependent on $\gamma$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance:
-\be
-J(n,\sigma,-i\gamma_1)  - J(n,\sigma,-i\gamma_2)& = &  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_1} -  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_2}
+where $C(\sigma)$ is weakly dependent on $\gamma$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance
+\be
+J(n,\sigma,-i\gamma_1)  - J(n,\sigma,-i\gamma_2)& = &  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_1} -  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_2},
 \ee
@@
 \end{figure}
-A set of eigenfunctions $J_{nm}(\sigma)$ are plotted in Fig.
-\ref{fig:jsoln} to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$.
+Fig.
+\ref{fig:jsoln} shows a set of eigenfunctions $J_{nm}(\sigma)$ to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$.
 The overall scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$ with $E$ arbitrarily set to 1, $k = \tau_0 \sqrt{\pi} \Delta / R$, and $R = 10^{11}$ cm.
 With this normalization, an eigenfunction has typical size ${\sim} E a / \left(R^2 \Delta \right) = 10^{-37}$.
-Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
+Additional terms add smaller-magnitude, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
 The oscillations of various modes must cancel perfectly to recreate the form of the solution in Eq.
@@
 \end{figure}
-The values of the $\gamma_{nm}$ resonant frequencies can be described approximately with Eq. \ref{eq:gamma_nm}. Their scale depends on $m$, $n$, and the factor $(a\tau_0)^{1/3}$ according to 
+The values of the $\gamma_{nm}$ resonant frequencies can be described approximately with Eq. \ref{eq:gamma_nm}. Their scale depends on $m$, $n$, and other physical parameters according to 
 \be \label{eq:gamma_nm}
@@
 \ee
-The size of additional eigenfrequencies scales as a powerlaw in $m$, yet as is seen in Fig.
-\ref{fig:gamma_nm} the scaling is weak, requiring up to 500 $m$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
+The size of additional eigenfrequencies scales as a power law in $m$, yet as is seen in Fig.
+\ref{fig:gamma_nm} the power is weak, requiring up to 500 $m$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
 When sweeping through the imaginary frequency domain to find resonances, this expression is used to set the scale of the sweep points to ensure no $\gamma_{nm}$ are missed.
@@
 \be
-\frac{d^2J}{d\sigma^2} & = & \left[ \left( \frac{\kappa_n \Delta }{k} \right)^2 - \frac{3\phi \gamma\Delta^2}{ck}\right] J
+\frac{d^2J}{d\sigma^2} & = & \left[ \left( \frac{\kappa_n \Delta }{k} \right)^2 - \frac{3\phi \gamma\Delta^2}{ck}\right] J,
 \ee
@@
 
-Integrating $dE/dt d\nu$ from Eq.
-\ref{eq:dEdtdnu} over all times should give a distribution for the emitted frequencies.
-It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the $H_0$ steady-state spectrum (Eq.
+We now calculate the distribution of the times it takes each photon to escape the sphere. This is obtained by integrating Eq. \ref{eq:dEdtdnu} over all frequencies. We find
+\be
+P(t)  & = & \sqrt{\frac{3}{2}} \frac{16\pi^2 R \Delta^2 }{3kE}     \sum_{nm} (-1)^n  e^{-\gamma_{nm}t} \int d\sigma J_{nm}(\sigma) 
+\nonumber \\ & = &  \sum_{nm} P_{nm} \gamma_{nm} e^{-\gamma_{nm}t},
+\label{eq:waittime}
+\ee
+which is normalized to unity.
+For a sufficiently large number of spatial modes $n$ and frequency modes $m$, the result of this sum agrees with Monte Carlo escape time distributions.
+% Not sure if we want to say this yet?
+Maybe save for the escape time figure.
+
+The eigenfunction expansion method is an effective characterization of the escape time distribution, yet not a fast enough computational method to use as a distribution for sampling.
+However, the behavior of the solution is well-understood since the late-time distribution is simply an exponential falloff.
+The rate constant is the lowest-order eigenfrequency, $\gamma_{00}$, and its scale is determined by the coefficient $P_{00}$ as in Eq.
+\ref{eq:pnmsoln}.
+Thus, an approximate ``fitting function'' that captures both the peak of the escape time distribution and the exponential falloff is
+\be \label{eq:fitting_function}
+P(t) = \exp{\left[-\left(\frac{t_{\rm diff}}{t}\right)^2\right]} \times \gamma_{00} P_{00} e^{-\gamma_{00}t}.
+\ee
+The first term represents the early-time distribution, which then transitions to an exponential falloff past a point $ct/R = ct_{\rm diff}/R = (a\tau_0)^{1/3}$, where $t_{\rm diff}$ is a characteristic diffusion timescale.
+
+In Fig.
+\ref{fig:tau_scaling}, it is shown that the rate constant of exponential decay $\gamma_00^{-1}$converges with the lowest-order eigenfrequency $\gamma_{00}$ at sufficiently high optical depths, following a $t\propto(a\tau_0)^{1/3}$ scaling.
+At lower optical depths $\tau_0$, the effects of core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
+Here, the Monte Carlo accurately characterizes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile and does not use enough spatial modes to accurately model the frequency regime near line center.
+However, as the optical depth grows, the effect of core scattering becomes smaller and the approximations hold much better, agreeing well with the expected analytic scaling for the rate constant.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.75\textwidth]{tau_scaling.pdf}
+    \caption{Characteristic timescales as a function of optical depth.
+$\gamma_{00}^{-1}$ and a fit of the exponential falloff for the Monte Carlo escape time distribution are shown to converge to a $t \propto (a\tau_0)^{1/3}$ scaling at large optical depths.
+The Monte Carlo points on this figure are obtained by fitting only the exponential piece of the escape time distribution to obtain the rate constant.}
+    \label{fig:tau_scaling}
+\end{figure}
+
+We now evaluate the time-integrated spectrum of the response to an impulse and compare it with the solution for the $H_0$ steady-state spectrum (Eq.
 \ref{eq:H0surf}).
+Integrating Eq.
+\ref{eq:dEdtdnu} over all times gives a distribution for the emitted frequencies.
 Dividing by the energy $E$, we find the probability distribution
@@
 \ee
-Integrating over $\nu$ gives unity according to the sum rule in Eq. \ref{eq:sumrule}.
+Integrating over $\nu$ then gives unity as required by the sum rule in Eq. \ref{eq:sumrule}.
 
 In Fig.
-\ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq.
+\ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq.
 \ref{eq:H0surf_sum}.
@@
 
-The distribution of the times it takes each photon to escape the sphere is calculated from Eq. \ref{eq:dEdtdnu} by integrating over all frequencies. We obtain
-\be
-P(t)  & = & \sqrt{\frac{3}{2}} \frac{16\pi^2 R \Delta^2 }{3kE}     \sum_{nm} (-1)^n  e^{-\gamma_{nm}t} \int d\sigma J_{nm}(\sigma) 
-\nonumber \\ & = &  \sum_{nm} P_{nm} \gamma_{nm} e^{-\gamma_{nm}t},
-\label{eq:waittime}
-\ee
-which is also normalized to unity.
-For a sufficient number of spatial modes $n$ and frequency modes $m$, this sum approaches the ``true'' distribution of photon escape times as modeled by Monte Carlo simulations.
-
-The eigenfunction expansion method is an effective characterization of the time-to-escape, yet not a fast enough computational method to use as a distribution for sampling.
-However, the behavior of the solution is well-understood since the late-time distribution is simply an exponential falloff in photon escape probability.
-The rate constant of the function is the lowest-order eigenfrequency, $\gamma_{00}$, and its scale is determined by the coefficient $P_{00}$ as in Eq.
-\ref{eq:pnmsoln}.
-Thus, an approximate ``fitting function'' that captures both the peak of the escape time distribution and the exponential falloff is
-\be \label{eq:fitting_function}
-P(t) = \exp{\left[-\left(\frac{t_{\rm diff}}{t}\right)^2\right]} \times \gamma_{00} P_{00} e^{-\gamma_{00}t}.
-\ee
-The first term represents the early-time distribution, which then transitions to an exponential falloff past a point $ct/R = ct_{\rm diff}/R = (a\tau_0)^{1/3}$, where $t_{\rm diff}$ is a characteristic diffusion timescale.
-This is shown in Fig.
-\ref{fig:escape_time} for two different line center optical depths.
+In Fig.
+\ref{fig:escape_time} escape time distributions are shown for $tau_0=10^6, 10^7$ with $x_s=0$.
+approaches the Monte Carlo escape time distributions.
 It is seen that the fitting function matches well with the late-time behavior of the eigenfunction solution, indicating that the tail of the escape time distribution can be modeled effectively by simple exponential decay.
@@
 The error in this rate constant is a function of line center optical depth, since the effect from the Doppler core is greatest when it extends into the area of the spectrum where photons most readily escape.
-In Fig.
-\ref{fig:tau_scaling}, it is shown that the rate constant of exponential decay converges with the lowest-order eigenfrequency $\gamma_{00}$ at sufficiently high optical depths, following a $t\propto(a\tau_0)^{1/3}$ scaling.
-At lower optical depths $\tau_0$, the effects of core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
-Here, the Monte Carlo accurately characterizes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile and does not use enough spatial modes to accurately model the frequency regime near line center.
-However, as the optical depth grows, the effect of core scattering becomes smaller and the approximations hold much better, agreeing well with the expected analytic scaling for the rate constant.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.75\textwidth]{tau_scaling.pdf}
-    \caption{Characteristic timescales as a function of optical depth.
-The reciprocal of the lowest-order eigenfrequency, $\gamma_{00}$, and a fit of the exponential falloff for the Monte Carlo data are shown to converge to a $t \propto (a\tau_0)^{1/3}$ scaling at large optical depths.
-The Monte Carlo points on this figure are obtained by fitting only the exponential piece of the escape time distribution to obtain the rate constant.}
-    \label{fig:tau_scaling}
-\end{figure}
-
-\subsection{Emission Away From Line Center}
 
@@
 The primary goal of this work is to present a solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere.
-We have generalized a solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center, and we have made a correction to the incorrect $J=0$ surface boundary condition.
-This correction allows the proper condition $J=\sqrt{3}H$ to be satisfied, and comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$ which are solved using a continuous Fourier expansion in frequency.
+We have generalized a solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center, and we have made a correction to their incorrect $J=0$ surface boundary condition.
+This correction allows the proper condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere, and comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$ which are solved using a continuous Fourier expansion in frequency.
 Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
 In practice, the continuous expansions are discretized and the Fourier coefficients solved for via a matrix equation.
-The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$ where $a$ is the damping parameter and $\tau_0$ is the line-center optical depth.
-Thus, for very large optical depths, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower optical depths.
+The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$.
+Thus, for very large $\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $\tau_0$.
 Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
-The peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$; as such, calculations performed at low optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core of the line profile.
+The peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$; as such, calculations performed at low optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
 By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions %and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency $x_s$ is altered,
-provided a sufficiently large optical depth $\tau_0$.
+provided a sufficiently large $\tau_0$.
 Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition, such as \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others.
+TODO: Give details.
 The surface boundary condition correction $H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which suggests the previously cited solutions are too large at the spectral peaks and too small further out in the wing, where the error scales approximately as $(a\tau_0)^{-1/3}$.

### 2021-09-24 ms.tex
Cleaning up sections up to Discussion

@@
 
-The eigenfunction expansion method is an effective characterization of the escape time distribution, yet not a fast enough computational method to use as a distribution for sampling.
+The eigenfunction expansion method utilized here can produce an effective characterization of the escape time distribution, yet it is not a fast enough computational method to use as a distribution for sampling.
 However, the behavior of the solution is well-understood since the late-time distribution is simply an exponential falloff.
-The rate constant is the lowest-order eigenfrequency, $\gamma_{00}$, and its scale is determined by the coefficient $P_{00}$ as in Eq.
+The rate constant of the falloff is the lowest-order eigenfrequency, $\gamma_{00}$, and its scale is determined by the coefficient $P_{00}$ as in Eq.
 \ref{eq:pnmsoln}.
@@
 In Fig.
-\ref{fig:tau_scaling}, it is shown that the rate constant of exponential decay $\gamma_00^{-1}$converges with the lowest-order eigenfrequency $\gamma_{00}$ at sufficiently high optical depths, following a $t\propto(a\tau_0)^{1/3}$ scaling.
-At lower optical depths $\tau_0$, the effects of core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
+\ref{fig:tau_scaling}, it is shown that the time constant of exponential decay in fitted Monte Carlo escape time distributions converges with $\gamma_{00}^{-1}$ at sufficiently high optical depths, following a $t\propto(a\tau_0)^{1/3}$ scaling.
+At lower optical depths $\tau_0$, the effects of line core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
 Here, the Monte Carlo accurately characterizes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile and does not use enough spatial modes to accurately model the frequency regime near line center.
-However, as the optical depth grows, the effect of core scattering becomes smaller and the approximations hold much better, agreeing well with the expected analytic scaling for the rate constant.
+However, as the optical depth grows, the effect of core scattering becomes smaller and the approximations hold, agreeing well with the expected $(a\tau_0)^{1/3}$ scaling for the rate constant.
 
@@
 \ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq.
-\ref{eq:H0surf_sum}.
+\ref{eq:H0surf}.
 Additional spatial modes contribute to the solutions' accuracy in the core of the line.
@@
 
-In Fig.
-\ref{fig:escape_time} escape time distributions are shown for $tau_0=10^6, 10^7$ with $x_s=0$.
-approaches the Monte Carlo escape time distributions.
+In Figure \ref{fig:escape_time} escape time distributions calculated from Eq.
+\ref{eq:waittime} are shown alongside Monte Carlo and the fitting function Eq.
+\ref{eq:fitting_function} for $\tau_0=10^6, 10^7$ with $x_s=0$.
 It is seen that the fitting function matches well with the late-time behavior of the eigenfunction solution, indicating that the tail of the escape time distribution can be modeled effectively by simple exponential decay.
-The remaining discrepancy between the tail of the distribution and the Monte Carlo data is due to core scattering, which is not accurately modeled by the eigenfunction solution.
+The remaining discrepancy between the tail of the distribution and the Monte Carlo data is likely due to line core scattering which is not modeled by the eigenfunction solution.
 A cumulative distribution function can be created from Eq.
@@
 
-The effect of many scatterings in the Doppler core affects the tail of the escape-time distribution, since photons that become trapped here will take much longer to escape on average.
-This explains the deficit of photons in the semi-analytic escape time distributions at late times, i.e., the rate constant for the exponential falloff is overestimated slightly as compared with the Monte Carlo.
-The error in this rate constant is a function of line center optical depth, since the effect from the Doppler core is greatest when it extends into the area of the spectrum where photons most readily escape.
+The effect of many scatterings in the Doppler core affects the tail of the escape-time distribution, since photons that become trapped here will take longer to escape.
+This explains the deficit of photons in the semi-analytic escape time distributions at late times, in that the rate constant for the exponential falloff is overestimated slightly as compared with the Monte Carlo.
+The error in this rate constant is a function of $\tau_0$ since the effect from the Doppler core is greatest when it extends into the peak of the spectrum.
 
 \section{Discussion}
-% How can you apply the solution?
-Talk about it as an application of the problem that justifies going through the effort of implementing it.
-It reads like an introduction right now, but we can modify it to include less detail.
-% Don't explain exactly what hybrid diffusion models are.
-Remove that paragraph.
-Put a ref in for Smith and Densmore - lot of applications to speed up lya, including core skipping & hybrid diffusion methods.
-Another method that's been widely applied is modified random walk methods, but htose require a solution of transfer in a sphere.
-So, the primary application of this calcuation is to develop that random walk model that will be used in future applicaitons.
-Keep reference to Ahn et al, since they did basically this but not in spherical symmetry.
-% Discussion section: tlak about the differences between what we find and the other results from other papers. Add this as well. 
-% First part of discussion - compare to previous work and summarize differences. Move some of the comparison with Dijkstra to the discussion.
-% Second part - application of solution
 

### 2021-09-24 ms.tex
Fixing formatting of appendix and changing instances of "line center optical depth" to \tau_0

@@
 The main impediment to performing magnetohydrodynamic simulations with fully a coupled radiative transfer solution via Monte Carlo methods is the prohibitive computational cost.
-The number of scatterings a photon undergoes is proportional to the line center optical depth.
+The number of scatterings a photon undergoes is proportional to the line center optical depth, $\tau_0$.
 Near the base of the atmosphere, the line center optical depth is ${\sim}10^9$, so most of the time is spent following photons in these cells.
@@
 
-Starting with the full transfer equation, Eq.
-\ref{app:rteqn_derivation}\ref{eq:finaleqn}, with no photon destruction and a photon emission term given by Eq.
-\ref{app:rteqn_derivation}\ref{eq:jem}, the steady-state transfer equation is
+Starting with the full transfer equation, Eq. \ref{eq:finaleqn}, with no photon destruction and a photon emission term given by Eq. \ref{eq:jem}, the steady-state transfer equation is
 \be
@@
 where $\sigma$ comes from a change of variables in photon frequency (Eq.
-\ref{app:rteqn_derivation}\ref{eq:change_of_variables}) and $\sigma_s$ is the photon frequency of the source.
+\ref{eq:change_of_variables}) and $\sigma_s$ is the photon frequency of the source.
 The boundary condition is that there is no incoming intensity at the surface, which can be written
@@
 
-\subsection{Scaling with Line Center Optical Depth}
+\subsection{Scaling with Line Center Optical Depth $\tau_0$}
 To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$.
@@
 Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value of the line-center optical depth at which the core of the line moves into the peak of the spectrum, which is $\tau_{\rm cp}=7.3\times10^4$.
-Solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower line center optical depths where the peak of the spectrum lies near the core and improve for larger optical depths where the spectral peak is well outside of the line core.
+Solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower $\tau_0$ where the peak of the spectrum lies near the core and improve for larger $\tau_0$ where the spectral peak is well outside of the line core.
 
@@
 The Monte Carlo method is used to solve the transfer equation numerically.
-This method is valid at arbitrarily large optical depths, being restricted only by its computational demand which grows proportionally to the number of photons used and $\tau_0$.
+This method is valid at arbitrarily large $\tau_0$, being restricted only by its computational demand which grows proportionally to the number of photons used and $\tau_0$.
 For each simulation, a total of ${\sim}10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the sphere until escaping, at which point their positions, outgoing angles, and escape frequencies are stored.
@@
     \includegraphics{taubc.pdf}
-    \caption{Boundary condition term $H_{\rm bc}$ scaled by $(a\tau_0)^{1/3}$ shown for increasing line center optical depths.
+    \caption{Boundary condition term $H_{\rm bc}$ scaled by $(a\tau_0)^{1/3}$ shown for increasing $\tau_0$.
 The Monte Carlo data minus the $H_0$ solution should be close to $H_{\rm bc}$ according to Eq.
@@
 In this figure, the photon initialization frequency $x_s$ is shifted by integer multiples of $\tau_0$ in $\sigma$ frequency units (Eq.
-\ref{app:rteqn_derivation}\ref{eq:change_of_variables}) such that the source, now written $\sigma_s$, falls near the peak of the spectrum for each $\tau_0$.
+\ref{eq:change_of_variables}) such that the source, now written $\sigma_s$, falls near the peak of the spectrum for each $\tau_0$.
 For clarity, only the $x > 0$ side of the spectrum is shown.
@@
 The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ is due to the width of the Doppler core with respect to the peak of the spectrum; at lower $\tau_0$, this causes the line profile approximation in the wing (Eq.
-\ref{app:rteqn_derivation}\ref{eq:line_profile_wing}) to break down.
+\ref{eq:line_profile_wing}) to break down.
 From this, we conclude that the errors introduced by the incorrect separation of variables in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others are proportional to $(a\tau_0)^{-1/3}$.
@@
 \ee
-
-% State that this works for some of the poles, but others are missing. Can't capture asymmetry in spectrum. There is some other term that's missing from this analysis.
-
-%The divergent pieces don't contain the piece that can be asymmetric --- the poles we're finding don't allow asymmetry in the specturm.
-
-% Missing something in our contour? Residue theorem doesn't apply in this case? Missing a pole or poles that are not present?
-
-% We're losing some poles due to the boundary but we think that the sum of the decaying solutions is converging fast enough to cut it off somewhere.
-
-% We try this ansatz for the symmetric case and it basically seems to work.
-We show this by numerical calculation.
-We have to point out that we've shown it doesn't work for an off-center source.
-But then what do we say?
-We don't really have an explanation for how it doens't work.
-WKB gives info about it, but we don't discuss thta in the paper either.
-
-% Put a little wkb in the appendix?
-We could show the dispersion relation, for instnace.
-d^2Jdsigma^2, equation for discontinuity...
-here is the solution far from LC, here is the solution near LC, by requiring these two solutions to match in the raea where they're both valid, here are the matching conditions.
-4-5 lines.
-Here's the presence of simple poles, gives us dispersion relation, but also here's the piece that is not divergent and containts the discontinuity.
-This term is not included in the sum over simple poles.
-Don't go through the derivation in a lot of detail.
-
-% After we do the symmetric case, note that due to what we found in the WKB, this does not capture the asymmetry in the source function.
-Leave it there and just.
-Don't say it's left for future work.
-Just leave it.
-Note that there's an issue and say "this suggests that our ansatz is incomplete in the asymmetric case."
-
-% WKB Approximation - could cite (Bender & Norzog)? Arfken might have it too?
-
-% Change ordering of figures. Have current fig 8 and 9 be the last thing since they contain a sum over modes. Put solid results first.
-
-% Go through derivation of dispersion relation, then say "the denominator being zero leads to the dispersion relation (cite eq 47 in time dependent section)".
+This ansatz captures the contributions from $n \times m$ simple poles, which seems to agree with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
+However, the analysis presented in Appendix \ref{app:wkb} suggests the ansatz is incomplete in the case where $x_s \neq 0$ and the spectrum is asymmetric.
 
@@
 where the line profile is approximated as in Eq.
-\ref{app:rteqn_derivation}\ref{eq:line_profile_wing}.
+\ref{eq:line_profile_wing}.
 When the coefficient on the right hand side is positive, exponential growth or decay solutions are found (evanescence).
@@
 In Fig.
-\ref{fig:tau_scaling}, it is shown that the time constant of exponential decay in fitted Monte Carlo escape time distributions converges with $\gamma_{00}^{-1}$ at sufficiently high optical depths, following a $t\propto(a\tau_0)^{1/3}$ scaling.
-At lower optical depths $\tau_0$, the effects of line core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
+\ref{fig:tau_scaling}, it is shown that the time constant of exponential decay in fitted Monte Carlo escape time distributions converges with $\gamma_{00}^{-1}$ at sufficiently high $\tau_0$, following a $t\propto(a\tau_0)^{1/3}$ scaling.
+At lower $\tau_0$, the effects of line core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
 Here, the Monte Carlo accurately characterizes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile and does not use enough spatial modes to accurately model the frequency regime near line center.
-However, as the optical depth grows, the effect of core scattering becomes smaller and the approximations hold, agreeing well with the expected $(a\tau_0)^{1/3}$ scaling for the rate constant.
+However, as $\tau_0$ grows, the effect of core scattering becomes smaller and the approximations hold, agreeing well with the expected $(a\tau_0)^{1/3}$ scaling for the rate constant.
 
@@
     \includegraphics[width=0.75\textwidth]{tau_scaling.pdf}
-    \caption{Characteristic timescales as a function of optical depth.
-$\gamma_{00}^{-1}$ and a fit of the exponential falloff for the Monte Carlo escape time distribution are shown to converge to a $t \propto (a\tau_0)^{1/3}$ scaling at large optical depths.
+    \caption{Characteristic timescales as a function of $\tau_0$.
+$\gamma_{00}^{-1}$ and a fit of the exponential falloff for the Monte Carlo escape time distribution are shown to converge to a $t \propto (a\tau_0)^{1/3}$ scaling at large $\tau_0$.
 The Monte Carlo points on this figure are obtained by fitting only the exponential piece of the escape time distribution to obtain the rate constant.}
@@
     \includegraphics{waittime.pdf}
-    \caption{A wait time distribution of escaping photons for two different line center optical depths $\tau_0$, which is fit using Eq.
+    \caption{Wait time distributions of escaping photons for $\tau_0=10^6$ and $10^7$, which is fit using Eq.
 \ref{eq:fitting_function}.
@@
 Models of heating and escape of hydrogen gas in exoplanet atmospheres can be constructed with an accurate treatment of resonant scattering of \lya in spherical geometry.
-The Monte Carlo method can be used for this problem, but requires a solution of radiative transfer in a sphere and is limited by its high computational demand for large optical depths where there are many photon scatterings before escape.
+The Monte Carlo method can be used for this problem, but requires a solution of radiative transfer in a sphere and is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
 The primary goal of this work is to present a solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere.
@@
 Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
-The peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$; as such, calculations performed at low optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
+The peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$; as such, calculations performed at low $\tau_0$ are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
 By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions %and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency $x_s$ is altered,
@@
 The key result is that the errors in the previously-cited works have been quantified via a corrective boundary term, $H_{\rm bc}$, which resolves an excess in flux at the spectral peak and a deficit in the line wing of the calculated spectrum of \lya radiation as compared with Monte Carlo.
-The size of $H_{\rm bc}$ diminishes at larger optical depths, following a predictable $(a\tau_0)^{-1/3}$ scaling.
+The size of $H_{\rm bc}$ diminishes at larger $\tau_0$, following a predictable $(a\tau_0)^{-1/3}$ scaling.
 Introducing time-dependence back into the transfer equation leads to another solution which is obtained with a discretized eigenfunction expansion and solved numerically.
@@
 The time-dependent solution is utilized to create wait-time distributions for photons escaping the sphere of optically-thick hydrogen gas, which can be sampled in lieu of direct Monte Carlo simulations that would ordinarily be computationally demanding.
-We compare the calculations from the time-dependent solution with Monte Carlo for a sample of line-center optical depths, noting general agreement in the resulting escape time distributions.
-In future work, these distributions will be fitted and used to accelerate Monte Carlo \lya transfer at large optical depths with potential applications in radiation hydrodynamic simulations of the atmospheres of exoplanets.
+We compare the calculations from the time-dependent solution with Monte Carlo for a sample of $\tau_0$, noting general agreement in the resulting escape time distributions.
+In future work, this will be used to accelerate Monte Carlo \lya transfer at large optical depths with potential applications in radiation hydrodynamic simulations of the atmospheres of exoplanets.
 
 \acknowledgments
+\restartappendixnumbering
 
 \appendix
-\restartappendixnumbering
 \section{ derivation of the transfer equation } \label{app:rteqn_derivation}
@@
 
+\section{WKB Approximation} \label{app:wkb}
+
+% Put a little wkb in the appendix?
+We could show the dispersion relation, for instnace.
+d^2Jdsigma^2, equation for discontinuity...
+here is the solution far from LC, here is the solution near LC, by requiring these two solutions to match in the raea where they're both valid, here are the matching conditions.
+4-5 lines.
+Here's the presence of simple poles, gives us dispersion relation, but also here's the piece that is not divergent and containts the discontinuity.
+This term is not included in the sum over simple poles.
+Don't go through the derivation in a lot of detail.
+
+% WKB Approximation - could cite (Bender & Norzog)? Arfken might have it too?
+
+% Go through derivation of dispersion relation, then say "the denominator being zero leads to the dispersion relation (cite eq 47 in time dependent section)".
+
 \bibliography{ref.bib}{}

### 2021-09-24 ms.tex
Adding WKB appendix

@@
 and the discontinuity in $dJ/d\sigma$  must be
-\be \label{matching_condition_2}
+\be \label{eq:matching_condition_2}
 \frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
@@
 We obtain
-\be
+\be \label{eq:wkb_differential_eqn}
 \frac{d^2J}{d\sigma^2} & = & \left[ \left( \frac{\kappa_n \Delta }{k} \right)^2 - \frac{3\phi \gamma\Delta^2}{ck}\right] J,
@@
 The boundary between propagation and evanescence occurs at the turning point, given by
-\be
+\be \label{eq:sigma_tp}
 \sigma_{tp} & = & \sqrt{\frac{2a}{\pi}}\left( \frac{k \gamma}{ \kappa_n^2 c \Delta} \right)^{3/2}
@@
 
+We start with the differential equation Eq. \ref{eq:wkb_differential_eqn}. Near line center, this has two independent solutions which can be written
+\be
+J(n,\sigma,s) & = & a_1 \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{1/2} J_{-3/4}\left[ k_c \left( \frac{\sigma}{\sigma_{\rm tp} }\right)^{2/3} \right]
+\nonumber \\ &  + &  a_2 \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{1/2} J_{3/4}\left[ k_c \left( \frac{\sigma}{\sigma_{\rm tp} }\right)^{2/3} \right],
+\ee
+where $a_1$ and $a_2$ are a normalization constants, $\sigma_{tp}$ is given in Eq. \ref{eq:sigma_tp}, and $k_c=3\kappa_n \Delta \sigma_{\rm tp}/2k$. The solution far from line center is 
+\be
+J(n,\sigma,s) & = & a_3 \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{1/6} Ai\left(k_c^{2/3} \left[ \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{2/3} - 1 \right]\right),
+\ee
+where $Ai(...)$ is the Airy function of the first kind. Again, $a_3$ is a normalization constant. When $\sigma_s=0$, we can enforce the discontinuity in Eq. \ref{eq:matching_condition_2} to find 
+\be
+a_2 & = & - \frac{\Gamma(7/4) \sigma_{\rm tp}}{ 2^{1/4} k_c^{3/4}} \frac{6^{1/2}}{8} n^2 \frac{E}{kR^3}.
+\ee
+The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$.
+However, we may also show that the solutions near and far from $\sigma=0$ have the same form where both functions have short-wavelength behavior.
+This allows us to relate the normalization coefficients $a_1$ and $a_3$, as well as quantize the phase of the solutions to determine a dispersion relation.
+The matching conditions are
+\be
+a_1 & = & |a_2| \\ 
+a_3 & = & |a_2| 2^{3/2} k_c^{-1/3}, \\
+\ee
+and the phase is set by
+\be
+\frac{\kappa_n \sigma_{tp} \Delta}{k} & = & 2\pi b
+\ee
+to match the two solutions, where $b$ is a positive integer.
+Since $\sigma_{tp}$ contains the eigenvalue, we can solve the expression for $\gamma_{nm}$ to find the dispersion relation in Eq.
+\ref{eq:gamma_nm}.
+
 \bibliography{ref.bib}{}

### 2021-09-27 ms.tex
Finishing first round of time-dependent edits

@@
 For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$.
-Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$.
-Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value of the line-center optical depth at which the core of the line moves into the peak of the spectrum, which is $\tau_{\rm cp}=7.3\times10^4$.
-Solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower $\tau_0$ where the peak of the spectrum lies near the core and improve for larger $\tau_0$ where the spectral peak is well outside of the line core.
+Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=4.6$.
+Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value of the line-center optical depth at which the core of the line moves into the peak of the spectrum, which is $\tau_{\rm cp} {\sim} 10^5$.
+At fixed temperature, solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower $\tau_0$ where the peak of the spectrum lies near the core and improve for larger $\tau_0$ where the spectral peak is well outside of the line core.
 
@@
 
-% TODO: Edits unclear. Organization of sentences OK? "Describe what's in the figure and then discuss" - Mention of Hd moved to end of paragraph, details of the Hbc term moved higher up.
-In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown with that of the solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
+In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown with that of the solutions $H_{\rm d}$, $H_0$, and $H_{\rm 0 + bc} = H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
 The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, it adequately corrects for the apparent excess of flux in the peaks of the spectrum.
-This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S} where the discrepancy is particularly noticeable for line center optical depths of $\tau_0=10^5$ and $10^6$ in the top panel of their Figure 5.
-The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
-The boundary term corrects the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
+The solution with the correct frequency-dependent boundary condition enforced, $H_{0 + \rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
+The boundary term corrects the slight deficit of $H_0$ in the line wings, further improving agreement with the numerical result.
 Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.
@@
 \ee
+as shown in Appendix \ref{app:wkb}.
 The size of additional eigenfrequencies scales as a power law in $m$, yet as is seen in Fig.
@@
 
-The effect of many scatterings in the Doppler core affects the tail of the escape-time distribution, since photons that become trapped here will take longer to escape.
+The effect of many scatterings in the Doppler core affects the tail of the escape-time distribution, since photons with frequencies near line center will take longer to escape.
 This explains the deficit of photons in the semi-analytic escape time distributions at late times, in that the rate constant for the exponential falloff is overestimated slightly as compared with the Monte Carlo.
@@
 
-Models of heating and escape of hydrogen gas in exoplanet atmospheres can be constructed with an accurate treatment of resonant scattering of \lya in spherical geometry.
-The Monte Carlo method can be used for this problem, but requires a solution of radiative transfer in a sphere and is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
+Models of the escape of hydrogen gas in exoplanet atmospheres can be constructed with a treatment of resonant scattering of \lya in spherical geometry.
+The Monte Carlo method can be used for this problem, but requires a solution of the radiative transfer equation in spherical geometry and is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
 The primary goal of this work is to present a solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere.
 We have generalized a solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center, and we have made a correction to their incorrect $J=0$ surface boundary condition.
-This correction allows the proper condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere, and comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$ which are solved using a continuous Fourier expansion in frequency.
+This correction allows the proper condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere, and comes from the introduction of the term $J_{\rm bc}$ which is solved using a continuous Fourier expansion in frequency.
 Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
-In practice, the continuous expansions are discretized and the Fourier coefficients solved for via a matrix equation.
+The continuous expansions are discretized and the Fourier coefficients solved for.
 The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$.
 Thus, for very large $\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $\tau_0$.
-Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
-The peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$; as such, calculations performed at low $\tau_0$ are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
-By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions %and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency $x_s$ is altered,
-provided a sufficiently large $\tau_0$.
-Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition, such as \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others.
-TODO: Give details.
-The surface boundary condition correction $H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which suggests the previously cited solutions are too large at the spectral peaks and too small further out in the wing, where the error scales approximately as $(a\tau_0)^{-1/3}$.
+Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, our solutions do not model areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
+The peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$; as such, calculations performed at low $\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
+This effect is especially prevalent for larger H gas temperature, as the boundary between the Doppler core and line wing extends further out as $T$ increases.
+
+By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions provided a sufficiently large $\tau_0$.
+Specifically, this solution shows improvement over previous solutions that utilized the $J=0$ surface boundary condition presented in \cite{1973MNRAS.162...43H} and \cite{1990ApJ...350..216N}.
+For example, in the top-left panel of Figure 1 from \cite{2006ApJ...649...14D}, the \lya spectrum emergent from a sphere of uniform optical depth is shown for $\tau_0=10^5, 10^6,$ and $10^7$ at a temperature of $T=10$ K, corresponding to $a=1.5 \times 10^{-2}$.
+The dotted line showing their theoretically-derived spectrum (called $H_0$ here) displays an excess at the peak of at least 5-10 percent as compared with the Monte Carlo for $\tau_0=10^5$ and $10^6$.
+Though our calculations were performed with a higher gas temperature of $T=10^4$ K, we show in Figure \ref{fig:sol_mc_tau} that the excess present in $H_0$ is corrected by our treatment of the boundary condition at $\tau_0 = 10^7$.
+In \citet{2015MNRAS.449.4336S}, the peak excess in the \lya spectrum is particularly noticeable for line center optical depths of $\tau_0=10^6$ and $10^7$ in the top panel of their Figure 5, which used slab geometry and a gas temperature of $T=10^4$ K.
+Again, the error in their solution is of order 5-10 percent, which our boundary condition treatment corrects for.
+$H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which matches with the discrepancies noted in the previously cited solutions.
+They are too large at the spectral peaks and too small further out in the wing, and the error scales approximately as $(a\tau_0)^{-1/3}$.
 This appears to be the consequence of not enforcing the correct frequency-dependent boundary conditions at the surface of the medium.
 
-Additionally, the time-dependence of the problem is solved under a $J=0$ boundary condition to characterize the distribution of photon escape times.
+The time-dependence of the problem is solved under a $J=0$ boundary condition to characterize the distribution of photon escape times.
 The differential equation cannot be solved except with a semi-analytic approach, utilizing an expansion in both space and photon frequency.
-By matching boundary conditions on either side of the photon source frequency $x_s$, the flux at the surface of the sphere is found as a function of $t$ and $\nu$, expressed as a sum over many eigenmodes $n$ and $m$---spatial and frequency modes, respectively.
+By matching boundary conditions on either side of the photon source frequency $x_s$, the flux at the surface of the sphere is found as a function of $t$ and $\nu$, expressed as a sum over spatial and frequency modes $n$ and $m$, respectively.
 Calculating additional spatial eigenmodes provides a more accurate model of the physics nearer to line center, but convergence is slow due to each eigenmode's weak dependence on $n$.
@@
 The sum over eigenmodes produces an escape-time distribution that broadly captures the behavior shown by Monte Carlo data---a rise at early times, transitioning to exponential decay in the tail of the distribution.
-It is expected that the accuracy of the rate constant for the tail of the distribution is limited by the number of spatial terms included in the sum over eigenmodes, as the Doppler core can trap photons at high optical depths until they diffuse outward in frequency, biasing the distribution toward later times.
+It is expected that the accuracy of the rate constant for the tail of the distribution is limited by the number of spatial terms included in the sum over eigenmodes, as the Doppler core can trap photons at high optical depths until they diffuse outward in frequency, weighting the distribution toward later times.
 This physics is not modeled by our solution for two reasons: 1) our calculations ignored the Gaussian component of the Voigt line profile, leaving the Lorentzian piece which is accurate only in the line wing, and 2) knowing the core is not modeled accurately, we do not include a large enough number of spatial eigenmodes in the sum to resolve it.
@@
 Another approach with wide application is modified random walk methods, such as those discussed in \citet{2002ApJ...567..922A,2015MNRAS.449.4336S} in which Monte Carlo code acceleration is performed for large optical depths in a uniform plane-parallel medium with no absorption.
-These calculations would need to be generalized to spherical symmetry in order to construct a models of resonant scattering in exoplanet atmospheres as discussed in Section \ref{sec:intro}.
-The underlying principle is the same, however: an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation.
+These calculations would need to be generalized to spherical geometry in order to construct a models of resonant scattering in exoplanet atmospheres as discussed in Section \ref{sec:intro}.
+The underlying principle is the same, however: an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.
 A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution, but this solution of course does not use the correct frequency-dependent boundary condition at the surface of the sphere.
@@
 The key result is that the errors in the previously-cited works have been quantified via a corrective boundary term, $H_{\rm bc}$, which resolves an excess in flux at the spectral peak and a deficit in the line wing of the calculated spectrum of \lya radiation as compared with Monte Carlo.
-The size of $H_{\rm bc}$ diminishes at larger $\tau_0$, following a predictable $(a\tau_0)^{-1/3}$ scaling.
-Introducing time-dependence back into the transfer equation leads to another solution which is obtained with a discretized eigenfunction expansion and solved numerically.
-We demonstrate that it agrees with the steady-state result when integrated over time, though its rate of numerical convergence is quite slow and requires a sum over many modes to become accurate.
+The size of $H_{\rm bc}$ diminishes at larger $\tau_0$, following a $(a\tau_0)^{-1/3}$ scaling.
+Introducing time-dependence to the transfer equation leads to another solution which is solved with an eigenfunction expansion and solved numerically.
+We demonstrate that it agrees with the steady-state spectrum for $x_s=0$ when integrated over time, though its rate of numerical convergence is slow and requires a sum over many modes to become accurate.
+This treatment is incomplete for emission away from line center ($x_s\neq0$), however, since any terms that would allow asymmetry in the spectrum are not present in the sum.
 The time-dependent solution is utilized to create wait-time distributions for photons escaping the sphere of optically-thick hydrogen gas, which can be sampled in lieu of direct Monte Carlo simulations that would ordinarily be computationally demanding.
@@
 
-Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
-The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
-The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$.
-For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
 The transfer equation is \citep{1986rpa..book.....R}
@@
 \be
-\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{\mathcal{H}(x,a)}{\sqrt{\pi} \Delta}
+\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{\mathcal{H}(x,a)}{\sqrt{\pi} \Delta}.
 = k \phi   
 \ee
-where $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
 The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section.
@@
 \be
-J(n,\sigma,s) & = & a_1 \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{1/2} J_{-3/4}\left[ k_c \left( \frac{\sigma}{\sigma_{\rm tp} }\right)^{2/3} \right]
-\nonumber \\ &  + &  a_2 \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{1/2} J_{3/4}\left[ k_c \left( \frac{\sigma}{\sigma_{\rm tp} }\right)^{2/3} \right],
-\ee
-where $a_1$ and $a_2$ are a normalization constants, $\sigma_{tp}$ is given in Eq. \ref{eq:sigma_tp}, and $k_c=3\kappa_n \Delta \sigma_{\rm tp}/2k$. The solution far from line center is 
+J(n,\sigma,s) & = & a_1 \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{1/2} J_{-3/4}\left( k_c \left[ \frac{\sigma}{\sigma_{\rm tp} }\right]^{2/3} \right)
+\nonumber \\ &  + &  a_2 \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{1/2} J_{3/4}\left( k_c \left[ \frac{\sigma}{\sigma_{\rm tp} }\right]^{2/3} \right),
+\ee
+where $J_\alpha(...)$ are Bessel functions of the first kind, $a_1$ and $a_2$ are normalization constants, $\sigma_{tp}$ is given in Eq.
+\ref{eq:sigma_tp}, and $k_c=3\kappa_n \Delta \sigma_{\rm tp}/2k$.
+The solution far from line center is
 \be

### 2021-09-28 ms.tex
Fixing matching conditions in WKB appendix

@@
 It is shown that the size of corrective term depends on the line center optical depth, and may explain discrepancies in previous studies that used a $J=0$ boundary condition.
-For the impulsive problem, the time dependence, spatial dependence, and photon frequency dependence of the diffusion equation is expressed using an eigenfunction expansion and solved numerically to characterize the escape time distribution and spectra of photons initialized at the center of the sphere.
+For the impulsive problem, the time dependence, spatial dependence, and photon frequency dependence of the diffusion equation are expressed using an eigenfunction expansion and solved numerically to characterize the escape time distribution and spectra of photons initialized at the center of the sphere.
 It is shown that the lowest-order eigenfrequency of the semi-analytic calculation agrees well with the decay constant of the Monte Carlo escape time distribution at line-center optical depths above ${\sim} 10^7$.
@@
 If more spatial modes are calculated, the agreement with the steady state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x_s$.
-If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over $\gamma$ which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
-Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would only affect the distribution at late times since photons are trapped for a longer duration before escaping.
+If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over eigenmodes which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
+Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would primarily affect the distribution at late times due to the large mean diffusion time of photons near the line core.
 This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated.
@@
 It is seen that the fitting function matches well with the late-time behavior of the eigenfunction solution, indicating that the tail of the escape time distribution can be modeled effectively by simple exponential decay.
-The remaining discrepancy between the tail of the distribution and the Monte Carlo data is likely due to line core scattering which is not modeled by the eigenfunction solution.
+The remaining disagreement between the tail of the distribution and the Monte Carlo data is likely due to line core scattering which is not modeled by the eigenfunction solution, but improves for larger optical depth as seen in the figure.
 A cumulative distribution function can be created from Eq.
@@
 The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$.
-However, we may also show that the solutions near and far from $\sigma=0$ have the same form where both functions have short-wavelength behavior.
-This allows us to relate the normalization coefficients $a_1$ and $a_3$, as well as quantize the phase of the solutions to determine a dispersion relation.
+However, where both functions have short-wavelength behavior we may show that the solutions near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines.
+This matched asymptotic expansion allows us to relate the normalization coefficients $a_1$ and $a_3$.
 The matching conditions are
 \be
-a_1 & = & |a_2| \\ 
-a_3 & = & |a_2| 2^{3/2} k_c^{-1/3}, \\
-\ee
-and the phase is set by
-\be
-\frac{\kappa_n \sigma_{tp} \Delta}{k} & = & 2\pi b
-\ee
-to match the two solutions, where $b$ is a positive integer.
-Since $\sigma_{tp}$ contains the eigenvalue, we can solve the expression for $\gamma_{nm}$ to find the dispersion relation in Eq.
+\frac{a_1}{a_2} & = & \frac{ \sin \left( \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} + \frac{\pi}{8} \right) }{ \sin \left(  \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} - \frac{\pi}{8} \right) }
+\\
+\frac{a_3}{a_2} & = & \frac{ k_c^{-1/3} }{ \sin \left(  \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} - \frac{\pi}{8} \right) }.
+\ee
+By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ which is contained in $\sigma_{tp}$, we find the dispersion relation in Eq.
 \ref{eq:gamma_nm}.

### 2021-09-29 ms.tex
Fixing undefined reference to eq:matching_condition_2

@@
 By enforcing the matching conditions, Eqs.
-\ref{eq:matching_condition_1} and \ref{matching_condition_2}, the eigenfunctions $J(n, \sigma, \omega)$ are obtained for all photon frequencies $\sigma$.
+\ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}, the eigenfunctions $J(n, \sigma, \omega)$ are obtained for all photon frequencies $\sigma$.
 Since the eigenfunctions are linear in the starting conditions, only two integrations with different starting values are necessary.
@@
 \ee
-By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ which is contained in $\sigma_{tp}$, we find the dispersion relation in Eq.
-\ref{eq:gamma_nm}.
+By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{tp}$, we find the dispersion relation in Eq. \ref{eq:gamma_nm}.
 

### 2021-10-05 ms.tex
removing a comment
incorporating Shane's edits to abstract, removing all instances of "very" as a descriptive term

@@
 \renewcommand{\vec}[1]{\mathbf{#1}}
-%\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}} %boldface vector style
 \newcommand{\grad}{\mathbf{\nabla}}
@@
 The intensity within the sphere and at its surface is found in the limit of large line-center optical depth using the Eddington approximation for the angular dependence.
-Two specific problems are studied: a steady source and an impulsive source.
-For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the homogeneous equation with the mean intensity $J=0$ at the surface, and a novel, semi-analytic solution of the homogeneous equation which enforces the correct, zero-ingoing intensity boundary conditions at the surface.
+Two specific limits are studied: a steady source and an impulsive source.
+For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with the mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct zero-ingoing intensity at the surface.
 This solution is compared to that of the Monte-Carlo method, which is valid at arbitrary optical depth.
 It is shown that the size of corrective term depends on the line center optical depth, and may explain discrepancies in previous studies that used a $J=0$ boundary condition.
-For the impulsive problem, the time dependence, spatial dependence, and photon frequency dependence of the diffusion equation are expressed using an eigenfunction expansion and solved numerically to characterize the escape time distribution and spectra of photons initialized at the center of the sphere.
+For the impulsive problem, the time, spatial, and frequency dependence of the diffusion equation are expressed using an eigenfunction expansion and solved numerically to characterize the escape time distribution and spectra of photons initialized at the center of the sphere.
 It is shown that the lowest-order eigenfrequency of the semi-analytic calculation agrees well with the decay constant of the Monte Carlo escape time distribution at line-center optical depths above ${\sim} 10^7$.
-A fitting function for the distribution is found which can be sampled to accelerate Monte Carlo radiation transfer calculations at very large optical depths.
+A fitting function for the distribution is found which can be sampled to accelerate Monte Carlo radiation transfer calculations at large optical depths.
 
@@
 \ee
-This solution is useful as a very simple analytic formula.
+This solution is useful as a simple analytic formula.
 However, it is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$ and does not adhere to the correct boundary condition.
@@
 \ee
-Again $J_0 \gg H_0$, except very near the $r=R$, where it goes to zero. The flux at $r=R$ can be written
+Again $J_0 \gg H_0$, except near the $r=R$, where it goes to zero. The flux at $r=R$ can be written
 \be
@@
 The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that  the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries.
-The number of points was increased until the solution was well-resolved near line center, and only became inaccurate very near the boundaries.
+The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries.
 Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq.
@@
 Thus, the fractional importance of the correct frequency-dependent boundary condition term $H_{\rm bc}$ scales as $(a\tau_0)^{-1/3}$.
-At very large $\tau_0$, it is expected that the correction term will be small, but will become increasingly important as $\tau_0$ decreases.
+At large $\tau_0$, it is expected that the correction term will be small, but will become increasingly important as $\tau_0$ decreases.
 
@@
 These coefficients are negative for odd values of $n$ and positive for even $n$.
-The size of each contribution scales roughly as $0.5/(m-7/8)^{2/3}$, with a very weak dependence on $n$.
+The size of each contribution scales roughly as $0.5/(m-7/8)^{2/3}$, with a weak dependence on $n$.
 This indicates the need for a large number of $n$ and $m$ to converge, in that it takes roughly ten times as many $m$ modes to reduce the size of $P_{nm}$ by a factor of ${\sim}$5.
@@
 The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$.
-Thus, for very large $\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $\tau_0$.
+Thus, for large $\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $\tau_0$.
 Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, our solutions do not model areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.

### 2021-10-05 ms.tex
Incorporating Shane's edits to introduction

@@
 The outer layers of planetary atmospheres are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
-Ionization and subsequent recombination can generate \lya within the planet's atmosphere, dissociating molecules in lower layers and creating pressure forces that drive an outflow of escaping H atoms.
+Ionization and subsequent recombination can generate \lya within the planet's atmosphere, dissociating molecules in lower layers and creating pressure forces that drive an outflow.
 \lya can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy \citep{2017ApJ...851..150H}.
@@
 
-Numerical simulations can be used to understand the complex layers of these irradiated exoplanet atmospheres.
-However, the extreme optical depths at \lya line center introduce a computational barrier to simulating radiative transfer via Monte Carlo methods.
-The main impediment to performing magnetohydrodynamic simulations with fully a coupled radiative transfer solution via Monte Carlo methods is the prohibitive computational cost.
+Numerical simulations can be used to understand the dynamics of these irradiated exoplanet atmospheres.
+The extreme optical depths at \lya line center impose a large computational cost for solving radiative transfer with Monte Carlo methods directly coupled with magnetohydrodynamic simulations.
 The number of scatterings a photon undergoes is proportional to the line center optical depth, $\tau_0$.
 Near the base of the atmosphere, the line center optical depth is ${\sim}10^9$, so most of the time is spent following photons in these cells.
-A method that can treat these zones via a simple solution rather than Monte Carlo has the potential to greatly accelerate the calculation.
+A method that can treat these zones incorporating a direct solution rather than traditional Monte Carlo has the potential to greatly accelerate the calculation.
+
 A complete, general analytic solution for the resonance scattering has never been derived but approximate solutions exist in certain limits.
-
 \citet{1973MNRAS.162...43H} demonstrated in slab geometry that resonance-line radiation transfer in optically-thick media can be described by the Poisson equation.
@@
 \ee
-where $2B$ is the slab optical depth at line center, and $\phi$ is the line profile.
+where $2B$ is the slab optical depth at line center, $\phi$ is the line profile, and $\Delta$ is the Doppler width.
 The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
-Thus, the separation constant is not constant, and it does not satisfy the Poisson equation since the frequency derivatives will act on the separation ``constant", giving extra terms.
+Thus, the separation constant is not constant, and the solution does not satisfy the Poisson equation since the frequency derivatives will act on the separation ``constant", giving extra terms.
 In the limit of large optical depth $B$, they approximate the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$.
@@
 \citet{2006ApJ...649...14D} generalize the same problem to spherical geometry, as is used here.
-Following this, \citet{2015MNRAS.449.4336S} employ a ``core skipping'' method to handle photon frequency redistribution within the Doppler core.
-This technique involves drawing the atom's velocity from a truncated Gaussian distribution, forcing photons back into the wing when they scatter into the core.
-% This is motivated by the assumption that all core scattering results in zero spatial diffusion until the photon is redistributed back out into the wing where the mean free path becomes much larger and it can diffuse in space again.
-However, it is not clear whether this prescription is fully independent of the choice of velocity distribution.
 

### 2021-10-05 ms.tex
plugging in -> inserting, edits up to eq. 14 from Shane

@@
 We aim to find the intensity within the sphere as a function of radius and photon frequency.
-Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered.
-The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
-The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$.
+Photons of frequency $\nu$ near the line center frequency $\nu_0$ are considered.
+The Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
+The photon frequency in Doppler units is $x = (\nu-\nu_0)/\Delta$.
 For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
-$n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
-The line center optical depth is then $\tau_0 = (k/\sqrt{\pi}\Delta)R$.
+$n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} \pi e^2 f/(m_e c)$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+The line center optical depth is then $\tau_0 = kR/(\sqrt{\pi}\Delta)$.
 
@@
 \ee
-where $\sigma$ comes from a change of variables in photon frequency (Eq.
-\ref{eq:change_of_variables}) and $\sigma_s$ is the photon frequency of the source.
-The boundary condition is that there is no incoming intensity at the surface, which can be written
-\citep{1986rpa..book.....R}
+where $J$ is the mean intensity, $\sigma$ represents a change of variables in photon frequency (Eq.
+\ref{eq:change_of_variables}) and $\sigma_s$ is is the photon frequency of the source.
+$\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler units or Hz, respectively.
+The boundary condition that there is no incoming intensity at the surface \citep{1986rpa..book.....R} can be written as
 \be
@@
 This solution is included in Fig.
-\ref{fig:sol_mc_residual_0} for illustration, but will not be discussed further.
+\ref{fig:sol_mc_residual_0} for illustration.
 
@@
 Eq.
-\ref{eq:H0surf} will be shown to be a much better approximation to the solution than Eq.
+\ref{eq:H0surf} will be shown to be a better approximation to the solution than Eq.
 \ref{eq:Hd}.
-It is still valid near the delta function at $r=0$, but is also a much better approximation at $r=R$.
-$J_0$ decreases exponentially rather than as a power-law in frequency as for $J_d$, giving a much smaller flux on the line wings as compared to the divergent solution.
+It is still valid near the delta function at $r=0$, but is also a better approximation at $r=R$.
+$J_0$ decreases exponentially rather than as a power-law in frequency as it does for $J_d$, giving a much smaller flux on the line wings as compared to the divergent solution.
 
@@
 \ee
-Here, $J_0$ and $H_0$ are the solutions of the homogeneous equation, given in Equations \ref{eq:J0} and \ref{eq:H0}.
-The additional term $J_{\rm bc}$ must then be a solution of the homogeneous equation
+Here, $J_0$ and $H_0$ are given in Equations \ref{eq:J0} and \ref{eq:H0}. The additional term $J_{\rm bc}$ must then be a solution of the homogeneous equation
 \be \label{eq:diffeq}
@@
 \ee
-Plugging in a frequency dependence $J_{\rm bc} \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$.
+Inserting a frequency dependence $J_{\rm bc} \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$.
 The solution can then be represented as
@@
 \ee
-where $A(s)$ is the Fourier amplitude. Plugging Eq. \ref{eq:Jbc} into Eq. \ref{eq:bc2} leads to the following equation for the Fourier amplitudes,
+where $A(s)$ is the Fourier amplitude. Inserting Eq. \ref{eq:Jbc} into Eq. \ref{eq:bc2} leads to the following equation for the Fourier amplitudes,
 \be
@@
 \ref{eq:jnsigmaomega} is in the same units, but with an additional unit of $t$ in the numerator as a result of the expansion.
-Plugging in Eq.
+Inserting Eq.
 \ref{eq:jnsigmaomega} for the eigenfunctions in Eq.

### 2021-10-05 ms.tex
Adding some description of derivation back into scaling with line center optical depth

@@
 
- %TODO
-
 A different solution method is attempted here, namely, a continuous Fourier expansion in the frequency variable $\sigma$.
@@
 \left[ 1 + \left( \frac{s}{\sqrt{3} \Delta \phi} \right) \left( \frac{i_0^\prime(kRs/\Delta)}{i_0(kRs/\Delta)} \right) \right]
-& = & \sqrt{3} H_0(R,\sigma)
+& = & \sqrt{3} H_0(R,\sigma).
 \label{eq:bc3}
 \ee
-where $H_0(R,\sigma)$ is given by Eq. \ref{eq:H0surf}. Discretization of Eq. \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
+Discretization of Eq. \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
 leads to a set of coupled linear equations for the $A(s_j)$.
@@
 The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that  the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries.
-The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries.
+The number of points was increased until the solution was well-resolved near line center, and only became inaccurate close to the boundaries.
 Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq.
@@
 \subsection{Scaling with Line Center Optical Depth $\tau_0$}
-To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$.
-We obtain the proportionality
+
+To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$.
+In this limit, $J_{\rm bc} \approx \sqrt{3} H_0$.
+We evaluate Eq.
+\ref{eq:Jbc} at $r=R$ and solve for the Fourier coefficients, $A(s)$.
+These are then used in Eq.
+\ref{eq:Hbc} to find $H_{\rm bc}(R, \sigma)$.
+Dividing by the contribution from $H_0$, we obtain the proportionality
 \be \label{eq:hbc_scaling}
@@
 \ee
-Thus, the fractional importance of the correct frequency-dependent boundary condition term $H_{\rm bc}$ scales as $(a\tau_0)^{-1/3}$.
 At large $\tau_0$, it is expected that the correction term will be small, but will become increasingly important as $\tau_0$ decreases.

### 2021-10-05 ms.tex
Incorporating shane's edits up to Comparison with Monte Carlo section

@@
 \ee
-The solutions of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
+Hence, the solution of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
 For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$.
@@
 Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value of the line-center optical depth at which the core of the line moves into the peak of the spectrum, which is $\tau_{\rm cp} {\sim} 10^5$.
-At fixed temperature, solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower $\tau_0$ where the peak of the spectrum lies near the core and improve for larger $\tau_0$ where the spectral peak is well outside of the line core.
+At fixed temperature, solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower $\tau_0$ where the peak of the spectrum lies near the core, but will improve for larger $\tau_0$.
+
+%%TODO: Pick up here. Shane's edits, top of page 5
 

### 2021-10-05 ms.tex
corrective term -> correction in abstract

@@
 This solution is compared to that of the Monte-Carlo method, which is valid at arbitrary optical depth.
-It is shown that the size of corrective term depends on the line center optical depth, and may explain discrepancies in previous studies that used a $J=0$ boundary condition.
+It is shown that the size of the correction depends on the line center optical depth, and may explain discrepancies in previous studies that used a $J=0$ boundary condition.
 For the impulsive problem, the time, spatial, and frequency dependence of the diffusion equation are expressed using an eigenfunction expansion and solved numerically to characterize the escape time distribution and spectra of photons initialized at the center of the sphere.

### 2021-10-06 ms.tex
Adding L luminosity parameter description after Eq. 2, adding definition of x (spatial variable)

@@
 \ee
-where $J$ is the mean intensity, $\sigma$ represents a change of variables in photon frequency (Eq.
-\ref{eq:change_of_variables}) and $\sigma_s$ is is the photon frequency of the source.
+where $J$ is the mean intensity, $L$ is a luminosity input, $\sigma$ represents a change of variables in photon frequency (Eq.
+\ref{eq:change_of_variables}), and $\sigma_s$ is is the photon frequency of the source.
 $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler units or Hz, respectively.
+The spatial variable is $\vec{x}$ and $\vec{x}_s$ is the position of the source.
 The boundary condition that there is no incoming intensity at the surface \citep{1986rpa..book.....R} can be written as

### 2021-10-12 ms.tex
Adding last of Shane's edits to time dependent section

@@
 This method is valid at arbitrarily large $\tau_0$, being restricted only by its computational demand which grows proportionally to the number of photons used and $\tau_0$.
-For each simulation, a total of ${\sim}10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the sphere until escaping, at which point their positions, outgoing angles, and escape frequencies are stored.
-A constant temperature of $T=10,000\ \rm K$ is set for the gas.
-Frequency redistribution is calculated at each scattering, including the effects of recoil, to obtain the spectrum at the surface of the spherical simulation domain.
+For each simulation, a total of ${\sim}10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the sphere until escaping, at which point their positions, outgoing angles, and escape frequencies are tabulated to obtain the spectrum at the surface of the spherical simulation domain.
+A constant temperature of $T=10^4\ \rm K$ is set for the gas.
+Frequency redistribution is calculated at each scattering, including the effects of recoil.
 In the comparisons shown in this section, the raw photon data is binned in frequency to obtain spectra.
-64 bins are used to ensure good statistics and minimal noise in each bin.
 Further details of the Monte Carlo implementation are discussed in \cite{2017ApJ...851..150H}.
@@
 
-We now compare each of the previously-discussed solutions for surface flux with Monte Carlo simulations.
+We now compare each of the previously-discussed solutions for surface flux to the Monte Carlo results.
 We return to the Doppler units $x$ for the photon frequency rather than the $\sigma$ units used in the solutions of the transfer equation.
@@
 In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown with that of the solutions $H_{\rm d}$, $H_0$, and $H_{\rm 0 + bc} = H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
-The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, it adequately corrects for the apparent excess of flux in the peaks of the spectrum.
-The solution with the correct frequency-dependent boundary condition enforced, $H_{0 + \rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
+The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to $H_0$, it adequately corrects for the apparent excess of flux in the peaks of the spectrum.
+The solution with the correct frequency-dependent boundary condition enforced, $H_{0 + \rm bc}$, has considerably lower residuals to Monte Carlo results than the other solutions, especially in the line wing.
 The boundary term corrects the slight deficit of $H_0$ in the line wings, further improving agreement with the numerical result.
@@
 \ref{eq:tau_peak_scaling}.
-This term is significant even at $\tau_0 {\sim} 10^7$ where $H_0$ solution is expected to perform its best, i.e., photons are pushed further out into the wing and thus the simplifying assumptions made in the solution of the differential equation are a better approximation.
+This term is significant even at $\tau_0 {\sim} 10^7$ where the $H_0$ solution is expected to perform best, i.e., photons are pushed further out into the wing where the simplifying assumptions made in the solution of the differential equation are a better approximation.
 
@@
 This scaling has also been applied to the y-axis to preserve normalization of the escape probability.
-At lower $\tau_0$, the scattering of photons within the Doppler core of the line becomes important, yet our solution does not include this effect.
+At lower $\tau_0$, the scattering of photons within the Doppler core of the line becomes important, but our solution does not include this effect.
 The effects of line core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift substantially outward in frequency from the line core for $\tau_0 = 10^5$.
@@
 Figure \ref{fig:sol_mc_xinit} shows calculations performed for three initial photon frequencies $\rm x_s = 0.0, 6.0$, and $12.0$ for a line center optical depth of $\tau_0=10^7$.
-The asymmetry of the spectrum is slight for $\rm x_s = 6.0$ where the cross section is still relatively large, but the increase in mean free path is much more substantial when photons are initialized with $\rm x_s=12.0$, further away from the line core.
+The asymmetry of the spectrum is slight for $\rm x_s = 6.0$ where the cross section is still relatively large, but the increase in mean free path is much more substantial when photons are initialized with $\rm x_s=12.0$, outside the line core.
 It is seen here that the difference between the Monte Carlo data and $H_0$ becomes larger as $\rm x_s$ increases.
@@
 The difference between the left and right side of the escaping spectrum is substantial at lower optical depths, since a change in $x_s$ of 6 is a larger fraction of the spectral peak location $(a\tau_0)^{1/3}$ for lower $\tau_0$.
-It is clear from the figure that as $x_s$ becomes further from the line core, the spectrum approaches a delta function in frequency.
-Additionally, since the material is optically thin here, we expect there to be a stronger disagreement between the Monte Carlo and the analytic solution as derivations assumed large optical depths.
+It is clear from the figure that as $x_s$ moves further from the line core, the spectrum becomes more strongly peaked in frequency.
+Additionally, since the material is increasingly optically thin in the wing, we expect there to be a stronger disagreement between the Monte Carlo and the analytic solution as our derivation assumed large optical depths.
 
@@
 
-Figure \ref{fig:xinit} shows quantitative examination of how the boundary term $H_{\rm bc}$ scales with both $\tau_0$ and $x_s$, motivated by the previous figures' demonstration that $H_0$ appears to become more accurate as $\tau_0$ increases.
-In this figure, the photon initialization frequency $x_s$ is shifted by integer multiples of $\tau_0$ in $\sigma$ frequency units (Eq.
+Figure \ref{fig:xinit} shows how the boundary term $H_{\rm bc}$ scales with both $\tau_0$ and $x_s$.%, motivated by the previous figures' demonstration that $H_0$ appears to become more accurate as $\tau_0$ increases.
+In this figure, $x_s$ is shifted by integer multiples of $\tau_0$ in $\sigma$ frequency units (Eq.
 \ref{eq:change_of_variables}) such that the source, now written $\sigma_s$, falls near the peak of the spectrum for each $\tau_0$.
@@
 From Eq.
-\ref{eq:hbc_scaling}, it is expected that the size of $H_{\rm bc}$ should become smaller with larger optical depths following a $(a\tau_0)^{-1/3}$ scaling as compared to $H_0$.
+\ref{eq:hbc_scaling}, it is expected that the fractional size of $H_{\rm bc}$ relative to $H_0$ should become smaller with larger optical depths following $(a\tau_0)^{-1/3}$.
 This factor has been scaled out of the figure such that solutions for different optical depths and the same source frequency $\sigma_s$ should show close agreement in scale on the figure's vertical axis if the relation holds.
 Indeed, the scaled solutions converge as the optical depth becomes larger, indicating general agreement with the $(a\tau_0)^{-1/3}$ scaling.
-The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ is due to the width of the Doppler core with respect to the peak of the spectrum; at lower $\tau_0$, this causes the line profile approximation in the wing (Eq.
+The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ is due to the width of the Doppler core with respect to the peak of the spectrum; at lower $\tau_0$, this causes our line profile approximation (Eq.
 \ref{eq:line_profile_wing}) to break down.
@@
 \acknowledgments
+
+NASA ATP grant 80NSSC18K0696, ``Exoplanetary MHD Outflows Driven by EUV Heating, Lyman alpha Radiation Forces and Stellar Tides".
 \restartappendixnumbering

### 2021-10-12 ms.tex
Phil's edits to abstract incorporated

@@
 
-The solution of the radiative transfer equation for resonant scattering of Lyman $\alpha$ photons is explored in spherical geometry.
+The radiation transfer equation for resonant scattering is solved in spherical geometry.
 A monochromatic source of photons is assumed at the center of a uniform sphere of constant gas density.
 The intensity within the sphere and at its surface is found in the limit of large line-center optical depth using the Eddington approximation for the angular dependence.
-Two specific limits are studied: a steady source and an impulsive source.
-For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with the mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct zero-ingoing intensity at the surface.
+Two limits are studied: a steady source and an impulsive source.
+For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with  mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct zero-ingoing intensity at the surface.
 This solution is compared to that of the Monte-Carlo method, which is valid at arbitrary optical depth.
-It is shown that the size of the correction depends on the line center optical depth, and may explain discrepancies in previous studies that used a $J=0$ boundary condition.
-For the impulsive problem, the time, spatial, and frequency dependence of the diffusion equation are expressed using an eigenfunction expansion and solved numerically to characterize the escape time distribution and spectra of photons initialized at the center of the sphere.
+It is shown that the size of the correction decreases with line center optical depth, which may explain discrepancies in previous studies.
+For the impulsive problem, the time, spatial, and frequency dependence of the diffusion equation are expressed using an eigenfunction expansion and solved numerically to characterize the escape time distribution and emergent spectra of photons.
 It is shown that the lowest-order eigenfrequency of the semi-analytic calculation agrees well with the decay constant of the Monte Carlo escape time distribution at line-center optical depths above ${\sim} 10^7$.

### 2021-10-12 ms.tex
Phil's edits up to time dependent diffusion section

@@
 
-The outer layers of planetary atmospheres are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
-Ionization and subsequent recombination can generate \lya within the planet's atmosphere, dissociating molecules in lower layers and creating pressure forces that drive an outflow.
+The outer layers of the atmosphere are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
+Given the abundance of hydrogen and its large cross section, Lyman $\alpha$ is an important component of the radiation field.
+There are two sources of Ly$\alpha$: the star, and recombinations in the atmosphere.
+\lya may ionize atoms and dissociate molecules, as well as exert pressure forces that drive an outflow.
 \lya can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy \citep{2017ApJ...851..150H}.
+Due to the low gas densities in the upper atmosphere, collisional de-excitation and broadening are of secondary importance and \lya may undergo ``resonant scattering''.
 
@@
 The extreme optical depths at \lya line center impose a large computational cost for solving radiative transfer with Monte Carlo methods directly coupled with magnetohydrodynamic simulations.
-The number of scatterings a photon undergoes is proportional to the line center optical depth, $\tau_0$.
+The number of scatterings a photon undergoes is proportional to the line center optical depth, $\tau_0$, of the domain.
 Near the base of the atmosphere, the line center optical depth is ${\sim}10^9$, so most of the time is spent following photons in these cells.
@@
 A complete, general analytic solution for the resonance scattering has never been derived but approximate solutions exist in certain limits.
-\citet{1973MNRAS.162...43H} demonstrated in slab geometry that resonance-line radiation transfer in optically-thick media can be described by the Poisson equation.
+\citet{1973MNRAS.162...43H} demonstrated that resonance-line radiation transfer in optically-thick media can be described by the Poisson equation.
 However, their solution contains an incorrect treatment of the boundary condition.
@@
 The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
-In order to satisfy the boundary conditions, the separation constant must satisfy an eigenvalue equation of the form
+In order to satisfy the boundary conditions, the separation constant is shown to satisfy an eigenvalue equation of the form
 \be
@@
 The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
-Thus, the separation constant is not constant, and the solution does not satisfy the Poisson equation since the frequency derivatives will act on the separation ``constant", giving extra terms.
+Thus, the separation ``constant'' is not constant, and the function does not satisfy the Poisson equation since the frequency derivatives will act on the separation ``constant" giving extra terms.
 In the limit of large optical depth $B$, they approximate the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$.
 However, this solution gives zero mean intensity at the surface.
-Their Eq.
-34 subsequently allowed the separation constant to have a small deviation from the above expression, which was explicitly frequency dependent.
+Their Equation 34 subsequently allowed $\lambda$ to have a small deviation from the above expression, which was explicitly frequency dependent.
 This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
@@
 
-Consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0$.
+Consider a sphere of radius $R$ and uniform density, with $n_{\rm sc}$ scatterers, luminosity $L$, and line-center optical depth $\tau_0$.
 We aim to find the intensity within the sphere as a function of radius and photon frequency.
@@
 For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
-$n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} \pi e^2 f/(m_e c)$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+Here $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} \pi e^2 f/(m_e c)$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
 The line center optical depth is then $\tau_0 = kR/(\sqrt{\pi}\Delta)$.
@@
 \ee
-where $J$ is the mean intensity, $L$ is a luminosity input, $\sigma$ represents a change of variables in photon frequency (Eq.
-\ref{eq:change_of_variables}), and $\sigma_s$ is is the photon frequency of the source.
+where $J$ is the mean intensity, $\sigma$ represents a change of variables in photon frequency (Eq.
+\ref{eq:change_of_variables}), and $\sigma_s$ is related to the photon frequency of the source.
 $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler units or Hz, respectively.
-The spatial variable is $\vec{x}$ and $\vec{x}_s$ is the position of the source.
-The boundary condition that there is no incoming intensity at the surface \citep{1986rpa..book.....R} can be written as
+The spatial variable is $\vec{x}$, and $\vec{x}_s$ is the position of the source.
+The boundary condition of no incoming intensity at the surface \citep{1986rpa..book.....R} is
 \be
@@
 
-A solution for the mean intensity $J_d$ which is divergent at the center of the coordinate system and at the emission frequency is presented in \citet{1990ApJ...350..216N}.
+A solution for the mean intensity $J_d$ which is divergent at $\vec{x}=\vec{x_s}$ and $\sigma=\sigma_s$ is presented in \citet{1990ApJ...350..216N}.
 Here it is extended to spherical geometry and generalized to allow emission frequencies away from line center:
@@
 \ee
-Again $J_0 \gg H_0$, except near the $r=R$, where it goes to zero. The flux at $r=R$ can be written
+These solutions agree with Equations \ref{eq:Jd} and \ref{eq:Hd} when the arguments of the trigonometric and hyperbolic functions are small.
+Again $J_0 \gg H_0$, except near $r=R$, where it goes to zero.
+The flux at $r=R$ can be written
 \be
@@
 
-A different solution method is attempted here, namely, a continuous Fourier expansion in the frequency variable $\sigma$.
+In order to enforce the boundary conditions, a different solution method is attempted here, namely, a continuous Fourier expansion in the frequency variable $\sigma$.
 The solution of this problem is split into two pieces: $J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
@@
 \ee
-Here, $J_0$ and $H_0$ are given in Equations \ref{eq:J0} and \ref{eq:H0}. The additional term $J_{\rm bc}$ must then be a solution of the homogeneous equation
+The additional term $J_{\rm bc}$ must then be a solution of the homogeneous equation
 \be \label{eq:diffeq}
@@
 \ee
-Inserting a frequency dependence $J_{\rm bc} \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$.
+Inserting a frequency dependence $J_{\rm bc} \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$ for the radial dependence.
 The solution can then be represented as
@@
 The number of points was increased until the solution was well-resolved near line center, and only became inaccurate close to the boundaries.
-Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq.
+Given the Fourier amplitudes $A(s)$, $J_{\rm bc}$ is computed using Eq.
 \ref{eq:Jbc}, and the flux is given by
@@
 \ee
-At large $\tau_0$, it is expected that the correction term will be small, but will become increasingly important as $\tau_0$ decreases.
+At large $\tau_0$, it is expected that the correction term will be small, but it will become increasingly important as $\tau_0$ decreases.
 
@@
 \ee
-Hence, the solution of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
+Hence, the analytic solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
 For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$.
 Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=4.6$.
-Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value of the line-center optical depth at which the core of the line moves into the peak of the spectrum, which is $\tau_{\rm cp} {\sim} 10^5$.
-At fixed temperature, solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower $\tau_0$ where the peak of the spectrum lies near the core, but will improve for larger $\tau_0$.
-
-%%TODO: Pick up here. Shane's edits, top of page 5
+Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} {\sim} 10^5$.
+Hence $H_{\rm bc}/H_0 {\sim} (\tau_{\rm cp}/\tau_0)^{1/3}$ is large at $\tau_0 \leq \tau_{\rm cp}$ and decreases relatively slowly as $\tau_0$ increases.
 
 \subsection{Comparison to Monte Carlo}
-The Monte Carlo method is used to solve the transfer equation numerically.
-This method is valid at arbitrarily large $\tau_0$, being restricted only by its computational demand which grows proportionally to the number of photons used and $\tau_0$.
+The Monte Carlo method is used to solve the transfer equation numerically in order to compare the analytic approximation to an ``exact'' solution.
+This method is valid at all $\tau_0$, being restricted only by its computational demand which grows proportionally to the number of photons used and $\tau_0$.
 For each simulation, a total of ${\sim}10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the sphere until escaping, at which point their positions, outgoing angles, and escape frequencies are tabulated to obtain the spectrum at the surface of the spherical simulation domain.
@@
 
-In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown with that of the solutions $H_{\rm d}$, $H_0$, and $H_{\rm 0 + bc} = H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
-The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to $H_0$, it adequately corrects for the apparent excess of flux in the peaks of the spectrum.
-The solution with the correct frequency-dependent boundary condition enforced, $H_{0 + \rm bc}$, has considerably lower residuals to Monte Carlo results than the other solutions, especially in the line wing.
-The boundary term corrects the slight deficit of $H_0$ in the line wings, further improving agreement with the numerical result.
+In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown along with that of the solutions $H_{\rm d}$, $H_0$, and $H_{\rm 0 + bc} = H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
+The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to $H_0$, it corrects for the apparent excess of flux in the peaks of the spectrum.
+The solution with the correct frequency-dependent boundary condition enforced, $H_{0 + \rm bc}$, has lower residuals to Monte Carlo results than the other solutions, especially in the line wing.
+The boundary term corrects the deficit of $H_0$ in the line wings, further improving agreement with the numerical result.
 Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.
@@
 \ref{eq:tau_peak_scaling}.
-This term is significant even at $\tau_0 {\sim} 10^7$ where the $H_0$ solution is expected to perform best, i.e., photons are pushed further out into the wing where the simplifying assumptions made in the solution of the differential equation are a better approximation.
+$H_{\rm bc}$ is significant even at $\tau_0 {\sim} 10^7$ where the $H_0$ solution is expected to perform well, i.e., photons are pushed further out into the wing where the simplifying assumptions made in the derivation of the differential equation are a better approximation.
 
@@
 This scaling has also been applied to the y-axis to preserve normalization of the escape probability.
-At lower $\tau_0$, the scattering of photons within the Doppler core of the line becomes important, but our solution does not include this effect.
-The effects of line core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift substantially outward in frequency from the line core for $\tau_0 = 10^5$.
+At lower $\tau_0$, the scattering of photons within the Doppler core of the line becomes important, but our analytic solution does not include this effect.
+The effects of line core scattering can be seen in the Monte Carlo data for $\tau_0=10^5$ and, to a lesser extent, $
+\tau_0=10^6$.
 
@@
 
-Since the solutions have been generalized to allow for a monochromatic source of photons at a frequency $x_s \neq 0$, their agreement with Monte Carlo as a function of source frequency can also be characterized.
+Next, we show $P(x)$ for $x_s \neq 0$.
 Photons initialized further out in the line wing have larger mean free paths.
-The larger spatial diffusion contributes to greater escape probability for these photons.
-In the limit that $|\rm x_s|$ becomes large, the distribution becomes a delta function in frequency as all photons escape the gas without scattering.
+The larger spatial diffusion implies greater escape probability for these photons.
+In the limit that $|\rm x_s|$ becomes large, the distribution becomes a delta function at $x_s$ as all photons escape the sphere without scattering.
 
@@
 Figure \ref{fig:sol_mc_xinit_lowtau} shows emission away from line center at the same values of $x_s$ as in Figure \ref{fig:sol_mc_xinit}, but for $\tau_0=10^6$ rather than $10^7$.
-The difference between the left and right side of the escaping spectrum is substantial at lower optical depths, since a change in $x_s$ of 6 is a larger fraction of the spectral peak location $(a\tau_0)^{1/3}$ for lower $\tau_0$.
-It is clear from the figure that as $x_s$ moves further from the line core, the spectrum becomes more strongly peaked in frequency.
-Additionally, since the material is increasingly optically thin in the wing, we expect there to be a stronger disagreement between the Monte Carlo and the analytic solution as our derivation assumed large optical depths.
+The difference between the left and right side of the escaping spectrum is substantial at lower optical depths, since $(a\tau_0)^{-1/3}$ increases by a factor of ${\sim}2$.
+It is clear from the figure that as $x_s$ extends further into the wing, the spectrum becomes more strongly peaked in frequency.
+Additionally, since the sphere is increasingly optically thin in the wing, we expect there to be a stronger disagreement between the Monte Carlo and the analytic solution as the equation assumed large optical depths.
 
@@
 Indeed, the scaled solutions converge as the optical depth becomes larger, indicating general agreement with the $(a\tau_0)^{-1/3}$ scaling.
-The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ is due to the width of the Doppler core with respect to the peak of the spectrum; at lower $\tau_0$, this causes our line profile approximation (Eq.
+The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ results from $x_{\rm peak}$ becoming close to $x_{\rm cw}$; at lower $\tau_0$, this causes the line profile approximation in the wing (Eq.
 \ref{eq:line_profile_wing}) to break down.

### 2021-10-12 ms.tex
Changing doppler core boundary label to x_cw on fig 5

@@
 Given the abundance of hydrogen and its large cross section, Lyman $\alpha$ is an important component of the radiation field.
-There are two sources of Ly$\alpha$: the star, and recombinations in the atmosphere.
+There are two sources of Ly$\alpha$: the star, and recombinations in the planet's atmosphere.
 \lya may ionize atoms and dissociate molecules, as well as exert pressure forces that drive an outflow.
@@
 For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$.
-Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=4.6$.
+Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$.
 Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} {\sim} 10^5$.

### 2021-10-13 ms.tex
Finishing Phil's edits to the time-dependent section

@@
 In order to understand how long it takes for the photons to escape the uniform sphere of gas we must reintroduce the time dependence of the diffusion equation, which was ignored in the steady-state calculations in Section \ref{sec:steadystate}.
-To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a fluid that is dynamic on timescales shorter than the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to an impulse is found, i.e., a delta function in time.
-This allows the distribution of photon escape times (the ``wait time distribution'') to be characterized and fit for efficient sampling.
-For simplicity a $J=0$ boundary condition will be used in the following derivations, which is a decent approximation for $\tau_0 \gg 1$.
+To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a radiation field that is dynamic on timescales comparable to the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to a delta function impulse is found.
+This allows the distribution of photon escape times (the ``wait time distribution'') to be characterized and fit.
+The wait time distribution can then be sampled to tabulate escape times instead of waiting for each photon to move outside the sphere.
+For simplicity a $J=0$ boundary condition will be used in the following derivations, which is a decent approximation for $a\tau_0 \gg 1$.
 
@@
 
-The source is changed to the form
+The emissivity for an impulsive source with energy E, source position $\vec{x}_s$, and frequency $\nu_s$ is 
 \be
@@
 \label{eq:jem2}
-\ee
-which is a standard expression for emissivity in CGS units where $E$ is the energy emitted in the impulse at time $t=0$. 
+\ee % TODO: Phil said to cite an equation from the appendix here?
 The resulting equation for $J(r,\sigma,t)$ is
@@
 \label{eq:jrsigmat_expansion}
-J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega),
+J(r, \sigma, t) = \sum_{n=1}^{\infty} \int_{-\infty}^\infty \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega),
 \ee
@@
 \be \label{eq:jnsigmaomega}
-J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{i\omega t} J(r, \sigma, t).
-\ee
-Eq.
-\ref{eq:jrsigmat_expansion} is the standard specific mean intensity $dE/dA dt d\nu$.
-Though $J(r, \sigma, t)$ is written as a function of the photon frequency variable $\sigma$, it should be integrated over $d\nu$ to preserve its normalization.
-Eq.
-\ref{eq:jnsigmaomega} is in the same units, but with an additional unit of $t$ in the numerator as a result of the expansion.
-Inserting Eq.
-\ref{eq:jnsigmaomega} for the eigenfunctions in Eq.
-\ref{eq:diffusion_eqn} and evaluating the integrals, we obtain
+J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_{-\infty}^\infty dt\ e^{i\omega t} J(r, \sigma, t).
+\ee
+%TODO: Put J after "specific mean intensity" from Phil's edits? What does that mean?
+Here $J(r, \sigma t)$ is the formula for specific mean intensity $dE/(dA dt d\nu)$.
+Though it is written as a function of the photon frequency variable $\sigma$, it should be integrated over $d\nu$ to preserve its normalization.
+$J(n, \sigma, \omega)$ has units $dE/(dA d\nu)$.
+Inserting the expansion in Eq.
+\ref{eq:jrsigmat_expansion} in to Eq.
+\ref{eq:diffusion_eqn} and integrating against $\omega$, we obtain
 \be \label{eq:diffusion_plugged_in}
@@
 \ee
-This cannot be solved analytically, so we turn now to a semi-analytic scheme to solve this equation for $J$.
-We start with a treatment of the boundary conditions.
-At $\sigma=\sigma_s$ continuity must be enforced,
+At $\sigma=\sigma_s$, continuity must be enforced,
 \be \label{eq:matching_condition_1}
@@
 \ee
-and the discontinuity in $dJ/d\sigma$  must be
+and the discontinuity in $dJ/d\sigma$ due to the source is
 \be \label{eq:matching_condition_2}
@@
 \ee
-At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes
+At large values of $\sigma$ the line profile $\phi$ is small and Eq. \ref{eq:diffusion_plugged_in} becomes
 \be \label{eq:diffusion_at_large_sigma}
-\frac{\partial^2J}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J,
+\frac{\partial^2J}{\partial\sigma^2} \approx \frac{\Delta^2\kappa_n^2}{k^2} J,
 \ee
@@
 \ee
-We then have
+This approximate solution implies a boundary condition at large $|\sigma|$
 \be \label{eq:single_j_derivative}
@@
 \ee
-where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$.
-Two numerical integrations are performed inward from large $\pm \sigma$ to $\sigma_s$, isolating the solution that increases exponentially toward the line center.
-Initial values for integration are obtained by setting $J=1$ in Eq.
-\ref{eq:single_j_derivative}.
-This gives $J$ and $J'$ on either side of $\sigma_s$, where a prime indicates the derivative $\partial/\partial \sigma$.
+where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$ to chose the finite solution as $|\sigma|\to 0$.
+Two numerical integrations are performed inward from large $|\sigma|$ to $\sigma_s$.
+Initial values for integration are obtained by setting $J=1$ and $dJ/d\sigma$ from Equation \ref{eq:single_j_derivative}.
+Integration gives $J$ and $J'$ on either side of $\sigma_s$, where a prime indicates the derivative $\partial/\partial \sigma$.
 By enforcing the matching conditions, Eqs.
-\ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}, the eigenfunctions $J(n, \sigma, \omega)$ are obtained for all photon frequencies $\sigma$.
-Since the eigenfunctions are linear in the starting conditions, only two integrations with different starting values are necessary.
-
-Let us define the damping frequency to be $\gamma \equiv i\omega$, which is real-valued and positive for damped solutions to the time-dependent equation.
-There are certain values of $\gamma$ for which a resonant response is produced which we will call $\gamma_{nm}$.
+\ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}, the eigenfunctions $J(n, \sigma, \omega)$ are obtained over the domain of photon frequencies $\sigma$.
+Since the solutions are linear in the starting conditions, only two integrations with different starting values are necessary.
+
+Let us define the damping rate to be $\gamma \equiv i\omega$, which is real and positive for damped solutions.
+At the eigenvalues $\gamma=\gamma_{nm}$, the response $J(n, \sigma, \omega)$ is resonant.
 Near these $\gamma_{nm}$ poles, the eigenfunctions will have the form

### 2021-10-13 ms.tex
Finishing Shane's edits to sections 4 and 5

@@
 
-Models of the escape of hydrogen gas in exoplanet atmospheres can be constructed with a treatment of resonant scattering of \lya in spherical geometry.
-The Monte Carlo method can be used for this problem, but requires a solution of the radiative transfer equation in spherical geometry and is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
-The primary goal of this work is to present a solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere.
-We have generalized a solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center, and we have made a correction to their incorrect $J=0$ surface boundary condition.
-This correction allows the proper condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere, and comes from the introduction of the term $J_{\rm bc}$ which is solved using a continuous Fourier expansion in frequency.
+A primary goal of this work is to present a solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere.
+We have generalized a spherically symmetric solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center.
+We have made a correction to their incorrect $J=0$ surface boundary condition that allows the proper condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere.
+This introduces a term $J_{\rm bc}$ which is solved using a continuous Fourier expansion in frequency.
 Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
@@
 Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, our solutions do not model areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
-The peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$; as such, calculations performed at low $\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
+Because the peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$, calculations performed at low $\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
 This effect is especially prevalent for larger H gas temperature, as the boundary between the Doppler core and line wing extends further out as $T$ increases.
@@
 Specifically, this solution shows improvement over previous solutions that utilized the $J=0$ surface boundary condition presented in \cite{1973MNRAS.162...43H} and \cite{1990ApJ...350..216N}.
+Several papers have previously compared these analytic models to Monte Carlo and seen discrepancies on the order of this correction.
 For example, in the top-left panel of Figure 1 from \cite{2006ApJ...649...14D}, the \lya spectrum emergent from a sphere of uniform optical depth is shown for $\tau_0=10^5, 10^6,$ and $10^7$ at a temperature of $T=10$ K, corresponding to $a=1.5 \times 10^{-2}$.
@@
 In \citet{2015MNRAS.449.4336S}, the peak excess in the \lya spectrum is particularly noticeable for line center optical depths of $\tau_0=10^6$ and $10^7$ in the top panel of their Figure 5, which used slab geometry and a gas temperature of $T=10^4$ K.
-Again, the error in their solution is of order 5-10 percent, which our boundary condition treatment corrects for.
-$H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which matches with the discrepancies noted in the previously cited solutions.
+Again, the error in their solution is of order 5-10 percent.
+$H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which matches with the discrepancies noted in these solutions.
 They are too large at the spectral peaks and too small further out in the wing, and the error scales approximately as $(a\tau_0)^{-1/3}$.
-This appears to be the consequence of not enforcing the correct frequency-dependent boundary conditions at the surface of the medium.
-
-The time-dependence of the problem is solved under a $J=0$ boundary condition to characterize the distribution of photon escape times.
-The differential equation cannot be solved except with a semi-analytic approach, utilizing an expansion in both space and photon frequency.
+
+The time-dependence of the problem is solved for a $J=0$ boundary condition to characterize the distribution of photon escape times.
+Solving the differential equation requires a semi-analytic approach, utilizing an expansion in both space and photon frequency.
 By matching boundary conditions on either side of the photon source frequency $x_s$, the flux at the surface of the sphere is found as a function of $t$ and $\nu$, expressed as a sum over spatial and frequency modes $n$ and $m$, respectively.
@@
 The sum over eigenmodes produces an escape-time distribution that broadly captures the behavior shown by Monte Carlo data---a rise at early times, transitioning to exponential decay in the tail of the distribution.
+% TODO: Shane suggests the following places too much emphasis on the number of spatial terms?
 It is expected that the accuracy of the rate constant for the tail of the distribution is limited by the number of spatial terms included in the sum over eigenmodes, as the Doppler core can trap photons at high optical depths until they diffuse outward in frequency, weighting the distribution toward later times.
 This physics is not modeled by our solution for two reasons: 1) our calculations ignored the Gaussian component of the Voigt line profile, leaving the Lorentzian piece which is accurate only in the line wing, and 2) knowing the core is not modeled accurately, we do not include a large enough number of spatial eigenmodes in the sum to resolve it.
+%
 However, a fitting function dependent on parameters $a$ and $\tau_0$ is found that adequately represents the escape time distribution within these constraints.
@@
 
-This leads in to the primary application of this work: to develop a computationally efficient random walk model in spherical geometry.
+This leads in to the primary application of this work.
+Models of the escape of hydrogen gas in exoplanet atmospheres can be constructed with a treatment of resonant scattering of \lya in spherical geometry.
+The Monte Carlo method can be used for this problem, but requires a solution of the radiative transfer equation in spherical geometry and is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
+We seek to develop a computationally efficient random walk model in spherical geometry.
 There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}.
-Another approach with wide application is modified random walk methods, such as those discussed in \citet{2002ApJ...567..922A,2015MNRAS.449.4336S} in which Monte Carlo code acceleration is performed for large optical depths in a uniform plane-parallel medium with no absorption.
-These calculations would need to be generalized to spherical geometry in order to construct a models of resonant scattering in exoplanet atmospheres as discussed in Section \ref{sec:intro}.
-The underlying principle is the same, however: an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.
+Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}; an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.
 A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution, but this solution of course does not use the correct frequency-dependent boundary condition at the surface of the sphere.
@@
 The size of $H_{\rm bc}$ diminishes at larger $\tau_0$, following a $(a\tau_0)^{-1/3}$ scaling.
-Introducing time-dependence to the transfer equation leads to another solution which is solved with an eigenfunction expansion and solved numerically.
+Introducing time-dependence to the transfer equation leads to another solution which is solved numerically with an eigenfunction expansion.
 We demonstrate that it agrees with the steady-state spectrum for $x_s=0$ when integrated over time, though its rate of numerical convergence is slow and requires a sum over many modes to become accurate.

### 2021-10-26 ms.tex
Adding short paragraph in WKB appendix that explains why the asymmetric piece of the solution is missing

@@
 \ee
-From Eq. \ref{eq:jrsigmat_expansion}, the contribution of a single pole to the total solution is
-\be
-J_{nm}(r,\sigma,t) & = &  -j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t}J(n,\sigma,-i\gamma)
-\\ & \simeq & j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}}.
-\ee
-We close the integral along the imaginary $\gamma$-axis  with a semi-circle at infinity and apply the residue theorem. The contribution from the semi-circle is zero, so we obtain
+for which an application of the residue theorem gives
 \be
@@
 Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, our solutions do not model areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
-Because the peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$, calculations performed at low $\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
+Because the peak of the spectral energy distribution of escaping photons is $x_{\rm peak} = (a\tau_0)^{1/3}$, calculations performed at low $\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
 This effect is especially prevalent for larger H gas temperature, as the boundary between the Doppler core and line wing extends further out as $T$ increases.
@@
 Here, we have derived the solution in spherical geometry with an appropriate treatment of the surface boundary condition as a frequency-dependent quantity, examining the spectral and time dependence of the resulting equations.
-The key result is that the errors in the previously-cited works have been quantified via a corrective boundary term, $H_{\rm bc}$, which resolves an excess in flux at the spectral peak and a deficit in the line wing of the calculated spectrum of \lya radiation as compared with Monte Carlo.
+The key result is that the errors in the previously-cited works have been quantified via a correction term, $H_{\rm bc}$, which resolves an excess in flux at the spectral peak and a deficit in the line wing of the calculated spectrum of \lya radiation as compared with Monte Carlo.
 The size of $H_{\rm bc}$ diminishes at larger $\tau_0$, following a $(a\tau_0)^{-1/3}$ scaling.
@@
 This treatment is incomplete for emission away from line center ($x_s\neq0$), however, since any terms that would allow asymmetry in the spectrum are not present in the sum.
-The time-dependent solution is utilized to create wait-time distributions for photons escaping the sphere of optically-thick hydrogen gas, which can be sampled in lieu of direct Monte Carlo simulations that would ordinarily be computationally demanding.
+The time-dependent solution is utilized to create wait-time distributions for photons escaping the sphere of optically-thick hydrogen gas, which can be sampled in lieu of traditional Monte Carlo simulations that would be computationally demanding.
 We compare the calculations from the time-dependent solution with Monte Carlo for a sample of $\tau_0$, noting general agreement in the resulting escape time distributions.
@@
 We start with the differential equation Eq. \ref{eq:wkb_differential_eqn}. Near line center, this has two independent solutions which can be written
-\be
+\be \label{eq:wkb_J}
 J(n,\sigma,s) & = & a_1 \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{1/2} J_{-3/4}\left( k_c \left[ \frac{\sigma}{\sigma_{\rm tp} }\right]^{2/3} \right)
@@
 \ee
-The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$.
-However, where both functions have short-wavelength behavior we may show that the solutions near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines.
+The discontinuity sets the value of $a_2$, and the corresponding term in Eq.
+\ref{eq:wkb_J} is non-resonant at $\sigma_s=0$.
+When $\sigma_s \neq 0$, however, this component contains the piece of the solution that is asymmetric about the line center.
+Notably, this piece of the solution is not included in Eq.
+\ref{eq:Jrsigmat} and thus our treatment using the residue theorem does not capture contributions from emission away from line center.
+
+%The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$. 
+Where both functions have short-wavelength behavior, we may show that the solutions near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines.
 This matched asymptotic expansion allows us to relate the normalization coefficients $a_1$ and $a_3$.

### 2021-10-26 ms.tex
rephrasing a sentence in the appendix

@@
 %The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$. 
-Where both functions have short-wavelength behavior, we may show that the solutions near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines.
+When $\sigma_s=0$, we may show that the solutions near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines where both functions have short-wavelength behavior.
 This matched asymptotic expansion allows us to relate the normalization coefficients $a_1$ and $a_3$.

### 2021-10-26 ms.tex
Revising discussion of incomplete residue theorem treatment - putting disclaimer first

@@
 
-To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$.
-In this limit, $J_{\rm bc} \approx \sqrt{3} H_0$.
+% Phil's edit:
+To estimate the scaling of $H_{\rm bc}$ with $\tau_0$, a change of variables to $\bar{\sigma} =  \sigma/\tau_0$ and $\bar{s}=s \tau_0$ is used in Equations 16 and 17.
+In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find
+
+%% TODO: Exclude this entirely or incorporate with Phil's edit?
+%To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$.
+In this limit, $J_{\rm bc} \approx \sqrt{3} H_0$ from Eq.
+\ref{eq:bc2}.
 We evaluate Eq.
@@
 
+We now employ an ansatz that agrees with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
+However, the analysis presented in Appendix \ref{app:wkb} suggests the ansatz is incomplete in the case where $x_s \neq 0$ and the solution is asymmetric about the line center.
 Let us define the damping rate to be $\gamma \equiv i\omega$, which is real and positive for damped solutions.
@@
 \ee
-This ansatz captures the contributions from $n \times m$ simple poles, which seems to agree with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
-However, the analysis presented in Appendix \ref{app:wkb} suggests the ansatz is incomplete in the case where $x_s \neq 0$ and the spectrum is asymmetric.
+This ansatz captures only the contributions from $n \times m$ simple poles, and does not contain the asymmetric piece of the solution for $\sigma_s \neq 0$.
 

### 2021-10-26 ms.tex
Reworking scaling with line center optical depth section based on Phil's edits
Edits through eq. 37 in time dependent section

@@
 Hence $H_{\rm bc}/H_0 {\sim} (\tau_{\rm cp}/\tau_0)^{1/3}$ is large at $\tau_0 \leq \tau_{\rm cp}$ and decreases relatively slowly as $\tau_0$ increases.
+Additionally, the optical depth at $x_{\rm peak}$ goes as $(a\tau_0)^{1/3}$, so photons here become optically thin when $a\tau_0 {\sim} 1$.
 
@@
 To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a radiation field that is dynamic on timescales comparable to the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to a delta function impulse is found.
-This allows the distribution of photon escape times (the ``wait time distribution'') to be characterized and fit.
-The wait time distribution can then be sampled to tabulate escape times instead of waiting for each photon to move outside the sphere.
-For simplicity a $J=0$ boundary condition will be used in the following derivations, which is a decent approximation for $a\tau_0 \gg 1$.
+This allows the distribution of photon escape times (the ``wait time distribution'') to be characterized.
+For simplicity a $J=0$ boundary condition will be used in the following derivations, which is a rough approximation for $a\tau_0 \gg 1$.
 
@@
 \ee
-We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$. The expansion for $J(r, \sigma, t)$ is
+We employ an expansion in terms of spherical Bessel functions in $r$ and Fourier transform in time. The expansion for $J(r, \sigma, t)$ is then
 \be
@@
 %TODO: Put J after "specific mean intensity" from Phil's edits? What does that mean?
-Here $J(r, \sigma t)$ is the formula for specific mean intensity $dE/(dA dt d\nu)$.
-Though it is written as a function of the photon frequency variable $\sigma$, it should be integrated over $d\nu$ to preserve its normalization.
-$J(n, \sigma, \omega)$ has units $dE/(dA d\nu)$.
-Inserting the expansion in Eq.
-\ref{eq:jrsigmat_expansion} in to Eq.
-\ref{eq:diffusion_eqn} and integrating against $\omega$, we obtain
+Here, $\omega$ describes the time-dependence of J.
+Though it is written as a function of the photon frequency variable $\sigma$, $J(r, \sigma, t)$ is the specific mean intensity $dE/(dA dt d\nu)$ and is a distribution in $\nu$.
+The Fourier coefficient $J(n, \sigma, \omega)$ has units $dE/(dA d\nu)$.
+Using Equation \ref{eq:jnsigmaomega}, we obtain
 \be \label{eq:diffusion_plugged_in}
@@
 \be \label{eq:matching_condition_1}
-J_+ = J_-,
+J(n, \sigma^-, \omega) = J(n, \sigma^+, \omega),
 \ee
@@
 \be \label{eq:matching_condition_2}
-\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
+\frac{\partial J(n, \sigma^+, \omega)}{\partial \sigma} - \frac{\partial J(n, \sigma^-, \omega)}{\partial \sigma} & = & 
 - \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}.
@@
 where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$ to chose the finite solution as $|\sigma|\to 0$.
-Two numerical integrations are performed inward from large $|\sigma|$ to $\sigma_s$.
-Initial values for integration are obtained by setting $J=1$ and $dJ/d\sigma$ from Equation \ref{eq:single_j_derivative}.
-Integration gives $J$ and $J'$ on either side of $\sigma_s$, where a prime indicates the derivative $\partial/\partial \sigma$.
-By enforcing the matching conditions, Eqs.
+Numerical integrations are performed inward toward $\sigma_s$ over several domains: from large $|\sigma|$ to $\sigma_s$, from large $|\sigma|$ to 0, and from 0 to $\sigma_s$, depending on whether $\sigma_s$ is positive or negative.
+If $\sigma_s=0$, just two integrations are performed inward from large $|\sigma|$ to 0.
+Initial values for integration are obtained either by setting $J=1$ and $dJ/d\sigma$ from Equation \ref{eq:single_j_derivative} at large $|\sigma|$ or by matching $J$ and $dJ/d\sigma$ at 0.
+This gives $J$ and $J'$ on either side of $\sigma_s$, where a prime indicates the derivative $\partial/\partial \sigma$.
+By enforcing the matching conditions Eqs.
 \ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}, the eigenfunctions $J(n, \sigma, \omega)$ are obtained over the domain of photon frequencies $\sigma$.
@@
 
-We now employ an ansatz that agrees with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
+We now employ an ansatz that roughly agrees with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
 However, the analysis presented in Appendix \ref{app:wkb} suggests the ansatz is incomplete in the case where $x_s \neq 0$ and the solution is asymmetric about the line center.
@@
 \be \label{eq:jnsigmaomega_approx}
-J(n,\sigma,-i\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma_{nm} - \gamma} + {\rm terms\ which\ vary\ slowly\ in\ \gamma}.
-\ee
-for which an application of the residue theorem gives
+J(n,\sigma,-i\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma_{nm} - \gamma} + C(\sigma),
+\ee
+where $C(\sigma)$ varies slowly in $\gamma$. An application of the residue theorem gives
 \be
@@
 \ee
+% TODO: PICK UP HERE
 Multiplying by $4\pi R^2$ gives the energy per time per frequency

### 2021-10-27 ms.tex
Fixing signs starting with Eq. 39 - integrals over t should have an extra -

@@
 \ee
-% TODO: PICK UP HERE
-Multiplying by $4\pi R^2$ gives the energy per time per frequency
+Multiplying by $4\pi R^2$ gives the energy per time per frequency emerging from the sphere to be
 \be
@@
 \ee
-Integrating over time yields a factor $-1/\gamma_{nm}$, and by integrating over $d\nu$ we find
+Integrating over time yields a factor $1/\gamma_{nm}$, and by integrating over $d\nu$ we find
 \be \label{eq:sum_rule}
-1 & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE} \sum_{nm} (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
+1 & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE} \sum_{nm} (-1)^{n+1} \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
 \ee
@@
 \be \label{eq:pnmsoln}
-P_{nm} & \equiv & \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE}  (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
+P_{nm} & \equiv & \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE}  (-1)^{n+1} \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
 \ee
@@
 \ee
-which is normalized to unity.
-For a sufficiently large number of spatial modes $n$ and frequency modes $m$, the result of this sum agrees with Monte Carlo escape time distributions.
-% Not sure if we want to say this yet?
-Maybe save for the escape time figure.
+which is normalized to unity. For a sufficiently large number of spatial modes $n$ and frequency modes $m$, the result of this sum agrees with Monte Carlo escape time distributions.
 
@@
 However, the behavior of the solution is well-understood since the late-time distribution is simply an exponential falloff.
-The rate constant of the falloff is the lowest-order eigenfrequency, $\gamma_{00}$, and its scale is determined by the coefficient $P_{00}$ as in Eq.
+The rate constant of the falloff is the lowest-order eigenfrequency, $\gamma_{11}$, and its scale is determined by the coefficient $P_{11}$ as in Eq.
 \ref{eq:pnmsoln}.
@@
 \be \label{eq:fitting_function}
-P(t) = \exp{\left[-\left(\frac{t_{\rm diff}}{t}\right)^2\right]} \times \gamma_{00} P_{00} e^{-\gamma_{00}t}.
+P(t) = \exp{\left[-\left(\frac{t_{\rm diff}}{t}\right)^2\right]} \times \gamma_{11} P_{11} e^{-\gamma_{11}t}.
 \ee
@@
 \be \label{eq:spectrum}
-P(\nu) & = &  \frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^n \gamma_{nm}^{-1} J_{nm}(\sigma).
+P(\nu) & = &  \frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^{n+1} \gamma_{nm}^{-1} J_{nm}(\sigma).
 \ee

### 2021-10-27 ms.tex
Finishing Phil's section 3 edits

@@
 
-We seek now to calculate all eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\gamma_{nm}$ for all spatial $n$ and for all eigenmodes $m$ at that given $n$.
-To measure the size of the response to detect where resonances occur, we sum the absolute value of $J(n,\sigma,-i\gamma)$ over $\sigma$ in array form.
-We call this response $f$, and use the index $j$ to represent the value of the response at discrete points over a range of $\gamma$.
+We seek now to calculate the eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\gamma_{nm}$ for a given spatial $n$.
+These will be labelled by an index $m=1, 2, ...$.
+To measure the size of the response to detect where resonances occur, we sum the absolute value of $J(n,\sigma,-i\gamma)$ over the array $\sigma$.
+We call this response $f$, and use the index $j$ to represent the value of the response at discrete points $\gamma_j$ over a range of $\gamma$.
 In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bounded a resonance that occurs in the interval $(\gamma_{j-1},\gamma_{j+1})$.
-We then call the ``solve'' step to hone in on the eigenvalue before continuing the sweep in $\gamma$.
-In the solve step, we evaluate the eigenfunctions at the points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ to obtain the responses $f_{j-1}$, $f_j$, and $f_{j+1}$.
-A ``guess'' at the correct eigenvalue $\gamma_{nm}$ can be calculated from
+We then hone in on the eigenvalue before continuing the sweep in $\gamma$.
+To refine the eigenmode solution, we evaluate $f_{j-1}$, $f_j$, and $f_{j+1}$ at the points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$.
+Assuming the form in Equation \ref{eq:jnsigmaomega_approx}, a guess at the correct eigenvalue $\gamma_{nm}$ can be calculated from
 \be
@@
 After iterating until an eigenvalue $\gamma_{nm}$ is accurately determined, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
-We can write down an approximate expression for the response near the resonances as
-\be
-J(n,\sigma,-i\gamma) & \simeq & \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma} + C(\sigma),
-\ee
-where $C(\sigma)$ is weakly dependent on $\gamma$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance
+We can solve for $J_{nm}(\sigma)$ by comparing two points near the resonance
 \be
@@
 \ee
-where $C(\sigma)$ has cancelled out in the difference. We can immediately solve as
+where $C(\sigma)$ has cancelled out in the difference. We can immediately solve for the eigenfunction as
 \be
@@
     \includegraphics{Jsoln_n1_m100.pdf}
-    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and a range of frequency eigenmodes up to $m=100$.
-Their oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity.
-The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.}
+    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.}
     \label{fig:jsoln}
 \end{figure}
+\noindent The form of a single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{tp}$, at which point the function becomes evanescent.
+The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Eq.
+\ref{eq:diffusion_plugged_in} and examining the resulting homogeneous differential equation.
+We obtain
+\be \label{eq:wkb_differential_eqn}
+\frac{d^2J}{d\sigma^2} & = & \left[ \left( \frac{\kappa_n \Delta }{k} \right)^2 - \frac{3\phi \gamma\Delta^2}{ck}\right] J,
+\ee
+where the line profile is approximated as in Eq.
+\ref{eq:line_profile_wing}.
+When the coefficient on the right hand side is positive, exponential growth or decaying evanescent solutions are found.
+This occurs on the line wings.
+When the coefficient on the right hand side is negative, oscillatory solutions are found (propagation), which occurs near the line core.
+The boundary between propagation and evanescence occurs at the turning point, given by
+\be \label{eq:sigma_tp}
+\sigma_{\rm tp} & = & \sqrt{\frac{2a}{\pi}}\left( \frac{k \gamma}{ \kappa_n^2 c \Delta} \right)^{3/2}
+\ee
+Thus, to ensure accuracy in each term of Eq.
+\ref{eq:Jrsigmat}, the bounds of $\sigma$ must be set sufficiently far outside of $\sigma_{\rm tp}$ such that the function is small at the edges.
+The scale of an $e$-folding in $J_{nm}(\sigma)$ is $k/(\kappa_n \Delta) = \tau_0 / (\sqrt{\pi} n)$, so a grid of $\sigma$ is chosen that spans a large enough number of $e$-foldings that no oscillatory behavior is present at the boundaries of the calculation.
+
+The eigenfunction's oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity.
+The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.
 Fig.
-\ref{fig:jsoln} shows a set of eigenfunctions $J_{nm}(\sigma)$ to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$.
+\ref{fig:jsoln} shows a set of eigenfunctions $J_{nm}(\sigma)$ to illustrate their relative scales for different $m$ at a fixed spatial eigenmode $n$.
 The overall scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$ with $E$ arbitrarily set to 1, $k = \tau_0 \sqrt{\pi} \Delta / R$, and $R = 10^{11}$ cm.
-With this normalization, an eigenfunction has typical size ${\sim} E a / \left(R^2 \Delta \right) = 10^{-37}$.
+For H atoms with $T=10^4$ K and $\tau_0=10^7$, an eigenfunction has typical size ${\sim} E a / \left(R^2 \Delta \right) = 10^{-37}$.
 Additional terms add smaller-magnitude, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
@@
 \end{figure}
-The values of the $\gamma_{nm}$ resonant frequencies can be described approximately with Eq. \ref{eq:gamma_nm}. Their scale depends on $m$, $n$, and other physical parameters according to 
+The values of the $\gamma_{nm}$ can be described approximately with Eq. \ref{eq:gamma_nm}. Their values depend on $m$, $n$, and other physical parameters according to 
 \be \label{eq:gamma_nm}
@@
 as shown in Appendix \ref{app:wkb}.
-The size of additional eigenfrequencies scales as a power law in $m$, yet as is seen in Fig.
-\ref{fig:gamma_nm} the power is weak, requiring up to 500 $m$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
-When sweeping through the imaginary frequency domain to find resonances, this expression is used to set the scale of the sweep points to ensure no $\gamma_{nm}$ are missed.
+The power law in $m$ is weak, requiring up to $m=500$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
+When sweeping through to find resonances, Equation \ref{eq:gamma_nm} is used to set the scale of the sweep points $\gamma_j$ to ensure no $\gamma_{nm}$ are missed.
 The continuity and close agreement with the analytic expression shown in Fig.
-\ref{fig:gamma_nm} indicate that the sweep routine accurately brackets and refines the locations of resonances.
-
-The form of a single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{tp}$, at which point the function becomes evanescent.
-The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Eq.
-\ref{eq:diffusion_plugged_in} and re-examining the resulting homogeneous differential equation.
-We obtain
-\be \label{eq:wkb_differential_eqn}
-\frac{d^2J}{d\sigma^2} & = & \left[ \left( \frac{\kappa_n \Delta }{k} \right)^2 - \frac{3\phi \gamma\Delta^2}{ck}\right] J,
-\ee
-where the line profile is approximated as in Eq.
-\ref{eq:line_profile_wing}.
-When the coefficient on the right hand side is positive, exponential growth or decay solutions are found (evanescence).
-This occurs on the line wings.
-When the coefficient on the right hand side is negative, oscillatory solutions are found (propagation), which occurs near the line core.
-The boundary between propagation and evanescence occurs at the turning point, given by
-\be \label{eq:sigma_tp}
-\sigma_{tp} & = & \sqrt{\frac{2a}{\pi}}\left( \frac{k \gamma}{ \kappa_n^2 c \Delta} \right)^{3/2}
-\ee
-Thus, to ensure accuracy in the final sum of Eq.
-\ref{eq:Jrsigmat}, the bounds of $\sigma$ must be set sufficiently far outside of $\sigma_{tp}$ such that the function is small at the edges.
-The scale of an $e$-folding in $J_{nm}(\sigma)$ is $k/(\kappa_n \Delta) = \tau_0 / (\sqrt{\pi} n)$, so a grid of $\sigma$ is chosen that spans a large enough number of $e$-foldings that no oscillatory behavior is present at the boundaries of the calculation.
+\ref{fig:gamma_nm} indicate that the numerical solutions are accurate.
 
@@
 \ee
-which is normalized to unity. For a sufficiently large number of spatial modes $n$ and frequency modes $m$, the result of this sum agrees with Monte Carlo escape time distributions.
-
-The eigenfunction expansion method utilized here can produce an effective characterization of the escape time distribution, yet it is not a fast enough computational method to use as a distribution for sampling.
-However, the behavior of the solution is well-understood since the late-time distribution is simply an exponential falloff.
+which is normalized to unity.
+For a sufficiently large number of spatial modes $n$ and frequency modes $m$, the result of this sum can agree with Monte Carlo escape time distributions when $x_s=0$, but it is not a fast enough computational method to use as a distribution for sampling.
+However, the late-time distribution is simply an exponential falloff.
 The rate constant of the falloff is the lowest-order eigenfrequency, $\gamma_{11}$, and its scale is determined by the coefficient $P_{11}$ as in Eq.
@@
 \ee
-The first term represents the early-time distribution, which then transitions to an exponential falloff past a point $ct/R = ct_{\rm diff}/R = (a\tau_0)^{1/3}$, where $t_{\rm diff}$ is a characteristic diffusion timescale.
+The first term represents the early-time distribution, which then transitions to an exponential falloff past a point $ct_{\rm diff}/R = (a\tau_0)^{1/3}$, where $t_{\rm diff}$ is the characteristic diffusion timescale.
 
@@
 This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated.
-%TODO: Include?
-As a result of this choice, we expect that our semianalytic approach will underestimate the number of escaping photon at late times as compared with the Monte Carlo.
 
@@
     \includegraphics{steadystate.pdf}
-    \caption{Comparison of steady-state and time-integrated spectra for 20 spatial eigenmodes and 500 frequency eigenmodes at a line center optical depth of $\tau_0=10^7$.
-The accuracy of the time-integrated solution is limited by the number of frequency eigenmodes summed.
-The accuracy of the core behavior for both the partial sum and the time-integrated solution is limited by the number of spatial eigenmodes summed, which is why both solutions fail in the core.}
+    \caption{Comparison of steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ for $\tau_0=10^7$.}
     \label{fig:steadystate}

### 2021-10-27 ms.tex
Changing \gamma_00 label in figure 8

@@
 \be
-\frac{dj_0(\kappa_n r)}{dr} \bigg\rvert_R & =& \frac{d}{dr} \left( \frac{\sin(\kappa_n r)}{\kappa_n r} \right)\bigg\rvert_R
+\frac{dj_0(\kappa_n r)}{dr} \bigg\rvert_R & =& \frac{d}{dr} \left[ \frac{\sin(\kappa_n r)}{\kappa_n r} \right]\bigg\rvert_R
 =  \left( \frac{\cos(\kappa_n R)}{R} - \frac{\sin(\kappa_n R)}{\kappa_n R^2} \right)
@@
 We call this response $f$, and use the index $j$ to represent the value of the response at discrete points $\gamma_j$ over a range of $\gamma$.
-In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bounded a resonance that occurs in the interval $(\gamma_{j-1},\gamma_{j+1})$.
+In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bracketed a resonance that occurs in the interval $(\gamma_{j-1},\gamma_{j+1})$.
 We then hone in on the eigenvalue before continuing the sweep in $\gamma$.
@@
 This is repeated by replacing initial points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ with closer estimates while the size of the response grows as the resonance is approached.
-After iterating until an eigenvalue $\gamma_{nm}$ is accurately determined, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
-We can solve for $J_{nm}(\sigma)$ by comparing two points near the resonance
-\be
-J(n,\sigma,-i\gamma_1)  - J(n,\sigma,-i\gamma_2)& = &  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_1} -  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_2},
-\ee
-where $C(\sigma)$ has cancelled out in the difference. We can immediately solve for the eigenfunction as
+After iterating an eigenvalue $\gamma_{nm}$ to convergence, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
+We can solve for $J_{nm}(\sigma)$ by comparing two points $\gamma_1$ and $\gamma_2$ near the resonance, cancelling $C(\sigma)$ in the difference to find
 \be
@@
 Additional terms add smaller-magnitude, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
-The oscillations of various modes must cancel perfectly to recreate the form of the solution in Eq.
-\ref{eq:Jrsigmat}, so many modes $m$ and $n$ are required for convergence to the correct solution.
-Too few (or imprecisely-calculated) modes creates ``ringing'' in the function that indicates the presence of imperfect cancellations in the positive and negative contributions of individual poles.
+The oscillations of various modes must cancel, so many modes $m$ and $n$ are required for convergence to the correct solution.
 \begin{figure}
@@
 In Fig.
-\ref{fig:tau_scaling}, it is shown that the time constant of exponential decay in fitted Monte Carlo escape time distributions converges with $\gamma_{00}^{-1}$ at sufficiently high $\tau_0$, following a $t\propto(a\tau_0)^{1/3}$ scaling.
+\ref{fig:tau_scaling}, it is shown that the time constant of exponential decay in fitted Monte Carlo escape time distributions converges with $\gamma_{11}^{-1}$ at sufficiently high $\tau_0$, following a $t\propto(a\tau_0)^{1/3}$ scaling.
 At lower $\tau_0$, the effects of line core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
@@
     \caption{Characteristic timescales as a function of $\tau_0$.
-$\gamma_{00}^{-1}$ and a fit of the exponential falloff for the Monte Carlo escape time distribution are shown to converge to a $t \propto (a\tau_0)^{1/3}$ scaling at large $\tau_0$.
+$\gamma_{11}^{-1}$ and a fit of the exponential falloff for the Monte Carlo escape time distribution are shown to converge to a $t \propto (a\tau_0)^{1/3}$ scaling at large $\tau_0$.
 The Monte Carlo points on this figure are obtained by fitting only the exponential piece of the escape time distribution to obtain the rate constant.}
@@
 Additional spatial modes contribute to the solutions' accuracy in the core of the line.
-If more spatial modes are calculated, the agreement with the steady state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x_s$.
+If more spatial modes are calculated, the agreement with the steady state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x=x_s=0$.
 If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over eigenmodes which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.

### 2021-11-01 ms.tex
Changing phrasing in last sentence of WKB approx appendix

@@
 
-Figure \ref{fig:xinit} shows how the boundary term $H_{\rm bc}$ scales with both $\tau_0$ and $x_s$.%, motivated by the previous figures' demonstration that $H_0$ appears to become more accurate as $\tau_0$ increases.
+Figure \ref{fig:xinit} shows how the boundary term $H_{\rm bc}$ scales with both $\tau_0$ and $x_s$.
 In this figure, $x_s$ is shifted by integer multiples of $\tau_0$ in $\sigma$ frequency units (Eq.
@@
 \ee
-%TODO: Put J after "specific mean intensity" from Phil's edits? What does that mean?
 Here, $\omega$ describes the time-dependence of J.
@@
 \be
-J_{nm}(r,\sigma,t) & \simeq & j_0(\kappa_n r) J_{nm}(\sigma) e^{-\gamma_{nm}t}.
+J(r,\sigma,t) & \simeq & j_0(\kappa_n r) J_{nm}(\sigma) e^{-\gamma_{nm}t}.
 \ee
@@
 \ee
-This ansatz captures only the contributions from $n \times m$ simple poles, and does not contain the asymmetric piece of the solution for $\sigma_s \neq 0$.
-
-Taking a derivative with respect to $r$ and evaluating at the surface $r=R$, we use
+This ansatz captures the contributions from $n \times m$ simple poles. Taking a derivative with respect to $r$ and evaluating at the surface $r=R$, we use
 \be
@@
     \includegraphics{Jsoln_n1_m100.pdf}
-    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.}
+    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $x_s=0$, $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.}
     \label{fig:jsoln}
@@
     \includegraphics{steadystate.pdf}
-    \caption{Comparison of steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ for $\tau_0=10^7$.}
+    \caption{Comparison of steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ with $x_s=0$, $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.}
     \label{fig:steadystate}
@@
 
-% Put a little wkb in the appendix?
-We could show the dispersion relation, for instnace.
-d^2Jdsigma^2, equation for discontinuity...
-here is the solution far from LC, here is the solution near LC, by requiring these two solutions to match in the raea where they're both valid, here are the matching conditions.
-4-5 lines.
-Here's the presence of simple poles, gives us dispersion relation, but also here's the piece that is not divergent and containts the discontinuity.
-This term is not included in the sum over simple poles.
-Don't go through the derivation in a lot of detail.
-
-% WKB Approximation - could cite (Bender & Norzog)? Arfken might have it too?
-
-% Go through derivation of dispersion relation, then say "the denominator being zero leads to the dispersion relation (cite eq 47 in time dependent section)".
-
 We start with the differential equation Eq. \ref{eq:wkb_differential_eqn}. Near line center, this has two independent solutions which can be written
@@
 where $Ai(...)$ is the Airy function of the first kind. Again, $a_3$ is a normalization constant. When $\sigma_s=0$, we can enforce the discontinuity in Eq. \ref{eq:matching_condition_2} to find 
-\be
+\be \label{eq:a2}
 a_2 & = & - \frac{\Gamma(7/4) \sigma_{\rm tp}}{ 2^{1/4} k_c^{3/4}} \frac{6^{1/2}}{8} n^2 \frac{E}{kR^3}.
@@
 The discontinuity sets the value of $a_2$, and the corresponding term in Eq.
-\ref{eq:wkb_J} is non-resonant at $\sigma_s=0$.
-When $\sigma_s \neq 0$, however, this component contains the piece of the solution that is asymmetric about the line center.
-Notably, this piece of the solution is not included in Eq.
-\ref{eq:Jrsigmat} and thus our treatment using the residue theorem does not capture contributions from emission away from line center.
-
-%The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$. 
-When $\sigma_s=0$, we may show that the solutions near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines where both functions have short-wavelength behavior.
+\ref{eq:wkb_J} is non-resonant.
+The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$.
+When $\sigma_s=0$, we may show that the solutions both near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines where both functions have short-wavelength behavior.
 This matched asymptotic expansion allows us to relate the normalization coefficients $a_1$ and $a_3$.
 The matching conditions are
-\be
+\be \label{eq:a1/a2}
 \frac{a_1}{a_2} & = & \frac{ \sin \left( \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} + \frac{\pi}{8} \right) }{ \sin \left(  \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} - \frac{\pi}{8} \right) }
-\\
+\ee
+\be \label{eq:a3/a2}
 \frac{a_3}{a_2} & = & \frac{ k_c^{-1/3} }{ \sin \left(  \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} - \frac{\pi}{8} \right) }.
 \ee
-By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{tp}$, we find the dispersion relation in Eq. \ref{eq:gamma_nm}.
+By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{\rm tp}$, we find the dispersion relation in Eq.
+\ref{eq:gamma_nm}.
+
+We have applied this approximation for $\sigma_s=0$.
+In this case, we have obtained Equations \ref{eq:a1/a2} and \ref{eq:a3/a2} which approach infinity near the eigenfrequencies $\gamma_{nm}$, so there will be no contribution from the $a_2$ term in Equation \ref{eq:wkb_J} at these resonant frequencies.
+We now seek to understand the behavior of the solution when emission is away from line center ($\sigma_s \neq 0$).
+The eigenfunction expansion in Equation \ref{eq:Jrsigmat} assumed that a closed contour at infinity, bounding an infinite number of simple poles along the real $\gamma$-axis, could be integrated to find that $J(r, \sigma, t)$ is the sum of the residues of the poles contained within the contour.
+Equation \ref{eq:a2} shows there is an additional contribution unrelated to the eigenfunctions that is non-resonant.
+In the case where $\sigma_s \neq 0$, this non-resonant piece contributes to the asymmetry of the the solution about line center.
+When $\sigma_s=0$, however, the solution is symmetric about line center and the non-resonant piece has no contribution except to produce the matching conditions in Equations \ref{eq:a1/a2} and \ref{eq:a3/a2}.
+Since we have applied the WKB approximation only when $\sigma_s = 0$, the non-resonant piece which allows the outgoing spectrum to be asymmetric is not captured by the methods outlined here.
 

### 2021-11-05 ms.tex
Changes before sec 2.1 edits
Adding phi and sigma definitions earlier in text

@@
 \ee
-where $J$ is the mean intensity, $\sigma$ represents a change of variables in photon frequency (Eq.
-\ref{eq:change_of_variables}), and $\sigma_s$ is related to the photon frequency of the source.
+where $J$ is the mean intensity, the spatial variable is $\vec{x}$, and $\vec{x}_s$ is the position of the source.
+Following \citet{1973MNRAS.162...43H}, we have used a change of variables from $x$ to $\sigma$,
+\be \label{eq:int_change_of_variables}
+\sigma = \sqrt{\frac{2}{3}}\int_0^x \frac{dx}{\phi(x) \Delta} \approx \sqrt{\frac{2}{3}}\frac{\pi}{a}\frac{x^3}{3}, 
+\ee
+where the approximation is applicable in the line wing. Then, the line profile is approximately (Equation \ref{eq:app:line_profile_wing})
+\be \label{eq:line_profile_approx}
+\phi \approx \frac{a}{\pi x^2 \Delta} \approx \left(\frac{2a}{\pi}\right)^{1/3} \frac{1}{3 \Delta} \sigma^{-2/3}.
+\ee
+$\sigma_s$ is related to the photon frequency of the source.
 $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler units or Hz, respectively.
-The spatial variable is $\vec{x}$, and $\vec{x}_s$ is the position of the source.
 The boundary condition of no incoming intensity at the surface \citep{1986rpa..book.....R} is
@@
 The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ results from $x_{\rm peak}$ becoming close to $x_{\rm cw}$; at lower $\tau_0$, this causes the line profile approximation in the wing (Eq.
-\ref{eq:line_profile_wing}) to break down.
+\ref{eq:app:line_profile_wing}) to break down.
 From this, we conclude that the errors introduced by the incorrect separation of variables in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others are proportional to $(a\tau_0)^{-1/3}$.
@@
 where the line profile is approximated as in Eq.
-\ref{eq:line_profile_wing}.
+\ref{eq:app:line_profile_wing}.
 When the coefficient on the right hand side is positive, exponential growth or decaying evanescent solutions are found.
@@
 As an example, on the damping wing, the line profile can be approximated as 
-\be \label{eq:line_profile_wing}
-\phi \simeq \frac{a}{\pi x^2}
+\be \label{eq:app:line_profile_wing}
+\phi \simeq \frac{a}{\pi x^2 \Delta}
 \ee

### 2021-11-05 ms.tex
Finishing changes to scaling with line center optical depth section

@@
 
-% Phil's edit:
-To estimate the scaling of $H_{\rm bc}$ with $\tau_0$, a change of variables to $\bar{\sigma} =  \sigma/\tau_0$ and $\bar{s}=s \tau_0$ is used in Equations 16 and 17.
-In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find
-
-%% TODO: Exclude this entirely or incorporate with Phil's edit?
-%To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$.
-In this limit, $J_{\rm bc} \approx \sqrt{3} H_0$ from Eq.
-\ref{eq:bc2}.
-We evaluate Eq.
-\ref{eq:Jbc} at $r=R$ and solve for the Fourier coefficients, $A(s)$.
-These are then used in Eq.
-\ref{eq:Hbc} to find $H_{\rm bc}(R, \sigma)$.
-Dividing by the contribution from $H_0$, we obtain the proportionality
+We now estimate the scaling of $H_{\rm bc}$ with $\tau_0$.
+In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc} {\sim} H_0$ from Equation \ref{eq:bc2}.
+We  calculate $H_{\rm bc}$ from $J_{\rm bc}$ using Equation \ref{eq:Hbc} and introduce a change of variables to $\bar{\sigma} =  \sigma/\tau_0$ and $\bar{s}=s \tau_0$.
+The ratio of $H_{\rm bc}$ and $H_0$ is then proportional to $s/(\phi \Delta)$.
+In the line wing, $\phi \approx a / (\pi x^2 \Delta)$ according to Eq.
+\ref{eq:line_profile_approx}, and we must choose an appropriate value to insert for $x$.
+Our dimensionalization $\bar\sigma = \sigma / \tau_0$ implies that $\sigma {\sim} \tau_0$, which, from Equation \ref{eq:int_change_of_variables}, gives us the characteristic frequency
+\be \label{eq:tau_peak_scaling}
+x_{\rm peak} {\sim} \left(a\tau_0\right)^{1/3}.
+\ee
+This is the location of the spectral peak of the distribution. Similarly, $s {\sim} 1/\tau_0$ from the change of variables, and for the ratio of $H_{\rm bc}$ and $H_0$ we find
+
 \be \label{eq:hbc_scaling}
@@
 At large $\tau_0$, it is expected that the correction term will be small, but it will become increasingly important as $\tau_0$ decreases.
-
-The location of the spectral peak of the distribution is
-\be \label{eq:tau_peak_scaling}
-x_{\rm peak} {\sim} \left(a\tau_0\right)^{1/3}.
-\ee
-Hence, the analytic solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
+From Equation \ref{eq:tau_peak_scaling}, we see that the analytic solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
 For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$.
 Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$.
-Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} {\sim} 10^5$.
+Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} \approx 10^5$.
 Hence $H_{\rm bc}/H_0 {\sim} (\tau_{\rm cp}/\tau_0)^{1/3}$ is large at $\tau_0 \leq \tau_{\rm cp}$ and decreases relatively slowly as $\tau_0$ increases.
-Additionally, the optical depth at $x_{\rm peak}$ goes as $(a\tau_0)^{1/3}$, so photons here become optically thin when $a\tau_0 {\sim} 1$.
+Additionally, the optical depth at $x_{\rm peak}$ is proportional to $(a\tau_0)^{1/3}$, so photons here become optically thin when $a\tau_0 {\sim} 1$.
 

### 2021-11-08 ms.tex
Incorporating Phil's edits up to sec 2.2

@@
 Two limits are studied: a steady source and an impulsive source.
-For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with  mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct zero-ingoing intensity at the surface.
+For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with  mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct boundary condition of zero-ingoing intensity at the surface.
 This solution is compared to that of the Monte-Carlo method, which is valid at arbitrary optical depth.
-It is shown that the size of the correction decreases with line center optical depth, which may explain discrepancies in previous studies.
-For the impulsive problem, the time, spatial, and frequency dependence of the diffusion equation are expressed using an eigenfunction expansion and solved numerically to characterize the escape time distribution and emergent spectra of photons.
-It is shown that the lowest-order eigenfrequency of the semi-analytic calculation agrees well with the decay constant of the Monte Carlo escape time distribution at line-center optical depths above ${\sim} 10^7$.
-A fitting function for the distribution is found which can be sampled to accelerate Monte Carlo radiation transfer calculations at large optical depths.
+It is shown that the size of the correction is order unity when the spectral peaks approach the Doppler core and decreases with line center optical depth, which may explain discrepancies in previous studies.
+For the impulsive problem, the time, spatial, and frequency dependence of the equation are expressed using an eigenfunction expansion and are obtained numerically to characterize the escape time distribution and emergent spectra of photons.
+It is shown that the lowest-order eigenfrequency of the semi-analytic calculation agrees well with the decay constant of the Monte Carlo escape time distribution at sufficiently large line-center optical depths.
+%A fitting function for the distribution is found which can be sampled to accelerate Monte Carlo radiation transfer calculations at large optical depths.
 
@@
 The outer layers of the atmosphere are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
-Given the abundance of hydrogen and its large cross section, Lyman $\alpha$ is an important component of the radiation field.
+Given the abundance of hydrogen and its large cross section, Lyman $\alpha$ (Ly$\alpha$) is an important component of the radiation field.
 There are two sources of Ly$\alpha$: the star, and recombinations in the planet's atmosphere.
@@
 These observations have revealed a population of atoms extending out to distances of order a few planetary radii for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with the H atom population.
-In atmospheres with thick layers of atomic hydrogen, stellar Lyman Alpha (Ly$\alpha$) radiation is especially important in the atmospheric dynamics of these systems as the optical depth at line center is large.
-The importance of the \lya line in this process necessitates a careful treatment of resonant scattering in order to construct accurate models of H atom excitation, heating, and radiative forces.
-
-Numerical simulations can be used to understand the dynamics of these irradiated exoplanet atmospheres.
-The extreme optical depths at \lya line center impose a large computational cost for solving radiative transfer with Monte Carlo methods directly coupled with magnetohydrodynamic simulations.
+In atmospheres with thick layers of atomic hydrogen, \lya radiation is especially important in the atmospheric dynamics of these systems as the optical depth at line center is large.
+This process necessitates a careful treatment of resonant scattering in order to construct accurate models of H atom excitation, heating, and radiative forces.
+
+Due to the technical challenge of including resonant scattering, the fully three-dimensional geometry, and the presence of an outflow, numerical simulations may be required to understand the dynamics of these irradiated exoplanet atmospheres.
+The extreme optical depths at \lya line center impose a large computational cost for solving radiative transfer with Monte Carlo methods directly coupled with fluid dynamics.
 The number of scatterings a photon undergoes is proportional to the line center optical depth, $\tau_0$, of the domain.
-Near the base of the atmosphere, the line center optical depth is ${\sim}10^9$, so most of the time is spent following photons in these cells.
+Near the base of the atomic layer, the line center optical depth is ${\sim}10^9$, so most of the time is spent following photons in these cells.
 A method that can treat these zones incorporating a direct solution rather than traditional Monte Carlo has the potential to greatly accelerate the calculation.
 
-A complete, general analytic solution for the resonance scattering has never been derived but approximate solutions exist in certain limits.
-\citet{1973MNRAS.162...43H} demonstrated that resonance-line radiation transfer in optically-thick media can be described by the Poisson equation.
+Approximate analytic solutions for resonant scattering exist in certain limits.
+\citet{1973MNRAS.162...43H} showed that when most of the radiation is out on the damping wings, the transfer equation reduces to the Poisson equation.
 However, their solution contains an incorrect treatment of the boundary condition.
@@
 
-Consider a sphere of radius $R$ and uniform density, with $n_{\rm sc}$ scatterers, luminosity $L$, and line-center optical depth $\tau_0$.
+Consider a sphere of radius $R$ with uniform density $n_{\rm sc}$, luminosity $L$, and line-center optical depth $\tau_0$.
 We aim to find the intensity within the sphere as a function of radius and photon frequency.
@@
 
-Starting with the full transfer equation, Eq. \ref{eq:finaleqn}, with no photon destruction and a photon emission term given by Eq. \ref{eq:jem}, the steady-state transfer equation is
+Appendix \ref{app:rteqn_derivation} contains a derivation of the transfer equation for convenience.
+The source is assumed to be a delta function in space and photon frequency.
+The photon frequency of the source is $\nu_s$, which is $x_s = (\nu_s - \nu_0)/\Delta$ in Doppler units.
+Starting with the full transfer equation, Eq.
+\ref{eq:finaleqn}, ignoring photon destruction and including a photon emission term given by Eq.
+\ref{eq:jem}, the steady-state transfer equation is
 \be
@@
 \be \label{eq:int_change_of_variables}
-\sigma = \sqrt{\frac{2}{3}}\int_0^x \frac{dx}{\phi(x) \Delta} \approx \sqrt{\frac{2}{3}}\frac{\pi}{a}\frac{x^3}{3}, 
-\ee
-where the approximation is applicable in the line wing. Then, the line profile is approximately (Equation \ref{eq:app:line_profile_wing})
+\sigma(x) = \sqrt{\frac{2}{3}}\int_0^x \frac{dx}{\phi(x) \Delta} \approx \sqrt{\frac{2}{3}}\frac{\pi}{a}\frac{x^3}{3}, 
+\ee
+where the approximation is applicable on the damping wing. The line profile is then approximately (Equation \ref{eq:app:line_profile_wing})
 \be \label{eq:line_profile_approx}
-\phi \approx \frac{a}{\pi x^2 \Delta} \approx \left(\frac{2a}{\pi}\right)^{1/3} \frac{1}{3 \Delta} \sigma^{-2/3}.
-\ee
-$\sigma_s$ is related to the photon frequency of the source.
+\phi \approx \frac{a}{\pi x^2 \Delta} \approx \frac{1}{3 \Delta}\left(\frac{2a}{\pi}\right)^{1/3}|\sigma^{-2/3}|.
+\ee
+$\sigma_s \equiv \sigma(x_s)$ is the photon frequency of the source.
 $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler units or Hz, respectively.
@@
 
-A solution for the mean intensity $J_d$ which is divergent at $\vec{x}=\vec{x_s}$ and $\sigma=\sigma_s$ is presented in \citet{1990ApJ...350..216N}.
+A solution for the mean intensity $J_d$ which is divergent at $\vec{x}=\vec{x_s}$ and $\sigma=\sigma_s$ and zero at infinity is presented in \citet{1990ApJ...350..216N}.
 Here it is extended to spherical geometry and generalized to allow emission frequencies away from line center:
@@
 A better approximation to the true solution has been derived by \citet{2006ApJ...649...14D}, who generalized the closed-form solution in slab geometry found in \citet{1990ApJ...350..216N}.
-They found a solution which satisfies a $J=0$ boundary condition at $r=R$.
+It satisfies a $J=0$ boundary condition at $r=R$.
 Again, we generalize their solution to allow emission at frequency $\sigma_{\rm s}$ away from line center.
@@
 \be \label{eq:J0_sum}
-J_0 = \frac{\sqrt{6}L}{16\pi \Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\frac{\sin{\kappa_n r}}{\kappa_n r}\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
+J_0 = \frac{\sqrt{6}L}{16\pi \Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\frac{\sin{\kappa_n r}}{\kappa_n r}\exp{\left(\frac{-\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
 \ee
@@
 \be \label{eq:H0_sum}
-H_0 = - \frac{1}{3k\phi} \frac{\partial J_0}{\partial r} = -\frac{1}{3k\phi}\frac{\sqrt{6}L}{16\pi\Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\left(\frac{\cos{\kappa_n r}}{r} - \frac{\sin{\kappa_n r}}{\kappa_n r^2}\right)\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
+H_0 = - \frac{1}{3k\phi} \frac{\partial J_0}{\partial r} = -\frac{1}{3k\phi}\frac{\sqrt{6}L}{16\pi\Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\left(\frac{\cos{\kappa_n r}}{r} - \frac{\sin{\kappa_n r}}{\kappa_n r^2}\right)\exp{\left(\frac{-\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
 \ee
@@
 \sum_{n=1}^{\infty} 
-n (-1)^n \exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)}\\
+n (-1)^n \exp{\left(\frac{-\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)}\\
 & = &  \frac{1}{3k\phi}
@@
 In order to enforce the boundary conditions, a different solution method is attempted here, namely, a continuous Fourier expansion in the frequency variable $\sigma$.
-The solution of this problem is split into two pieces: $J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied.
+The solution of this problem is split into two pieces: $J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied at $r=R$.
 The total solution is
@@
 \be
-H_{\rm bc}(r,\sigma) & = & \left( \frac{-1}{3k\phi} \right)
+H_{\rm bc}(r,\sigma) & = & -\frac{1}{3k\phi}
 \frac{\partial J_{\rm bc}(r,\sigma)}{\partial r}
-= \left( \frac{-1}{3k\phi} \right)
+= -\frac{1}{3k\phi}
 \int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s) 
@@
 We now estimate the scaling of $H_{\rm bc}$ with $\tau_0$.
-In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc} {\sim} H_0$ from Equation \ref{eq:bc2}.
-We  calculate $H_{\rm bc}$ from $J_{\rm bc}$ using Equation \ref{eq:Hbc} and introduce a change of variables to $\bar{\sigma} =  \sigma/\tau_0$ and $\bar{s}=s \tau_0$.
-The ratio of $H_{\rm bc}$ and $H_0$ is then proportional to $s/(\phi \Delta)$.
-In the line wing, $\phi \approx a / (\pi x^2 \Delta)$ according to Eq.
-\ref{eq:line_profile_approx}, and we must choose an appropriate value to insert for $x$.
-Our dimensionalization $\bar\sigma = \sigma / \tau_0$ implies that $\sigma {\sim} \tau_0$, which, from Equation \ref{eq:int_change_of_variables}, gives us the characteristic frequency
-\be \label{eq:tau_peak_scaling}
-x_{\rm peak} {\sim} \left(a\tau_0\right)^{1/3}.
-\ee
-This is the location of the spectral peak of the distribution. Similarly, $s {\sim} 1/\tau_0$ from the change of variables, and for the ratio of $H_{\rm bc}$ and $H_0$ we find
-
+Balancing the two terms on the left hand side of Equation \ref{eq:rt_no_destr} gives $\sigma \ {\sim}\ \tau_0$, or $x_{\rm peak}\ {\sim}\ (a\tau_0)^{1/3}$.
+In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc}\ {\sim}\ H_0$ from Equation \ref{eq:bc2}.
+We  calculate $H_{\rm bc}$ from $J_{\rm bc}$ using Equation \ref{eq:Hbc} as
+\be
+H_{\rm bc}(R, \sigma)\ {\sim}\ \frac{1}{3k\phi}\frac{ks}{\Delta}H_0\ {\sim}\ H_0 s \frac{x^2}{a}\ {\sim}\ H_0 \frac{1}{\tau_0}\frac{(a\tau_0)^{2/3}}{a}\ {\sim}\ H_0 (a\tau_0)^{-1/3},
+\ee
+so that
 \be \label{eq:hbc_scaling}
-\frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto \frac{1}{(a\tau_0)^{1/3}}.
+\frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto (a\tau_0)^{-1/3}.
 \ee
 At large $\tau_0$, it is expected that the correction term will be small, but it will become increasingly important as $\tau_0$ decreases.
-From Equation \ref{eq:tau_peak_scaling}, we see that the analytic solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
-For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$.
+Our solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
+For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = 4.72\times 10^{-4}$.
 Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$.

### 2021-11-09 ms.tex
Changes discussed in 2021-11-09 meeting

@@
 
-Consider a sphere of radius $R$ with uniform density $n_{\rm sc}$, luminosity $L$, and line-center optical depth $\tau_0$.
+Consider a sphere of radius $R$ with uniform density $n_{\rm sc}$, luminosity $L$, and line-center optical depth $\tau_0$ containing a point source of photons.
 We aim to find the intensity within the sphere as a function of radius and photon frequency.
+The point source is assumed to be a delta function in space and photon frequency.
 Photons of frequency $\nu$ near the line center frequency $\nu_0$ are considered.
+The photon frequency of the source is $\nu_s$.
 The Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
-The photon frequency in Doppler units is $x = (\nu-\nu_0)/\Delta$.
+The photon frequency in Doppler widths is $x = (\nu-\nu_0)/\Delta$, and $x_s = (\nu_s - \nu_0)/\Delta$ is the corresponding source frequency.
 For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
@@
 Appendix \ref{app:rteqn_derivation} contains a derivation of the transfer equation for convenience.
-The source is assumed to be a delta function in space and photon frequency.
-The photon frequency of the source is $\nu_s$, which is $x_s = (\nu_s - \nu_0)/\Delta$ in Doppler units.
 Starting with the full transfer equation, Eq.
@@
 \be \label{eq:line_profile_approx}
-\phi \approx \frac{a}{\pi x^2 \Delta} \approx \frac{1}{3 \Delta}\left(\frac{2a}{\pi}\right)^{1/3}|\sigma^{-2/3}|.
+\phi \approx \frac{a}{\pi x^2 \Delta} \approx \frac{1}{3 \Delta}\left(\frac{2a}{\pi}\right)^{1/3}|\sigma|^{-2/3}.
 \ee
 $\sigma_s \equiv \sigma(x_s)$ is the photon frequency of the source.
-$\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler units or Hz, respectively.
+$\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler widths or Hz, respectively.
+Balancing the two terms on the left hand side of Equation \ref{eq:rt_no_destr} gives $\sigma \ {\sim}\ \tau_0$, or $x_{\rm peak}\ {\sim}\ (a\tau_0)^{1/3}$.
 The boundary condition of no incoming intensity at the surface \citep{1986rpa..book.....R} is
@@
 We now estimate the scaling of $H_{\rm bc}$ with $\tau_0$.
-Balancing the two terms on the left hand side of Equation \ref{eq:rt_no_destr} gives $\sigma \ {\sim}\ \tau_0$, or $x_{\rm peak}\ {\sim}\ (a\tau_0)^{1/3}$.
 In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc}\ {\sim}\ H_0$ from Equation \ref{eq:bc2}.
@@
 \ee
-so that
+where we have used $s\ {\sim}\ 1/\sigma\ {\sim}\ 1/\tau_0$ so that
 \be \label{eq:hbc_scaling}

### 2021-11-10 ms.tex
adding clarity to source frequency in sigma units
adding ORCID ids

@@
 
-\author{B. Connor McClellan}
-\author{Shane Davis}
-\author{Phil Arras}
+\author[0000-0002-6040-8281]{B. Connor McClellan}
+\author[0000-0001-7488-4468]{Shane Davis}
+\author[0000-0001-5611-1349]{Phil Arras}
 \affiliation{Department of Astronomy, University of Virginia, Charlottesville, VA 22904, USA}
@@
 \ee
-$\sigma_s \equiv \sigma(x_s)$ is the photon frequency of the source.
+In Equation \ref{eq:rt_no_destr}, $\sigma_s \equiv \sigma(x_s)$ is the photon frequency of the source.
 $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler widths or Hz, respectively.
@@
 In order to enforce the boundary conditions, a different solution method is attempted here, namely, a continuous Fourier expansion in the frequency variable $\sigma$.
-The solution of this problem is split into two pieces: $J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied at $r=R$.
+The solution of this problem is split into two pieces: $J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $J_{\rm bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied at $r=R$.
 The total solution is
@@
 Further details of the Monte Carlo implementation are discussed in \cite{2017ApJ...851..150H}.
-
-\ifx
-\begin{figure}
-    \centering
-    \includegraphics{taubc.pdf}
-    \caption{Boundary condition term $H_{\rm bc}$ scaled by $(a\tau_0)^{1/3}$ shown for increasing $\tau_0$.
-The Monte Carlo data minus the $H_0$ solution should be close to $H_{\rm bc}$ according to Eq.
-\ref{eq:totalflux}.
-As $\tau_0$ becomes larger, the agreement between these two improves, indicating that at large optical depths the relative size of the corrective boundary condition term scales as $(a\tau_0)^{-1/3}$}.
-    \label{fig:taubc}
-\end{figure}
-\fi
 

### 2021-11-10 ms.tex
Rephrasing some things in discussion of Harrington separation of variables

@@
 where $2B$ is the slab optical depth at line center, $\phi$ is the line profile, and $\Delta$ is the Doppler width.
-The key point is that the line profile depends on one of the coordinates, frequency, and this causes the eigenvalues of the separation constant to depend on frequency.
-Thus, the separation ``constant'' is not constant, and the function does not satisfy the Poisson equation since the frequency derivatives will act on the separation ``constant" giving extra terms.
+The key point is that the line profile depends on one of the coordinates: frequency.
+This causes the eigenvalues of the separation constant to be frequency-dependent.
+Thus, the separation ``constant'' is not constant, and the function does not satisfy the Poisson equation since the frequency derivatives will act on the separation ``constant", giving extra terms.
 In the limit of large optical depth $B$, they approximate the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$.
-However, this solution gives zero mean intensity at the surface.
-Their Equation 34 subsequently allowed $\lambda$ to have a small deviation from the above expression, which was explicitly frequency dependent.
-This allowed a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
+However, this gives zero mean intensity at the surface.
+Their Equation 34 subsequently allows $\lambda$ to have a small deviation from the above expression, which is explicitly frequency dependent.
+This allows a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
 Our treatment, using the correct boundary condition, quantifies the errors in their ansatz.

### 2021-11-10 ms.tex
Finishing shane's edits to discussion and summary

@@
 \ee
-Here, $\omega$ describes the time-dependence of J.
+Here, $\omega$ describes the time-dependence of $J$.
 Though it is written as a function of the photon frequency variable $\sigma$, $J(r, \sigma, t)$ is the specific mean intensity $dE/(dA dt d\nu)$ and is a distribution in $\nu$.
@@
 The sum over eigenmodes produces an escape-time distribution that broadly captures the behavior shown by Monte Carlo data---a rise at early times, transitioning to exponential decay in the tail of the distribution.
-% TODO: Shane suggests the following places too much emphasis on the number of spatial terms?
-It is expected that the accuracy of the rate constant for the tail of the distribution is limited by the number of spatial terms included in the sum over eigenmodes, as the Doppler core can trap photons at high optical depths until they diffuse outward in frequency, weighting the distribution toward later times.
+It is expected that the accuracy of the rate constant for the tail of the distribution is limited by the effect of the Doppler core, which can trap photons at high optical depths until they diffuse outward in frequency, weighting the distribution toward later times.
 This physics is not modeled by our solution for two reasons: 1) our calculations ignored the Gaussian component of the Voigt line profile, leaving the Lorentzian piece which is accurate only in the line wing, and 2) knowing the core is not modeled accurately, we do not include a large enough number of spatial eigenmodes in the sum to resolve it.
-%
-However, a fitting function dependent on parameters $a$ and $\tau_0$ is found that adequately represents the escape time distribution within these constraints.
-The cumulative distribution function could be calculated using a rejection method, which would then be used to sample photon escape times directly rather than computing their travel times by the Monte Carlo method.
+However, an approximate fitting function dependent on parameters $a$ and $\tau_0$ is found that adequately represents the escape time distribution within these constraints.
 
@@
 Models of the escape of hydrogen gas in exoplanet atmospheres can be constructed with a treatment of resonant scattering of \lya in spherical geometry.
-The Monte Carlo method can be used for this problem, but requires a solution of the radiative transfer equation in spherical geometry and is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
-We seek to develop a computationally efficient random walk model in spherical geometry.
-There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}.
+The Monte Carlo method can be used for this problem, but is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
+We seek to develop a computationally efficient random walk model which requires a solution in spherical geometry.
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S} but we believe that these methods are not sufficient for our application.
 Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}; an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.
@@
 For this work, it would be necessary to model line center optical depths of up to 1 million or more.
-Such considerations will be taken in future work while developing this solution into a 1D hydrodynamic simulation using radiation forces from accelerated Monte Carlo \lya transfer.
+We will utilize the solution derived here as the basis for our own novel implementation of the modified random walk method.
 
@@
 We have examined previous solutions to \lya transfer in the limit of large optical depth, noting that the separation of variables and treatment of the boundary condition in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others does not produce a valid solution to the transfer equation.
-Here, we have derived the solution in spherical geometry with an appropriate treatment of the surface boundary condition as a frequency-dependent quantity, examining the spectral and time dependence of the resulting equations.
+Here, we have derived the solution in spherical geometry with an appropriate treatment of the surface boundary condition, examining the spectral and time dependence of the resulting equations.
 The key result is that the errors in the previously-cited works have been quantified via a correction term, $H_{\rm bc}$, which resolves an excess in flux at the spectral peak and a deficit in the line wing of the calculated spectrum of \lya radiation as compared with Monte Carlo.
-The size of $H_{\rm bc}$ diminishes at larger $\tau_0$, following a $(a\tau_0)^{-1/3}$ scaling.
+The size of $H_{\rm bc}$ is of order unity when the spectral peaks are near the Doppler core, and diminishes at larger $\tau_0$ following a $(a\tau_0)^{-1/3}$ scaling.
 Introducing time-dependence to the transfer equation leads to another solution which is solved numerically with an eigenfunction expansion.
@@
 \be
-\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{\mathcal{H}(x,a)}{\sqrt{\pi} \Delta}.
-= k \phi   
+\alpha_{\rm sc} & = & n_{\rm sc}\, \frac{\pi e^2}{m_e c}\, f\, \frac{\mathcal{H}(x,a)}{\sqrt{\pi} \Delta}
+= k \phi.
 \ee
@@
 \langle \Delta \nu^2 \rangle
-\right]
+\right].
 \ee 
@@
 \simeq k\phi J + \frac{1}{2} k \Delta^2 \frac{\partial }{\partial \nu} 
-\left( \phi \frac{\partial J}{\partial \nu}  \right)
+\left( \phi \frac{\partial J}{\partial \nu}  \right),
 \ee

### 2021-11-11 ms.tex
Changing sentence in introduction --- adding citation to Chenliang's paper and mention of pressure at atomic transition layer

@@
 It is shown that the lowest-order eigenfrequency of the semi-analytic calculation agrees well with the decay constant of the Monte Carlo escape time distribution at sufficiently large line-center optical depths.
-%A fitting function for the distribution is found which can be sampled to accelerate Monte Carlo radiation transfer calculations at large optical depths.
 
@@
 These observations have revealed a population of atoms extending out to distances of order a few planetary radii for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with the H atom population.
-In atmospheres with thick layers of atomic hydrogen, \lya radiation is especially important in the atmospheric dynamics of these systems as the optical depth at line center is large.
-This process necessitates a careful treatment of resonant scattering in order to construct accurate models of H atom excitation, heating, and radiative forces.
+The transition from the atomic to the molecular layer in these atmospheres may take place at pressures of order ${\sim}\ 10\ \mu$bar (see discussion in \citet{2017ApJ...851..150H} for details).
+This suggests the presence of a thick layer of atomic H which can have a line center optical depth of $\tau_0\ {\sim}\ 10^8$.
+A careful treatment of resonant scattering is necessary in order to construct accurate models of H atom excitation, heating, and radiative forces.
 
@@
 The number of scatterings a photon undergoes is proportional to the line center optical depth, $\tau_0$, of the domain.
-Near the base of the atomic layer, the line center optical depth is ${\sim}10^9$, so most of the time is spent following photons in these cells.
+Near the base of the atomic layer, the line center optical depth is ${\sim}10^8$, so most of the time is spent following photons in these cells.
 A method that can treat these zones incorporating a direct solution rather than traditional Monte Carlo has the potential to greatly accelerate the calculation.
@@
 \ref{eq:rteqn} that corresponds to excitation of the atom.
-The terms involving frequency derivatives of $\vec{H}$, if carried through the calculation,end up giving terms smaller than then largest terms by a factor of $1/x^2$, which is small on the line wing.
+The terms involving frequency derivatives of $\vec{H}$, if carried through the calculation, end up giving terms smaller than then largest terms by a factor of $1/x^2$, which is small on the line wing.
 These terms are ignored from here on.
@@
 When $\sigma_s=0$, we may show that the solutions both near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines where both functions have short-wavelength behavior.
-This matched asymptotic expansion allows us to relate the normalization coefficients $a_1$ and $a_3$.
+Matched asymptotic expansion \citep{1999amms.book.....B} allows us to relate the normalization coefficients $a_1$ and $a_3$.
 The matching conditions are

### 2021-11-15 ms.tex
Phil's last changes to the appendix

@@
 This solution is compared to that of the Monte-Carlo method, which is valid at arbitrary optical depth.
-It is shown that the size of the correction is order unity when the spectral peaks approach the Doppler core and decreases with line center optical depth, which may explain discrepancies in previous studies.
-For the impulsive problem, the time, spatial, and frequency dependence of the equation are expressed using an eigenfunction expansion and are obtained numerically to characterize the escape time distribution and emergent spectra of photons.
-It is shown that the lowest-order eigenfrequency of the semi-analytic calculation agrees well with the decay constant of the Monte Carlo escape time distribution at sufficiently large line-center optical depths.
+It is shown that the size of the correction is order unity when the spectral peaks approach the Doppler core and decreases slowly with line center optical depth, which may explain discrepancies in previous studies.
+For the impulsive problem, the time, spatial, and frequency dependence of the solution are expressed using an eigenfunction expansion in order to characterize the escape time distribution and emergent spectra of photons.
+It is shown that the lowest-order eigenfrequency agrees well with the decay rate found in the Monte Carlo escape time distribution at sufficiently large line-center optical depths.
 

### 2021-11-16 ms.tex
Phil's final changes up to eq 25

@@
 The outer layers of the atmosphere are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
-Given the abundance of hydrogen and its large cross section, Lyman $\alpha$ (Ly$\alpha$) is an important component of the radiation field.
+Given the abundance of hydrogen and its large cross section, the Lyman $\alpha$ (Ly$\alpha$) line is an important component of the radiation field.
 There are two sources of Ly$\alpha$: the star, and recombinations in the planet's atmosphere.
@@
 Hubble Space Telescope (HST) observations with the STIS have found large \lya transit depths around a handful of exoplanets \citep{2003Natur.422..143V, 2012A&A...543L...4L, 2012A&A...547A..18E, 2015Natur.522..459E,  2017A&A...597A..26B, 2017A&A...599L...3B, 2017A&A...602A.106B, 2018A&A...620A.147B, 2019AJ....158...50W, 2019EPSC...13.1928L, 2020ApJ...888L..21G,2021arXiv210309864B}.
-These observations have revealed a population of atoms extending out to distances of order a few planetary radii for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with the H atom population.
-The transition from the atomic to the molecular layer in these atmospheres may take place at pressures of order ${\sim}\ 10\ \mu$bar (see discussion in \citet{2017ApJ...851..150H} for details).
+These observations have revealed a population of atoms extending out to distances of order a few planetary radii or more for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with the H atom population.
+The transition from the atomic to the molecular layer in these hot upper atmospheres may take place at pressures of order ${\sim}\ 10\ \mu$bar (see discussion in \citet{2017ApJ...851..150H} for details).
 This suggests the presence of a thick layer of atomic H which can have a line center optical depth of $\tau_0\ {\sim}\ 10^8$.
@@
 
-Due to the technical challenge of including resonant scattering, the fully three-dimensional geometry, and the presence of an outflow, numerical simulations may be required to understand the dynamics of these irradiated exoplanet atmospheres.
-The extreme optical depths at \lya line center impose a large computational cost for solving radiative transfer with Monte Carlo methods directly coupled with fluid dynamics.
+Due to the technical challenge of including resonant scattering, the fully three-dimensional geometry, and the presence of an outflow, numerical simulations may be required to fully understand the dynamics of these irradiated exoplanet atmospheres.
+The large optical depths at \lya line center impose a steep computational cost for solving radiative transfer with Monte Carlo methods directly coupled with fluid dynamics.
 The number of scatterings a photon undergoes is proportional to the line center optical depth, $\tau_0$, of the domain.
@@
 To our knowledge, the errors introduced by this treatment have never been quantified.
-They attempt a separation of variables $J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ (their Equations 16 and 23).
+They attempt a separation of variables as $J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ (their Equations 16 and 23).
 The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
@@
 
-A solution for the mean intensity $J_d$ which is divergent at $\vec{x}=\vec{x_s}$ and $\sigma=\sigma_s$ and zero at infinity is presented in \citet{1990ApJ...350..216N}.
-Here it is extended to spherical geometry and generalized to allow emission frequencies away from line center:
+A solution for the mean intensity $J_d$ which is divergent at $\vec{x}=\vec{x_s}=0$ %TODO: This ok?
+and $\sigma=\sigma_s$ and zero at infinity is presented in \citet{1990ApJ...350..216N}. Here it is extended to spherical geometry and generalized to allow emission frequencies away from line center: 
 \be
@@
 We now estimate the scaling of $H_{\rm bc}$ with $\tau_0$.
-In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc}\ {\sim}\ H_0$ from Equation \ref{eq:bc2}.
+In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc} \approx \sqrt{3} H_0$ from Equation \ref{eq:bc2}.
 We  calculate $H_{\rm bc}$ from $J_{\rm bc}$ using Equation \ref{eq:Hbc} as
 \be
-H_{\rm bc}(R, \sigma)\ {\sim}\ \frac{1}{3k\phi}\frac{ks}{\Delta}H_0\ {\sim}\ H_0 s \frac{x^2}{a}\ {\sim}\ H_0 \frac{1}{\tau_0}\frac{(a\tau_0)^{2/3}}{a}\ {\sim}\ H_0 (a\tau_0)^{-1/3},
+H_{\rm bc}(R, \sigma) \approx \frac{1}{\sqrt{3}k\phi}\frac{ks}{\Delta}H_0\ {\sim}\ H_0 s \frac{x^2}{a}\ {\sim}\ H_0 \frac{1}{\tau_0}\frac{(a\tau_0)^{2/3}}{a}\ {\sim}\ H_0 (a\tau_0)^{-1/3},
 \ee
@@
 Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$.
-Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} \approx 10^5$.
+Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} \approx 10^5$ (``core-peak'' optical depth).
 Hence $H_{\rm bc}/H_0 {\sim} (\tau_{\rm cp}/\tau_0)^{1/3}$ is large at $\tau_0 \leq \tau_{\rm cp}$ and decreases relatively slowly as $\tau_0$ increases.
@@
     \includegraphics{final_residual.pdf}
-    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
-Photons are initialized with $\rm x = 0.0$.
-In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$ to examine the contributions of both positive and negative pieces.
-Residuals of each solution to the Monte Carlo data points are shown in the third panel.}
+    \caption{Spectrum $P(x)$ vs.
+frequency $x$.
+The analytic solutions for the outgoing spectrum are calculated at a line center optical depth of $\tau_0 = 1 \times 10^7$ and $a = 4.72\times 10^{-4}$ with $x_s = 0.0$.
+The top panel is linear scale, the middle panel is log scale with $|\rm H_{bc}|$ shown instead of $\rm H_{bc}$, and the bottom panel is the residual of each solution with Monte Carlo.}
     \label{fig:sol_mc_residual_0}
@@
 We now compare each of the previously-discussed solutions for surface flux to the Monte Carlo results.
-We return to the Doppler units $x$ for the photon frequency rather than the $\sigma$ units used in the solutions of the transfer equation.
 The spectrum $P(x)$ is defined as the specific luminosity at the surface divided by the source luminosity, or
-\be
+\be \label{eq:prob_spectrum}
 P(x) = \frac{16\pi^2R^2H(R, x)\Delta}{L}.
 \ee
-This is normalized such that $\int P(x)dx = 1$. Since $H(r, x)$ is per $d\nu$, a factor of $\Delta$ gives the expression the correct units.
+This is normalized as $\int P(x)dx = 1$. Since $H(r, x)$ is per $d\nu$, a factor of $\Delta$ gives the expression the correct units.
 
@@
 
-The size of $H_{\rm bc}$ is dependent on $\tau_0$, which also dictates the x-position of the peak of spectrum according to Eq.
-\ref{eq:tau_peak_scaling}.
+The size of $H_{\rm bc}$ is dependent on $\tau_0$.
 $H_{\rm bc}$ is significant even at $\tau_0 {\sim} 10^7$ where the $H_0$ solution is expected to perform well, i.e., photons are pushed further out into the wing where the simplifying assumptions made in the derivation of the differential equation are a better approximation.
@@
 \ref{fig:sol_mc_tau} improves as $\tau_0$ increases, with $H_{\rm bc}$ providing a fractionally smaller correction to $H_0$.
-One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis such that the peaks of the distributions are vertically aligned.
+One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis such that the peaks of the distributions are horizontally aligned.
 This scaling has also been applied to the y-axis to preserve normalization of the escape probability.
@@
     \includegraphics{xinit_threepanel.pdf}
-    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$.
-Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency.
-The optical depth at each of these source frequencies is $\tau_s = 10^7, 77,$ and $19$, respectively.}
+    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\rm x_s = 0.0, 6.0, 12.0$. The optical depth at each of these source frequencies is $\tau_s = 10^7, 77,$ and $19$, respectively.} 
     \label{fig:sol_mc_xinit}
@@
     \includegraphics{xinit_threepanel_tau1e6.pdf}
-    \caption{Again changing $x_s$, but at a lower optical depth of $\tau_0 = 10^6$.
-The shift in $x$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the bias in the spectrum is much more drastic.
+    \caption{The same as Fig.
+\ref{fig:sol_mc_xinit}, but at a lower optical depth $\tau_0 = 10^6$.
+The shift $x_s$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the asymmetry in the spectrum is much larger.
 The optical depth at the source frequency is $\tau_s = 10^6$, $7.7$, and $1.9$ for $x_s=0.0, 6.0,$ and $12.0$, respectively.
@@
 
-Figure \ref{fig:sol_mc_xinit} shows calculations performed for three initial photon frequencies $\rm x_s = 0.0, 6.0$, and $12.0$ for a line center optical depth of $\tau_0=10^7$.
-The asymmetry of the spectrum is slight for $\rm x_s = 6.0$ where the cross section is still relatively large, but the increase in mean free path is much more substantial when photons are initialized with $\rm x_s=12.0$, outside the line core.
+Figure \ref{fig:sol_mc_xinit} shows calculations performed for $x_s = 0.0, 6.0$, and $12.0$ and $\tau_0=10^7$.
+The asymmetry of the spectrum is slight for $\rm x_s = 6.0$ where $\tau(x_s)=77$, but is larger for $\rm x_s=12.0$ outside the line core where $\tau(x_s)=19$.
 It is seen here that the difference between the Monte Carlo data and $H_0$ becomes larger as $\rm x_s$ increases.
-Thus, for sufficiently large $\tau_0$ and emission away from line center ($x_s \neq 0$), the importance of enforcing frequency-dependent boundary conditions at the surface of the sphere grows.
+Thus, for large $|x_s|$, inclusion of $H_{\rm bc}$ is more important.
 
 Figure \ref{fig:sol_mc_xinit_lowtau} shows emission away from line center at the same values of $x_s$ as in Figure \ref{fig:sol_mc_xinit}, but for $\tau_0=10^6$ rather than $10^7$.
-The difference between the left and right side of the escaping spectrum is substantial at lower optical depths, since $(a\tau_0)^{-1/3}$ increases by a factor of ${\sim}2$.
+The difference between the left and right side of the escaping spectrum is now substantial since $(a\tau_0)^{-1/3}$ increased by a factor of ${\sim}2$.
 It is clear from the figure that as $x_s$ extends further into the wing, the spectrum becomes more strongly peaked in frequency.
-Additionally, since the sphere is increasingly optically thin in the wing, we expect there to be a stronger disagreement between the Monte Carlo and the analytic solution as the equation assumed large optical depths.
+Additionally, since the sphere is increasingly optically thin on the wing, we expect there to be a stronger disagreement with the Monte Carlo as the analytic solution assumed large optical depths.
 
@@
     \includegraphics[width=\textwidth]{xinit.pdf}
-    \caption{$H_{\rm bc}$ solutions shown at three line center optical depths, $\tau_0=10^5, 10^7,$ and $10^9$, for photon source frequencies $\sigma_s=0.0, \tau_0, 2\tau_0$.
-Thicker lines indicate larger optical depth, and darker lines indicate $\sigma_s$ further from line center.
+    \caption{$H_{\rm bc}$ vs.
+frequency.
+Here $P(x) = 16\pi^2R^2H_{\rm bc}(R, x)\Delta/L$, as in Eq.
+\ref{eq:prob_spectrum}.
+Thicker lines indicate larger optical depth labeled by $\tau_0=10^5, 10^7,$ and $10^9$, and darker lines indicate $\sigma_s$ further from line center, labeled by $\sigma_s=0.0, \tau_0, 2\tau_0$.
+The location of the core-wing boundary $x_{cw}$ is shown with green vertical lines of increasing thickness for each $\tau_0$.
 The axes are scaled to show that the size of the corrective factor agrees with the predicted $(a\tau_0)^{-1/3}$ scaling.}
@@
 Figure \ref{fig:xinit} shows how the boundary term $H_{\rm bc}$ scales with both $\tau_0$ and $x_s$.
-In this figure, $x_s$ is shifted by integer multiples of $\tau_0$ in $\sigma$ frequency units (Eq.
-\ref{eq:change_of_variables}) such that the source, now written $\sigma_s$, falls near the peak of the spectrum for each $\tau_0$.
+In this figure, $\sigma_s$ is shifted by integer multiples of $\tau_0$ (Eq.
+\ref{eq:change_of_variables}) such that the source falls near the peak of the spectrum for each $\tau_0$.
 For clarity, only the $x > 0$ side of the spectrum is shown.
@@
 \ref{eq:hbc_scaling}, it is expected that the fractional size of $H_{\rm bc}$ relative to $H_0$ should become smaller with larger optical depths following $(a\tau_0)^{-1/3}$.
-This factor has been scaled out of the figure such that solutions for different optical depths and the same source frequency $\sigma_s$ should show close agreement in scale on the figure's vertical axis if the relation holds.
-Indeed, the scaled solutions converge as the optical depth becomes larger, indicating general agreement with the $(a\tau_0)^{-1/3}$ scaling.
+This factor has been scaled out of the figure such that solutions for different $\tau_0$ and the same $\sigma_s$ should show close agreement in scale on the figure's vertical axis if the relation holds.
+Indeed, the scaled solutions converge as $\tau_0$ becomes larger, indicating agreement with the $(a\tau_0)^{-1/3}$ scaling.
 The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ results from $x_{\rm peak}$ becoming close to $x_{\rm cw}$; at lower $\tau_0$, this causes the line profile approximation in the wing (Eq.
 \ref{eq:app:line_profile_wing}) to break down.
-From this, we conclude that the errors introduced by the incorrect separation of variables in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others are proportional to $(a\tau_0)^{-1/3}$.
+From this, we conclude that the errors introduced by the incorrect separation of variables in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others are indeed proportional to $(a\tau_0)^{-1/3}$.
 
@@
 In order to understand how long it takes for the photons to escape the uniform sphere of gas we must reintroduce the time dependence of the diffusion equation, which was ignored in the steady-state calculations in Section \ref{sec:steadystate}.
-To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a radiation field that is dynamic on timescales comparable to the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to a delta function impulse is found.
+To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ on timescales comparable to the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to a delta function impulse is found.
 This allows the distribution of photon escape times (the ``wait time distribution'') to be characterized.
-For simplicity a $J=0$ boundary condition will be used in the following derivations, which is a rough approximation for $a\tau_0 \gg 1$.
+For simplicity, a $J=0$ boundary condition will be used in the following derivations, which is a rough approximation for $a\tau_0 \gg 1$.
 
@@
 
-The emissivity for an impulsive source with energy E, source position $\vec{x}_s$, and frequency $\nu_s$ is 
-\be
-j_{\rm em} & = & \frac{E}{4\pi} \delta^3(\vec{x} - \vec{x}_s) \delta(\nu-\nu_{\rm s})\delta (t) ,
+The emissivity for an impulsive source with energy E, source position $\vec{x}_s$, and frequency $\nu_s$ is derived in Appendix \ref{app:rteqn_derivation}.
+Considering a photon source at $\vec{x}_s=0$, we have (Eq.
+\ref{eq:jem})
+\be
+j_{\rm em} & = & \frac{E}{4\pi} \delta^3(\vec{x}) \delta(\nu-\nu_{\rm s})\delta (t) ,
 \label{eq:jem2}
-\ee % TODO: Phil said to cite an equation from the appendix here?
+\ee 
 The resulting equation for $J(r,\sigma,t)$ is

### 2021-11-18 ms.tex
Finishing up Phil's last edits up to discussion section

@@
 \be
--3 \frac{k\phi}{c} \frac{\partial J}{\partial t} + \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2}
+ \frac{-3k\phi}{c} \frac{\partial J}{\partial t} + \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2}
 & = & - \frac{\sqrt{6} kE}{4\pi \Delta^2} \delta^3(\vec{x}) \delta (\sigma - \sigma_s ) \delta (t).
@@
 \ee
-We employ an expansion in terms of spherical Bessel functions in $r$ and Fourier transform in time. The expansion for $J(r, \sigma, t)$ is then
+We employ an expansion in terms of spherical Bessel functions in $r$ and Fourier transform in time.
+The zeroth spherical Bessel function is $j_0(x) = \sin{x}/x$.
+The expansion for $J(r, \sigma, t)$ is then
 \be
@@
 \ee
-Here, $\omega$ describes the time-dependence of $J$.
+Here, $\kappa_n = n\pi/R$ and $\omega$ describes the time-dependence of $J$.
 Though it is written as a function of the photon frequency variable $\sigma$, $J(r, \sigma, t)$ is the specific mean intensity $dE/(dA dt d\nu)$ and is a distribution in $\nu$.
@@
 \ee
-where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$ to chose the finite solution as $|\sigma|\to 0$.
+where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$ to choose the finite solution as $|\sigma|\to 0$.
 Numerical integrations are performed inward toward $\sigma_s$ over several domains: from large $|\sigma|$ to $\sigma_s$, from large $|\sigma|$ to 0, and from 0 to $\sigma_s$, depending on whether $\sigma_s$ is positive or negative.
@@
 
-We now employ an ansatz that roughly agrees with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
+We now wish to find an expression for the eigenfunctions $J(n, \sigma, \omega)$ in order to express the specific mean intensity $J(r, \sigma, t)$ as a sum over both spatial and frequency modes.
+To do so, we employ an ansatz that roughly agrees with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
 However, the analysis presented in Appendix \ref{app:wkb} suggests the ansatz is incomplete in the case where $x_s \neq 0$ and the solution is asymmetric about the line center.
@@
 \be \label{eq:jnsigmaomega_approx}
-J(n,\sigma,-i\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma_{nm} - \gamma} + C(\sigma),
-\ee
-where $C(\sigma)$ varies slowly in $\gamma$. An application of the residue theorem gives
+J(n,\sigma,-i\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma_{nm} - \gamma} + C(\gamma, \sigma),
+\ee
+where $C(\gamma, \sigma)$ varies slowly in $\gamma$. An application of the residue theorem gives %TODO: Problematic, but can this be improved given that we know it doesn't work?
 \be
@@
 \be \label{eq:sum_rule}
-1 & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE} \sum_{nm} (-1)^{n+1} \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
+E & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3k} \sum_{nm} (-1)^{n+1} \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
 \ee
@@
 After iterating an eigenvalue $\gamma_{nm}$ to convergence, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
-We can solve for $J_{nm}(\sigma)$ by comparing two points $\gamma_1$ and $\gamma_2$ near the resonance, cancelling $C(\sigma)$ in the difference to find
+We can solve for $J_{nm}(\sigma)$ by comparing two points $\gamma_1$ and $\gamma_2$ near the resonance, cancelling $C(\gamma, \sigma)$ in the difference to find
 \be
@@
     \includegraphics{Jsoln_n1_m100.pdf}
-    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $x_s=0$, $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.}
+    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $x_s=0$, $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.
+} %TODO: Mentioned in previous caption that 'a' needs to be included.
+What's the solution here?
+Include or not?
+Reference?
     \label{fig:jsoln}
 \end{figure}
-\noindent The form of a single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{tp}$, at which point the function becomes evanescent.
+\noindent The form of a single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{\rm tp}$, at which point the function becomes evanescent.
 The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Eq.
@@
 \ref{eq:Jrsigmat}, the bounds of $\sigma$ must be set sufficiently far outside of $\sigma_{\rm tp}$ such that the function is small at the edges.
-The scale of an $e$-folding in $J_{nm}(\sigma)$ is $k/(\kappa_n \Delta) = \tau_0 / (\sqrt{\pi} n)$, so a grid of $\sigma$ is chosen that spans a large enough number of $e$-foldings that no oscillatory behavior is present at the boundaries of the calculation.
+The scale of an $e$-folding in $J_{nm}(\sigma)$ is $k/(\kappa_n \Delta) = \tau_0 / (\sqrt{\pi} n)$, so a grid of $\sigma$ is chosen that spans a large enough number of $e$-foldings that no oscillatory behavior is present at the boundaries of the domain.
 
 The eigenfunction's oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity.
-The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.
+The largest contribution at late times always comes from the ($n=1, m=1$) lowest-order eigenfunction.
 Fig.
 \ref{fig:jsoln} shows a set of eigenfunctions $J_{nm}(\sigma)$ to illustrate their relative scales for different $m$ at a fixed spatial eigenmode $n$.
-The overall scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$ with $E$ arbitrarily set to 1, $k = \tau_0 \sqrt{\pi} \Delta / R$, and $R = 10^{11}$ cm.
-For H atoms with $T=10^4$ K and $\tau_0=10^7$, an eigenfunction has typical size ${\sim} E a / \left(R^2 \Delta \right) = 10^{-37}$.
+The overall scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$ with $E$ arbitrarily set to 1.
+For H atoms with $T=10^4$ K and $\tau_0=10^7$, an eigenfunction has typical size ${\sim} E a / \left(R^2 \Delta \right) = 10^{-37}$ in units of specific mean intensity times time.
 Additional terms add smaller-magnitude, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
@@
     \includegraphics[width=\textwidth]{gamma_nm.pdf}
-    \caption{The scaling of numerically-obtained resonant frequencies as compared with the analytic expression in Eq. \ref{eq:gamma_nm}. The data shown is for $\tau_0=10^7$ and $x_s=0.0$.}
+    \caption{Decay rate vs.
+mode number.
+Overlapping solid lines are plotted for each $n$.
+The thickness of the lines decrease with $n$ in order to clearly show where they are in agreement.
+These numerically-obtained resonant frequencies are compared with the analytic expression in Eq.
+\ref{eq:gamma_nm}.
+The parameters for the calculation are $\tau_0=10^7$ and $x_s=0.0$.}
     \label{fig:gamma_nm}
@@
 which is normalized to unity.
-For a sufficiently large number of spatial modes $n$ and frequency modes $m$, the result of this sum can agree with Monte Carlo escape time distributions when $x_s=0$, but it is not a fast enough computational method to use as a distribution for sampling.
-However, the late-time distribution is simply an exponential falloff.
+For a sufficiently large number of spatial modes $n$ and frequency modes $m$, the result of this sum can agree with Monte Carlo escape time distributions when $x_s=0$.
+The late-time distribution is simply an exponential falloff.
 The rate constant of the falloff is the lowest-order eigenfrequency, $\gamma_{11}$, and its scale is determined by the coefficient $P_{11}$ as in Eq.
@@
 At lower $\tau_0$, the effects of line core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
-Here, the Monte Carlo accurately characterizes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile and does not use enough spatial modes to accurately model the frequency regime near line center.
-However, as $\tau_0$ grows, the effect of core scattering becomes smaller and the approximations hold, agreeing well with the expected $(a\tau_0)^{1/3}$ scaling for the rate constant.
+Here, the Monte Carlo accurately includes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile, and also does not use enough spatial modes to accurately model the frequency regime near line center.
+However, as $\tau_0$ grows, the effect of core scattering becomes smaller and the approximations hold, agreeing well with the expected $(a\tau_0)^{1/3}$ scaling for the rate constant at late times.
 
@@
     \includegraphics[width=0.75\textwidth]{tau_scaling.pdf}
-    \caption{Characteristic timescales as a function of $\tau_0$.
+    \caption{Late-time decay timescale as a function of $\tau_0$.
 $\gamma_{11}^{-1}$ and a fit of the exponential falloff for the Monte Carlo escape time distribution are shown to converge to a $t \propto (a\tau_0)^{1/3}$ scaling at large $\tau_0$.
@@
     \includegraphics{steadystate.pdf}
-    \caption{Comparison of steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ with $x_s=0$, $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.}
+    \caption{Time-integrated spectrum $P(x)$ vs.
+$x$.
+The steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ are shown with $x_s=0$, $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.}
     \label{fig:steadystate}
@@
     \includegraphics{waittime.pdf}
-    \caption{Wait time distributions of escaping photons for $\tau_0=10^6$ and $10^7$, which is fit using Eq.
+    \caption{Wait-time distribution of escaping photons $P(t)$ vs.
+t  for $\tau_0=10^6$ and $10^7$, which is fit using Eq.
 \ref{eq:fitting_function}.
@@
 
-A primary goal of this work is to present a solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere.
+\subsection{Steady State Source}
+A primary goal of this work is to present a solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near the line-center frequency $\nu_0$ in a uniform sphere.
 We have generalized a spherically symmetric solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center.
-We have made a correction to their incorrect $J=0$ surface boundary condition that allows the proper condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere.
+We have included a correction to their incorrect $J=0$ surface boundary condition that allows the proper condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere.
 This introduces a term $J_{\rm bc}$ which is solved using a continuous Fourier expansion in frequency.
-Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions.
 The continuous expansions are discretized and the Fourier coefficients solved for.
-The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$.
+The resulting flux correction, $H_{\rm bc}$, scales as $H_0(a\tau_0)^{-1/3}$.
 Thus, for large $\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $\tau_0$.
-Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, our solutions do not model areas where the Doppler core of the \lya line has a significant effect on the scattering of photons.
+Since the Laplacian form of the differential equation is only correct when the line profile is $\phi \approx a/(\pi x^2)$, our solutions do not accurately model the Doppler core of the \lya line.
 Because the peak of the spectral energy distribution of escaping photons is $x_{\rm peak} = (a\tau_0)^{1/3}$, calculations performed at low $\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
-This effect is especially prevalent for larger H gas temperature, as the boundary between the Doppler core and line wing extends further out as $T$ increases.
 
@@
 
+\subsection{Impulsive Source}
 The time-dependence of the problem is solved for a $J=0$ boundary condition to characterize the distribution of photon escape times.
@@
 Additional frequency eigenmodes introduce fast-oscillating terms that improve the accuracy of the sum, as their contributions cancel with components of lower-order terms to better represent the true solution.
-Integrating the solution over time produces a spectrum that is shown to agree well with the steady-state calculations in Section \ref{sec:steadystate}, provided a sufficient number of terms in the sum.
+Integrating the solution over time produces a spectrum that is shown to broadly agree with the steady-state calculations in Section \ref{sec:steadystate}, provided a sufficient number of terms in the sum and emission at the line-center frequency $\nu_0$.
 Integrating the solution over frequency leads to a distribution of photon escape times, which can be compared directly with Monte Carlo simulations.
@@
 
-This leads in to the primary application of this work.
+This leads in to a possible application of this work.
 Models of the escape of hydrogen gas in exoplanet atmospheres can be constructed with a treatment of resonant scattering of \lya in spherical geometry.
@@
 There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S} but we believe that these methods are not sufficient for our application.
+%TODO: Why?
+Not bc of Fokker-Planck---we use that too.
+Core skipping obviously oversimplifies the spatial / frequency redistribution, but why not hybrid diffusion?
+Smith et al 2018 outlines this in sec 5.1 but has it actually been implemented?
 Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}; an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.

### 2021-11-18 ms.tex
fixing abs val signs in eqs 10, 11, 12
Rewording computational barrier sentence in introduction

@@
 Near the base of the atomic layer, the line center optical depth is ${\sim}10^8$, so most of the time is spent following photons in these cells.
-A method that can treat these zones incorporating a direct solution rather than traditional Monte Carlo has the potential to greatly accelerate the calculation.
+A method that can accurately characterize transfer through these zones without following every photon scattering has the potential to greatly accelerate the calculation.
 
@@
 \left( 
-\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
+\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] - \cos(\pi r/R)}
 \right)
@@
 \left( 
-\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
+\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] - \cos(\pi r/R)}
 \right. \nonumber \\ & & \left. - \left( \frac{\pi r}{R} \right)
-\frac{ \cos(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
+\frac{ \cos(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] - \cos(\pi r/R)}
 + \left( \frac{\pi r}{R} \right)
-\frac{ \sin^2(\pi r/R) }{ \left[ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R) \right]^2 }
+\frac{ \sin^2(\pi r/R) }{ \left[ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] - \cos(\pi r/R) \right]^2 }
 \right).
@@
 \left( 
-\frac{ 1 }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] +1 }
+\frac{ 1 }{ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] +1 }
 \right).

### 2021-11-18 ms.tex
Changing absolute values back to parentheses inside cosh functions

@@
 For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
-Here $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} \pi e^2 f/(m_e c)$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+For the \lya transition and T=$10^4$ K, $a = 4.72\times 10^{-4}$.
+$\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} \pi e^2 f/(m_e c)$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
 The line center optical depth is then $\tau_0 = kR/(\sqrt{\pi}\Delta)$.
+% Here $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, 
+% Add the oscillator strength (number) cite Rybicki and Lightman
 
@@
 where $J$ is the mean intensity, the spatial variable is $\vec{x}$, and $\vec{x}_s$ is the position of the source.
+We will consider only the case where $\vec{x}_s=0$.
 Following \citet{1973MNRAS.162...43H}, we have used a change of variables from $x$ to $\sigma$,
@@
 at $r=R$. 
-
-A solution for the mean intensity $J_d$ which is divergent at $\vec{x}=\vec{x_s}=0$ %TODO: This ok?
-and $\sigma=\sigma_s$ and zero at infinity is presented in \citet{1990ApJ...350..216N}. Here it is extended to spherical geometry and generalized to allow emission frequencies away from line center: 
+%TODO: Remove all references to \vec{x}_s in the paper. Specify once that it's set to zero.
+A solution for the mean intensity $J_d$ which is divergent at the origin
+and $\sigma=\sigma_s$ and is zero at infinity is presented in \citet{1990ApJ...350..216N}.
+Here it is extended to spherical geometry and generalized to allow emission frequencies away from line center:
 \be
@@
 \left( 
-\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] - \cos(\pi r/R)}
+\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_s) \right] - \cos(\pi r/R)}
 \right)
@@
 \left( 
-\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] - \cos(\pi r/R)}
+\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_s) \right] - \cos(\pi r/R)}
 \right. \nonumber \\ & & \left. - \left( \frac{\pi r}{R} \right)
-\frac{ \cos(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] - \cos(\pi r/R)}
+\frac{ \cos(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_s) \right] - \cos(\pi r/R)}
 + \left( \frac{\pi r}{R} \right)
-\frac{ \sin^2(\pi r/R) }{ \left[ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] - \cos(\pi r/R) \right]^2 }
+\frac{ \sin^2(\pi r/R) }{ \left[ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_s) \right] - \cos(\pi r/R) \right]^2 }
 \right).
@@
 \left( 
-\frac{ 1 }{ \cosh \left[ \frac{\pi \Delta}{k R} |\sigma - \sigma_s| \right] +1 }
+\frac{ 1 }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_s) \right] +1 }
 \right).
@@
 Our solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
-For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = 4.72\times 10^{-4}$.
 Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$.
@@
     \includegraphics[width=\textwidth]{xinit.pdf}
-    \caption{$H_{\rm bc}$ vs.
-frequency.
-Here $P(x) = 16\pi^2R^2H_{\rm bc}(R, x)\Delta/L$, as in Eq.
-\ref{eq:prob_spectrum}.
+    \caption{$P_{\rm bc}(x) = 16\pi^2R^2H_{\rm bc}(R, x)\Delta/L$ (Eq.
+\ref{eq:prob_spectrum} with $H \rightarrow H_{\rm bc}$) vs.
+frequency $x$.
 Thicker lines indicate larger optical depth labeled by $\tau_0=10^5, 10^7,$ and $10^9$, and darker lines indicate $\sigma_s$ further from line center, labeled by $\sigma_s=0.0, \tau_0, 2\tau_0$.
 The location of the core-wing boundary $x_{cw}$ is shown with green vertical lines of increasing thickness for each $\tau_0$.
-The axes are scaled to show that the size of the corrective factor agrees with the predicted $(a\tau_0)^{-1/3}$ scaling.}
+The axes are scaled to show that the size of the correction factor agrees with the predicted $(a\tau_0)^{-1/3}$ scaling.}
     \label{fig:xinit}
@@
 
-Figure \ref{fig:xinit} shows how the boundary term $H_{\rm bc}$ scales with both $\tau_0$ and $x_s$.
+Figure \ref{fig:xinit} shows how the correction $P_{\rm bc}(x)$ (Eq.
+\ref{eq:prob_spectrum} with $H \rightarrow H_{\rm bc}$) scales with both $\tau_0$ and $x_s$.
 In this figure, $\sigma_s$ is shifted by integer multiples of $\tau_0$ (Eq.
@@
 
-We now wish to find an expression for the eigenfunctions $J(n, \sigma, \omega)$ in order to express the specific mean intensity $J(r, \sigma, t)$ as a sum over both spatial and frequency modes.
-To do so, we employ an ansatz that roughly agrees with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
-However, the analysis presented in Appendix \ref{app:wkb} suggests the ansatz is incomplete in the case where $x_s \neq 0$ and the solution is asymmetric about the line center.
+We now wish to reconstruct the specific mean intensity $J(r, \sigma, t)$.
+While one might expect this could be expressed as a sum over eigenmodes, the analysis presented in Appendix \ref{app:wkb} suggests this ansatz is incomplete in the case where $x_s \neq 0$ and the solution is asymmetric about the line center.
+This treatment roughly agrees with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
+
 Let us define the damping rate to be $\gamma \equiv i\omega$, which is real and positive for damped solutions.
@@
 \ee
-where $C(\gamma, \sigma)$ varies slowly in $\gamma$. An application of the residue theorem gives %TODO: Problematic, but can this be improved given that we know it doesn't work?
+where $C(\gamma, \sigma)$ varies slowly in $\gamma$.
+If the $\omega$-integral in Equation \ref{eq:jrsigmat_expansion} could be closed at infinity and evaluated using the residue theorem, the result would be
 \be
@@
     \includegraphics{Jsoln_n1_m100.pdf}
-    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $x_s=0$, $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.
-} %TODO: Mentioned in previous caption that 'a' needs to be included.
-What's the solution here?
-Include or not?
-Reference?
+    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $x_s=0$ and $\tau_0=10^7$. }
     \label{fig:jsoln}
@@
 Smith et al 2018 outlines this in sec 5.1 but has it actually been implemented?
+% Core skipping only really gives a good speedup for low tau0, 10^4 or 10^5.
+You still have tau0 scatterings on the wing.
+You also don't know how long you spend in the core, which prevents you from getting the intensity.
 Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}; an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.
@@
 
-We start with the differential equation Eq. \ref{eq:wkb_differential_eqn}. Near line center, this has two independent solutions which can be written
+In this appendix, we will find a WKB solution for the differential equation Eq. \ref{eq:wkb_differential_eqn} subject to the boundary conditions in Equations %TODO: Ref 28 and 29. 
+We will find this solution for the case $\sigma_s = 0$.
+
+% TODO: All the sigma in this appendix are presumed to be positive, but we've just assumed thta. It happens to be symmetric in this case;
+
+Near line center, this has two independent solutions which can be written
 \be \label{eq:wkb_J}
@@
 \ee
-where $J_\alpha(...)$ are Bessel functions of the first kind, $a_1$ and $a_2$ are normalization constants, $\sigma_{tp}$ is given in Eq.
+where $J_\alpha(x)$ are Bessel functions of the first kind, $a_1$ and $a_2$ are normalization constants, $\sigma_{tp}$ is given in Eq.
 \ref{eq:sigma_tp}, and $k_c=3\kappa_n \Delta \sigma_{\rm tp}/2k$.
 The solution far from line center is
-\be
+\be \label{eq:wkb_J_far}
 J(n,\sigma,s) & = & a_3 \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{1/6} Ai\left(k_c^{2/3} \left[ \left( \frac{\sigma}{\sigma_{\rm tp}} \right)^{2/3} - 1 \right]\right),
 \ee
-where $Ai(...)$ is the Airy function of the first kind. Again, $a_3$ is a normalization constant. When $\sigma_s=0$, we can enforce the discontinuity in Eq. \ref{eq:matching_condition_2} to find 
+where $Ai(x)$ is the Airy function of the first kind. Again, $a_3$ is a normalization constant. We can enforce the discontinuity in Eq. \ref{eq:matching_condition_2} to find 
 \be \label{eq:a2}
@@
 \ref{eq:wkb_J} is non-resonant.
-The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$.
-When $\sigma_s=0$, we may show that the solutions both near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines where both functions have short-wavelength behavior.
-Matched asymptotic expansion \citep{1999amms.book.....B} allows us to relate the normalization coefficients $a_1$ and $a_3$.
+The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$.
+Matched asymptotic expansions \citep{1999amms.book.....B} allows us to relate the normalization coefficients $a_1$ and $a_3$.
 The matching conditions are
@@
 
-We have applied this approximation for $\sigma_s=0$.
-In this case, we have obtained Equations \ref{eq:a1/a2} and \ref{eq:a3/a2} which approach infinity near the eigenfrequencies $\gamma_{nm}$, so there will be no contribution from the $a_2$ term in Equation \ref{eq:wkb_J} at these resonant frequencies.
+%The eigenfunctions themselves are symmetric
+% ^^^ Put this as the first thing we're saying.
+
+% Summarize the necessary points of the sigmas=0 solution
+
+%
+
+% In this case, we have obtained Equations \ref{eq:a1/a2} and \ref{eq:a3/a2} which approach infinity near the eigenfrequencies $\gamma_{nm}$, so there will be no contribution from the $a_2$ term in Equation \ref{eq:wkb_J} at these resonant frequencies.
 We now seek to understand the behavior of the solution when emission is away from line center ($\sigma_s \neq 0$).
-The eigenfunction expansion in Equation \ref{eq:Jrsigmat} assumed that a closed contour at infinity, bounding an infinite number of simple poles along the real $\gamma$-axis, could be integrated to find that $J(r, \sigma, t)$ is the sum of the residues of the poles contained within the contour.
-Equation \ref{eq:a2} shows there is an additional contribution unrelated to the eigenfunctions that is non-resonant.
-In the case where $\sigma_s \neq 0$, this non-resonant piece contributes to the asymmetry of the the solution about line center.
+
+While the solution above is specific to the case $\sigma_s = 0$, we can extend this approach to understand the case where $\sigma_s \neq 0$.
+We have found that, even in this case of emission away from the line center, the eigenfunctions are symmetric about the line center.
+This is because Equation \ref{eq:wkb_J_far} has dropped a term, $Bi(x)$, that is infinite far from line center; yet, in the region $0 < \sigma < \sigma_s$, this term is finite and contributes an asymmetric piece to the solution.
+This term is missing from the Equations \ref{eq:wkb_J} and \ref{eq:wkb_J_far}, meaning any solution produced by a sum over eigenmodes will always be symmetric about the line-center since the eigenfunctions themselves are always symmetric even when $\sigma_s \neq 0$.
+
+%The eigenfunction expansion in Equation \ref{eq:Jrsigmat} assumed that a closed contour at infinity, bounding an infinite number of simple poles along the real $\gamma$-axis, could be integrated to find that $J(r, \sigma, t)$ is the sum of the residues of the poles contained within the contour.
+
+% Equation \ref{eq:a2} shows there is an additional contribution unrelated to the eigenfunctions that is non-resonant.
+In the case where $\sigma_s \neq 0$, this non-resonant piece contributes to the asymmetry of the solution about line center.
 When $\sigma_s=0$, however, the solution is symmetric about line center and the non-resonant piece has no contribution except to produce the matching conditions in Equations \ref{eq:a1/a2} and \ref{eq:a3/a2}.
 Since we have applied the WKB approximation only when $\sigma_s = 0$, the non-resonant piece which allows the outgoing spectrum to be asymmetric is not captured by the methods outlined here.
+Thus,
 

### 2021-11-19 ms.tex
Addressing TODOs, most of what was discussed in today's meeting

@@
 at $r=R$.
-%TODO: Remove all references to \vec{x}_s in the paper. Specify once that it's set to zero.
+
 A solution for the mean intensity $J_d$ which is divergent at the origin
@@
 
-In order to enforce the boundary conditions, a different solution method is attempted here, namely, a continuous Fourier expansion in the frequency variable $\sigma$.
+In order to enforce the boundary conditions, a different solution method is attempted here, namely a continuous Fourier expansion in the frequency variable $\sigma$.
 The solution of this problem is split into two pieces: $J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $J_{\rm bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied at $r=R$.
@@
 We seek to develop a computationally efficient random walk model which requires a solution in spherical geometry.
-There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S} but we believe that these methods are not sufficient for our application.
-%TODO: Why?
-Not bc of Fokker-Planck---we use that too.
-Core skipping obviously oversimplifies the spatial / frequency redistribution, but why not hybrid diffusion?
-Smith et al 2018 outlines this in sec 5.1 but has it actually been implemented?
-% Core skipping only really gives a good speedup for low tau0, 10^4 or 10^5.
-You still have tau0 scatterings on the wing.
-You also don't know how long you spend in the core, which prevents you from getting the intensity.
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}, but these methods are not sufficient for our application since they do not track the amount of time photons spend in the line core.
 Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}; an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.
@@
 
-In this appendix, we will find a WKB solution for the differential equation Eq. \ref{eq:wkb_differential_eqn} subject to the boundary conditions in Equations %TODO: Ref 28 and 29. 
-We will find this solution for the case $\sigma_s = 0$.
-
-% TODO: All the sigma in this appendix are presumed to be positive, but we've just assumed thta. It happens to be symmetric in this case;
-
-Near line center, this has two independent solutions which can be written
+In this appendix, we will find a WKB solution for the differential equation Eq.
+\ref{eq:wkb_differential_eqn} subject to the boundary conditions in Equations \ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}.
+We will find this solution for the case $\sigma_s = 0$, assuming $\sigma \geq 0$ for simplicity since the solution is symmetric about $0$.
+
+Near the line center, this has two independent solutions which can be written
 \be \label{eq:wkb_J}
@@
 While the solution above is specific to the case $\sigma_s = 0$, we can extend this approach to understand the case where $\sigma_s \neq 0$.
-We have found that, even in this case of emission away from the line center, the eigenfunctions are symmetric about the line center.
+We have found that even in this case of emission away from the line center, the eigenfunctions are symmetric about the line center.
 This is because Equation \ref{eq:wkb_J_far} has dropped a term, $Bi(x)$, that is infinite far from line center; yet, in the region $0 < \sigma < \sigma_s$, this term is finite and contributes an asymmetric piece to the solution.
-This term is missing from the Equations \ref{eq:wkb_J} and \ref{eq:wkb_J_far}, meaning any solution produced by a sum over eigenmodes will always be symmetric about the line-center since the eigenfunctions themselves are always symmetric even when $\sigma_s \neq 0$.
+This term is missing from the Equations \ref{eq:wkb_J} and \ref{eq:wkb_J_far}, meaning any solution produced by a sum over eigenmodes will always be symmetric about the line-center since the eigenfunctions themselves are symmetric even when $\sigma_s \neq 0$.
 

### 2021-11-19 ms.tex
Fixing order of variable definitions and adding oscillator strength of lya from rybicki and lightman

@@
 For the \lya transition and T=$10^4$ K, $a = 4.72\times 10^{-4}$.
-$\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} \pi e^2 f/(m_e c)$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
-The line center optical depth is then $\tau_0 = kR/(\sqrt{\pi}\Delta)$.
-% Here $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, 
-% Add the oscillator strength (number) cite Rybicki and Lightman
+$\mathcal{H}(x,a)$ is the Voigt function, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$.
+The line center optical depth is $\tau_0 = kR/(\sqrt{\pi}\Delta)$, where $k = n_{\rm sc} \pi e^2 f/(m_e c)$.
+Here, $e$ and $m_e$ are the charge and mass of the electron, and $f$ is the oscillator strength of the transition, which is 0.4162 for \lya \citep{1986rpa..book.....R}.
 

### 2021-11-19 ms.tex
A few last corrections & equation checks

@@
 \ee
-which can be summed to give the closed form expressions
+where $\kappa_n=n\pi/R$. These can be summed to give the closed form expressions
 \be
@@
 
+\begin{figure}
+    \centering
+    \includegraphics{final_residual.pdf}
+    \caption{Spectrum $P(x)$ vs.
+frequency $x$.
+The analytic solutions for the outgoing spectrum are calculated at a line center optical depth of $\tau_0 = 1 \times 10^7$ with $x_s = 0.0$.
+The top panel is linear scale, the middle panel is log scale with $|\rm H_{bc}|$ shown instead of $\rm H_{bc}$, and the bottom panel is the residual of each solution with Monte Carlo.}
+    \label{fig:sol_mc_residual_0}
+\end{figure}
+
 \subsection{Comparison to Monte Carlo}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{final_residual.pdf}
-    \caption{Spectrum $P(x)$ vs.
-frequency $x$.
-The analytic solutions for the outgoing spectrum are calculated at a line center optical depth of $\tau_0 = 1 \times 10^7$ and $a = 4.72\times 10^{-4}$ with $x_s = 0.0$.
-The top panel is linear scale, the middle panel is log scale with $|\rm H_{bc}|$ shown instead of $\rm H_{bc}$, and the bottom panel is the residual of each solution with Monte Carlo.}
-    \label{fig:sol_mc_residual_0}
-\end{figure}
-
 We now compare each of the previously-discussed solutions for surface flux to the Monte Carlo results.
@@
 
-In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown along with that of the solutions $H_{\rm d}$, $H_0$, and $H_{\rm 0 + bc} = H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
+In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown along with that of the solutions $H_{\rm d}$, $H_0$, and $H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
 The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to $H_0$, it corrects for the apparent excess of flux in the peaks of the spectrum.
-The solution with the correct frequency-dependent boundary condition enforced, $H_{0 + \rm bc}$, has lower residuals to Monte Carlo results than the other solutions, especially in the line wing.
+The solution with the correct frequency-dependent boundary condition enforced, $H_0 + H_{\rm bc}$, has lower residuals to Monte Carlo results than the other solutions, especially in the line wing.
 The boundary term corrects the deficit of $H_0$ in the line wings, further improving agreement with the numerical result.
@@
     \centering
-    \includegraphics{tau_threepanel.pdf}
+    \includegraphics[width=\textwidth]{tau_threepanel.pdf}
     \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\tau_0 = 10^5, 10^6, 10^7$.
@@
     \centering
-    \includegraphics{xinit_threepanel.pdf}
+    \includegraphics[width=\textwidth]{xinit_threepanel.pdf}
     \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\rm x_s = 0.0, 6.0, 12.0$. The optical depth at each of these source frequencies is $\tau_s = 10^7, 77,$ and $19$, respectively.} 
@@
     \centering
-    \includegraphics{xinit_threepanel_tau1e6.pdf}
+    \includegraphics[width=\textwidth]{xinit_threepanel_tau1e6.pdf}
     \caption{The same as Fig.
@@
     \centering
-    \includegraphics[width=\textwidth]{xinit.pdf}
+    \includegraphics[width=0.8\textwidth]{xinit.pdf}
     \caption{$P_{\rm bc}(x) = 16\pi^2R^2H_{\rm bc}(R, x)\Delta/L$ (Eq.
@@
 \ee
-Integrating over time yields a factor $1/\gamma_{nm}$, and by integrating over $d\nu$ we find
+Integrating over time yields a factor $-1/\gamma_{nm}$, and by integrating over $d\nu$ we find
 \be \label{eq:sum_rule}
@@
     \centering
-    \includegraphics[width=\textwidth]{gamma_nm.pdf}
+    \includegraphics[width=0.8\textwidth]{gamma_nm.pdf}
     \caption{Decay rate vs.
@@
     \includegraphics{steadystate.pdf}
-    \caption{Time-integrated spectrum $P(x)$ vs.
-$x$.
-The steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ are shown with $x_s=0$, $a = 4.72\times 10^{-4}$ and $\tau_0=10^7$.}
+    \caption{Time-integrated spectrum $P(x)$ vs. $x$. The steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ are shown with $x_s=0$ and $\tau_0=10^7$.}
     \label{fig:steadystate}

### 2021-12-02 ms.tex
Fixing sign error - Eq 38 correct but some of the following steps dropped a sign
Adding line numbers to manuscript

@@
-\documentclass{aastex63}
+\documentclass[linenumbers]{aastex63}
 \usepackage{amsmath}
@@
 leads to a set of coupled linear equations for the $A(s_j)$.
-We use equally-spaced points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid.
+We use equally-spaced points $\delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\delta s = 2\pi/(N\delta \sigma)$, where $N$ is the number of points for each grid.
 The result is a linear system to solve for the $A(s)$.
@@
 \ee
-This is normalized as $\int P(x)dx = 1$. Since $H(r, x)$ is per $d\nu$, a factor of $\Delta$ gives the expression the correct units.
+This is normalized as $\int P(x)dx = 1$. Since $H(R, x)$ is per $d\nu$, a factor of $\Delta$ gives the expression the correct units.
 
@@
 \be
-J(n, \sigma, \omega)\ {\sim}\ e^{\pm \Delta \kappa_n \sigma / k}.
+J(n, \sigma, \omega)\ {\sim}\ e^{\pm \kappa_n \sigma \Delta / k}.
 \ee
@@
 \be \label{eq:single_j_derivative}
-\frac{\partial J}{\partial \sigma} = \mp \frac{\Delta\kappa_n}{k} J,
+\frac{\partial J}{\partial \sigma} = \mp \frac{\kappa_n\Delta}{k} J,
 \ee
@@
 We now wish to reconstruct the specific mean intensity $J(r, \sigma, t)$.
-While one might expect this could be expressed as a sum over eigenmodes, the analysis presented in Appendix \ref{app:wkb} suggests this ansatz is incomplete in the case where $x_s \neq 0$ and the solution is asymmetric about the line center.
-This treatment roughly agrees with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
+While one might expect this could be expressed as a sum over eigenmodes, the analysis presented in Appendix \ref{app:wkb} suggests this treatment is incomplete in the case where $x_s \neq 0$ and the solution is asymmetric about the line center.
+This ansatz does, however, roughly agree with Monte Carlo results for $x_s=0$ based on numerical calculations of this result.
 
@@
 \ee
-Integrating over time yields a factor $-1/\gamma_{nm}$, and by integrating over $d\nu$ we find
+Integrating over time yields a factor $1/\gamma_{nm}$, and by integrating over $d\nu$ we find
 \be \label{eq:sum_rule}
@@
 \be
-P(t)  & = & \sqrt{\frac{3}{2}} \frac{16\pi^2 R \Delta^2 }{3kE}     \sum_{nm} (-1)^n  e^{-\gamma_{nm}t} \int d\sigma J_{nm}(\sigma) 
+P(t)  & = & \sqrt{\frac{3}{2}} \frac{16\pi^2 R \Delta^2 }{3kE}     \sum_{nm} (-1)^{n+1}  e^{-\gamma_{nm}t} \int d\sigma J_{nm}(\sigma) 
 \nonumber \\ & = &  \sum_{nm} P_{nm} \gamma_{nm} e^{-\gamma_{nm}t},

### 2021-12-02 ms.tex
Rewording last paragraph before discussion --- condensing discussion of rate constant overestimation in eigenfunction solution, removing mention of cumulative distribution function

@@
 It is seen that the fitting function matches well with the late-time behavior of the eigenfunction solution, indicating that the tail of the escape time distribution can be modeled effectively by simple exponential decay.
-The remaining disagreement between the tail of the distribution and the Monte Carlo data is likely due to line core scattering which is not modeled by the eigenfunction solution, but improves for larger optical depth as seen in the figure.
-A cumulative distribution function can be created from Eq.
-\ref{eq:fitting_function} using a simple rejection method, which allows the function to be sampled rapidly.
+The remaining disagreement between the tail of the distribution and the Monte Carlo data is due to line core scattering which is not modeled by the eigenfunction solution, but improves for larger optical depth as seen in the figure.
+Many scatterings in the Doppler core affects the tail of the escape-time distribution, since photons with frequencies near line center will take longer to escape.
+Thus, the rate constant for the exponential falloff is overestimated slightly in the eigenfunction solution as compared with the Monte Carlo.
+The error in this rate constant is a function of $\tau_0$ since the effect from the Doppler core is greatest when it extends into the peak of the spectrum.
 
@@
 \end{figure}
-
-The effect of many scatterings in the Doppler core affects the tail of the escape-time distribution, since photons with frequencies near line center will take longer to escape.
-This explains the deficit of photons in the semi-analytic escape time distributions at late times, in that the rate constant for the exponential falloff is overestimated slightly as compared with the Monte Carlo.
-The error in this rate constant is a function of $\tau_0$ since the effect from the Doppler core is greatest when it extends into the peak of the spectrum.
 

### 2021-12-07 ms.tex
Fixing missing term in appendix and adding Phils edits

@@
 The radiative intensity $I = dE/(dA dt d\Omega d\nu)$ is the energy per perpendicular area $dA$, per time $dt$, per solid angle $d\Omega$ and per frequency $d\nu$ \citep{1986rpa..book.....R}.
-Here the time-dependence of $I$ has been ignored, which assumes the fluid is changing on timescales long compared to a light-crossing time.
-The intensity $I=I(\vec{x},\vec{n}, \nu)$ will be considered a function of position $\vec{x}$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$.
+The intensity $I=I(\vec{x}, t, \vec{n}, \nu)$ will be considered a function of position $\vec{x}$, time $t$, photon (unit) direction vector $\vec{n}$, and cyclic frequency $\nu$.
 In the Eddington and two-stream approximations, $I(\vec{x},\nu) \simeq J(\vec{x},\nu) + 3 \vec{n} \cdot \vec{H}(\vec{x},\nu)$, where $J=(1/4\pi) \int d\Omega I$ is the mean intensity and $\vec{F} = 4\pi \vec{H}= \int d\Omega \vec{n} I$ is the flux.
@@
 \ee
-The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over number density of the absorber times absorption cross section.
+The absorption coefficient $\alpha_{\rm abs}$, or inverse mean free path to true absorption, is a sum over species number density times absorption cross section.
 Once the incoming photon has promoted the electron to an excited state, the collisional de-excitation probability is $p$, and hence only a fraction $1-p$ of the excitations lead to re-emission of photons.
-Photon destruction will not be considered, so $p$ is set to 0 in this work.
-
-\citet{1973MNRAS.162...43H} first showed that the transfer equation for the mean  intensity $J$ will satisfy a Poisson equation involving second derivatives of space and frequency variables.
+
+\citet{1973MNRAS.162...43H} first showed that the transfer equation for the mean intensity $J$ will satisfy a Poisson equation involving space and frequency.
 In this section we will briefly review the derivation of this equation including photon destruction terms and an emission term.
 
- ``Hummer Case II-b"  \citep{1962MNRAS.125...21H} will be used for the redistribution function, for which the incoming photon is absorbed by the atom according to the natural broadening in the rest frame, re-emitted with a dipole phase function $g(\vec{n},\vec{n}^\prime)=(3/16\pi)(1+[\vec{n}\cdot \vec{n}^\prime]^2)$, which is appropriate for a 1s-2p transition \citep{1982qe}, and the result is averaged over a Maxwell-Boltzmann distribution of speeds for the atom.
+ ``Hummer Case II-b"  \citep{1962MNRAS.125...21H} will be used for the redistribution function, for which the incoming photon is absorbed by the atom according to the natural broadening profile in the rest frame, then is re-emitted with a dipole phase function $g(\vec{n},\vec{n}^\prime)=(3/16\pi)(1+[\vec{n}\cdot \vec{n}^\prime]^2)$, which is appropriate for a 1s-2p transition \citep{1982qe}, and then is averaged over a Maxwell-Boltzmann distribution of speeds for the atom.
 The result can be written
@@
 The former result implies that the integrated source and sink terms for scattering cancel for $p=1$.
-In addition, $d\nu d\Omega 4\pi R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime)/\phi(\nu^\prime) $ is the normalized distribution for the outgoing $\vec{n}$ and $\nu$ given the incoming $\vec{n}^\prime$ and $\nu^\prime$.
+In addition, $4\pi R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime)/\phi(\nu^\prime) $ is the normalized distribution for the outgoing $\vec{n}$ and $\nu$ given the incoming $\vec{n}^\prime$ and $\nu^\prime$.
 
@@
 \be
-\langle \Delta \nu^n \rangle & = & \frac{ \int d\nu^\prime R (\nu-\nu^\prime)^n}{\int d\nu^\prime R}
+\langle \delta \nu^n \rangle & = & \frac{ \int d\nu^\prime R (\nu^\prime-\nu)^n}{\int d\nu^\prime R}
 = \frac{1}{\phi(\nu)}
 \int \frac{ d^3v}{ \pi^{3/2} v_{\rm th}^3} e^{-v^2/v_{\rm th}^2}\,
-\left( \frac{\nu_0 \vec{v} \cdot (\vec{n}-\vec{n}^\prime) }{c} \right)^n
+\left( \frac{\nu_0 \vec{v} \cdot (\vec{n}^\prime-\vec{n}) }{c} \right)^n
 \left( \frac{\Gamma/4\pi^2}{ \left(\nu - \nu_0 - \nu_0 \vec{v} \cdot \vec{n}/c \right)^2 + (\Gamma/4\pi)^2 } \right),
@@
 \be
-\langle \Delta \nu \rangle & = & \Delta \langle u_\parallel \rangle \left( 1 - \vec{n} \cdot \vec{n}^\prime \right)
+\langle \delta \nu \rangle & = & -\langle u_\parallel \rangle \left( 1 - \vec{n} \cdot \vec{n}^\prime \right) \Delta 
 \\
-\langle \Delta \nu^2 \rangle & = & \Delta^2 
+\langle \delta \nu^2 \rangle & = & 
 \left[ \langle u_\parallel^2 \rangle
 \left( 1 - \vec{n} \cdot \vec{n}^\prime \right)^2
-+ \frac{1}{2} \left( 1 - \left( \vec{n} \cdot \vec{n}^\prime\right)^2 \right) \right].
-\ee
-
-For small frequency shifts $\nu-\nu^\prime$, the incoming intensity may be expanded as 
++ \frac{1}{2} \left( 1 - \left( \vec{n} \cdot \vec{n}^\prime\right)^2 \right) \right] \Delta^2 .
+\ee
+
+For small frequency shifts $\nu^\prime-\nu$, the incoming intensity may be expanded as 
 \be
@@
 I(\vec{x},\vec{n}^\prime,\nu) 
-- \frac{\partial I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu }
-\langle \Delta \nu \rangle
++ \frac{\partial I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu }
+\langle \delta \nu \rangle
 + \frac{1}{2} \frac{\partial^2 I(\vec{x},\vec{n}^\prime,\nu)}{\partial \nu^2 }
-\langle \Delta \nu^2 \rangle
+\langle \delta \nu^2 \rangle
 \right].
@@
 \ref{eq:rteqn} that corresponds to excitation of the atom.
-The terms involving frequency derivatives of $\vec{H}$, if carried through the calculation, end up giving terms smaller than then largest terms by a factor of $1/x^2$, which is small on the line wing.
-These terms are ignored from here on.
+The terms involving frequency derivatives of $\vec{H}$, if carried through the calculation, end up giving terms smaller than the largest terms by a factor of $1/x^2$, which is small on the line wing.
+These terms are ignored from here onward.
 
@@
 + \vec{n} \cdot \grad \left( J + 3\vec{n} \cdot \vec{H} \right)
-& = & - k\phi \Delta \langle u_\parallel \rangle  \frac{\partial J}{\partial \nu} 
+& = & -3k\phi \vec{n} \cdot \vec{H} - k\phi \Delta \langle u_\parallel \rangle  \frac{\partial J}{\partial \nu} 
 + \frac{1}{2} \Delta^2 k\phi \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10} \right)
@@
 \ee
-where the last equality (see e.g. \citealt{1994ApJ...427..603R}) is valid on the damping wing where $\langle u_\parallel^2 \rangle \simeq 1/2$.
-The following equations will use the approximations for the damping wing.
-
-Thus far the transfer equation is
+%TODO: where the last equality (see e.g. \citealt{1994ApJ...427..603R}) is valid on the damping wing.
+The following equations will use the approximations for the damping wing. Thus far the transfer equation is
 \be
@@
 \nonumber \\ & \simeq & 
-j_{\rm em} - 3k\phi \vec{n} \cdot \vec{H} - \left( p k\phi  + \alpha_{\rm abs} \right) J 
+j_{\rm em} - 3(k\phi + \alpha_{\rm abs}) \vec{n} \cdot \vec{H} - \left( p k\phi  + \alpha_{\rm abs} \right) J 
 + \frac{1}{2} k \Delta^2 \frac{\partial }{\partial \nu} 

### 2021-12-10 ms.tex
previous uncommitted changes

@@
 
-\shorttitle{Resonant Scattering of \lya}
+\shorttitle{Resonant Scattering}
 \shortauthors{McClellan et al.}
@@
 \author[0000-0002-6040-8281]{B. Connor McClellan}
+\address{} %TODO: McCormick address
 \author[0000-0001-7488-4468]{Shane Davis}
@@
 \affiliation{Department of Astronomy, University of Virginia, Charlottesville, VA 22904, USA}
+%TODO: Complete postal address for each author, including zip code
 
 \begin{abstract}
-
+%TODO: 225 words! All done.
 The radiation transfer equation for resonant scattering is solved in spherical geometry.
@@
 Our solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
-Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$.
+Thus, the value of $x$ at which the Doppler and Lorentzian components of the line profile are equal is $x_{\rm cw}=3.3$.
 Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} \approx 10^5$ (``core-peak'' optical depth).
@@
 \subsection{Steady State Source}
-A primary goal of this work is to present a solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near the line-center frequency $\nu_0$ in a uniform sphere.
+A primary goal of this work is to present a solution for resonant scattering near the line-center frequency $\nu_0$ in a uniform sphere.
 We have generalized a spherically symmetric solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center.
@@
 
-We have examined previous solutions to \lya transfer in the limit of large optical depth, noting that the separation of variables and treatment of the boundary condition in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others does not produce a valid solution to the transfer equation.
+We have examined previous solutions to \lya transfer including resonant scattering in the limit of large optical depth, noting that the separation of variables and treatment of the boundary condition in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others does not produce a valid solution to the transfer equation.
 Here, we have derived the solution in spherical geometry with an appropriate treatment of the surface boundary condition, examining the spectral and time dependence of the resulting equations.
@@
 The size of $H_{\rm bc}$ is of order unity when the spectral peaks are near the Doppler core, and diminishes at larger $\tau_0$ following a $(a\tau_0)^{-1/3}$ scaling.
+
 Introducing time-dependence to the transfer equation leads to another solution which is solved numerically with an eigenfunction expansion.
@@
 This treatment is incomplete for emission away from line center ($x_s\neq0$), however, since any terms that would allow asymmetry in the spectrum are not present in the sum.
-The time-dependent solution is utilized to create wait-time distributions for photons escaping the sphere of optically-thick hydrogen gas, which can be sampled in lieu of traditional Monte Carlo simulations that would be computationally demanding.
+The time-dependent solution is utilized to create wait-time distributions for photons escaping the sphere of optically-thick hydrogen gas.
 We compare the calculations from the time-dependent solution with Monte Carlo for a sample of $\tau_0$, noting general agreement in the resulting escape time distributions.
@@
 
-NASA ATP grant 80NSSC18K0696, ``Exoplanetary MHD Outflows Driven by EUV Heating, Lyman alpha Radiation Forces and Stellar Tides".
+This research was funded by NASA ATP grant 80NSSC18K0696, ``Exoplanetary MHD Outflows Driven by EUV Heating, Lyman alpha Radiation Forces and Stellar Tides". % TODO: Add Pleiades computer.
 \restartappendixnumbering
+
+%TODO: Add code acknowledgements.
 
@@
 \ee
-with $\langle u_\parallel \rangle \simeq 1/x$ and $\langle u_\parallel^2 \rangle \simeq 1/2$, and so this identity is satisfied. The redistribution function can then be rewritten
+with $\langle u_\parallel \rangle \simeq 1/x$ and $\langle u_\parallel^2 \rangle \simeq 1/2$, and so this identity is satisfied. The scattering source function can then be rewritten
 \be
@@
 This is because Equation \ref{eq:wkb_J_far} has dropped a term, $Bi(x)$, that is infinite far from line center; yet, in the region $0 < \sigma < \sigma_s$, this term is finite and contributes an asymmetric piece to the solution.
-This term is missing from the Equations \ref{eq:wkb_J} and \ref{eq:wkb_J_far}, meaning any solution produced by a sum over eigenmodes will always be symmetric about the line-center since the eigenfunctions themselves are symmetric even when $\sigma_s \neq 0$.
+This term is not included in the Equations \ref{eq:wkb_J} and \ref{eq:wkb_J_far}, meaning any solution produced by a sum over eigenmodes will always be symmetric about the line-center since the eigenfunctions themselves are symmetric even when $\sigma_s \neq 0$.
 

### 2021-12-13 ms.tex
Rewording the steady-state discussion section, changing ordering of sentences

@@
 \subsection{Steady State Source}
-A primary goal of this work is to present a solution for resonant scattering near the line-center frequency $\nu_0$ in a uniform sphere.
+A primary goal of this work is to present a solution for resonant scattering of photons near the line-center frequency $\nu_0$ in a uniform sphere.
 We have generalized a spherically symmetric solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center.
-We have included a correction to their incorrect $J=0$ surface boundary condition that allows the proper condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere.
-This introduces a term $J_{\rm bc}$ which is solved using a continuous Fourier expansion in frequency.
-The continuous expansions are discretized and the Fourier coefficients solved for.
+We introduce a new term to this solution, $J_{\rm bc}$, which allows the boundary condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere.
+This is solved using a continuous Fourier expansion in frequency.
+The integrals are discretized and the Fourier coefficients solved for numerically.
 The resulting flux correction, $H_{\rm bc}$, scales as $H_0(a\tau_0)^{-1/3}$.
-Thus, for large $\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $\tau_0$.
-Since the Laplacian form of the differential equation is only correct when the line profile is $\phi \approx a/(\pi x^2)$, our solutions do not accurately model the Doppler core of the \lya line.
-Because the peak of the spectral energy distribution of escaping photons is $x_{\rm peak} = (a\tau_0)^{1/3}$, calculations performed at low $\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
-
-By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions provided a sufficiently large $\tau_0$.
-Specifically, this solution shows improvement over previous solutions that utilized the $J=0$ surface boundary condition presented in \cite{1973MNRAS.162...43H} and \cite{1990ApJ...350..216N}.
+Thus, for large $a\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $a\tau_0$.
+Since the Laplacian form of the differential equation is only correct when the line profile is $\phi \approx a/(\pi x^2 \Delta)$, our solutions do not accurately model the Doppler core of the \lya line.
+Because the peak of the spectral energy distribution of escaping photons is $x_{\rm peak} {\sim} (a\tau_0)^{1/3}$, calculations performed at small $a\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
+
+By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions provided a sufficiently large $a\tau_0$.
+Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition presented in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, and \cite{2006ApJ...649...14D}.
 Several papers have previously compared these analytic models to Monte Carlo and seen discrepancies on the order of this correction.
 For example, in the top-left panel of Figure 1 from \cite{2006ApJ...649...14D}, the \lya spectrum emergent from a sphere of uniform optical depth is shown for $\tau_0=10^5, 10^6,$ and $10^7$ at a temperature of $T=10$ K, corresponding to $a=1.5 \times 10^{-2}$.
-The dotted line showing their theoretically-derived spectrum (called $H_0$ here) displays an excess at the peak of at least 5-10 percent as compared with the Monte Carlo for $\tau_0=10^5$ and $10^6$.
-Though our calculations were performed with a higher gas temperature of $T=10^4$ K, we show in Figure \ref{fig:sol_mc_tau} that the excess present in $H_0$ is corrected by our treatment of the boundary condition at $\tau_0 = 10^7$.
-In \citet{2015MNRAS.449.4336S}, the peak excess in the \lya spectrum is particularly noticeable for line center optical depths of $\tau_0=10^6$ and $10^7$ in the top panel of their Figure 5, which used slab geometry and a gas temperature of $T=10^4$ K.
+The dotted line showing their theoretically-derived spectrum ($H_0$) displays an excess at the peak of at least 5-10 percent as compared with the Monte Carlo for $\tau_0=10^5$ and $10^6$.
+Another example is in \citet{2015MNRAS.449.4336S}, where the peak excess in the \lya spectrum is particularly noticeable for line center optical depths of $\tau_0=10^6$ and $10^7$ in the top panel of their Figure 5, which used slab geometry and a gas temperature of $T=10^4$ K.
 Again, the error in their solution is of order 5-10 percent.
-$H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which matches with the discrepancies noted in these solutions.
-They are too large at the spectral peaks and too small further out in the wing, and the error scales approximately as $(a\tau_0)^{-1/3}$.
+Both of these solutions are too large at the spectral peaks and too small further out in the wing, and the error scales approximately as $(a\tau_0)^{-1/3}$.
+We show in our Figure \ref{fig:sol_mc_tau} that the error present in $H_0$ is corrected by our treatment of the boundary condition at $\tau_0 = 10^7$ for T$=10^4$ K, corresponding to $a=4.72 \times 10^{-4}$.
+We note that our corrective term $H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which matches with the discrepancies noted in the aforementioned solutions.
 

### 2021-12-13 ms.tex
changing \cite{} to \citet{} according to manuscript guidelines

@@
 In the comparisons shown in this section, the raw photon data is binned in frequency to obtain spectra.
-Further details of the Monte Carlo implementation are discussed in \cite{2017ApJ...851..150H}.
+Further details of the Monte Carlo implementation are discussed in \citet{2017ApJ...851..150H}.
 
@@
 \ref{eq:app:line_profile_wing}) to break down.
-From this, we conclude that the errors introduced by the incorrect separation of variables in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others are indeed proportional to $(a\tau_0)^{-1/3}$.
+From this, we conclude that the errors introduced by the incorrect separation of variables in \citet{1973MNRAS.162...43H}, \citet{1990ApJ...350..216N}, \citet{2006ApJ...649...14D} and others are indeed proportional to $(a\tau_0)^{-1/3}$.
 
@@
 A primary goal of this work is to present a solution for resonant scattering of photons near the line-center frequency $\nu_0$ in a uniform sphere.
-We have generalized a spherically symmetric solution derived by \cite{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center.
+We have generalized a spherically symmetric solution derived by \citet{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center.
 We introduce a new term to this solution, $J_{\rm bc}$, which allows the boundary condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere.
@@
 By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions provided a sufficiently large $a\tau_0$.
-Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition presented in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, and \cite{2006ApJ...649...14D}.
+Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition presented in \citet{1973MNRAS.162...43H}, \citet{1990ApJ...350..216N}, and \citet{2006ApJ...649...14D}.
 Several papers have previously compared these analytic models to Monte Carlo and seen discrepancies on the order of this correction.
-For example, in the top-left panel of Figure 1 from \cite{2006ApJ...649...14D}, the \lya spectrum emergent from a sphere of uniform optical depth is shown for $\tau_0=10^5, 10^6,$ and $10^7$ at a temperature of $T=10$ K, corresponding to $a=1.5 \times 10^{-2}$.
+For example, in the top-left panel of Figure 1 from \citet{2006ApJ...649...14D}, the \lya spectrum emergent from a sphere of uniform optical depth is shown for $\tau_0=10^5, 10^6,$ and $10^7$ at a temperature of $T=10$ K, corresponding to $a=1.5 \times 10^{-2}$.
 The dotted line showing their theoretically-derived spectrum ($H_0$) displays an excess at the peak of at least 5-10 percent as compared with the Monte Carlo for $\tau_0=10^5$ and $10^6$.
@@
 \subsection{Impulsive Source}
-The time-dependence of the problem is solved for a $J=0$ boundary condition to characterize the distribution of photon escape times.
-Solving the differential equation requires a semi-analytic approach, utilizing an expansion in both space and photon frequency.
-By matching boundary conditions on either side of the photon source frequency $x_s$, the flux at the surface of the sphere is found as a function of $t$ and $\nu$, expressed as a sum over spatial and frequency modes $n$ and $m$, respectively.
+The time-dependent transfer equation is solved in order to characterize the distribution of photon escape times.
+A semi-analytic approach is used, utilizing an expansion in both space and photon frequency.
+This boundary value problem is solved to find the flux at the surface of the sphere as a function of $t$ and $\nu$, enforcing matching conditions on either side of the photon source frequency $x_s$.
+This solution is expressed as a sum over spatial and frequency modes $n$ and $m$, respectively.
 Calculating additional spatial eigenmodes provides a more accurate model of the physics nearer to line center, but convergence is slow due to each eigenmode's weak dependence on $n$.
@@
 This physics is not modeled by our solution for two reasons: 1) our calculations ignored the Gaussian component of the Voigt line profile, leaving the Lorentzian piece which is accurate only in the line wing, and 2) knowing the core is not modeled accurately, we do not include a large enough number of spatial eigenmodes in the sum to resolve it.
-However, an approximate fitting function dependent on parameters $a$ and $\tau_0$ is found that adequately represents the escape time distribution within these constraints.
-
-This leads in to a possible application of this work.
+However, an approximate fitting function dependent on parameters $a$ and $\tau_0$ is found that adequately represents the escape time distribution of the Monte Carlo results within these constraints.
+
+Our characterization of the escape time distribution leads in to a possible application of this work.
 Models of the escape of hydrogen gas in exoplanet atmospheres can be constructed with a treatment of resonant scattering of \lya in spherical geometry.
@@
 Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}; an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.
-A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \cite{1990ApJ...350..216N} solution, but this solution of course does not use the correct frequency-dependent boundary condition at the surface of the sphere.
+A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \citet{1990ApJ...350..216N} solution, but this solution of course does not utilize the frequency-dependent boundary condition at the surface of the sphere.
 Furthermore, to perform a full radiation hydrodynamic simulation with Monte Carlo acceleration, it will be necessary to calculate radiation forces due to \lya transfer on the faces of each grid cell in the simulation.
@@
 
-We have examined previous solutions to \lya transfer including resonant scattering in the limit of large optical depth, noting that the separation of variables and treatment of the boundary condition in \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others does not produce a valid solution to the transfer equation.
-Here, we have derived the solution in spherical geometry with an appropriate treatment of the surface boundary condition, examining the spectral and time dependence of the resulting equations.
+We have examined previous solutions to \lya transfer including resonant scattering in the limit of large optical depth, noting that the separation of variables and treatment of the boundary condition in \citet{1973MNRAS.162...43H}, \citet{1990ApJ...350..216N}, \citet{2006ApJ...649...14D} and others produces a discrepancy in the outgoing spectrum as compared with Monte Carlo.
+Here, we have derived the solution in spherical geometry with an appropriate treatment of the surface boundary condition.
 The key result is that the errors in the previously-cited works have been quantified via a correction term, $H_{\rm bc}$, which resolves an excess in flux at the spectral peak and a deficit in the line wing of the calculated spectrum of \lya radiation as compared with Monte Carlo.
-The size of $H_{\rm bc}$ is of order unity when the spectral peaks are near the Doppler core, and diminishes at larger $\tau_0$ following a $(a\tau_0)^{-1/3}$ scaling.
-
-Introducing time-dependence to the transfer equation leads to another solution which is solved numerically with an eigenfunction expansion.
+The size of $H_{\rm bc}/H_0$ is of order unity when the spectral peaks are near the Doppler core, and diminishes at larger $\tau_0$ following a $(a\tau_0)^{-1/3}$ scaling.
+
+The time-dependent transfer equation is solved numerically with an eigenfunction expansion.
 We demonstrate that it agrees with the steady-state spectrum for $x_s=0$ when integrated over time, though its rate of numerical convergence is slow and requires a sum over many modes to become accurate.
-This treatment is incomplete for emission away from line center ($x_s\neq0$), however, since any terms that would allow asymmetry in the spectrum are not present in the sum.
 The time-dependent solution is utilized to create wait-time distributions for photons escaping the sphere of optically-thick hydrogen gas.
@@
 
-This research was funded by NASA ATP grant 80NSSC18K0696, ``Exoplanetary MHD Outflows Driven by EUV Heating, Lyman alpha Radiation Forces and Stellar Tides". % TODO: Add Pleiades computer.
+This research was funded by NASA ATP grant 80NSSC18K0696, ``Exoplanetary MHD Outflows Driven by EUV Heating, Lyman alpha Radiation Forces and Stellar Tides".
+Resources supporting this work were provided by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center.
 \restartappendixnumbering
 
-%TODO: Add code acknowledgements.
+\software{\texttt{numpy} \citep{2020NumPy-Array}, \texttt{scipy} \citep{2020SciPy-NMeth}}
 

### 2021-12-13 ms.tex
Replacing Eq. with Equation

@@
 \author[0000-0002-6040-8281]{B. Connor McClellan}
-\address{} %TODO: McCormick address
 \author[0000-0001-7488-4468]{Shane Davis}
 \author[0000-0001-5611-1349]{Phil Arras}
-\affiliation{Department of Astronomy, University of Virginia, Charlottesville, VA 22904, USA}
-%TODO: Complete postal address for each author, including zip code
+\address{Department of Astronomy, University of Virginia, Charlottesville, VA 22904, USA}
 
@@
 Appendix \ref{app:rteqn_derivation} contains a derivation of the transfer equation for convenience.
-Starting with the full transfer equation, Eq.
-\ref{eq:finaleqn}, ignoring photon destruction and including a photon emission term given by Eq.
-\ref{eq:jem}, the steady-state transfer equation is
+Starting with the full transfer equation, Equation \ref{eq:finaleqn}, ignoring photon destruction and including a photon emission term given by Equation \ref{eq:jem}, the steady-state transfer equation is
 \be
@@
 \ee
-Eq.
-\ref{eq:H0surf} will be shown to be a better approximation to the solution than Eq.
-\ref{eq:Hd}.
+Equation \ref{eq:H0surf} will be shown to be a better approximation to the solution than Equation \ref{eq:Hd}.
 It is still valid near the delta function at $r=0$, but is also a better approximation at $r=R$.
@@
 \ee
-where $A(s)$ is the Fourier amplitude. Inserting Eq. \ref{eq:Jbc} into Eq. \ref{eq:bc2} leads to the following equation for the Fourier amplitudes,
+where $A(s)$ is the Fourier amplitude. Inserting Equation \ref{eq:Jbc} into Equation \ref{eq:bc2} leads to the following equation for the Fourier amplitudes,
 \be
@@
 \ee
-Discretization of Eq. \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
+Discretization of Equation \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
 leads to a set of coupled linear equations for the $A(s_j)$.
@@
 The number of points was increased until the solution was well-resolved near line center, and only became inaccurate close to the boundaries.
-Given the Fourier amplitudes $A(s)$, $J_{\rm bc}$ is computed using Eq.
-\ref{eq:Jbc}, and the flux is given by
+Given the Fourier amplitudes $A(s)$, $J_{\rm bc}$ is computed using Equation \ref{eq:Jbc}, and the flux is given by
 \be
@@
 In Figure \ref{fig:sol_mc_tau} we show the solutions alongside Monte Carlo for $\tau_0=10^5, 10^6$, and $10^7$.
-From Eq.
-\ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-Indeed, agreement between Eq.
-\ref{eq:H0surf} and the Monte Carlo points in Fig.
+From Equation \ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
+Indeed, agreement between Equation \ref{eq:H0surf} and the Monte Carlo points in Fig.
 \ref{fig:sol_mc_tau} improves as $\tau_0$ increases, with $H_{\rm bc}$ providing a fractionally smaller correction to $H_0$.
@@
     \includegraphics[width=0.8\textwidth]{xinit.pdf}
-    \caption{$P_{\rm bc}(x) = 16\pi^2R^2H_{\rm bc}(R, x)\Delta/L$ (Eq.
-\ref{eq:prob_spectrum} with $H \rightarrow H_{\rm bc}$) vs.
+    \caption{$P_{\rm bc}(x) = 16\pi^2R^2H_{\rm bc}(R, x)\Delta/L$ (Equation \ref{eq:prob_spectrum} with $H \rightarrow H_{\rm bc}$) vs.
 frequency $x$.
@@
 
-Figure \ref{fig:xinit} shows how the correction $P_{\rm bc}(x)$ (Eq.
-\ref{eq:prob_spectrum} with $H \rightarrow H_{\rm bc}$) scales with both $\tau_0$ and $x_s$.
-In this figure, $\sigma_s$ is shifted by integer multiples of $\tau_0$ (Eq.
-\ref{eq:change_of_variables}) such that the source falls near the peak of the spectrum for each $\tau_0$.
+Figure \ref{fig:xinit} shows how the correction $P_{\rm bc}(x)$ (Equation \ref{eq:prob_spectrum} with $H \rightarrow H_{\rm bc}$) scales with both $\tau_0$ and $x_s$.
+In this figure, $\sigma_s$ is shifted by integer multiples of $\tau_0$ (Equation \ref{eq:change_of_variables}) such that the source falls near the peak of the spectrum for each $\tau_0$.
 For clarity, only the $x > 0$ side of the spectrum is shown.
-From Eq.
-\ref{eq:hbc_scaling}, it is expected that the fractional size of $H_{\rm bc}$ relative to $H_0$ should become smaller with larger optical depths following $(a\tau_0)^{-1/3}$.
+From Equation \ref{eq:hbc_scaling}, it is expected that the fractional size of $H_{\rm bc}$ relative to $H_0$ should become smaller with larger optical depths following $(a\tau_0)^{-1/3}$.
 This factor has been scaled out of the figure such that solutions for different $\tau_0$ and the same $\sigma_s$ should show close agreement in scale on the figure's vertical axis if the relation holds.
 Indeed, the scaled solutions converge as $\tau_0$ becomes larger, indicating agreement with the $(a\tau_0)^{-1/3}$ scaling.
-The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ results from $x_{\rm peak}$ becoming close to $x_{\rm cw}$; at lower $\tau_0$, this causes the line profile approximation in the wing (Eq.
-\ref{eq:app:line_profile_wing}) to break down.
+The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ results from $x_{\rm peak}$ becoming close to $x_{\rm cw}$; at lower $\tau_0$, this causes the line profile approximation in the wing (Equation \ref{eq:app:line_profile_wing}) to break down.
 From this, we conclude that the errors introduced by the incorrect separation of variables in \citet{1973MNRAS.162...43H}, \citet{1990ApJ...350..216N}, \citet{2006ApJ...649...14D} and others are indeed proportional to $(a\tau_0)^{-1/3}$.
@@
 The emissivity for an impulsive source with energy E, source position $\vec{x}_s$, and frequency $\nu_s$ is derived in Appendix \ref{app:rteqn_derivation}.
-Considering a photon source at $\vec{x}_s=0$, we have (Eq.
-\ref{eq:jem})
+Considering a photon source at $\vec{x}_s=0$, we have (Equation \ref{eq:jem})
 \be
@@
 \ee
-At large values of $\sigma$ the line profile $\phi$ is small and Eq. \ref{eq:diffusion_plugged_in} becomes
+At large values of $\sigma$ the line profile $\phi$ is small and Equation \ref{eq:diffusion_plugged_in} becomes
 \be \label{eq:diffusion_at_large_sigma}
@@
 \noindent The form of a single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{\rm tp}$, at which point the function becomes evanescent.
-The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Eq.
-\ref{eq:diffusion_plugged_in} and examining the resulting homogeneous differential equation.
+The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Equation \ref{eq:diffusion_plugged_in} and examining the resulting homogeneous differential equation.
 We obtain
@@
 \ee
-where the line profile is approximated as in Eq.
-\ref{eq:app:line_profile_wing}.
+where the line profile is approximated as in Equation \ref{eq:app:line_profile_wing}.
 When the coefficient on the right hand side is positive, exponential growth or decaying evanescent solutions are found.
@@
 \ee
-Thus, to ensure accuracy in each term of Eq.
-\ref{eq:Jrsigmat}, the bounds of $\sigma$ must be set sufficiently far outside of $\sigma_{\rm tp}$ such that the function is small at the edges.
+Thus, to ensure accuracy in each term of Equation \ref{eq:Jrsigmat}, the bounds of $\sigma$ must be set sufficiently far outside of $\sigma_{\rm tp}$ such that the function is small at the edges.
 The scale of an $e$-folding in $J_{nm}(\sigma)$ is $k/(\kappa_n \Delta) = \tau_0 / (\sqrt{\pi} n)$, so a grid of $\sigma$ is chosen that spans a large enough number of $e$-foldings that no oscillatory behavior is present at the boundaries of the domain.
@@
 The thickness of the lines decrease with $n$ in order to clearly show where they are in agreement.
-These numerically-obtained resonant frequencies are compared with the analytic expression in Eq.
-\ref{eq:gamma_nm}.
+These numerically-obtained resonant frequencies are compared with the analytic expression in Equation \ref{eq:gamma_nm}.
 The parameters for the calculation are $\tau_0=10^7$ and $x_s=0.0$.}
@@
 \end{figure}
-The values of the $\gamma_{nm}$ can be described approximately with Eq. \ref{eq:gamma_nm}. Their values depend on $m$, $n$, and other physical parameters according to 
+The values of the $\gamma_{nm}$ can be described approximately with Equation \ref{eq:gamma_nm}. Their values depend on $m$, $n$, and other physical parameters according to 
 \be \label{eq:gamma_nm}
@@
 
-We now calculate the distribution of the times it takes each photon to escape the sphere. This is obtained by integrating Eq. \ref{eq:dEdtdnu} over all frequencies. We find
+We now calculate the distribution of the times it takes each photon to escape the sphere. This is obtained by integrating Equation \ref{eq:dEdtdnu} over all frequencies. We find
 \be
@@
 The late-time distribution is simply an exponential falloff.
-The rate constant of the falloff is the lowest-order eigenfrequency, $\gamma_{11}$, and its scale is determined by the coefficient $P_{11}$ as in Eq.
-\ref{eq:pnmsoln}.
+The rate constant of the falloff is the lowest-order eigenfrequency, $\gamma_{11}$, and its scale is determined by the coefficient $P_{11}$ as in Equation \ref{eq:pnmsoln}.
 Thus, an approximate ``fitting function'' that captures both the peak of the escape time distribution and the exponential falloff is
@@
 
-We now evaluate the time-integrated spectrum of the response to an impulse and compare it with the solution for the $H_0$ steady-state spectrum (Eq.
-\ref{eq:H0surf}).
-Integrating Eq.
-\ref{eq:dEdtdnu} over all times gives a distribution for the emitted frequencies.
+We now evaluate the time-integrated spectrum of the response to an impulse and compare it with the solution for the $H_0$ steady-state spectrum (Equation \ref{eq:H0surf}).
+Integrating Equation \ref{eq:dEdtdnu} over all times gives a distribution for the emitted frequencies.
 Dividing by the energy $E$, we find the probability distribution
@@
 \ee
-Integrating over $\nu$ then gives unity as required by the sum rule in Eq. \ref{eq:sumrule}.
+Integrating over $\nu$ then gives unity as required by the sum rule in Equation \ref{eq:sumrule}.
 
 In Fig.
-\ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq.
-\ref{eq:H0surf}.
+\ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Equation \ref{eq:H0surf}.
 Additional spatial modes contribute to the solutions' accuracy in the core of the line.
@@
 
-In Figure \ref{fig:escape_time} escape time distributions calculated from Eq.
-\ref{eq:waittime} are shown alongside Monte Carlo and the fitting function Eq.
-\ref{eq:fitting_function} for $\tau_0=10^6, 10^7$ with $x_s=0$.
+In Figure \ref{fig:escape_time} escape time distributions calculated from Equation \ref{eq:waittime} are shown alongside Monte Carlo and the fitting function Equation \ref{eq:fitting_function} for $\tau_0=10^6, 10^7$ with $x_s=0$.
 It is seen that the fitting function matches well with the late-time behavior of the eigenfunction solution, indicating that the tail of the escape time distribution can be modeled effectively by simple exponential decay.
@@
     \caption{Wait-time distribution of escaping photons $P(t)$ vs.
-t  for $\tau_0=10^6$ and $10^7$, which is fit using Eq.
-\ref{eq:fitting_function}.
+t  for $\tau_0=10^6$ and $10^7$, which is fit using Equation \ref{eq:fitting_function}.
 A sum over 20 spatial eigenmodes and 500 frequency eigenmodes is labeled ``Eigenfunctions''.
@@
 \ee
-The first term in Eq.
-\ref{eq:jsc}, $k\phi J$, represents re-emission of the photon through de-excitation of the atom.
-It cancels the $-k\phi J$ term in Eq.
-\ref{eq:rteqn} that corresponds to excitation of the atom.
+The first term in Equation \ref{eq:jsc}, $k\phi J$, represents re-emission of the photon through de-excitation of the atom.
+It cancels the $-k\phi J$ term in Equation \ref{eq:rteqn} that corresponds to excitation of the atom.
 The terms involving frequency derivatives of $\vec{H}$, if carried through the calculation, end up giving terms smaller than the largest terms by a factor of $1/x^2$, which is small on the line wing.
@@
 \ee
-Multiplying by a factor $-3k\phi$, as appears in Eq. \ref{eq:finaleqn}, the delta function in $\nu$ becomes a delta function in $\sigma$ of the form
+Multiplying by a factor $-3k\phi$, as appears in Equation \ref{eq:finaleqn}, the delta function in $\nu$ becomes a delta function in $\sigma$ of the form
 \be
@@
 
-In this appendix, we will find a WKB solution for the differential equation Eq.
-\ref{eq:wkb_differential_eqn} subject to the boundary conditions in Equations \ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}.
+In this appendix, we will find a WKB solution for the differential equation Equation \ref{eq:wkb_differential_eqn} subject to the boundary conditions in Equations \ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}.
 We will find this solution for the case $\sigma_s = 0$, assuming $\sigma \geq 0$ for simplicity since the solution is symmetric about $0$.
@@
 \ee
-where $J_\alpha(x)$ are Bessel functions of the first kind, $a_1$ and $a_2$ are normalization constants, $\sigma_{tp}$ is given in Eq.
-\ref{eq:sigma_tp}, and $k_c=3\kappa_n \Delta \sigma_{\rm tp}/2k$.
+where $J_\alpha(x)$ are Bessel functions of the first kind, $a_1$ and $a_2$ are normalization constants, $\sigma_{tp}$ is given in Equation \ref{eq:sigma_tp}, and $k_c=3\kappa_n \Delta \sigma_{\rm tp}/2k$.
 The solution far from line center is
@@
 \ee
-where $Ai(x)$ is the Airy function of the first kind. Again, $a_3$ is a normalization constant. We can enforce the discontinuity in Eq. \ref{eq:matching_condition_2} to find 
+where $Ai(x)$ is the Airy function of the first kind. Again, $a_3$ is a normalization constant. We can enforce the discontinuity in Equation \ref{eq:matching_condition_2} to find 
 \be \label{eq:a2}
@@
 \ee
-The discontinuity sets the value of $a_2$, and the corresponding term in Eq.
-\ref{eq:wkb_J} is non-resonant.
+The discontinuity sets the value of $a_2$, and the corresponding term in Equation \ref{eq:wkb_J} is non-resonant.
 The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$.
@@
 \ee
-By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{\rm tp}$, we find the dispersion relation in Eq.
-\ref{eq:gamma_nm}.
-
-%The eigenfunctions themselves are symmetric
-% ^^^ Put this as the first thing we're saying.
-
-% Summarize the necessary points of the sigmas=0 solution
-
-%
-
-% In this case, we have obtained Equations \ref{eq:a1/a2} and \ref{eq:a3/a2} which approach infinity near the eigenfrequencies $\gamma_{nm}$, so there will be no contribution from the $a_2$ term in Equation \ref{eq:wkb_J} at these resonant frequencies.
-We now seek to understand the behavior of the solution when emission is away from line center ($\sigma_s \neq 0$).
+By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{\rm tp}$, we find the dispersion relation in Equation \ref{eq:gamma_nm}.
 
@@
 
-%The eigenfunction expansion in Equation \ref{eq:Jrsigmat} assumed that a closed contour at infinity, bounding an infinite number of simple poles along the real $\gamma$-axis, could be integrated to find that $J(r, \sigma, t)$ is the sum of the residues of the poles contained within the contour.
-
-% Equation \ref{eq:a2} shows there is an additional contribution unrelated to the eigenfunctions that is non-resonant.
-In the case where $\sigma_s \neq 0$, this non-resonant piece contributes to the asymmetry of the solution about line center.
-When $\sigma_s=0$, however, the solution is symmetric about line center and the non-resonant piece has no contribution except to produce the matching conditions in Equations \ref{eq:a1/a2} and \ref{eq:a3/a2}.
-Since we have applied the WKB approximation only when $\sigma_s = 0$, the non-resonant piece which allows the outgoing spectrum to be asymmetric is not captured by the methods outlined here.
-Thus,
-
 \bibliography{ref.bib}{}

### 2021-12-13 ms.tex
Changing phrasing of "incorrect treatment", etc, to give more specifics about what is wrong

@@
 Thus, the separation ``constant'' is not constant, and the function does not satisfy the Poisson equation since the frequency derivatives will act on the separation ``constant", giving extra terms.
-In the limit of large optical depth $B$, they approximate the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$.
-However, this gives zero mean intensity at the surface.
+In the limit of large optical depth $B$, they approximate the eigenvalues as $\lambda_n B \simeq \pi (n-1/2)$, which gives zero mean intensity at the surface.
 Their Equation 34 subsequently allows $\lambda$ to have a small deviation from the above expression, which is explicitly frequency dependent.
 This allows a nonzero intensity at the surface, but at the cost of rendering the separation of variables assumption invalid.
-Our treatment, using the correct boundary condition, quantifies the errors in their ansatz.
-
-Several other works have followed \citet{1973MNRAS.162...43H}, building upon their result without addressing the incorrect boundary condition.
-\citet{1990ApJ...350..216N} attempts to extend the solution to media of intermediate optical depth, including the effects of scattering in the Doppler core of the line, but again does not use the correct boundary condition.
+Our treatment, using the correct boundary condition, quantifies the errors in this ansatz.
+
+Several other works have followed \citet{1973MNRAS.162...43H}.
+\citet{1990ApJ...350..216N} extends the solution to media of intermediate optical depth, including the effects of scattering in the Doppler core of the line.
 \citet{2006ApJ...649...14D} generalize the same problem to spherical geometry, as is used here.
+Both works, however, use the same surface boundary condition and ansatz as \citet{1973MNRAS.162...43H}.
 
@@
 Here, we have derived the solution in spherical geometry with an appropriate treatment of the surface boundary condition.
-The key result is that the errors in the previously-cited works have been quantified via a correction term, $H_{\rm bc}$, which resolves an excess in flux at the spectral peak and a deficit in the line wing of the calculated spectrum of \lya radiation as compared with Monte Carlo.
+The key result is that the errors in the previously-cited works have been quantified via a correction term, $H_{\rm bc}$, which explains an excess in flux at the spectral peak and a deficit in the line wing of the calculated spectrum of \lya radiation as compared with Monte Carlo.
 The size of $H_{\rm bc}/H_0$ is of order unity when the spectral peaks are near the Doppler core, and diminishes at larger $\tau_0$ following a $(a\tau_0)^{-1/3}$ scaling.
@@
 \ee
-%TODO: where the last equality (see e.g. \citealt{1994ApJ...427..603R}) is valid on the damping wing.
 The following equations will use the approximations for the damping wing. Thus far the transfer equation is

### 2021-12-20 ms.tex
Adding parentheses around equation numbers

@@
 \begin{abstract}
-%TODO: 225 words! All done.
 The radiation transfer equation for resonant scattering is solved in spherical geometry.
@@
 Appendix \ref{app:rteqn_derivation} contains a derivation of the transfer equation for convenience.
-Starting with the full transfer equation, Equation \ref{eq:finaleqn}, ignoring photon destruction and including a photon emission term given by Equation \ref{eq:jem}, the steady-state transfer equation is
+Starting with the full transfer equation, Equation (\ref{eq:finaleqn}), ignoring photon destruction and including a photon emission term given by Equation (\ref{eq:jem}), the steady-state transfer equation is
 \be
@@
 \ee
-where the approximation is applicable on the damping wing. The line profile is then approximately (Equation \ref{eq:app:line_profile_wing})
+where the approximation is applicable on the damping wing. From Equation (\ref{eq:app:line_profile_wing}), the line profile is then approximately 
 \be \label{eq:line_profile_approx}
@@
 \ee
-In Equation \ref{eq:rt_no_destr}, $\sigma_s \equiv \sigma(x_s)$ is the photon frequency of the source.
+In Equation (\ref{eq:rt_no_destr}), $\sigma_s \equiv \sigma(x_s)$ is the photon frequency of the source.
 $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler widths or Hz, respectively.
-Balancing the two terms on the left hand side of Equation \ref{eq:rt_no_destr} gives $\sigma \ {\sim}\ \tau_0$, or $x_{\rm peak}\ {\sim}\ (a\tau_0)^{1/3}$.
+Balancing the two terms on the left hand side of Equation (\ref{eq:rt_no_destr}) gives $\sigma \ {\sim}\ \tau_0$, or $x_{\rm peak}\ {\sim}\ (a\tau_0)^{1/3}$.
 The boundary condition of no incoming intensity at the surface \citep{1986rpa..book.....R} is
@@
 \ee
-These solutions agree with Equations \ref{eq:Jd} and \ref{eq:Hd} when the arguments of the trigonometric and hyperbolic functions are small.
+These solutions agree with Equations (\ref{eq:Jd}) and (\ref{eq:Hd}) when the arguments of the trigonometric and hyperbolic functions are small.
 Again $J_0 \gg H_0$, except near $r=R$, where it goes to zero.
@@
 \ee
-Equation \ref{eq:H0surf} will be shown to be a better approximation to the solution than Equation \ref{eq:Hd}.
+Equation (\ref{eq:H0surf}) will be shown to be a better approximation to the solution than Equation (\ref{eq:Hd}).
 It is still valid near the delta function at $r=0$, but is also a better approximation at $r=R$.
@@
 \ee
-where $A(s)$ is the Fourier amplitude. Inserting Equation \ref{eq:Jbc} into Equation \ref{eq:bc2} leads to the following equation for the Fourier amplitudes,
+where $A(s)$ is the Fourier amplitude. Inserting Equation (\ref{eq:Jbc}) into Equation (\ref{eq:bc2}) leads to the following equation for the Fourier amplitudes,
 \be
@@
 \ee
-Discretization of Equation \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
+Discretization of Equation (\ref{eq:bc3}) for frequency variables $\sigma_i$ and wavenumbers $s_j$
 leads to a set of coupled linear equations for the $A(s_j)$.
@@
 The number of points was increased until the solution was well-resolved near line center, and only became inaccurate close to the boundaries.
-Given the Fourier amplitudes $A(s)$, $J_{\rm bc}$ is computed using Equation \ref{eq:Jbc}, and the flux is given by
+Given the Fourier amplitudes $A(s)$, $J_{\rm bc}$ is computed using Equation (\ref{eq:Jbc}), and the flux is given by
 \be
@@
 We now estimate the scaling of $H_{\rm bc}$ with $\tau_0$.
-In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc} \approx \sqrt{3} H_0$ from Equation \ref{eq:bc2}.
-We  calculate $H_{\rm bc}$ from $J_{\rm bc}$ using Equation \ref{eq:Hbc} as
+In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc} \approx \sqrt{3} H_0$ from Equation (\ref{eq:bc2}).
+We  calculate $H_{\rm bc}$ from $J_{\rm bc}$ using Equation (\ref{eq:Hbc}) as
 \be
@@
 In Figure \ref{fig:sol_mc_tau} we show the solutions alongside Monte Carlo for $\tau_0=10^5, 10^6$, and $10^7$.
-From Equation \ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-Indeed, agreement between Equation \ref{eq:H0surf} and the Monte Carlo points in Fig.
+From Equation (\ref{eq:hbc_scaling}), the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
+Indeed, agreement between Equation (\ref{eq:H0surf}) and the Monte Carlo points in Fig.
 \ref{fig:sol_mc_tau} improves as $\tau_0$ increases, with $H_{\rm bc}$ providing a fractionally smaller correction to $H_0$.
@@
     \includegraphics[width=0.8\textwidth]{xinit.pdf}
-    \caption{$P_{\rm bc}(x) = 16\pi^2R^2H_{\rm bc}(R, x)\Delta/L$ (Equation \ref{eq:prob_spectrum} with $H \rightarrow H_{\rm bc}$) vs.
+    \caption{$P_{\rm bc}(x) = 16\pi^2R^2H_{\rm bc}(R, x)\Delta/L$ (Equation (\ref{eq:prob_spectrum}) with $H \rightarrow H_{\rm bc}$) vs.
 frequency $x$.
@@
 
-Figure \ref{fig:xinit} shows how the correction $P_{\rm bc}(x)$ (Equation \ref{eq:prob_spectrum} with $H \rightarrow H_{\rm bc}$) scales with both $\tau_0$ and $x_s$.
+Figure \ref{fig:xinit} shows how the correction $P_{\rm bc}(x)$, Equation (\ref{eq:prob_spectrum}) with $H \rightarrow H_{\rm bc}$, scales with both $\tau_0$ and $x_s$.
 In this figure, $\sigma_s$ is shifted by integer multiples of $\tau_0$ (Equation \ref{eq:change_of_variables}) such that the source falls near the peak of the spectrum for each $\tau_0$.
 For clarity, only the $x > 0$ side of the spectrum is shown.
-From Equation \ref{eq:hbc_scaling}, it is expected that the fractional size of $H_{\rm bc}$ relative to $H_0$ should become smaller with larger optical depths following $(a\tau_0)^{-1/3}$.
+From Equation (\ref{eq:hbc_scaling}), it is expected that the fractional size of $H_{\rm bc}$ relative to $H_0$ should become smaller with larger optical depths following $(a\tau_0)^{-1/3}$.
 This factor has been scaled out of the figure such that solutions for different $\tau_0$ and the same $\sigma_s$ should show close agreement in scale on the figure's vertical axis if the relation holds.
 Indeed, the scaled solutions converge as $\tau_0$ becomes larger, indicating agreement with the $(a\tau_0)^{-1/3}$ scaling.
-The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ results from $x_{\rm peak}$ becoming close to $x_{\rm cw}$; at lower $\tau_0$, this causes the line profile approximation in the wing (Equation \ref{eq:app:line_profile_wing}) to break down.
+The remaining discrepancy present in the vertical axis for fixed $\sigma_s$ results from $x_{\rm peak}$ becoming close to $x_{\rm cw}$; at lower $\tau_0$, this causes the line profile approximation in the wing, Equation (\ref{eq:app:line_profile_wing}), to break down.
 From this, we conclude that the errors introduced by the incorrect separation of variables in \citet{1973MNRAS.162...43H}, \citet{1990ApJ...350..216N}, \citet{2006ApJ...649...14D} and others are indeed proportional to $(a\tau_0)^{-1/3}$.
@@
 The Fourier coefficient $J(n, \sigma, \omega)$ has units $dE/(dA d\nu)$.
-Using Equation \ref{eq:jnsigmaomega}, we obtain
+Using Equation (\ref{eq:jnsigmaomega}), we obtain
 \be \label{eq:diffusion_plugged_in}
@@
 \ee
-At large values of $\sigma$ the line profile $\phi$ is small and Equation \ref{eq:diffusion_plugged_in} becomes
+At large values of $\sigma$ the line profile $\phi$ is small and Equation (\ref{eq:diffusion_plugged_in}) becomes
 \be \label{eq:diffusion_at_large_sigma}
@@
 If $\sigma_s=0$, just two integrations are performed inward from large $|\sigma|$ to 0.
-Initial values for integration are obtained either by setting $J=1$ and $dJ/d\sigma$ from Equation \ref{eq:single_j_derivative} at large $|\sigma|$ or by matching $J$ and $dJ/d\sigma$ at 0.
+Initial values for integration are obtained either by setting $J=1$ and $dJ/d\sigma$ from Equation (\ref{eq:single_j_derivative}) at large $|\sigma|$ or by matching $J$ and $dJ/d\sigma$ at 0.
 This gives $J$ and $J'$ on either side of $\sigma_s$, where a prime indicates the derivative $\partial/\partial \sigma$.
-By enforcing the matching conditions Eqs.
-\ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}, the eigenfunctions $J(n, \sigma, \omega)$ are obtained over the domain of photon frequencies $\sigma$.
+By enforcing the matching conditions Equations (\ref{eq:matching_condition_1}) and (\ref{eq:matching_condition_2}), the eigenfunctions $J(n, \sigma, \omega)$ are obtained over the domain of photon frequencies $\sigma$.
 Since the solutions are linear in the starting conditions, only two integrations with different starting values are necessary.
@@
 where $C(\gamma, \sigma)$ varies slowly in $\gamma$.
-If the $\omega$-integral in Equation \ref{eq:jrsigmat_expansion} could be closed at infinity and evaluated using the residue theorem, the result would be
+If the $\omega$-integral in Equation (\ref{eq:jrsigmat_expansion}) could be closed at infinity and evaluated using the residue theorem, the result would be
 \be
@@
 To refine the eigenmode solution, we evaluate $f_{j-1}$, $f_j$, and $f_{j+1}$ at the points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$.
-Assuming the form in Equation \ref{eq:jnsigmaomega_approx}, a guess at the correct eigenvalue $\gamma_{nm}$ can be calculated from
+Assuming the form in Equation (\ref{eq:jnsigmaomega_approx}), a guess at the correct eigenvalue $\gamma_{nm}$ can be calculated from
 \be
@@
 \noindent The form of a single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{\rm tp}$, at which point the function becomes evanescent.
-The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Equation \ref{eq:diffusion_plugged_in} and examining the resulting homogeneous differential equation.
+The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Equation (\ref{eq:diffusion_plugged_in}) and examining the resulting homogeneous differential equation.
 We obtain
@@
 \ee
-where the line profile is approximated as in Equation \ref{eq:app:line_profile_wing}.
+where the line profile is approximated as in Equation (\ref{eq:app:line_profile_wing}).
 When the coefficient on the right hand side is positive, exponential growth or decaying evanescent solutions are found.
@@
 \ee
-Thus, to ensure accuracy in each term of Equation \ref{eq:Jrsigmat}, the bounds of $\sigma$ must be set sufficiently far outside of $\sigma_{\rm tp}$ such that the function is small at the edges.
+Thus, to ensure accuracy in each term of Equation (\ref{eq:Jrsigmat}), the bounds of $\sigma$ must be set sufficiently far outside of $\sigma_{\rm tp}$ such that the function is small at the edges.
 The scale of an $e$-folding in $J_{nm}(\sigma)$ is $k/(\kappa_n \Delta) = \tau_0 / (\sqrt{\pi} n)$, so a grid of $\sigma$ is chosen that spans a large enough number of $e$-foldings that no oscillatory behavior is present at the boundaries of the domain.
@@
 The thickness of the lines decrease with $n$ in order to clearly show where they are in agreement.
-These numerically-obtained resonant frequencies are compared with the analytic expression in Equation \ref{eq:gamma_nm}.
+These numerically-obtained resonant frequencies are compared with the analytic expression in Equation (\ref{eq:gamma_nm}).
 The parameters for the calculation are $\tau_0=10^7$ and $x_s=0.0$.}
@@
 \end{figure}
-The values of the $\gamma_{nm}$ can be described approximately with Equation \ref{eq:gamma_nm}. Their values depend on $m$, $n$, and other physical parameters according to 
+The values of the $\gamma_{nm}$ can be described approximately with Equation (\ref{eq:gamma_nm}). Their values depend on $m$, $n$, and other physical parameters according to 
 \be \label{eq:gamma_nm}
@@
 The power law in $m$ is weak, requiring up to $m=500$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
-When sweeping through to find resonances, Equation \ref{eq:gamma_nm} is used to set the scale of the sweep points $\gamma_j$ to ensure no $\gamma_{nm}$ are missed.
+When sweeping through to find resonances, Equation (\ref{eq:gamma_nm}) is used to set the scale of the sweep points $\gamma_j$ to ensure no $\gamma_{nm}$ are missed.
 The continuity and close agreement with the analytic expression shown in Fig.
@@
 
-We now calculate the distribution of the times it takes each photon to escape the sphere. This is obtained by integrating Equation \ref{eq:dEdtdnu} over all frequencies. We find
+We now calculate the distribution of the times it takes each photon to escape the sphere. This is obtained by integrating Equation (\ref{eq:dEdtdnu}) over all frequencies. We find
 \be
@@
 The late-time distribution is simply an exponential falloff.
-The rate constant of the falloff is the lowest-order eigenfrequency, $\gamma_{11}$, and its scale is determined by the coefficient $P_{11}$ as in Equation \ref{eq:pnmsoln}.
+The rate constant of the falloff is the lowest-order eigenfrequency, $\gamma_{11}$, and its scale is determined by the coefficient $P_{11}$ as in Equation (\ref{eq:pnmsoln}).
 Thus, an approximate ``fitting function'' that captures both the peak of the escape time distribution and the exponential falloff is
@@
 We now evaluate the time-integrated spectrum of the response to an impulse and compare it with the solution for the $H_0$ steady-state spectrum (Equation \ref{eq:H0surf}).
-Integrating Equation \ref{eq:dEdtdnu} over all times gives a distribution for the emitted frequencies.
+Integrating Equation (\ref{eq:dEdtdnu}) over all times gives a distribution for the emitted frequencies.
 Dividing by the energy $E$, we find the probability distribution
@@
 \ee
-Integrating over $\nu$ then gives unity as required by the sum rule in Equation \ref{eq:sumrule}.
+Integrating over $\nu$ then gives unity as required by the sum rule in Equation (\ref{eq:sumrule}).
 
 In Fig.
-\ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Equation \ref{eq:H0surf}.
+\ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Equation (\ref{eq:H0surf}).
 Additional spatial modes contribute to the solutions' accuracy in the core of the line.
@@
 
-In Figure \ref{fig:escape_time} escape time distributions calculated from Equation \ref{eq:waittime} are shown alongside Monte Carlo and the fitting function Equation \ref{eq:fitting_function} for $\tau_0=10^6, 10^7$ with $x_s=0$.
+In Figure \ref{fig:escape_time} escape time distributions calculated from Equation (\ref{eq:waittime}) are shown alongside Monte Carlo and the fitting function Equation (\ref{eq:fitting_function}) for $\tau_0=10^6, 10^7$ with $x_s=0$.
 It is seen that the fitting function matches well with the late-time behavior of the eigenfunction solution, indicating that the tail of the escape time distribution can be modeled effectively by simple exponential decay.
@@
     \caption{Wait-time distribution of escaping photons $P(t)$ vs.
-t  for $\tau_0=10^6$ and $10^7$, which is fit using Equation \ref{eq:fitting_function}.
+t  for $\tau_0=10^6$ and $10^7$, which is fit using Equation (\ref{eq:fitting_function}).
 A sum over 20 spatial eigenmodes and 500 frequency eigenmodes is labeled ``Eigenfunctions''.
@@
 \ee
-The first term in Equation \ref{eq:jsc}, $k\phi J$, represents re-emission of the photon through de-excitation of the atom.
-It cancels the $-k\phi J$ term in Equation \ref{eq:rteqn} that corresponds to excitation of the atom.
+The first term in Equation (\ref{eq:jsc}), $k\phi J$, represents re-emission of the photon through de-excitation of the atom.
+It cancels the $-k\phi J$ term in Equation (\ref{eq:rteqn}) that corresponds to excitation of the atom.
 The terms involving frequency derivatives of $\vec{H}$, if carried through the calculation, end up giving terms smaller than the largest terms by a factor of $1/x^2$, which is small on the line wing.
@@
 Integration by parts has been used to factor $J$ out, assuming each term goes to zero at infinity.
-The quantity inside brackets must be constant, and since each term should go to zero at infinity, that constant is zero.
+The quantity inside parentheses must be constant, and since each term should go to zero at infinity, that constant is zero.
 Hence the first and second moments of the frequency shift are related by
@@
 \ee
-Multiplying by a factor $-3k\phi$, as appears in Equation \ref{eq:finaleqn}, the delta function in $\nu$ becomes a delta function in $\sigma$ of the form
+Multiplying by a factor $-3k\phi$, as appears in Equation (\ref{eq:finaleqn}), the delta function in $\nu$ becomes a delta function in $\sigma$ of the form
 \be
@@
 
-In this appendix, we will find a WKB solution for the differential equation Equation \ref{eq:wkb_differential_eqn} subject to the boundary conditions in Equations \ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}.
+In this appendix, we will find a WKB solution for the differential equation Equation (\ref{eq:wkb_differential_eqn}) subject to the boundary conditions in Equations (\ref{eq:matching_condition_1}) and (\ref{eq:matching_condition_2}).
 We will find this solution for the case $\sigma_s = 0$, assuming $\sigma \geq 0$ for simplicity since the solution is symmetric about $0$.
@@
 \ee
-where $J_\alpha(x)$ are Bessel functions of the first kind, $a_1$ and $a_2$ are normalization constants, $\sigma_{tp}$ is given in Equation \ref{eq:sigma_tp}, and $k_c=3\kappa_n \Delta \sigma_{\rm tp}/2k$.
+where $J_\alpha(x)$ are Bessel functions of the first kind, $a_1$ and $a_2$ are normalization constants, $\sigma_{tp}$ is given in Equation (\ref{eq:sigma_tp}), and $k_c=3\kappa_n \Delta \sigma_{\rm tp}/2k$.
 The solution far from line center is
@@
 \ee
-where $Ai(x)$ is the Airy function of the first kind. Again, $a_3$ is a normalization constant. We can enforce the discontinuity in Equation \ref{eq:matching_condition_2} to find 
+where $Ai(x)$ is the Airy function of the first kind. Again, $a_3$ is a normalization constant. We can enforce the discontinuity in Equation (\ref{eq:matching_condition_2}) to find 
 \be \label{eq:a2}
@@
 \ee
-The discontinuity sets the value of $a_2$, and the corresponding term in Equation \ref{eq:wkb_J} is non-resonant.
+The discontinuity sets the value of $a_2$, and the corresponding term in Equation (\ref{eq:wkb_J}) is non-resonant.
 The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$.
@@
 \ee
-By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{\rm tp}$, we find the dispersion relation in Equation \ref{eq:gamma_nm}.
+By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{\rm tp}$, we find the dispersion relation in Equation (\ref{eq:gamma_nm}).
 
@@
 We have found that even in this case of emission away from the line center, the eigenfunctions are symmetric about the line center.
-This is because Equation \ref{eq:wkb_J_far} has dropped a term, $Bi(x)$, that is infinite far from line center; yet, in the region $0 < \sigma < \sigma_s$, this term is finite and contributes an asymmetric piece to the solution.
-This term is not included in the Equations \ref{eq:wkb_J} and \ref{eq:wkb_J_far}, meaning any solution produced by a sum over eigenmodes will always be symmetric about the line-center since the eigenfunctions themselves are symmetric even when $\sigma_s \neq 0$.
+This is because Equation (\ref{eq:wkb_J_far}) has dropped a term, $Bi(x)$, that is infinite far from line center; yet, in the region $0 < \sigma < \sigma_s$, this term is finite and contributes an asymmetric piece to the solution.
+This term is not included in the Equations (\ref{eq:wkb_J}) and (\ref{eq:wkb_J_far}), meaning any solution produced by a sum over eigenmodes will always be symmetric about the line-center since the eigenfunctions themselves are symmetric even when $\sigma_s \neq 0$.
 

### 2021-12-20 ms.tex
Finishing Shane's edits

@@
 \ee
-This is normalized as $\int P(x)dx = 1$. Since $H(R, x)$ is per $d\nu$, a factor of $\Delta$ gives the expression the correct units.
+This is normalized so that $\int P(x)dx = 1$. Since $H(R, x)$ is per $d\nu$, a factor of $\Delta$ gives the expression the correct units.
 
@@
 The remaining disagreement between the tail of the distribution and the Monte Carlo data is due to line core scattering which is not modeled by the eigenfunction solution, but improves for larger optical depth as seen in the figure.
-Many scatterings in the Doppler core affects the tail of the escape-time distribution, since photons with frequencies near line center will take longer to escape.
+A large number of scatterings in the Doppler core affects the tail of the escape-time distribution, since photons with frequencies near line center will take longer to escape.
 Thus, the rate constant for the exponential falloff is overestimated slightly in the eigenfunction solution as compared with the Monte Carlo.
@@
 \be
-\langle \delta \nu^n \rangle & = & \frac{ \int d\nu^\prime R (\nu^\prime-\nu)^n}{\int d\nu^\prime R}
+\langle \delta \nu^n \rangle & = & \frac{ \int d\nu^\prime (\nu^\prime-\nu)^n R}{\int d\nu^\prime R}
 = \frac{1}{\phi(\nu)}

### 2021-12-20 ms.tex
Using "steady-state" as an adjective and "steady state" as a noun

@@
 In Fig.
-\ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Equation (\ref{eq:H0surf}).
+\ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Equation (\ref{eq:H0surf}).
 Additional spatial modes contribute to the solutions' accuracy in the core of the line.
-If more spatial modes are calculated, the agreement with the steady state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x=x_s=0$.
+If more spatial modes are calculated, the agreement with the steady-state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x=x_s=0$.
 If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over eigenmodes which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
@@
 
-\subsection{Steady State Source}
+\subsection{Steady-State Source}
 A primary goal of this work is to present a solution for resonant scattering of photons near the line-center frequency $\nu_0$ in a uniform sphere.

### 2021-12-20 ms.tex
Removing figures subdirectory to satisfy same-level zip archive requirement
A few small changes

@@
 
-\graphicspath{{./}{figures/}}
+\graphicspath{./}
 
@@
 For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with  mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct boundary condition of zero-ingoing intensity at the surface.
-This solution is compared to that of the Monte-Carlo method, which is valid at arbitrary optical depth.
+This solution is compared to that of the Monte Carlo method, which is valid at arbitrary optical depth.
 It is shown that the size of the correction is order unity when the spectral peaks approach the Doppler core and decreases slowly with line center optical depth, which may explain discrepancies in previous studies.
@@
 We will consider only the case where $\vec{x}_s=0$.
-Following \citet{1973MNRAS.162...43H}, we have used a change of variables from $x$ to $\sigma$,
+Following \citet{1973MNRAS.162...43H}, we have used a change of variables in photon frequency from $x$ to $\sigma$,
 \be \label{eq:int_change_of_variables}
@@
 $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler widths or Hz, respectively.
-Balancing the two terms on the left hand side of Equation (\ref{eq:rt_no_destr}) gives $\sigma \ {\sim}\ \tau_0$, or $x_{\rm peak}\ {\sim}\ (a\tau_0)^{1/3}$.
+Balancing the two terms on the left-hand side of Equation (\ref{eq:rt_no_destr}) gives $\sigma \ {\sim}\ \tau_0$, or $x_{\rm peak}\ {\sim}\ (a\tau_0)^{1/3}$.
 The boundary condition of no incoming intensity at the surface \citep{1986rpa..book.....R} is

### 2021-12-21 ms.tex
Phil's edits from final read-through

@@
 \citet{1973MNRAS.162...43H} showed that when most of the radiation is out on the damping wings, the transfer equation reduces to the Poisson equation.
-However, their solution contains an incorrect treatment of the boundary condition.
+However, their solution uses an ansatz to handle the boundary condition.
 To our knowledge, the errors introduced by this treatment have never been quantified.
@@
 
-Consider a sphere of radius $R$ with uniform density $n_{\rm sc}$, luminosity $L$, and line-center optical depth $\tau_0$ containing a point source of photons.
+Consider a sphere of radius $R$ with uniform density $n_{\rm sc}$, luminosity $L$, and line-center optical depth $\tau_0$, containing a point source of photons.
 We aim to find the intensity within the sphere as a function of radius and photon frequency.
@@
 The Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light.
-The photon frequency in Doppler widths is $x = (\nu-\nu_0)/\Delta$, and $x_s = (\nu_s - \nu_0)/\Delta$ is the corresponding source frequency.
+The photon frequency in Doppler units is $x = (\nu-\nu_0)/\Delta$, and $x_s = (\nu_s - \nu_0)/\Delta$ is the corresponding source frequency.
 For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$.
@@
 However, it is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$ and does not adhere to the correct boundary condition.
-This solution is included in Fig.
-\ref{fig:sol_mc_residual_0} for illustration.
+This solution is included in Figure \ref{fig:sol_mc_residual_0} for illustration.
 
@@
 It is still valid near the delta function at $r=0$, but is also a better approximation at $r=R$.
-$J_0$ decreases exponentially rather than as a power-law in frequency as it does for $J_d$, giving a much smaller flux on the line wings as compared to the divergent solution.
+$J_0$ decreases exponentially, rather than as a power-law in frequency as it does for $J_d$, giving a much smaller flux on the line wings as compared to the divergent solution.
 
@@
 We use equally-spaced points $\delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\delta s = 2\pi/(N\delta \sigma)$, where $N$ is the number of points for each grid.
-The result is a linear system to solve for the $A(s)$.
 The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries.
@@
 In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc} \approx \sqrt{3} H_0$ from Equation (\ref{eq:bc2}).
-We  calculate $H_{\rm bc}$ from $J_{\rm bc}$ using Equation (\ref{eq:Hbc}) as
+We  estimate $H_{\rm bc}$ from $J_{\rm bc}$ using Equation (\ref{eq:Hbc}) as
 \be
@@
 Our solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
-Thus, the value of $x$ at which the Doppler and Lorentzian components of the line profile are equal is $x_{\rm cw}=3.3$.
+The value of $x$ at which the Doppler and Lorentzian components of the line profile are equal is $x_{\rm cw}=3.3$.
 Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} \approx 10^5$ (``core-peak'' optical depth).
@@
     \caption{Spectrum $P(x)$ vs.
-frequency $x$.
-The analytic solutions for the outgoing spectrum are calculated at a line center optical depth of $\tau_0 = 1 \times 10^7$ with $x_s = 0.0$.
+frequency $x$ for $\tau_0 = 1 \times 10^7$ with $x_s = 0.0$.
+The legend to the right describes each line style.
 The top panel is linear scale, the middle panel is log scale with $|\rm H_{bc}|$ shown instead of $\rm H_{bc}$, and the bottom panel is the residual of each solution with Monte Carlo.}
@@
 The Monte Carlo method is used to solve the transfer equation numerically in order to compare the analytic approximation to an ``exact'' solution.
-This method is valid at all $\tau_0$, being restricted only by its computational demand which grows proportionally to the number of photons used and $\tau_0$.
+This method is valid at all $\tau_0$, being restricted only by the computational demand, which grows proportionally to the number of photons used and $\tau_0$.
 For each simulation, a total of ${\sim}10^6$ photon packets are initialized at a monochromatic source frequency $x_s$ and are allowed to propagate through the sphere until escaping, at which point their positions, outgoing angles, and escape frequencies are tabulated to obtain the spectrum at the surface of the spherical simulation domain.
 A constant temperature of $T=10^4\ \rm K$ is set for the gas.
-Frequency redistribution is calculated at each scattering, including the effects of recoil.
+Frequency redistribution is calculated at each scattering.
 In the comparisons shown in this section, the raw photon data is binned in frequency to obtain spectra.
@@
 
-In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown along with that of the solutions $H_{\rm d}$, $H_0$, and $H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
+In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo spectrum is shown along with that of the solutions $H_{\rm d}$, $H_0$, and $H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
 The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to $H_0$, it corrects for the apparent excess of flux in the peaks of the spectrum.
@@
     \includegraphics[width=\textwidth]{tau_threepanel.pdf}
-    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\tau_0 = 10^5, 10^6, 10^7$.
-The $x$ and $y$ axes are scaled by $(a\tau_0)^{1/3}$.
-Photons are initialized with $\rm x_s = 0.0$ in each case.}
+    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\tau_0 = 10^5$ (top panel), $10^6$ (middle panel), and $10^7$ (bottom panel).
+The $x$ and $y$ axes are scaled by $(a\tau_0)^{1/3}$.}
     \label{fig:sol_mc_tau}
@@
 
-In Figure \ref{fig:sol_mc_tau} we show the solutions alongside Monte Carlo for $\tau_0=10^5, 10^6$, and $10^7$.
+In Figure \ref{fig:sol_mc_tau} we show the solutions alongside Monte Carlo, now for three different optical depths $\tau_0=10^5, 10^6$, and $10^7$.
 From Equation (\ref{eq:hbc_scaling}), the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling.
-Indeed, agreement between Equation (\ref{eq:H0surf}) and the Monte Carlo points in Fig.
-\ref{fig:sol_mc_tau} improves as $\tau_0$ increases, with $H_{\rm bc}$ providing a fractionally smaller correction to $H_0$.
+Indeed, agreement between Equation (\ref{eq:H0surf}) and the Monte Carlo points in Figure \ref{fig:sol_mc_tau} improves as $\tau_0$ increases, with $H_{\rm bc}$ providing a fractionally smaller correction to $H_0$.
 One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis such that the peaks of the distributions are horizontally aligned.
@@
     \includegraphics[width=\textwidth]{xinit_threepanel.pdf}
-    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\rm x_s = 0.0, 6.0, 12.0$. The optical depth at each of these source frequencies is $\tau_s = 10^7, 77,$ and $19$, respectively.} 
+    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\rm x_s = 0.0$ (top panel), $6.0$ (middle panel), and $12.0$ (bottom panel).
+The optical depth at each of these source frequencies is $\tau_s = 10^7, 77,$ and $19$, respectively.}
     \label{fig:sol_mc_xinit}
@@
     \includegraphics[width=\textwidth]{xinit_threepanel_tau1e6.pdf}
-    \caption{The same as Fig.
-\ref{fig:sol_mc_xinit}, but at a lower optical depth $\tau_0 = 10^6$.
+    \caption{The same as Figure \ref{fig:sol_mc_xinit}, but at a lower optical depth $\tau_0 = 10^6$.
 The shift $x_s$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the asymmetry in the spectrum is much larger.
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{xinit.pdf}
+    \includegraphics[width=0.9\textwidth]{xinit.pdf}
     \caption{$P_{\rm bc}(x) = 16\pi^2R^2H_{\rm bc}(R, x)\Delta/L$ (Equation (\ref{eq:prob_spectrum}) with $H \rightarrow H_{\rm bc}$) vs.
@@
 \frac{dj_0(\kappa_n r)}{dr} \bigg\rvert_R & =& \frac{d}{dr} \left[ \frac{\sin(\kappa_n r)}{\kappa_n r} \right]\bigg\rvert_R
-=  \left( \frac{\cos(\kappa_n R)}{R} - \frac{\sin(\kappa_n R)}{\kappa_n R^2} \right)
-\nonumber \\ & = & \frac{(-1)^n}{R}
+=  \left( \frac{\cos(\kappa_n R)}{R} - \frac{\sin(\kappa_n R)}{\kappa_n R^2} \right)  =  \frac{(-1)^n}{R}
 \ee
@@
 
-The eigenfunction's oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity.
+The eigenfunction's oscillatory forms have varying amplitudes which sum in Equation (\ref{eq:Jrsigmat}) to create the final form of the mean intensity.
 The largest contribution at late times always comes from the ($n=1, m=1$) lowest-order eigenfunction.
-Fig.
-\ref{fig:jsoln} shows a set of eigenfunctions $J_{nm}(\sigma)$ to illustrate their relative scales for different $m$ at a fixed spatial eigenmode $n$.
+Figure \ref{fig:jsoln} shows a set of eigenfunctions $J_{nm}(\sigma)$ to illustrate their relative scales for different $m$ at a fixed spatial eigenmode $n$.
 The overall scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$ with $E$ arbitrarily set to 1.
 For H atoms with $T=10^4$ K and $\tau_0=10^7$, an eigenfunction has typical size ${\sim} E a / \left(R^2 \Delta \right) = 10^{-37}$ in units of specific mean intensity times time.
-Additional terms add smaller-magnitude, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
-The oscillations of various modes must cancel, so many modes $m$ and $n$ are required for convergence to the correct solution.
+Additional terms add smaller-magnitude, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms in Equation (\ref{eq:Jrsigmat}).
+The oscillations of various modes must cancel in the Fourier sum, so many modes $m$ and $n$ are required for convergence to the solution.
 \begin{figure}
     \centering
-    \includegraphics[width=0.8\textwidth]{gamma_nm.pdf}
+    \includegraphics[width=0.9\textwidth]{gamma_nm.pdf}
     \caption{Decay rate vs.
@@
 The thickness of the lines decrease with $n$ in order to clearly show where they are in agreement.
-These numerically-obtained resonant frequencies are compared with the analytic expression in Equation (\ref{eq:gamma_nm}).
-The parameters for the calculation are $\tau_0=10^7$ and $x_s=0.0$.}
+These numerically-obtained resonant frequencies are compared with the analytic expression in Equation (\ref{eq:gamma_nm}), shown as a dashed line.
+The parameters for the calculation are $\tau_0=10^7$ and $x_s=0.0$.
+The value of $n$ is given by the color bar on the right-hand side.}
     \label{fig:gamma_nm}
@@
 as shown in Appendix \ref{app:wkb}.
-The power law in $m$ is weak, requiring up to $m=500$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
+The power law in $m$ is weak, requiring up to $m=1000$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
 When sweeping through to find resonances, Equation (\ref{eq:gamma_nm}) is used to set the scale of the sweep points $\gamma_j$ to ensure no $\gamma_{nm}$ are missed.
-The continuity and close agreement with the analytic expression shown in Fig.
-\ref{fig:gamma_nm} indicate that the numerical solutions are accurate.
+The continuity and close agreement with the analytic expression shown in Figure \ref{fig:gamma_nm} indicate that the numerical solutions are accurate.
 
@@
 
-We now calculate the distribution of the times it takes each photon to escape the sphere. This is obtained by integrating Equation (\ref{eq:dEdtdnu}) over all frequencies. We find
+We now calculate the wait time distribution for escape from the sphere. This is obtained by integrating Equation (\ref{eq:dEdtdnu}) over all frequencies. We find
 \be
@@
 
-In Fig.
-\ref{fig:tau_scaling}, it is shown that the time constant of exponential decay in fitted Monte Carlo escape time distributions converges with $\gamma_{11}^{-1}$ at sufficiently high $\tau_0$, following a $t\propto(a\tau_0)^{1/3}$ scaling.
+In Figure \ref{fig:tau_scaling}, the late-time decay timescale of the wait time distribution is shown as a function of $\tau_0$.
+It is shown that the time constant of exponential decay in fitted Monte Carlo escape time distributions converges with $\gamma_{11}^{-1}$ at sufficiently high $\tau_0$, following a $t\propto(a\tau_0)^{1/3}$ scaling.
 At lower $\tau_0$, the effects of line core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
@@
     \includegraphics[width=0.75\textwidth]{tau_scaling.pdf}
-    \caption{Late-time decay timescale as a function of $\tau_0$.
-$\gamma_{11}^{-1}$ and a fit of the exponential falloff for the Monte Carlo escape time distribution are shown to converge to a $t \propto (a\tau_0)^{1/3}$ scaling at large $\tau_0$.
+    \caption{Late-time exponential decay timescale as a function of $\tau_0$.
 The Monte Carlo points on this figure are obtained by fitting only the exponential piece of the escape time distribution to obtain the rate constant.}
@@
 
-We now evaluate the time-integrated spectrum of the response to an impulse and compare it with the solution for the $H_0$ steady-state spectrum (Equation \ref{eq:H0surf}).
-Integrating Equation (\ref{eq:dEdtdnu}) over all times gives a distribution for the emitted frequencies.
-Dividing by the energy $E$, we find the probability distribution
+We now evaluate the time-integrated spectrum (fluence) of the response to an impulse and compare it with the solution for the $H_0$ steady-state spectrum (Equation \ref{eq:H0surf}).
+Integrating Equation (\ref{eq:dEdtdnu}) over all times and dividing by the energy $E$, we find the fluence
 \be \label{eq:spectrum}
-P(\nu) & = &  \frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^{n+1} \gamma_{nm}^{-1} J_{nm}(\sigma).
+P(x) & = &  \frac{16\pi^2 R \Delta}{3k\phi E}  \sum_{nm} (-1)^{n+1} \gamma_{nm}^{-1} J_{nm}(\sigma).
 \ee
@@
 
-In Fig.
-\ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Equation (\ref{eq:H0surf}).
-Additional spatial modes contribute to the solutions' accuracy in the core of the line.
-If more spatial modes are calculated, the agreement with the steady-state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x=x_s=0$.
-If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over eigenmodes which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
+In Figure \ref{fig:steadystate}, the fluence for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated''), and is compared with two analytic solutions: the steady-state $H_0$ solution (Equation \ref{eq:H0surf}) with no time dependence (labelled ``Steady State''), and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in the first line of Equation (\ref{eq:H0surf}).
+Additional spatial modes $n$ increase the solutions' accuracy in the core of the line.
+If more spatial modes are included, the agreement with the steady-state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x=x_s=0$.
+If additional frequency modes are included, faster-oscillating terms are incorporated into the Fourier sum over eigenmodes which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
 Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would primarily affect the distribution at late times due to the large mean diffusion time of photons near the line core.
@@
     \includegraphics{steadystate.pdf}
-    \caption{Time-integrated spectrum $P(x)$ vs. $x$. The steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ are shown with $x_s=0$ and $\tau_0=10^7$.}
+    \caption{Fluence $P(x)$ vs. $x$. The steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ are shown with $x_s=0$ and $\tau_0=10^7$.}
     \label{fig:steadystate}
@@
 
-In Figure \ref{fig:escape_time} escape time distributions calculated from Equation (\ref{eq:waittime}) are shown alongside Monte Carlo and the fitting function Equation (\ref{eq:fitting_function}) for $\tau_0=10^6, 10^7$ with $x_s=0$.
-It is seen that the fitting function matches well with the late-time behavior of the eigenfunction solution, indicating that the tail of the escape time distribution can be modeled effectively by simple exponential decay.
-The remaining disagreement between the tail of the distribution and the Monte Carlo data is due to line core scattering which is not modeled by the eigenfunction solution, but improves for larger optical depth as seen in the figure.
+In Figure \ref{fig:escape_time}, the escape time distributions calculated from Equation (\ref{eq:waittime}) are shown alongside Monte Carlo and the fitting function Equation (\ref{eq:fitting_function}) for $\tau_0=10^6, 10^7$ with $x_s=0$.
+The disagreement between the tail of the distribution and the Monte Carlo data is due to line core scattering which is not modeled by the eigenfunction solution, but improves for larger optical depth as seen in the figure.
 A large number of scatterings in the Doppler core affects the tail of the escape-time distribution, since photons with frequencies near line center will take longer to escape.
@@
     \caption{Wait-time distribution of escaping photons $P(t)$ vs.
-t  for $\tau_0=10^6$ and $10^7$, which is fit using Equation (\ref{eq:fitting_function}).
+t  for $\tau_0=10^6$ and $10^7$, including the fitting function from Equation (\ref{eq:fitting_function}).
 A sum over 20 spatial eigenmodes and 500 frequency eigenmodes is labeled ``Eigenfunctions''.
@@
 
-By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions provided a sufficiently large $a\tau_0$.
+By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions for $a\tau_0 \geq 1$.
 Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition presented in \citet{1973MNRAS.162...43H}, \citet{1990ApJ...350..216N}, and \citet{2006ApJ...649...14D}.
@@
 The time-dependent transfer equation is solved in order to characterize the distribution of photon escape times.
-A semi-analytic approach is used, utilizing an expansion in both space and photon frequency.
-This boundary value problem is solved to find the flux at the surface of the sphere as a function of $t$ and $\nu$, enforcing matching conditions on either side of the photon source frequency $x_s$.
+A semi-analytic approach is used, utilizing an expansion in space, time, and photon frequency.
+This boundary value problem in frequency $\sigma$ is solved to find the flux at the surface of the sphere as a function of $t$ and $\nu$.
 This solution is expressed as a sum over spatial and frequency modes $n$ and $m$, respectively.
-Calculating additional spatial eigenmodes provides a more accurate model of the physics nearer to line center, but convergence is slow due to each eigenmode's weak dependence on $n$.
-Additional frequency eigenmodes introduce fast-oscillating terms that improve the accuracy of the sum, as their contributions cancel with components of lower-order terms to better represent the true solution.
-Integrating the solution over time produces a spectrum that is shown to broadly agree with the steady-state calculations in Section \ref{sec:steadystate}, provided a sufficient number of terms in the sum and emission at the line-center frequency $\nu_0$.
-Integrating the solution over frequency leads to a distribution of photon escape times, which can be compared directly with Monte Carlo simulations.
+Calculating additional spatial eigenmodes increases the accuracy nearer to line center, but convergence is slow due to each eigenmode's weak dependence on $n$.
+Additional frequency eigenmodes introduce fast-oscillating terms that improve the accuracy of the Fourier sum, as their contributions cancel with components of lower-order terms to better represent the true solution.
+Integrating the solution over time produces a fluence that is shown to broadly agree with the steady-state calculations in Section \ref{sec:steadystate}, provided a sufficient number of terms in the sum and emission at the line-center frequency $\nu_0$.
+Integrating the solution over frequency leads to a distribution of photon escape time, which can be compared directly with Monte Carlo simulations.
 The sum over eigenmodes produces an escape-time distribution that broadly captures the behavior shown by Monte Carlo data---a rise at early times, transitioning to exponential decay in the tail of the distribution.
@@
 
-Our characterization of the escape time distribution leads in to a possible application of this work.
+Our characterization of the escape time distribution leads to a possible application of this work.
 Models of the escape of hydrogen gas in exoplanet atmospheres can be constructed with a treatment of resonant scattering of \lya in spherical geometry.
 The Monte Carlo method can be used for this problem, but is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
-We seek to develop a computationally efficient random walk model which requires a solution in spherical geometry.
-There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}, but these methods are not sufficient for our application since they do not track the amount of time photons spend in the line core.
-Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}; an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.
+We seek to develop a method to accelerate the radiative transfer calculation.
+
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}, but these methods are not sufficient for our application since they do not track the amount of time photons spend in the line core, which is needed to tabulate the intensity.
+Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}.
+In this approach, an outgoing photon is randomly sampled on the surface of the outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions, and escape times, based on solutions to the diffusion equation.
 A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \citet{1990ApJ...350..216N} solution, but this solution of course does not utilize the frequency-dependent boundary condition at the surface of the sphere.
@@
 For this work, it would be necessary to model line center optical depths of up to 1 million or more.
-We will utilize the solution derived here as the basis for our own novel implementation of the modified random walk method.
 
@@
 
-The time-dependent transfer equation is solved numerically with an eigenfunction expansion.
+The time-dependent transfer equation for the impulsive source is solved numerically with an eigenfunction expansion.
 We demonstrate that it agrees with the steady-state spectrum for $x_s=0$ when integrated over time, though its rate of numerical convergence is slow and requires a sum over many modes to become accurate.
@@
 We compare the calculations from the time-dependent solution with Monte Carlo for a sample of $\tau_0$, noting general agreement in the resulting escape time distributions.
-In future work, this will be used to accelerate Monte Carlo \lya transfer at large optical depths with potential applications in radiation hydrodynamic simulations of the atmospheres of exoplanets.
+The solution derived in our work here may be used as the basis for a novel implementation of the modified random walk method, which would accelerate Monte Carlo \lya transfer at large optical depths with potential applications in radiation hydrodynamic simulations of the atmospheres of exoplanets.
 
@@
 
-Near the line center, this has two independent solutions which can be written
+Near the line center, there are two independent solutions which can be written
 \be \label{eq:wkb_J}
@@
 \ee
-By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{\rm tp}$, we find the dispersion relation in Equation (\ref{eq:gamma_nm}).
+By setting the to denominator of this expression equal to zero and solving for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{\rm tp}$, we find the dispersion relation in Equation (\ref{eq:gamma_nm}).
 
 While the solution above is specific to the case $\sigma_s = 0$, we can extend this approach to understand the case where $\sigma_s \neq 0$.
-We have found that even in this case of emission away from the line center, the eigenfunctions are symmetric about the line center.
+In the interval $\sigma \in (0, \sigma_s)$, both the $Ai$ and $Bi$ Airy function solutions must be included, while for $\sigma \in (-\infty, 0)$ only $Ai$ is finite.
+The $Bi$ term causes the asymmetry.
+As $\gamma \rightarrow \gamma_{nm}$, however, it is small compared to the $Ai$ term, and hence the eigenfunctions are symmetric.
+
+%have found that even in this case of emission away from the line center, the eigenfunctions are symmetric about the line center.
 This is because Equation (\ref{eq:wkb_J_far}) has dropped a term, $Bi(x)$, that is infinite far from line center; yet, in the region $0 < \sigma < \sigma_s$, this term is finite and contributes an asymmetric piece to the solution.

### 2022-03-15 ms.tex
Syncing checkpoint before starting work on reviewer comments

@@
 At large $\tau_0$, it is expected that the correction term will be small, but it will become increasingly important as $\tau_0$ decreases.
-Our solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$.
+Our solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, i.e., for large $\tau_0$.
 The value of $x$ at which the Doppler and Lorentzian components of the line profile are equal is $x_{\rm cw}=3.3$.
@@
     \includegraphics[width=\textwidth]{xinit_threepanel.pdf}
-    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\rm x_s = 0.0$ (top panel), $6.0$ (middle panel), and $12.0$ (bottom panel).
+    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\tau_0=10^7$ and $\rm x_s = 0.0$ (top panel), $6.0$ (middle panel), and $12.0$ (bottom panel).
 The optical depth at each of these source frequencies is $\tau_s = 10^7, 77,$ and $19$, respectively.}
@@
 If additional frequency modes are included, faster-oscillating terms are incorporated into the Fourier sum over eigenmodes which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
-Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would primarily affect the distribution at late times due to the large mean diffusion time of photons near the line core.
+Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would primarily affect the distribution at early times since the late time distribution is determined by the lowest order modes.
 This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated.
@@
 Our characterization of the escape time distribution leads to a possible application of this work.
-Models of the escape of hydrogen gas in exoplanet atmospheres can be constructed with a treatment of resonant scattering of \lya in spherical geometry.
+Models of the interaction of stellar \lya with the upper atmosphere of exoplanets and the associated transmission spectrum can be constructed with a treatment of resonant scattering in spherical geometry \citep{2017ApJ...851..150H}.
 The Monte Carlo method can be used for this problem, but is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
@@
 
-%have found that even in this case of emission away from the line center, the eigenfunctions are symmetric about the line center.
-This is because Equation (\ref{eq:wkb_J_far}) has dropped a term, $Bi(x)$, that is infinite far from line center; yet, in the region $0 < \sigma < \sigma_s$, this term is finite and contributes an asymmetric piece to the solution.
-This term is not included in the Equations (\ref{eq:wkb_J}) and (\ref{eq:wkb_J_far}), meaning any solution produced by a sum over eigenmodes will always be symmetric about the line-center since the eigenfunctions themselves are symmetric even when $\sigma_s \neq 0$.
-
 \bibliography{ref.bib}{}

### 2022-03-15 ms.tex
Initial changes to address comments in the abstract and introduction

@@
 
+\newcommand{\todo}{\textbf{TODO: }}
+
 \received{}
@@
 \begin{abstract}
-The radiation transfer equation for resonant scattering is solved in spherical geometry.
+%ORIGINAL: 
+%The radiation transfer equation for resonant scattering is solved in spherical geometry.
 A monochromatic source of photons is assumed at the center of a uniform sphere of constant gas density.
@@
 
+\textbf{We present two novel additions to the semi-analytic solution of Lyman $\alpha$ (Ly$\alpha$) radiative transfer in spherical geometry: (1) a correction to the boundary conditions for a steady source, and (2) an eigenfunction expansion to handle the time dependence of an impulsive source.} For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with  mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct boundary condition of zero-ingoing intensity at the surface.
+This solution is compared to that of the Monte Carlo method, which is valid at arbitrary optical depth.
+It is shown that the size of the correction is of order unity when the spectral peaks approach the Doppler core and decreases slowly with line center optical depth, \textbf{specifically $(a \tau_0)^{-1/3}$}, which may explain discrepancies in previous studies.
+For the impulsive problem, the time, spatial, and frequency dependence of the solution are expressed using an eigenfunction expansion in order to characterize the escape time distribution and emergent spectra of photons.
+It is shown that the lowest-order eigenfrequency agrees well with the decay rate found in the Monte Carlo escape time distribution at sufficiently large line-center optical depths.
+\textbf{The new additions presented in this work have important applications in the study of planetary atmospheres irradiated by \lya, as the correction term is significant for line-center optical depths as low as $\tau_0 \approx 10^5$ (\todo As low as?
+As high as?
+How do we stress the importance of the bc correction proprely?).
+Additionally, the characterization of the escape-time distribution highlights the potential for a Monte Carlo acceleration method, which would sample photon escape properties from distributions rather than calculate every photon scattering, which may be computationally expensive at large line-center optical depths.}
+
 \end{abstract}
@@
 
-The outer layers of the atmosphere are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
-Given the abundance of hydrogen and its large cross section, the Lyman $\alpha$ (Ly$\alpha$) line is an important component of the radiation field.
+Given the abundance of hydrogen in our universe and its large cross section, \textbf{the Lyman $\alpha$ (Ly$\alpha$) line is an important component of radiation fields in wide range of astrophysical settings.
+\lya radiation transport is an active area of research in the study of planets, stars, galaxies, and cosmology.
+In this work, however, we consider the role \lya radiation transport plays in planetary atmospheres.} The outer layers of the atmosphere are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
 There are two sources of Ly$\alpha$: the star, and recombinations in the planet's atmosphere.
-\lya may ionize atoms and dissociate molecules, as well as exert pressure forces that drive an outflow.
+\lya may ionize atoms and dissociate molecules, as well as exert pressure forces that drive an outflow (\todo Citation needed).
 \lya can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy \citep{2017ApJ...851..150H}.

### 2022-03-22 ms.tex
Adding citations discussed in group meeting

@@
 It is shown that the lowest-order eigenfrequency agrees well with the decay rate found in the Monte Carlo escape time distribution at sufficiently large line-center optical depths.
-\textbf{The new additions presented in this work have important applications in the study of planetary atmospheres irradiated by \lya, as the correction term is significant for line-center optical depths as low as $\tau_0 \approx 10^5$ (\todo As low as?
-As high as?
-How do we stress the importance of the bc correction proprely?).
-Additionally, the characterization of the escape-time distribution highlights the potential for a Monte Carlo acceleration method, which would sample photon escape properties from distributions rather than calculate every photon scattering, which may be computationally expensive at large line-center optical depths.}
+\textbf{The new additions presented in this work have a broad range of important applications, since the correction term is significant any time the \lya line center optical depths exceed ${\sim}10^5$.
+Additionally, the characterization of the escape-time distribution highlights the potential for a Monte Carlo acceleration method, which would sample photon escape properties from distributions rather than calculate every photon scattering, which may be computationally expensive.}
 
@@
 Given the abundance of hydrogen in our universe and its large cross section, \textbf{the Lyman $\alpha$ (Ly$\alpha$) line is an important component of radiation fields in wide range of astrophysical settings.
-\lya radiation transport is an active area of research in the study of planets, stars, galaxies, and cosmology.
-In this work, however, we consider the role \lya radiation transport plays in planetary atmospheres.} The outer layers of the atmosphere are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
+\lya radiation transport is an active area of research in the study of planets, stars, galaxies, and cosmology \citep{2019SAAS...46....1D}.
+An example application motivating our work is the role \lya radiation transport plays in planetary atmospheres.} The outer layers of the atmosphere are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
 There are two sources of Ly$\alpha$: the star, and recombinations in the planet's atmosphere.
-\lya may ionize atoms and dissociate molecules, as well as exert pressure forces that drive an outflow (\todo Citation needed).
+\lya may ionize atoms and dissociate molecules, as well as exert pressure forces that drive an outflow \textbf{ \citep{2018A&A...620A.147B}}.
 \lya can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy \citep{2017ApJ...851..150H}.

### 2022-03-24 ms.tex
Adding a rough introduction of the time-dependent motivation, including references to Roy et al 2010 and Xu et al 2011

@@
 Both works, however, use the same surface boundary condition and ansatz as \citet{1973MNRAS.162...43H}.
+
+\textbf{NOT SURE WHERE TO PUT THIS: Steady-state solutions to this problem, while informative, are not always sufficient to describe all the physics of \lya transport.
+Time-variable, optically-thick environments necessitate a time-dependent solution to include the dynamic effects of \lya transfer.
+For example, \lya radiation pressure is dynamically significant in the case of CR7, a \lya emitter in which radiation-driven winds and line cooling play an important role \citep{2017A&G....58c3.22S}.
+Other time-dependent \lya sources include the optical afterglow of gamma-ray bursts \citep{2010ApJ...716..604R} and sources redshifted by cosmological expansion, which may reveal information about their neutral hydrogen halos and the intergalactic medium \citep{2011MNRAS.418..853X}.}
 

### 2022-03-28 ms.tex
Adjusting content of time-dependent motivation paragraph

--- 2022-03-22 ms.tex
@@
 Both works, however, use the same surface boundary condition and ansatz as \citet{1973MNRAS.162...43H}.
+
+\textbf{The motivation for including time-dependence in the transfer equation is to characterize the time it takes photons to escape the sphere.
+This information is needed to calculate the energy deposited into the gas by the scattered photon, which would be necessary for performing radiation hydrodynamics simulations using escape times sampled from this solution.
+Additionally, steady-state solutions to this problem, while informative, are not always sufficient to describe all the physics of \lya transport.
+Time-variable, optically-thick environments necessitate a time-dependent solution to include the dynamic effects of \lya transfer.
+Time-dependent \lya sources include the optical afterglow of gamma-ray bursts \citep{2010ApJ...716..604R} and sources redshifted by cosmological expansion, which may reveal information about their neutral hydrogen halos and the intergalactic medium \citep{2011MNRAS.418..853X}.}
 

### 2022-03-29 ms.tex
Changing title and further adjusting time dependence motivation paragraph

--- 2022-03-22 ms.tex
@@
 
-\title{Resonant Scattering in a Uniform Sphere with Large Optical Depth}
-
+\title{Boundary Conditions and Time Dependence of a Semi-Analytic Solution for Resonant Scattering}
+% the paper formerly known as Resonant Scattering in a Uniform Sphere with Large Optical Depth
 \correspondingauthor{B. Connor McClellan}
@@
 Both works, however, use the same surface boundary condition and ansatz as \citet{1973MNRAS.162...43H}.
+
+\textbf{The motivation for including time-dependence in the transfer equation is to characterize the distribution of photon escape times, which is needed to calculate the energy deposited into the gas by an escaping photon.
+Additionally, steady-state solutions to this problem are not always sufficient to describe all the physics of \lya transport.
+Time-variable, optically-thick environments necessitate a time-dependent solution to include the dynamic effects of \lya transfer.
+These include the optical afterglow of gamma-ray bursts \citep{2010ApJ...716..604R} and \lya sources redshifted by cosmological expansion %, which may reveal information about their neutral hydrogen halos and the intergalactic medium
+\citep{2011MNRAS.418..853X}.}
 

### 2022-03-29 ms.tex
Changing all instances of "on the wing" to "in the wing"

@@
 \textbf{The new additions presented in this work have a broad range of important applications, since the correction term is significant any time the \lya line center optical depths exceed ${\sim}10^5$.
-Additionally, the characterization of the escape-time distribution highlights the potential for a Monte Carlo acceleration method, which would sample photon escape properties from distributions rather than calculate every photon scattering, which may be computationally expensive.}
+Additionally, the characterization of the escape-time distribution highlights the potential for a Monte Carlo acceleration method, which would sample photon escape properties from distributions rather than calculate every photon scattering, reducing computational demand.}
 
@@
 Due to the technical challenge of including resonant scattering, the fully three-dimensional geometry, and the presence of an outflow, numerical simulations may be required to fully understand the dynamics of these irradiated exoplanet atmospheres.
-The large optical depths at \lya line center impose a steep computational cost for solving radiative transfer with Monte Carlo methods directly coupled with fluid dynamics.
-The number of scatterings a photon undergoes is proportional to the line center optical depth, $\tau_0$, of the domain.
+The large optical depths at \lya line center impose a steep computational cost for solving radiative transfer with Monte Carlo methods directly coupled with fluid dynamics \textbf{\citep{2017MNRAS.464.2963S}}.
+The number of scatterings a photon undergoes is proportional to the line center optical depth, $\tau_0$, of the domain \textbf{\citep{1972ApJ...174..439A}}.
 Near the base of the atomic layer, the line center optical depth is ${\sim}10^8$, so most of the time is spent following photons in these cells.
 A method that can accurately characterize transfer through these zones without following every photon scattering has the potential to greatly accelerate the calculation.
+\textbf{Dynamic core-skipping methods are often used, but }
 
 Approximate analytic solutions for resonant scattering exist in certain limits.
-\citet{1973MNRAS.162...43H} showed that when most of the radiation is out on the damping wings, the transfer equation reduces to the Poisson equation.
+\citet{1973MNRAS.162...43H} showed that when most of the radiation is in the damping wings, the transfer equation reduces to the Poisson equation.
 However, their solution uses an ansatz to handle the boundary condition.
@@
 \ee
-where the approximation is applicable on the damping wing. From Equation (\ref{eq:app:line_profile_wing}), the line profile is then approximately 
+where the approximation is applicable in the damping wing. From Equation (\ref{eq:app:line_profile_wing}), the line profile is then approximately 
 \be \label{eq:line_profile_approx}
@@
 It is still valid near the delta function at $r=0$, but is also a better approximation at $r=R$.
-$J_0$ decreases exponentially, rather than as a power-law in frequency as it does for $J_d$, giving a much smaller flux on the line wings as compared to the divergent solution.
+$J_0$ decreases exponentially, rather than as a power-law in frequency as it does for $J_d$, giving a much smaller flux in the line wings as compared to the divergent solution.
 
@@
 It is clear from the figure that as $x_s$ extends further into the wing, the spectrum becomes more strongly peaked in frequency.
-Additionally, since the sphere is increasingly optically thin on the wing, we expect there to be a stronger disagreement with the Monte Carlo as the analytic solution assumed large optical depths.
+Additionally, since the sphere is increasingly optically thin in the wing, we expect there to be a stronger disagreement with the Monte Carlo as the analytic solution assumed large optical depths.
 
@@
 When the coefficient on the right hand side is positive, exponential growth or decaying evanescent solutions are found.
-This occurs on the line wings.
+This occurs in the line wings.
 When the coefficient on the right hand side is negative, oscillatory solutions are found (propagation), which occurs near the line core.
@@
 It cancels the $-k\phi J$ term in Equation (\ref{eq:rteqn}) that corresponds to excitation of the atom.
-The terms involving frequency derivatives of $\vec{H}$, if carried through the calculation, end up giving terms smaller than the largest terms by a factor of $1/x^2$, which is small on the line wing.
+The terms involving frequency derivatives of $\vec{H}$, if carried through the calculation, end up giving terms smaller than the largest terms by a factor of $1/x^2$, which is small in the line wing.
 These terms are ignored from here onward.
@@
 \ee
-As an example, on the damping wing, the line profile can be approximated as 
+As an example, in the damping wing, the line profile can be approximated as 
 \be \label{eq:app:line_profile_wing}

### 2022-04-01 ms.tex
Changes to figure 1, captions, initial corrections based on reviewer comments up to Section 3

@@
 A method that can accurately characterize transfer through these zones without following every photon scattering has the potential to greatly accelerate the calculation.
-\textbf{Dynamic core-skipping methods are often used, but }
+\todo \textbf{Dynamic core-skipping methods are often used, but}
 
@@
 However, their solution uses an ansatz to handle the boundary condition.
-To our knowledge, the errors introduced by this treatment have never been quantified.
-They attempt a separation of variables as $J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ (their Equations 16 and 23).
+To our knowledge, the errors introduced by this treatment have never been quantified, \todo \textbf{though \cite{2020MNRAS.497.3925L} introduce a physically-motivated parametrized boundary condition } They attempt a separation of variables as $J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ (their Equations 16 and 23).
 The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
@@
 \citet{2006ApJ...649...14D} generalize the same problem to spherical geometry, as is used here.
-Both works, however, use the same surface boundary condition and ansatz as \citet{1973MNRAS.162...43H}.
+\textbf{\cite{2020MNRAS.497.3925L} generalize both the slab and sphere solutions to arbitrary power-law density and emissivity profiles.}  Each of these works, however, use the same surface boundary condition and ansatz as \citet{1973MNRAS.162...43H}.
 
@@
 \ee
-Equation (\ref{eq:H0surf}) will be shown to be a better approximation to the solution than Equation (\ref{eq:Hd}).
+\textbf{Equation (\ref{eq:H0})} will be shown to be a better approximation to the solution than Equation (\ref{eq:Hd}).
 It is still valid near the delta function at $r=0$, but is also a better approximation at $r=R$.
@@
 The number of points was increased until the solution was well-resolved near line center, and only became inaccurate close to the boundaries.
-Given the Fourier amplitudes $A(s)$, $J_{\rm bc}$ is computed using Equation (\ref{eq:Jbc}), and the flux is given by
+\textbf{We found that values of $N=4097$ and $\sigma_{\rm max} = 60 \tau_0$ were sufficient.} Given the Fourier amplitudes $A(s)$, $J_{\rm bc}$ is computed using Equation (\ref{eq:Jbc}), and the flux is given by
 \be
@@
     \caption{Spectrum $P(x)$ vs.
-frequency $x$ for $\tau_0 = 1 \times 10^7$ with $x_s = 0.0$.
-The legend to the right describes each line style.
-The top panel is linear scale, the middle panel is log scale with $|\rm H_{bc}|$ shown instead of $\rm H_{bc}$, and the bottom panel is the residual of each solution with Monte Carlo.}
+frequency $x$ for $\tau_0 = 10^7$ with $x_s = 0$.
+\textbf{At $T=10^4$ K, this corresponds to $a\tau_0=4.7 \times 10^3$.} The legend to the right describes each line style.
+\textbf{For reference, $\rm H_{0}$: fiducial solution, $\rm H_{d}$: divergent solution, $\rm H_{bc}$: our boundary condition correction to the fiducial solution.} The top panel is linear scale, the middle panel is log scale with $|\rm H_{bc}|$ shown instead of $\rm H_{bc}$, and the bottom panel is the residual of each solution with Monte Carlo.}
     \label{fig:sol_mc_residual_0}

### 2022-04-06 ms.tex
Adding time-dependent section edits up to figure 8, replacing figure 8 with exact atau0 scaling coefficient shown

@@
 
-\title{Boundary Conditions and Time Dependence of a Semi-Analytic Solution for Resonant Scattering}
+\title{A Novel Solution to Resonant Scattering with Self-Consistent Boundary Conditions}
 % the paper formerly known as Resonant Scattering in a Uniform Sphere with Large Optical Depth
+
 \correspondingauthor{B. Connor McClellan}
@@
 \textbf{The new additions presented in this work have a broad range of important applications, since the correction term is significant any time the \lya line center optical depths exceed ${\sim}10^5$.
-Additionally, the characterization of the escape-time distribution highlights the potential for a Monte Carlo acceleration method, which would sample photon escape properties from distributions rather than calculate every photon scattering, reducing computational demand.}
+Additionally, the characterization of the escape-time distribution highlights the potential for a Monte Carlo acceleration method, which would sample photon escape properties from distributions rather than calculating every photon scattering, reducing computational demand.}
 
@@
 A method that can accurately characterize transfer through these zones without following every photon scattering has the potential to greatly accelerate the calculation.
-\todo \textbf{Dynamic core-skipping methods are often used, but}
 
@@
 However, their solution uses an ansatz to handle the boundary condition.
-To our knowledge, the errors introduced by this treatment have never been quantified, \todo \textbf{though \cite{2020MNRAS.497.3925L} introduce a physically-motivated parametrized boundary condition } They attempt a separation of variables as $J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ (their Equations 16 and 23).
+To our knowledge, the errors introduced by this treatment have never been quantified.
+They attempt a separation of variables as $J(\tau,\sigma) = \theta(\tau) j(\sigma)$ in spatial variable $\tau$ and frequency variable $\sigma$ (their Equations 16 and 23).
 The solutions for the eigenfunctions $\theta(\tau)$ and $j(\sigma)$ then depend explicitly on the separation constant $\lambda$.
@@
 It is evident that the divergent solution $H_{\rm d}$ fails in the line wings.
+\textbf{Also note that the ``V'' shape of the solution in the line core is due simply to the low number of points we chose to use, as the analytic solutions are not valid in this frequency regime since they utilize the damping wing approximation of the Voigt line profile.}
 
@@
 At the eigenvalues $\gamma=\gamma_{nm}$, the response $J(n, \sigma, \omega)$ is resonant.
-Near these $\gamma_{nm}$ poles, the eigenfunctions will have the form
+Near these $\gamma_{nm}$ poles, \textbf{an approximate expression for the resonant response of the eigenfunctions is}
 \be \label{eq:jnsigmaomega_approx}
@@
 The size of each contribution scales roughly as $0.5/(m-7/8)^{2/3}$, with a weak dependence on $n$.
-This indicates the need for a large number of $n$ and $m$ to converge, in that it takes roughly ten times as many $m$ modes to reduce the size of $P_{nm}$ by a factor of ${\sim}$5.
+This indicates the need for a large number of $n$ and $m$ to converge, in that it takes roughly ten times as many $m$ modes \textbf{for a given $n$} to reduce the size of $P_{nm}$ by a factor of ${\sim}$5 \textbf{(see the discussion of Figure \ref{fig:steadystate} in Section \ref{subsec:steadystatemc})}.
 
@@
 In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bracketed a resonance that occurs in the interval $(\gamma_{j-1},\gamma_{j+1})$.
-We then hone in on the eigenvalue before continuing the sweep in $\gamma$.
-To refine the eigenmode solution, we evaluate $f_{j-1}$, $f_j$, and $f_{j+1}$ at the points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$.
-Assuming the form in Equation (\ref{eq:jnsigmaomega_approx}), a guess at the correct eigenvalue $\gamma_{nm}$ can be calculated from
+\textbf{To refine the value of the eigenfrequency before continuing the sweep in $\gamma$}, we evaluate $f_{j-1}$, $f_j$, and $f_{j+1}$ at the points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$.
+Assuming the form in Equation (\ref{eq:jnsigmaomega_approx}), a guess at the correct eigenvalue $\gamma_{nm}$ can be calculated \textbf{by linear interpolation} from
 \be
@@
 \ee
-This is repeated by replacing initial points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ with closer estimates while the size of the response grows as the resonance is approached.
+\textbf{The error of the current guess is $|\gamma_{\rm guess} - \gamma_{j}|$.
+This error is reduced iteratively by} replacing initial points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ with closer estimates while the size of the response grows as the resonance is approached.
 After iterating an eigenvalue $\gamma_{nm}$ to convergence, we now find the corresponding eigenfunction $J_{nm}(\sigma)$.
-We can solve for $J_{nm}(\sigma)$ by comparing two points $\gamma_1$ and $\gamma_2$ near the resonance, cancelling $C(\gamma, \sigma)$ in the difference to find
-\be
-J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,-i\gamma_1)  - J(n,\sigma,-i\gamma_2) }{ 1/(\gamma_{nm}-\gamma_1) - 1/(\gamma_{nm}-\gamma_2)}.
-\ee
+\textbf{We evaluate Equation \ref{eq:jnsigmaomega_approx} at two points $\gamma_1$ and $\gamma_2$ near the resonance, subtracting them and solving for $J_{nm}(\sigma)$ to find}
+\be
+J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,-i\gamma_1)  - J(n,\sigma,-i\gamma_2) }{ 1/(\gamma_{nm}-\gamma_1) - 1/(\gamma_{nm}-\gamma_2)},
+\ee
+\noindent \textbf{where  $C(\gamma, \sigma)$ has cancelled in the difference.}
+
 \begin{figure}
@@
     \includegraphics{Jsoln_n1_m100.pdf}
-    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $x_s=0$ and $\tau_0=10^7$. }
+    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $x_s=0$ and $\tau_0=10^7$.
+\textbf{The scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$, which here is ${\sim}10^{-37}$ in units of specific mean intensity times time.}}
     \label{fig:jsoln}
 \end{figure}
-\noindent The form of a single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{\rm tp}$, at which point the function becomes evanescent.
+
+The form of a single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{\rm tp}$, at which point the function becomes evanescent.
 The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Equation (\ref{eq:diffusion_plugged_in}) and examining the resulting homogeneous differential equation.
@@
 \ee
-as shown in Appendix \ref{app:wkb}.
+as shown in Appendix \ref{app:wkb} using the WKB approximation.
 The power law in $m$ is weak, requiring up to $m=1000$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
@@
 
-\subsection{Comparison with Steady State and Monte Carlo}
+\subsection{Comparison with Steady State and Monte Carlo} \label{subsec:steadystatemc}
 
@@
 Here, the Monte Carlo accurately includes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile, and also does not use enough spatial modes to accurately model the frequency regime near line center.
-However, as $\tau_0$ grows, the effect of core scattering becomes smaller and the approximations hold, agreeing well with the expected $(a\tau_0)^{1/3}$ scaling for the rate constant at late times.
+However, as $\tau_0$ grows, the effect of core scattering becomes smaller and the approximations hold, agreeing well with the expected $(a\tau_0)^{1/3}$ scaling \citep{1975ApJ...201..350A} for the rate constant at late times.
 

### 2022-04-06 ms.tex
Addressing reviewer comments up to the appendix

@@
 Here, the Monte Carlo accurately includes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile, and also does not use enough spatial modes to accurately model the frequency regime near line center.
-However, as $\tau_0$ grows, the effect of core scattering becomes smaller and the approximations hold, agreeing well with the expected $(a\tau_0)^{1/3}$ scaling \citep{1975ApJ...201..350A} for the rate constant at late times.
+However, as $\tau_0$ grows, the effect of core scattering becomes smaller and the approximations hold, agreeing better with the expected $(a\tau_0)^{1/3}$ scaling \textbf{\citep{1975ApJ...201..350A}} for the rate constant at late times.
+\textbf{The excess in the Monte Carlo data points due to core scattering decreases exponentially at higher $\tau_0$, and though these points are not shown at $\tau_0=10^8$ and $10^9$ due to computational expense, it is expected that the fractional error between the Monte Carlo and the $(a\tau_0)^{1/3}$ scaling would be less than 2\% at $\tau_0=10^9$.}
 
@@
 
-In Figure \ref{fig:steadystate}, the fluence for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated''), and is compared with two analytic solutions: the steady-state $H_0$ solution (Equation \ref{eq:H0surf}) with no time dependence (labelled ``Steady State''), and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in the first line of Equation (\ref{eq:H0surf}).
+In Figure \ref{fig:steadystate}, the fluence for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated''), and is compared with two analytic solutions: the steady-state $H_0$ solution (Equation \ref{eq:H0surf}) with no time dependence (labelled ``Steady State''), and the result for summing \textbf{a finite number of} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in the first line of Equation (\ref{eq:H0surf}).
 Additional spatial modes $n$ increase the solutions' accuracy in the core of the line.
@@
     \includegraphics{steadystate.pdf}
-    \caption{Fluence $P(x)$ vs. $x$. The steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ are shown with $x_s=0$ and $\tau_0=10^7$.}
+    \caption{Fluence $P(x)$ vs.
+$x$ \textbf{(see Equation \ref{eq:spectrum}).
+Fluence is the radiation flux integrated over time.
+}Steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ are shown with $x_s=0$ and $\tau_0=10^7$.
+\textbf{Note that the x-axis begins near the line core, as we are only concerned with the solutions' accuracy in the line wing.}}
     \label{fig:steadystate}
@@
 Thus, for large $a\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $a\tau_0$.
-Since the Laplacian form of the differential equation is only correct when the line profile is $\phi \approx a/(\pi x^2 \Delta)$, our solutions do not accurately model the Doppler core of the \lya line.
+Since the Laplacian form \textbf{for frequency redistribution in }the differential equation is only correct \textbf{for photons in the wing where the} line profile is $\phi \approx a/(\pi x^2 \Delta)$, our solutions do not accurately model the Doppler core of the \lya line.
 Because the peak of the spectral energy distribution of escaping photons is $x_{\rm peak} {\sim} (a\tau_0)^{1/3}$, calculations performed at small $a\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
 
-By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions for $a\tau_0 \geq 1$.
+By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions for $a\tau_0 \gg 1$.
 Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition presented in \citet{1973MNRAS.162...43H}, \citet{1990ApJ...350..216N}, and \citet{2006ApJ...649...14D}.
@@
 
-There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}, but these methods are not sufficient for our application since they do not track the amount of time photons spend in the line core, which is needed to tabulate the intensity.
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}, but these methods are not sufficient for our application since they do not \textbf{directly measure or sample} the amount of time photons spend in the line core, which is needed to tabulate the intensity.
 Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}.
@@
 A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \citet{1990ApJ...350..216N} solution, but this solution of course does not utilize the frequency-dependent boundary condition at the surface of the sphere.
-Furthermore, to perform a full radiation hydrodynamic simulation with Monte Carlo acceleration, it will be necessary to calculate radiation forces due to \lya transfer on the faces of each grid cell in the simulation.
+Furthermore, to perform a full radiation hydrodynamic simulation with Monte Carlo acceleration, it will be necessary to calculate radiation forces due to \lya transfer.
 Similar calculations have been done in \citet{1976ApJ...208..286W} in plane-parallel geometry.

### 2022-04-06 ms.tex
First pass at addressing reviewer comments

@@
 \delta \left( \nu - \nu^\prime - \nu_0 \vec{v} \cdot (\vec{n}-\vec{n}^\prime)/c \right)
-\left( \frac{\Gamma/4\pi^2}{ \left(\nu^\prime - \nu_0 - \nu_0 \vec{v} \cdot \vec{n}^\prime/c \right)^2 + (\Gamma/4\pi)^2 } \right)
-\ee
-found in \citet{1962MNRAS.125...21H}.
+\left( \frac{\Gamma/4\pi^2}{ \left(\nu^\prime - \nu_0 - \nu_0 \vec{v} \cdot \vec{n}^\prime/c \right)^2 + (\Gamma/4\pi)^2 } \right),
+\ee
+\textbf{\citep{1952PASJ....4..100U, 1962MNRAS.125...21H}}.
 
@@
 where the right hand side is the usual Voigt function, the thermal average of the Lorentzian.
-The former result implies that the integrated source and sink terms for scattering cancel for $p=1$.
+The former result implies that the integrated source and sink terms for scattering cancel for $p=0$.
 In addition, $4\pi R(\vec{n},\nu; \vec{n}^\prime,\nu^\prime)/\phi(\nu^\prime) $ is the normalized distribution for the outgoing $\vec{n}$ and $\nu$ given the incoming $\vec{n}^\prime$ and $\nu^\prime$.
 
-This probability distribution can be used to define the moments of the frequency shift
+This probability distribution can be used to define the moments of the frequency shift \citep{1962ApJ...135..195O}
 \be
@@
 \ee 
-and the Fokker-Planck expansion of $j_{\rm sc}$ is
+and the Fokker-Planck expansion of $j_{\rm sc}$ is \citep{1994ApJ...427..603R}
 \be
@@
 \left( \frac{7}{5} \langle u_\parallel^2 \rangle + \frac{3}{10}  \right) \right]
-\right) = 0,
+\right),
 \ee
@@
 \ee
-By setting the to denominator of this expression equal to zero and solving for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{\rm tp}$, we find the dispersion relation in Equation (\ref{eq:gamma_nm}).
+By setting the denominator of this expression equal to zero and solving for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{\rm tp}$, we find the dispersion relation in Equation (\ref{eq:gamma_nm}).
 

### 2022-04-12 ms.tex
Changes to figure 5

@@
 In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo spectrum is shown along with that of the solutions $H_{\rm d}$, $H_0$, and $H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
-The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to $H_0$, it corrects for the apparent excess of flux in the peaks of the spectrum.
+\textbf{Note that the errorbars shown on the Monte Carlo data points are $\sqrt{N}$, with $N$ being the photon count in each frequency bin, since the photons are all equally weighted.} The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to $H_0$, it corrects for the apparent excess of flux in the peaks of the spectrum.
 The solution with the correct frequency-dependent boundary condition enforced, $H_0 + H_{\rm bc}$, has lower residuals to Monte Carlo results than the other solutions, especially in the line wing.
 The boundary term corrects the deficit of $H_0$ in the line wings, further improving agreement with the numerical result.
-Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.
+The residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.
 It is evident that the divergent solution $H_{\rm d}$ fails in the line wings.
-\textbf{Also note that the ``V'' shape of the solution in the line core is due simply to the low number of points we chose to use, as the analytic solutions are not valid in this frequency regime since they utilize the damping wing approximation of the Voigt line profile.}
+\textbf{Also note that the ``V'' shape of the solution in the line core is due simply to the low number of points we chose to use, as the analytic solutions are not valid in this frequency regime since they utilize the damping wing approximation of the Voigt line profile.
+}
 
@@
 frequency $x$.
-Thicker lines indicate larger optical depth labeled by $\tau_0=10^5, 10^7,$ and $10^9$, and darker lines indicate $\sigma_s$ further from line center, labeled by $\sigma_s=0.0, \tau_0, 2\tau_0$.
-The location of the core-wing boundary $x_{cw}$ is shown with green vertical lines of increasing thickness for each $\tau_0$.
+\textbf{Each panel shows $\sigma_s$ further from line center, labeled by $\sigma_s=0, \tau_0, 2\tau_0$.
+The solution is shown at a range of line center optical depths between $\tau_0=10^5$ and $10^9$ with solid overlapping lines.
+The thickness of the lines decreases with increasing optical depth to more clearly show where they overlap.
+The location of the core-wing boundary $x_{cw}$ for each $\tau_0$ is shown with dashed vertical lines which match the color of the corresponding solution}.
 The axes are scaled to show that the size of the correction factor agrees with the predicted $(a\tau_0)^{-1/3}$ scaling.}
@@
 Figure \ref{fig:xinit} shows how the correction $P_{\rm bc}(x)$, Equation (\ref{eq:prob_spectrum}) with $H \rightarrow H_{\rm bc}$, scales with both $\tau_0$ and $x_s$.
-In this figure, $\sigma_s$ is shifted by integer multiples of $\tau_0$ (Equation \ref{eq:change_of_variables}) such that the source falls near the peak of the spectrum for each $\tau_0$.
+In this figure, $\sigma_s$ is shifted by integer multiples of $\tau_0$ (Equation \ref{eq:change_of_variables}) in each panel such that the source falls near the peak of the spectrum for each $\tau_0$.
 For clarity, only the $x > 0$ side of the spectrum is shown.
@@
 At the eigenvalues $\gamma=\gamma_{nm}$, the response $J(n, \sigma, \omega)$ is resonant.
-Near these $\gamma_{nm}$ poles, \textbf{an approximate expression for the resonant response of the eigenfunctions is}
+\textbf{We find that} near these $\gamma_{nm}$ poles \textbf{an approximate expression for the resonant response of the eigenfunctions is}
 \be \label{eq:jnsigmaomega_approx}
@@
 The size of each contribution scales roughly as $0.5/(m-7/8)^{2/3}$, with a weak dependence on $n$.
-This indicates the need for a large number of $n$ and $m$ to converge, in that it takes roughly ten times as many $m$ modes \textbf{for a given $n$} to reduce the size of $P_{nm}$ by a factor of ${\sim}$5 \textbf{(see the discussion of Figure \ref{fig:steadystate} in Section \ref{subsec:steadystatemc})}.
+This indicates the need for a large number of $n$ and $m$ to converge, in that it takes roughly ten times as many $m$ modes \textbf{for a given $n$} to reduce the size of $P_{nm}$ by a factor of ${\sim}$5.
+\textbf{The physical intuition for the convergence of these terms is that the $n$ spatial terms must provide sufficient spatial resolution to resolve the steep falloff in intensity at the surface of the sphere.
+Additionally, the function falls off steeply in frequency in the line wing, which requires more $m$ terms in the Fourier sum to resolve (also see the discussion of Figure \ref{fig:steadystate} in Section \ref{subsec:steadystatemc})}.
 
@@
 \ee
-as shown in Appendix \ref{app:wkb} using the WKB approximation.
+as shown \textbf{by setting the denominator of Equation \ref{eq:a3/a2} to zero in WKB approximation of} Appendix \ref{app:wkb}.
 The power law in $m$ is weak, requiring up to $m=1000$ to reduce the scale of $\gamma_{nm}^{\ \ -1}$ by two orders of magnitude.
@@
 It is shown that the time constant of exponential decay in fitted Monte Carlo escape time distributions converges with $\gamma_{11}^{-1}$ at sufficiently high $\tau_0$, following a $t\propto(a\tau_0)^{1/3}$ scaling.
-At lower $\tau_0$, the effects of line core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
+\textbf{The coefficient of this scaling ($0.51$) is within a factor of 2 of the approximate ``light-trapping time'' defined in \citet{2020MNRAS.497.3925L}, which predicts $ct/R=0.901(a\tau_0)^{1/3}$.} At lower $\tau_0$, the effects of line core scattering are most important, leading to a larger discrepancy in the characteristic escape timescale.
 Here, the Monte Carlo accurately includes the photons which scatter in the core many times before escaping, while the semi-analytic solution does not capture this behavior as it uses only the Lorentzian piece of the line profile, and also does not use enough spatial modes to accurately model the frequency regime near line center.

### 2022-04-12 ms.tex
Removing all instances of redundant significant figures in plots, captions, and text

@@
 \citet{2006ApJ...649...14D} generalize the same problem to spherical geometry, as is used here.
-\textbf{\cite{2020MNRAS.497.3925L} generalize both the slab and sphere solutions to arbitrary power-law density and emissivity profiles.}  Each of these works, however, use the same surface boundary condition and ansatz as \citet{1973MNRAS.162...43H}.
+\textbf{\cite{2020MNRAS.497.3925L} generalize both the slab and sphere solutions to arbitrary power-law density and emissivity profiles.
+Each of these works, and several others \citep{2020ApJS..250....9S, 2021MNRAS.504...89T}, use either the same surface boundary condition and ansatz as \citet{1973MNRAS.162...43H}, or use a solution that does not handle the frequency-dependence of the boundary condition.
+Our novel steady-state solution involves a frequency-dependent correction to the boundary condition that fixes an excess at the spectral peaks as compared with Monte Carlo, which is present in many of the works cited above.}
 
@@
 These include the optical afterglow of gamma-ray bursts \citep{2010ApJ...716..604R} and \lya sources redshifted by cosmological expansion %, which may reveal information about their neutral hydrogen halos and the intergalactic medium
-\citep{2011MNRAS.418..853X}.}
+\citep{2011MNRAS.418..853X}, among others.}
 
@@
     \includegraphics[width=\textwidth]{xinit_threepanel.pdf}
-    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\tau_0=10^7$ and $\rm x_s = 0.0$ (top panel), $6.0$ (middle panel), and $12.0$ (bottom panel).
+    \caption{The same as Figure \ref{fig:sol_mc_residual_0}, but for $\tau_0=10^7$ and $\rm x_s = 0$ (top panel), $6$ (middle panel), and $12$ (bottom panel).
 The optical depth at each of these source frequencies is $\tau_s = 10^7, 77,$ and $19$, respectively.}
@@
 The shift $x_s$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the asymmetry in the spectrum is much larger.
-The optical depth at the source frequency is $\tau_s = 10^6$, $7.7$, and $1.9$ for $x_s=0.0, 6.0,$ and $12.0$, respectively.
+The optical depth at the source frequency is $\tau_s = 10^6$, $7.7$, and $1.9$ for $x_s=0, 6,$ and $12$, respectively.
 }
@@
 
-Figure \ref{fig:sol_mc_xinit} shows calculations performed for $x_s = 0.0, 6.0$, and $12.0$ and $\tau_0=10^7$.
-The asymmetry of the spectrum is slight for $\rm x_s = 6.0$ where $\tau(x_s)=77$, but is larger for $\rm x_s=12.0$ outside the line core where $\tau(x_s)=19$.
+Figure \ref{fig:sol_mc_xinit} shows calculations performed for $x_s = 0, 6$, and $12$ and $\tau_0=10^7$.
+The asymmetry of the spectrum is slight for $\rm x_s = 6$ where $\tau(x_s)=77$, but is larger for $\rm x_s=12$ outside the line core where $\tau(x_s)=19$.
 It is seen here that the difference between the Monte Carlo data and $H_0$ becomes larger as $\rm x_s$ increases.
@@
 These numerically-obtained resonant frequencies are compared with the analytic expression in Equation (\ref{eq:gamma_nm}), shown as a dashed line.
-The parameters for the calculation are $\tau_0=10^7$ and $x_s=0.0$.
+The parameters for the calculation are $\tau_0=10^7$ and $x_s=0$.
 The value of $n$ is given by the color bar on the right-hand side.}
@@
 A sum over 20 spatial eigenmodes and 500 frequency eigenmodes is labeled ``Eigenfunctions''.
-All calculations were performed with a monochromatic source of photons at line center ($x_s = 0.0$).}
+All calculations were performed with a monochromatic source of photons at line center ($x_s = 0$).}
     \label{fig:escape_time}
@@
 
-There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}, but these methods are not sufficient for our application since they do not \textbf{directly measure or sample} the amount of time photons spend in the line core, which is needed to tabulate the intensity.
+There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations, including core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A} and hybrid diffusion methods \citep{2018MNRAS.479.2065S}.
 Another approach with wide application is modified random walk methods, such as those discussed in \citet{1984JCoPh..54..508F, 2009A&A...497..155M, 2010A&A...520A..70R}.

### 2022-05-03 ms.tex
Adjusting fig 5 since thinner lines show the convergence at large optical depths more clearly
Incorporating Phil's most recent edits

@@
 
-\title{A Novel Solution to Resonant Scattering with Self-Consistent Boundary Conditions}
+\title{A Novel Solution for Resonant Scattering Using Self-Consistent Boundary Conditions}
 % the paper formerly known as Resonant Scattering in a Uniform Sphere with Large Optical Depth
@@
 \begin{abstract}
-%ORIGINAL: 
-%The radiation transfer equation for resonant scattering is solved in spherical geometry.
-A monochromatic source of photons is assumed at the center of a uniform sphere of constant gas density.
-The intensity within the sphere and at its surface is found in the limit of large line-center optical depth using the Eddington approximation for the angular dependence.
-Two limits are studied: a steady source and an impulsive source.
-For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with  mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct boundary condition of zero-ingoing intensity at the surface.
+
+\textbf{We present two novel additions to the semi-analytic solution of Lyman $\alpha$ (Ly$\alpha$) radiative transfer in spherical geometry: (1) implementation of the correct boundary condition for a steady source, and (2) solution of the time-dependent problem for an impulsive source.} For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with  mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct boundary condition of zero-ingoing intensity at the surface.
 This solution is compared to that of the Monte Carlo method, which is valid at arbitrary optical depth.
-It is shown that the size of the correction is order unity when the spectral peaks approach the Doppler core and decreases slowly with line center optical depth, which may explain discrepancies in previous studies.
+It is shown that the size of the correction is of order unity when the spectral peaks approach the Doppler core and decreases slowly with line center optical depth, \textbf{specifically as $(a \tau_0)^{-1/3}$}, which may explain discrepancies seen in previous studies.
 For the impulsive problem, the time, spatial, and frequency dependence of the solution are expressed using an eigenfunction expansion in order to characterize the escape time distribution and emergent spectra of photons.
 It is shown that the lowest-order eigenfrequency agrees well with the decay rate found in the Monte Carlo escape time distribution at sufficiently large line-center optical depths.
-
-\textbf{We present two novel additions to the semi-analytic solution of Lyman $\alpha$ (Ly$\alpha$) radiative transfer in spherical geometry: (1) a correction to the boundary conditions for a steady source, and (2) an eigenfunction expansion to handle the time dependence of an impulsive source.} For the steady-state problem, the solution can be represented as a sum of two terms: a previously-known analytic solution of the equation with  mean intensity $J=0$ at the surface, and a novel, semi-analytic solution which enforces the correct boundary condition of zero-ingoing intensity at the surface.
-This solution is compared to that of the Monte Carlo method, which is valid at arbitrary optical depth.
-It is shown that the size of the correction is of order unity when the spectral peaks approach the Doppler core and decreases slowly with line center optical depth, \textbf{specifically $(a \tau_0)^{-1/3}$}, which may explain discrepancies in previous studies.
-For the impulsive problem, the time, spatial, and frequency dependence of the solution are expressed using an eigenfunction expansion in order to characterize the escape time distribution and emergent spectra of photons.
-It is shown that the lowest-order eigenfrequency agrees well with the decay rate found in the Monte Carlo escape time distribution at sufficiently large line-center optical depths.
-\textbf{The new additions presented in this work have a broad range of important applications, since the correction term is significant any time the \lya line center optical depths exceed ${\sim}10^5$.
-Additionally, the characterization of the escape-time distribution highlights the potential for a Monte Carlo acceleration method, which would sample photon escape properties from distributions rather than calculating every photon scattering, reducing computational demand.}
+\textbf{The characterization of the escape-time distribution highlights the potential for a Monte Carlo acceleration method, which would sample photon escape properties from distributions rather than calculating every photon scattering, thereby reducing computational demand.}
 
@@
 
-Given the abundance of hydrogen in our universe and its large cross section, \textbf{the Lyman $\alpha$ (Ly$\alpha$) line is an important component of radiation fields in wide range of astrophysical settings.
+Given the abundance of hydrogen in the universe, \textbf{the Lyman $\alpha$ (Ly$\alpha$) line is an important component of radiation fields in a wide range of astrophysical settings.
 \lya radiation transport is an active area of research in the study of planets, stars, galaxies, and cosmology \citep{2019SAAS...46....1D}.
-An example application motivating our work is the role \lya radiation transport plays in planetary atmospheres.} The outer layers of the atmosphere are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
+An example application motivating our work is the role of \lya in planetary atmospheres.} The outer layers of the atmosphere are central to a planet's evolution, since they can shelter the lower atmosphere from high energy radiation as well as regulate the escape of gas into space.
 There are two sources of Ly$\alpha$: the star, and recombinations in the planet's atmosphere.
@@
 Near the base of the atomic layer, the line center optical depth is ${\sim}10^8$, so most of the time is spent following photons in these cells.
-A method that can accurately characterize transfer through these zones without following every photon scattering has the potential to greatly accelerate the calculation.
+A method that can accurately characterize transfer through these zones without following every photon scattering has the potential to greatly accelerate the calculation \textbf{(see e.g.
+\citealt{1968ApJ...153..783A,2002ApJ...567..922A}).}
 
@@
 Each of these works, and several others \citep{2020ApJS..250....9S, 2021MNRAS.504...89T}, use either the same surface boundary condition and ansatz as \citet{1973MNRAS.162...43H}, or use a solution that does not handle the frequency-dependence of the boundary condition.
-Our novel steady-state solution involves a frequency-dependent correction to the boundary condition that fixes an excess at the spectral peaks as compared with Monte Carlo, which is present in many of the works cited above.}
-
-\textbf{The motivation for including time-dependence in the transfer equation is to characterize the distribution of photon escape times, which is needed to calculate the energy deposited into the gas by an escaping photon.
+Our novel steady-state solution involves a frequency-dependent correction to the solution that fixes an observed excess at the spectral peaks as compared with Monte Carlo, which is present in many of the works cited above.}
+
+\textbf{The motivation for including time-dependence in the transfer equation is to characterize the distribution of photon escape times, which is needed to calculate the radiation moments in the Monte Carlo simulation.
 Additionally, steady-state solutions to this problem are not always sufficient to describe all the physics of \lya transport.
@@
 
-A better approximation to the true solution has been derived by \citet{2006ApJ...649...14D}, who generalized the closed-form solution in slab geometry found in \citet{1990ApJ...350..216N}.
+A better approximation to the true solution has been derived by \citet{2006ApJ...649...14D}, who generalized the closed-form solution in slab geometry found in \citet{1973MNRAS.162...43H}.
 It satisfies a $J=0$ boundary condition at $r=R$.
@@
 In Figure \ref{fig:sol_mc_residual_0}, the Monte Carlo spectrum is shown along with that of the solutions $H_{\rm d}$, $H_0$, and $H_0 + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$.
-\textbf{Note that the errorbars shown on the Monte Carlo data points are $\sqrt{N}$, with $N$ being the photon count in each frequency bin, since the photons are all equally weighted.} The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to $H_0$, it corrects for the apparent excess of flux in the peaks of the spectrum.
+\textbf{Note that the errorbars shown on the Monte Carlo data points are proportional to $\sqrt{N}$, with $N$ being the photon count in each frequency bin, since the photons are all equally weighted.} The $H_{\rm bc}$ term is negative at the peak of the spectrum and positive in the line wing such that, when added to $H_0$, it corrects for the apparent excess of flux in the peaks of the spectrum.
 The solution with the correct frequency-dependent boundary condition enforced, $H_0 + H_{\rm bc}$, has lower residuals to Monte Carlo results than the other solutions, especially in the line wing.
@@
 It is evident that the divergent solution $H_{\rm d}$ fails in the line wings.
-\textbf{Also note that the ``V'' shape of the solution in the line core is due simply to the low number of points we chose to use, as the analytic solutions are not valid in this frequency regime since they utilize the damping wing approximation of the Voigt line profile.
+\textbf{Also note that the ``V'' shape of the solution in the line core is due to the low number of points plotted, as the analytic solutions are not valid in this frequency regime since they utilize the damping wing approximation of the Voigt line profile.
 }
@@
 frequency $x$.
-\textbf{Each panel shows $\sigma_s$ further from line center, labeled by $\sigma_s=0, \tau_0, 2\tau_0$.
+%\textbf{Each panel shows $\sigma_s$ further from line center, labeled by $\sigma_s=0, \tau_0, 2\tau_0$.
 The solution is shown at a range of line center optical depths between $\tau_0=10^5$ and $10^9$ with solid overlapping lines.
 The thickness of the lines decreases with increasing optical depth to more clearly show where they overlap.
+The location of the core-wing boundary $x_{cw}$ for each $\tau_0$ is shown with dashed vertical lines which match the color of the corresponding solution}.
+The axes are scaled to show that the size of the correction factor agrees with the predicted $(a\tau_0)^{-1/3}$ scaling.
+    \textbf{Each panel shows $\sigma_s$ further from line center, labeled by $\sigma_s=0, \tau_0, 2\tau_0$.
+The solution is shown at a range of line center optical depths between $\tau_0=10^5$ and $10^9$ with solid lines.
 The location of the core-wing boundary $x_{cw}$ for each $\tau_0$ is shown with dashed vertical lines which match the color of the corresponding solution}.
@@
 \ee
-where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$ to choose the finite solution as $|\sigma|\to 0$.
+where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$ to choose the finite solution as $|\sigma|\to \infty$.
 Numerical integrations are performed inward toward $\sigma_s$ over several domains: from large $|\sigma|$ to $\sigma_s$, from large $|\sigma|$ to 0, and from 0 to $\sigma_s$, depending on whether $\sigma_s$ is positive or negative.
@@
 This gives $J$ and $J'$ on either side of $\sigma_s$, where a prime indicates the derivative $\partial/\partial \sigma$.
-By enforcing the matching conditions Equations (\ref{eq:matching_condition_1}) and (\ref{eq:matching_condition_2}), the eigenfunctions $J(n, \sigma, \omega)$ are obtained over the domain of photon frequencies $\sigma$.
+By enforcing the matching conditions, Equations (\ref{eq:matching_condition_1}) and (\ref{eq:matching_condition_2}), the eigenfunctions $J(n, \sigma, \omega)$ are obtained over the domain of photon frequencies $\sigma$.
 Since the solutions are linear in the starting conditions, only two integrations with different starting values are necessary.
@@
 \ee
-These coefficients are negative for odd values of $n$ and positive for even $n$.
+These coefficients $P_{nm}$ are negative for odd values of $n$ and positive for even $n$.
 The size of each contribution scales roughly as $0.5/(m-7/8)^{2/3}$, with a weak dependence on $n$.
@@
     \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $x_s=0$ and $\tau_0=10^7$.
-\textbf{The scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$, which here is ${\sim}10^{-37}$ in units of specific mean intensity times time.}}
+\textbf{The scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$, which here is ${\sim}10^{-37}$ in units of ergs/(cm$^2$ Hz).}}
     \label{fig:jsoln}
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{gamma_nm.pdf}
-    \caption{Decay rate vs.
+    \includegraphics[width=1.0\textwidth]{gamma_nm.pdf}
+    \caption{Decay time vs.
 mode number.
@@
 When sweeping through to find resonances, Equation (\ref{eq:gamma_nm}) is used to set the scale of the sweep points $\gamma_j$ to ensure no $\gamma_{nm}$ are missed.
-The continuity and close agreement with the analytic expression shown in Figure \ref{fig:gamma_nm} indicate that the numerical solutions are accurate.
+The close agreement with the analytic expression shown in Figure \ref{fig:gamma_nm} indicate that the numerical solutions are accurate.
 
@@
 
-In Figure \ref{fig:steadystate}, the fluence for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated''), and is compared with two analytic solutions: the steady-state $H_0$ solution (Equation \ref{eq:H0surf}) with no time dependence (labelled ``Steady State''), and the result for summing \textbf{a finite number of} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in the first line of Equation (\ref{eq:H0surf}).
+In Figure \ref{fig:steadystate}, the fluence for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$, labelled ``Time-integrated'', and is compared with two analytic solutions: the steady-state $H_0$ solution (Equation \ref{eq:H0surf}), labelled ``Steady State'', and the result for summing \textbf{a finite number of} spatial modes in the steady-state eigenfunction expansion as in the first line of Equation (\ref{eq:H0surf}), labelled ``Partial Sum''.
 Additional spatial modes $n$ increase the solutions' accuracy in the core of the line.
-If more spatial modes are included, the agreement with the steady-state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x=x_s=0$.
+If more spatial modes are included, the agreement with the steady-state spectrum extends further toward the line core.
 If additional frequency modes are included, faster-oscillating terms are incorporated into the Fourier sum over eigenmodes which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum.
@@
 }Steady-state and time-integrated spectra for $n=1, ..., 20$ and $m=1, ..., 500$ are shown with $x_s=0$ and $\tau_0=10^7$.
-\textbf{Note that the x-axis begins near the line core, as we are only concerned with the solutions' accuracy in the line wing.}}
+\textbf{Note that the x-axis begins near the edge of the line core, as we are only concerned with the solutions' accuracy near the line wing.}}
     \label{fig:steadystate}
@@
 We show in our Figure \ref{fig:sol_mc_tau} that the error present in $H_0$ is corrected by our treatment of the boundary condition at $\tau_0 = 10^7$ for T$=10^4$ K, corresponding to $a=4.72 \times 10^{-4}$.
-We note that our corrective term $H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which matches with the discrepancies noted in the aforementioned solutions.
+We note that our correction term $H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which matches with the discrepancies noted in the aforementioned solutions.
 
@@
 Our characterization of the escape time distribution leads to a possible application of this work.
-Models of the interaction of stellar \lya with the upper atmosphere of exoplanets and the associated transmission spectrum can be constructed with a treatment of resonant scattering in spherical geometry \citep{2017ApJ...851..150H}.
+Models of the interaction of stellar \lya with the upper atmosphere of exoplanets and the associated transmission spectrum can be constructed with a treatment of resonant scattering in spherical geometry \citep{2017ApJ...851..150H, 2021ApJ...907L..47Y}.
 The Monte Carlo method can be used for this problem, but is limited by its high computational demand for large $\tau_0$ where there are many photon scatterings before escape.
@@
 A method similar to this has been applied by \citet{2006ApJ...645..792T} to Lyman $\alpha$ transfer using the \citet{1990ApJ...350..216N} solution, but this solution of course does not utilize the frequency-dependent boundary condition at the surface of the sphere.
-Furthermore, to perform a full radiation hydrodynamic simulation with Monte Carlo acceleration, it will be necessary to calculate radiation forces due to \lya transfer.
+Furthermore, to perform a full radiation hydrodynamic simulation with Monte Carlo acceleration, it will be necessary to calculate radiation forces within each cell due to \lya transfer.
 Similar calculations have been done in \citet{1976ApJ...208..286W} in plane-parallel geometry.
@@
 Resources supporting this work were provided by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center.
+We thank the referee for a detailed report that helped improve the presentation of our work.
 \restartappendixnumbering

### 2022-05-05 ms.tex
Final changes from Thursday meeting

@@
 \def\ga{\mathbin{\lower 3pt\hbox
-      {$\rlap{\raise 5pt\hbox{$\char'076$}}\mathchar"7218$}}} %> or of order
+      {$\rlap{\raise 5pt\hbox{$\char'076$}}\mathchar"7218$}}}
 \renewcommand{\vec}[1]{\mathbf{#1}}
@@
 
-\newcommand{\todo}{\textbf{TODO: }}
-
-\received{}
-\revised{}
-\accepted{\today}
-\submitjournal{APJ}
+\submitjournal{ApJ}
 
@@
 \title{A Novel Solution for Resonant Scattering Using Self-Consistent Boundary Conditions}
-% the paper formerly known as Resonant Scattering in a Uniform Sphere with Large Optical Depth
 
@@
 \lya may ionize atoms and dissociate molecules, as well as exert pressure forces that drive an outflow \textbf{ \citep{2018A&A...620A.147B}}.
-\lya can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy \citep{2017ApJ...851..150H}.
+\lya can also excite H atoms to the 2p state, creating a population of Balmer-line absorbers that can be observed via transmission spectroscopy \citep{2017ApJ...851..150H, 2021ApJ...907L..47Y}.
 Due to the low gas densities in the upper atmosphere, collisional de-excitation and broadening are of secondary importance and \lya may undergo ``resonant scattering''.
@@
 These observations have revealed a population of atoms extending out to distances of order a few planetary radii or more for several planets around bright, nearby stars, motivating a study of the physics of \lya interactions with the H atom population.
-The transition from the atomic to the molecular layer in these hot upper atmospheres may take place at pressures of order ${\sim}\ 10\ \mu$bar (see discussion in \citet{2017ApJ...851..150H} for details).
+The transition from the atomic to the molecular layer in these hot upper atmospheres may take place at pressures of order ${\sim}\ 10\ \mu$bar (see discussion in \citealt{2017ApJ...851..150H} for details).
 This suggests the presence of a thick layer of atomic H which can have a line center optical depth of $\tau_0\ {\sim}\ 10^8$.
@@
 Time-variable, optically-thick environments necessitate a time-dependent solution to include the dynamic effects of \lya transfer.
-These include the optical afterglow of gamma-ray bursts \citep{2010ApJ...716..604R} and \lya sources redshifted by cosmological expansion %, which may reveal information about their neutral hydrogen halos and the intergalactic medium
+These include the optical afterglow of gamma-ray bursts \citep{2010ApJ...716..604R} and \lya sources redshifted by cosmological expansion
 \citep{2011MNRAS.418..853X}, among others.}
@@
 frequency $x$.
-%\textbf{Each panel shows $\sigma_s$ further from line center, labeled by $\sigma_s=0, \tau_0, 2\tau_0$.
-The solution is shown at a range of line center optical depths between $\tau_0=10^5$ and $10^9$ with solid overlapping lines.
-The thickness of the lines decreases with increasing optical depth to more clearly show where they overlap.
-The location of the core-wing boundary $x_{cw}$ for each $\tau_0$ is shown with dashed vertical lines which match the color of the corresponding solution}.
-The axes are scaled to show that the size of the correction factor agrees with the predicted $(a\tau_0)^{-1/3}$ scaling.
 \textbf{Each panel shows $\sigma_s$ further from line center, labeled by $\sigma_s=0, \tau_0, 2\tau_0$.
@@
     \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and $m=1, ..., 100$ with $x_s=0$ and $\tau_0=10^7$.
-\textbf{The scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$, which here is ${\sim}10^{-37}$ in units of ergs/(cm$^2$ Hz).}}
+\textbf{The scale of the $J_{nm}(\sigma)$ are set by the factor $E/(kR^3)$, which here is ${\sim}10^{-37}$ in ergs/(cm$^2$ Hz).}}
     \label{fig:jsoln}
@@
     \includegraphics[width=1.0\textwidth]{gamma_nm.pdf}
-    \caption{Decay time vs.
+    \caption{Dimensionless decay time vs.
 mode number.
@@
 
-\software{\texttt{numpy} \citep{2020NumPy-Array}, \texttt{scipy} \citep{2020SciPy-NMeth}}
+\software{\texttt{numpy} \citep{2020NumPy-Array}, \texttt{scipy} \citep{2020SciPy-NMeth}, Coblis - Color Blindness Simulator (\href{https://www.color-blindness.com/coblis-color-blindness-simulator/}{color-blindness.com})}}
 
